### 2022-11-09 responses/R0_response.tex
Initial commit

\documentclass{mdolab-response}

\title{AIAA Paper Template \\
\emph{Journal of Aircraft} \\
Manuscript ID 20XX-XX-XXXXXX}

\author{
Author1,
Author2
and
Joaquim R. R. A. Martins
}
\date{}
\begin{document}

\maketitle

%=========================================================
%=========================================================
%=========================================================

\action{Note: Actions taken to address the reviewers comments are highlighted in red.}

% Initialize section for a new reviewer
\newreviewer

%=========================================================

\begin{revcom}
    Should the associated conference paper~\cite{secco2018sbw} be cited and referred to?
\end{revcom}

\begin{response}
    We did not cite the conference paper in the references, but declared the conference paper in the submission process.
    This information is used by the journal typesetting team to mention the conference paper in the footnotes of the first page of the final paper.
\end{response}

%=========================================================

\begin{revcom}
    Page 1, lines 46-47: ``is'' $\rightarrow$ ``in''?
\end{revcom}

\begin{response}
    \action{We corrected the error.}
\end{response}

%=========================================================

\begin{revcom}
    Page 3, lines 11-12: should also mention the use of empirical models for interference drag, which may use wind tunnel or CFD data to form polynomial approximation models (functions of normal loading, Mach number, incidence angle, sweep angle, etc.) – c.f. Tetrault's work at Virginia Tech.
\end{revcom}

\begin{response}
    \action{We added sentences to page 2 discussing the use of interference drag surrogate models for SBW and TBW conceptual design.}
\end{response}

%=========================================================
\newreviewersection{Methods}
\begin{revcom}
    Page 17, lines 46-47: Do each of the 69 CFD simulations include both a direct and adjoint solution?
\end{revcom}

\begin{response}
    These 69 CFD simulations include line search evaluations, which have no associated adjoint solution.
    \action{We modified the text in the first paragraph of Section IV to mention the number of adjoint evaluations.
        We also modified Fig. 10 to indicate the adjoint solutions.}
\end{response}

%=========================================================

\newreviewersection{Results}
\begin{revcom}
    Page 24: might be worth noting how your finding regarding the downward-lifting strut compares to other works (e.g. NASA SUGAR reports, Virginia Tech research) – I believe I've seen the same trend elsewhere.
\end{revcom}

\begin{response}
    We already mentioned the work of \citet{gagnon2014tbw,gagnon2016euler}, \citet{Ivaldi2015a}, and \citet{Hwang2014a}, which found negative lifting struts for Euler- and RANS-based optimizations.
    \action{We added a new reference from Virginia Tech in which they show parametric studies that suggest the advantages of a negative lifting strut~\cite{ko2003_paramStudy}.}
    We could not find any direct reference to a negative lifting strut in the publicly available NASA SUGAR reports.
\end{response}

%=========================================================
% Final text to thank the reviewer

Thank you for your review.

%=========================================================
%=========================================================
%=========================================================

% Initialize section for a new reviewer
\newreviewer

%=========================================================

\begin{revcom}
    Please send through a technical editor for minor grammar/English corrections. There is also some informal/slang language.
\end{revcom}

\begin{response}
    \action{We sent the manuscript to a technical editor for a complete review of the text.}
    We also checked the text to remove informal language.
\end{response}

%=========================================================

\begin{revcom}
    Fig 14 is confusing.
\end{revcom}

\begin{response}
    \action{We modified Fig. 14 to highlight the contributions of each component.}
\end{response}

%=========================================================
% Final text to thank the reviewer

Thank you for your comments and suggestions.

%=========================================================
% Extra section for other modifications
\section*{Other modifications}

\begin{itemize}

    \item We modified the document to follow the new AIAA \LaTeX \ template.

    \item Added missing DOIs to the Reference Section.

\end{itemize}

%=========================================================
% REFERENCES
\bibliographystyle{new-aiaa}
\bibliography{../tbwbib,../mdolab}

\end{document}

### 2022-11-09 responses/R0_response_multiple_colors.tex
Initial commit

\documentclass[dvipsnames]{article}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{doi}
\usepackage{parskip}
\usepackage{color}
\usepackage{subfigure}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage{color,soul}
% Define custom color
\usepackage{hyperref}
\usepackage{ulem}

\usepackage{soul} % for highlighting; use this in manuscript
\soulregister\cite7 % need these lines to include refs and cites inside highlighted region
\soulregister\citep7
\soulregister\citet7
\soulregister\ref7
\soulregister\eqnref7

\definecolor{rev1}{HTML}{FF999A} % red
\definecolor{rev2}{HTML}{F3F298} % yellow
\definecolor{rev3}{HTML}{B2E0AE} % green
\definecolor{other}{HTML}{C8C7FF} % blue

\DeclareRobustCommand{\hlone}[1]{{\sethlcolor{rev1}\hl{#1}}}
\DeclareRobustCommand{\hltwo}[1]{{\sethlcolor{rev2}\hl{#1}}}
\DeclareRobustCommand{\hlthree}[1]{{\sethlcolor{rev3}\hl{#1}}}
\DeclareRobustCommand{\hlo}[1]{{\sethlcolor{other}\hl{#1}}}

% We can use these colors for different reviewers.
% \definecolor{rev1}{HTML}{FF999A} % red
% \definecolor{rev2}{HTML}{F3F298} % yellow
% \definecolor{rev3}{HTML}{B2E0AE} % green
% \DeclareRobustCommand{\hlone}[1]{{\sethlcolor{rev1}\hl{#1}}}
% \DeclareRobustCommand{\hltwo}[1]{{\sethlcolor{rev2}\hl{#1}}}
% \DeclareRobustCommand{\hlthree}[1]{{\sethlcolor{rev3}\hl{#1}}}

\colorlet{mblue}{blue!40!black}
\hypersetup{bookmarksnumbered=true,colorlinks=true,linkcolor=mblue,citecolor=mblue,urlcolor=mblue}

% Bibtex stuff:
\usepackage[square,sort,comma,numbers]{natbib}
% use the natbib options below when using the AIAA style:
%\usepackage[numbers,sort]{natbib}
%\usepackage{hypernat} % To get natbib to play nicely with hyperref

%===================================================================
% STANDARD COLORS

% Response color
\newcommand{\responsecolor}{MidnightBlue}

% Action color
\newcommand{\actioncolor}{RedOrange}

%===================================================================
% COUNTERS

% Counter for the number of comments addressed so far.
% We reset this counter when we move on to another reviewer
% (This is why we have [section], since we have one section for each reviewer).
\newcounter{CommentCounter}[section]

%===================================================================
% ENVIRONMENT DEFINITION

% Quotes
\newenvironment{myquote}{\begin{quote}\em}{\color{black}\end{quote}}

% Reviewer's comments
\newenvironment{revcom}
{
% Increment counter
\stepcounter{CommentCounter}
%
\textbf{Comment \arabic{CommentCounter}:}
}

% Author's response
\newenvironment{response}
{
\textbf{\color{\responsecolor} Response:}
\color{\responsecolor}
}
{
\vspace{20pt}
}

%===================================================================
% NEW COMMANDS

% Author's action
\newcommand{\action}[1]{{\color{\actioncolor} {#1}}}

% Modify section header to include additional text
\renewcommand{\thesection}{Reviewer \arabic{section} Comments and Response}

% Define dummy command that creates a section just to make the LaTeX more readable
\newcommand{\newreviewer}{\section{}}

%===================================================================
% FIGURE CAPTIONS
% Set all colors to the response format
\usepackage[font={color=\responsecolor}]{caption}

%===================================================================
% MANUSCRIPT INFORMATION

\title{A Jacobian-free approximate Newton--Krylov startup strategy for RANS simulations \\
\emph{Journal of Computational Physics} \\
Manuscript ID JCOMP-D-18-01226}

\author{
Anil Yildirim,
Gaetan K.~W.~Kenway
Charles A.~Mader,
Joaquim R.~R.~A.~Martins,
}
\date{}
\begin{document}

\maketitle

%=========================================================
%=========================================================
%=========================================================

Notes:
\begin{itemize}
    \item {\color{MidnightBlue}Our direct responses to reviewers' comments are written in blue in this response.}
    \item \action{Actions taken to address the reviewers' comments are written in red in this response.}
    \item \hlone{Reviewer 1 modifications are highlighted in red in the manuscript.}
    \item \hltwo{Reviewer 2 modifications  are highlighted in yellow in the manuscript.}
    \item \hlthree{Reviewer 3 modifications are highlighted in green in the manuscript.}
    \item \hlo{Other modifications are highlighted in blue in the manuscript.}
\end{itemize}

\newreviewer

%=========================================================
% General comments
\setcounter{CommentCounter}{-1}
\begin{revcom}
The paper outlines residual routines in the context of Jacobian-free approximate Newton—Krylov solvers for RANS simulations. Two different residual approximations are introduced: 1) omitting the 4th order scalar dissipation of the JST scheme in the advection terms and 2) assuming an orthogonal-mesh assumption for the diffusion term. In addition, the simplification of the turbulence model residual consists of omitting the production term. The advection of the turbulence model is always treated first order accurate.

Using these residual approximations, the aim of the paper is to investigate the convergence rate of the RANS solver in combination with several other solver settings - for example, coupled/uncouled turbulence, lagging of preconditioner, matrix based and matrix free approximate Newton-Krylov method, or even using the option of using a multigrid scheme. The convergence results are quantified in terms of linear and nonlinear iteration counts and amount of tau-code workbench units.
\end{revcom}

% \begin{response}
% Thank you for reviewing our work.
% \end{response}

\begin{revcom}
While the paper is well written and clear, I am left with the impression that the results presented are very specific to their solver. I believe that the presented tweaks and solver settings might give very different results for different RANS solvers with different turbulence models, second order accurate advection schemes for the turbulence models themselves, using approximate Riemann solvers instead of using the JST scheme, etc. Moreover, the authors present in table 2 a list of 19 tunable parameters that are also very specific to their solver.

Given these points, the character of the manuscript corresponds more to a manual for their solver, rather than a general contribution presentation of new significantly improved techniques that can be reproduced by others using a different RANS solver.
\end{revcom}

% second order turbulence does not work with a large enough case. The turbulence model variable wants to get negative values, we probably need to constrain it in a similar way in Marco Ceze's paper on constrained pseudo transient continuation.
% I can show a converged case with the RAE2822 airfoil with second order accurate turbulence.
% we will deflect now since reviewer #3 did not ask for results, he/she said mention this in the paper.
% if the reviewers come back asking for results with second order turbulence, I can get those.

\begin{response}

The approximate Jacobian-free formulation is generalizable to other discretization methods.
\action{To demonstrate this, we added a set of results using the JST scheme with matrix dissipation, and upwind method using the Roe flux in Section~5.3 (Pages~25--27).}
The case using the upwind method failed to converge during the NK stage; however, the same case without the switch to the NK solver successfully converged to $\eta_{\text{rel}} = 10^{-12}$.
This shows that the approximations improve the convergence of the system, even with a different discretization method that uses a Riemann solver.

We agree with the reviewer regarding the spatial order of accuracy of the turbulence model implementation.
This affects the end result of the simulations and the nonlinear convergence rates compared to using a second-order accurate turbulence model.
For our purpose, which is to develop a CFD solver to be used for aerodynamic shape optimization and MDO, we saw little difference in the optimized designs between using a second-order accurate turbulence discretization and a first-order accurate one.
Therefore, we tuned our solver with the first-order accurate discretization for the SA turbulence model.
However, the solver we describe in this work is still applicable to second-order accurate discretizations for the turbulence model, or even to turbulence models other than the SA model.

\action{We added a discussion on this in Section~2.2 (Page~7).}

Regarding the tunable options, we listed all the options we used in this work for the sake of transparency and replicability.
The options are tuned with our solver; however, we see similar trends for other CFD codes with similar solvers that we cite.
Even though other solvers may not have the exact set of tunable parameters we have, these parameters can be grouped into their respective components in the complete solver algorithm.
These groups usually have direct analogies to other methods.
For example, tunings parameters for the linear solver and preconditioner strength can be grouped together, and even though other CFD codes might contain very different linear solvers, the tuning parameters for these solvers can be modified to achieve the same effect we get with our solver.

\action{To better present these tuning parameters, we grouped them into relevant components in Table 2, and added a discussion in Section~3.9 (Pages~17, 19).}
% Furthermore, \citet{osusky_steady_2014} state that it is very difficult to obtain a set of tunings that is applicable to all cases for a CFD solver.
% Even if it is possible, this would be very conservative and yield poor performance with majority of the cases.
% However with a set of tunings that perform well for most of the cases, the users can tweak this baseline set for more problematic cases where the solver might fail or perform sub-optimally with the default set.
% Therefore we stress that having access to many tunable parameters is a desirable property from a nonlinear solver.
\end{response}

\begin{revcom}
Moreover, in my opinion the result presented in the current manuscript also do not allow a clear conclusion which strategy is best. For example, table 4 summarizes the convergence behavior for the common research wing-body model. Analyzing the data, there is no clear trend in terms of PC lag and matrix-based vs matrix-free scheme. In terms of workbench units, it seems that using no residual approximation with the automatic algorithm to determine the PC lag for the matrix free NK gives the best results. For the Onera M6 test case reported in table 2, it seems that the best performance is achieved using the most aggressive residual approximation, while for the wing body case with a multiblock mesh case, only the algorithm with the medium approximation was able to converge.
\end{revcom}

\begin{response}
We agree that there is no definite trend in terms of performance; however, there is a trend in terms of \emph{robustness}.
The approximation level $\mathcal{R}_1$ was the only one that could converge all the test cases we included here, and many other test cases we used while developing the solver.
We tried showing a wide variety of results that would not only showcase when our approach is fastest but also demonstrate the tradeoffs depending on the cases we considered.

In the context of aerodynamic shape optimization and multidisciplinary design optimization, robustness of the CFD solver is much more important than performance.
This is because repeated failures of the CFD solver cause the optimization to fail, and this requires human intervention.
Instead, it is more beneficial to have a robust solver, at the cost of worse performance.
In the long run, the solver robustness will make up for the slower convergence because the optimizations will require less human intervention, and users can obtain final results faster.

\action{We added a discussion on this in the introduction, Section~1 (Page~2), and in the conclusions, in Section~6 (Page~36).}

\end{response}

% \begin{revcom}
% Based on these conclusions, I do not recommend the manuscript for publication in the Journal of Computational Physics.
% \end{revcom}

% \begin{response}
% Thank you for your critical review.
% \end{response}

% JM: Thank you for the rejection? :)

%=========================================================
% Final text to thank the reviewer

Thank you so much for your diligent comments and suggestions.

%=========================================================
%=========================================================
%=========================================================
% Initialize section for the second reviewer
\newreviewer

%=========================================================
% General comments
\setcounter{CommentCounter}{-1}
\begin{revcom}
In this manuscript, the authors introduce the use of approximate residual schemes
in the context of a Jacobian-free approximate Newton-Krylov algorithm for large-scale
Reynolds-averages Navier-Stokes simulations.  In the proposed method, the
Jacobian matrix is not explicitly formed; rather, it is approximated to various levels
using residual routines computed at each iteration of the nonlinear solve.
In contrast, the preconditioner is lagged by some number of iterations which
increases the efficiency of the method without causing it to stall or diverge as
failing to update the (approximate) Jacobian might. The authors further propose a
method to auto-adaptively decide when to recompute the preconditioner.

Large-scale CFD problems are computationally challenging, and a substantial amount
of technology has been developed to address the convergence and computational cost
issues therein. The authors provide a literature review summarizing the main results
and methods they build upon and they describe how their method relates to these.
The main contributions appear to be the residual-based matrix free strategy of
Jacobian approximation and the approach towards preconditioner lagging.
The discussion of Jacobian approximation includes three different stencils the use
of which can provide a balance between robustness and efficiency.
The numerical results do a nice job of illustrating the difference between the
different approximation levels.  I appreciate the eigenvalue discussion as an
illustration of lagging the preconditioner. Overall I find the paper very nicely
written, and I think the results are interesting enough to publish, after some
revision.
\end{revcom}

% \begin{response}
% Thank you for reviewing our work.
% % \action{Action.}
% \end{response}

\begin{revcom}
My main criticism of the paper is that it must be read very carefully to detect
the novel contributions in comparison to the previously developed methods and
accompanying heuristics which are described with essentially the same level of
detail.  For instance in Section 3 it is my understanding that Section 3.2 and 3.4
contain the novel contributions of this paper, whereas 3.1, 3.3, 3.5-3.9 contain
important implementation details and parameter choices, mostly using previously
developed methods and heuristics.  I would suggest the novel parts should be separated
out so readers can learn the new ideas introduced by the authors.
\end{revcom}

\begin{response}
Our goal was to describe all the elements of the ANK solver in enough detail for the sake of transparency and reproducibility.
There is no single paper in the literature that describes such a solver completely, so we believe this is needed.
This goal meant that there are a lot of subsections on state of the art methods and heuristics.
We can see how this makes it difficult to understand what aspects of the algorithm is our novel contributions.
We describe the algorithm in a way that each section builds on what was explained in the previous ones, so separating out Sections~3.2 and 3.4 as suggested would break the flow of the paper.

\action{To address the reviewer's concern, we clearly stated our novel contributions in the introduction of Section~3 (Page~9) and highlighted the novel contributions in Sections~3.2 (Page~10) and 3.4 (Page~11). We also highlighted the novel contributions in the conclusions, in Section~6  (Page~36).}
\end{response}

%Additional comments:
\begin{revcom}
Under equation (8): in describing the diagonal time-stepping term $I/Delta t^{(n)}$
it should be mentioned that a shorthand notation is used. Otherwise from a
mathematical notation standpoint this term does not make sense.
\end{revcom}
\begin{response}
\action{We modified the notation in Section~3 as suggested (Page~9).}
\end{response}

\begin{revcom}
At the end of p. 10 it is stated: ``Even with an up to date PC, if the linear system fails to converge to the prescribed tolerance with the maximum iteration limit, we simply terminate the linear solution and proceed to the next nonlinear iteration for the sake of computational cost.''
Does this tend to lead to a sequence of failures of the nonlinear solve?
Is the successfully converged iterate from the previous step rather than the
current failed one (or something else) used to start the next linear solve?
\end{revcom}

\begin{response}
On the first question, yes, not updating the preconditioner might lead to sequence of failed linear solutions, that might cause the nonlinear convergence to stall.
In most cases, the iteration limit yields a ``good enough'' linear solution so that the nonlinear convergence can progress.
In some rare cases, the linear solver completely stalls; however, at this point there is nothing that the preconditioner lagging algorithm can do.
This issue arises due to inadequate preconditioning of the linear system, and in these situations we restart the simulation with linear solver options that yield better PCs and higher iteration limits.

\action{We added a discussion for these scenarios in Section~3.4 (Page~12).}

Regarding the second question, we do not use the previous linear solution as the initial guess for the next linear solution.
The linear systems we solve do not change drastically between nonlinear iterations.
If the right hand side vector, that is the residual vector in our case, is also similar, restarting the linear solution from a previous solution would improve linear convergence.
However, because we are performing linear solutions in the context of a Newton type method to solve a system of nonlinear equations, we expect the subsequent update directions to be different from each other.
Therefore, there is no benefit to restarting linear solutions between nonlinear updates.

\action{We added a discussion on this topic in Section~3.1 (Page~10).}

\end{response}

\begin{revcom}
In Section~3.5 on Linear Solution Tolerance: It is stated that many low-cost
nonlinear iterations are preferred in the startup-stage, and that a tolerance of
0.05 is used with a maximum of 40 linear iterations.
Is the tolerance updated to require more accuracy as the simulation progresses?
Can this be done adaptively, or is that done already?
\end{revcom}

\begin{response}
There is an algorithm that changes the linear solution tolerance adaptively, developed by~\citet{eisenstat_choosing_1996}.
However, this algorithm is tuned for Newton's method with exact Jacobian formulations, and therefore it is not applicable to our nonlinear solver where we have approximations in the Jacobian.
As we noted in Section~4, the Newton--Krylov solver we have in our CFD code does use this algorithm; however, the approximate Newton--Krylov uses a fixed tolerance for the linear solutions.

\action{We added a discussion for this in Section~3.5 of the manuscript (Page~13).}
\end{response}

\begin{revcom}
p. 31: ``Rest of the failed cases represent...'' should probably read
 ``The rest of the failed cases represent...''
\end{revcom}

\begin{response}
\action{We changed the wording in Section~5.7 as suggested (Page~35).}
\end{response}

%=========================================================
% Final text to thank the reviewer

% Thank you so much for your diligent comments and suggestions.

%=========================================================
%=========================================================
%=========================================================
% Initialize section for the second reviewer
\newreviewer

%=========================================================
% General comments
\setcounter{CommentCounter}{-1}
\begin{revcom}
In general, the authors discuss several aspects of their ANK instead of focusing on their startup (globalization) strategy. This makes the article longer than necessary and gets the reader distracted from their main contribution: an algorithm for switching between approximated residual routines to accelerate the global convergence phase of pseudo-transient continuation for RANS problems.
\end{revcom}

\begin{response}
    Thank you for reviewing our work.
    We agree that the manuscript is long; we wanted to include enough detail for the sake of transparency and reproducibility.
    There is no single paper that describes this type of solver completely, and we believe this is needed in the literature.
    \action{To better guide the readers, we stated our novel contributions more clearly in the introduction of Section~3 (Page~9), and highlighted the novel contributions in Sections~3.2 (Page~10) and 3.4 (Page~11).}
    We used \hltwo{yellow} to highlight this change, since this issue was also raised by the second reviewer.
\end{response}

\begin{revcom}
Literature Review:
To my knowledge the authors covered well most of the relevant research works but I believe they missed some approximate, matrix-free NK approaches in the high-order finite elements community, e.g.: where a coarser (collocated) quadrature is used for the residual Jacobian yielding an approximate linearization. The same approach can be used for the adjoint solve.
\end{revcom}

\begin{response}
\action{We added a paragraph in the literature review on the methods the reviewer mentioned in the high-order finite element community in Section~1 (Page~4).}
\end{response}

\begin{revcom}
In the second bullet of the research highlights: ``Matrix-free approach improves robustness..'', I believe the authors mean the approach improves computational efficiency?
\end{revcom}

% These are the rules for "research highlights":
% Highlights
% Highlights are a short collection of bullet points that convey the core findings of the article. Highlights are optional and should be submitted in a separate editable file in the online submission system. Please use 'Highlights' in the file name and include 3 to 5 bullet points (maximum 85 characters, including spaces, per bullet point). You can view example Highlights on our information site.

% todo AY-:
% the highlight the reviewer is talking about was:
% •	Matrix-free approach improves robustness, while the preconditioner is lagged.
% I changed it to
% •	Matrix-free approach improves robustness despite the lagged preconditioner.
% Let me know if you have better suggestions
% You can find the research highlights document under "ank_paper/Additional Documents/"
\begin{response}
There is a coupled effect that is very difficult to convey with 85 characters (including spaces), which is the limit for each point in ``Research Highlights'' document.
The point we were trying to make is:
Alternative ANK methods are based on the matrix-based preconditioner.
Lagging the preconditioner introduces instabilities in the nonlinear solver.
To avoid this, we use matrix-free approximate routines, and the approximate Jacobian we use is always up to date.
As a result, the use of matrix-free approach improves robustness.

\action{We re-worded this point as ``Matrix-free approach improves robustness despite the lagged preconditioner.'' in the Research Highlights document (Page~1, second bullet point).}
\end{response}

\begin{revcom}
In the abstract, fifth line, the authors refer to globalization methods and in the next sentence they wrongly lead the reader towards thinking that all globalization methods use a pseudo-time approach. Please consider rewording.
\end{revcom}

\begin{response}
\action{We reworded the relevant sentence in the abstract (Page~1).}
\end{response}

\begin{revcom}
In the introduction, at paragraph starting with ``In this work..'', the authors refer to the linear systems being easier to solve due to the lower bandwidth of the approximate Jacobian but there is also the diagonal dominance effect of the pseudo-transient term. I think it would be better to rephrase the paragraph to either point out this added effect or show that linear systems with and without the temporal term are equally easy to solve.
\end{revcom}

\begin{response}
That is correct; the diagonal time-stepping term improves the diagonal dominance of the linear system, therefore making it easier to solve compared to not having the time-stepping term.
We were trying to describe that a linear system with an approximate Jacobian and a time-stepping term is easier to solve compared to a linear system with an exact Jacobian and the same time-stepping term.

\action{We added a sentence describing this detail in Section~1 (Page~4).}
\end{response}

\begin{revcom}
The authors use a first-order discretization of the SA turbulence model. My impression is that this approach has a significant impact on the final result and on the nonlinear solver performance. I think it would be important to highlight this topic given that the paper is about a solver strategy for RANS.
\end{revcom}

\begin{response}
\action{We highlighted this aspect in Section~2.2 (Page~7).}
We used \hlone{red} to highlight this change, since this issue was also raised by the first reviewer.
\end{response}

\begin{revcom}
When discussing the variable scaling in the text, It would be beneficial to the reader to either add a comment to the chosen value of the scaling or refer the reader to a reference.
\end{revcom}

\begin{response}
\action{We added the reference where we adopted the scaling strategy from in Section~2.4 (Page~9)}.
\end{response}

\begin{revcom}
The back-tracking line search approach relies on the updated direction being a descent direction for the L2-norm of the globalized (unsteady) residual. This is indeed the case for an exact NK approach. It is unclear that the approximations used in the residual routines proposed by the authors would retain such a property and I think it would significantly improve the quality of the paper if this was discussed or shown mathematically. Furthermore, if a residual approximation would be guaranteed to preserve that property, the resulting scheme is expected to be both robust and efficient.
\end{revcom}

\begin{response}
This is a very good point; however, we cannot guarantee a descent in the unsteady residual when we use an approximate Jacobian.
These Jacobian matrices are simply linearizations of the nonlinear system governed by the RANS equations.
For most practical cases of interest, the approximate Jacobian matrices do indeed generate updates that are in the descent direction.
However, we can engineer nonlinear states that destroy this property of the approximate Jacobian.
Furthermore, we sometimes see updates that fail to reduce the unsteady residual norm.
If this happens, the solver algorithm reduces the global CFL number and tries again.
This is done to increase the weight of the time-stepping term compared to the approximate Jacobian.

\action{We added a discussion on this topic in Section~3.6 (Page~14).}
\end{response}

%=========================================================
% Final text to thank the reviewer

Thank you so much for your diligent comments and suggestions.
\bibliographystyle{unsrtnat}
\bibliography{../R1_journal/ankbib}

\end{document}

### 2022-11-09 conference-abstract/main.tex
Create main.tex

\documentclass[]{icas2022}

\usepackage{float}

\usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
\usepackage{hypernat} % To get natbib to play nicely with hyperref
\usepackage{doi} % For getting hyperlinked DOI in the references

\graphicspath{{../figures/}}

\TitlePaper{Coupled Low-Emission Propulsion Analysis and Optimization of a High Bypass Turbofan Engine}
\AuthorPaper[1]{Peter N. Atma}
\AuthorPaper[2]{Andrew H.~R.~Lamkin}
\AuthorPaper[3]{Joaquim R.~R.~A.~Martins}
\affil[1]{MSE Student, Department of Aerospace Engineering, University of Michigan}
\affil[2]{Ph.D.~Candidate, Department of Aerospace Engineering, University of Michigan}
\affil[3]{Professor, Department of Aerospace Engineering, University of Michigan}

% ==================================================
%	Abstract
% ==================================================
\abstractEnglish{
    Advances in commercial propulsion technology has lead to the development of larger and more advanced high-bypass turbofan engines with larger bypass ratios, pressure ratios, and internal temperatures. 
    With the impending climate crisis, aircraft and engine manufacturers have been pushing for greener fuels and more efficient engines to lower greenhouse and NOx emissions. 
    This has revitalized research into using liquid hydrogen as a fuel for aircraft turbine engines in addition to using known thrust augmentation techniques to reduce NOx emissions and improve fuel efficiency. 
    The high-bypass turbofan study investigates the industry-proposed benefits of using a closed-loop water injection and water vapor recovery system with two types of fuels. 
    We will perform a single point analysis to explore the design space and a multi-point gradient-based optimization to determine and validate the efficiency and emission improvements associated with the proposed engine model. 
    Finally, we will present the results from the design space analysis and multi-point optimization from this model. These developments will accelerate and validate current research into the next generation of fuel-efficient, low emission high-bypass turbofan engines.

}
\keywords{Propulsion, Optimization, Emissions}

% ==================================================
\begin{document}

% ==================================================
%	Body of Document
% ==================================================
\body  %%% Do not remove

\section{Introduction}
% Message 1: Motivation to incorporate low-emission fuels and techniques
In the commercial aviation industry today, the global effects of climate change and high gas prices have motivated the development of more efficient and cleaner propulsion systems. 
Most development so far has been targeted at making existing engine architectures more efficient with the fuels and technologies we currently have to reduce fuel consumption and thus release fewer carbon and NOx emissions. 
By continuing this trend of development, high-bypass turbofan engines can be improved by lowering the pressure ratio of the fan to enable a higher bypass ratio of the engine.
Furthermore, higher overall pressure ratios and more advanced metals with higher melting temperatures can allow larger burner temperatures both of which improve thermal efficiency.

Additionally, greener fuels can be used that have fewer products that are harmful to the environment and human health. 
Liquid hydrogen has been proposed as a possible replacement fuel for hydrocarbon fuel such as Jet-A due to the fact that hydrogen has zero carbon emissions and the combustion products mainly consist of water vapor. 
A consequence of using hydrogen as a fuel and designing higher pressure ratios is that hydrogen burns at higher temperatures than hydrocarbon fuels and higher pressure ratios result in higher combustion pressures. 
High combustion temperatures and pressures tend to increase NOx formation and emissions in aircraft engines.

% Message 2: Background and references to support using H2 and water injection in HBTF engines
Therefore, a potential solution to these downsides is to inject finely atomized water droplets into the core air stream of a high-bypass turbofan engine. 
While water injection is generally an old technology, studies conducted by NASA, Boeing, and Rolls-Royce suggest that this technique can be used to reduce the NOx emissions in high-bypass turbofan engines by as much as 47\%. 
Additional benefits include improvements in fuel efficiency and thrust, lower burner temperatures to improve the lifetime of high-temperature components, and engine noise reduction \cite{nasa_inject}. 
While water injection may provide all of these benefits, water would still have to be stored on the aircraft and increase the weight of the aircraft. 
Therefore, a method currently being investigated in industry is to use a closed-loop system that uses water vapor recovery from the exhaust to provide the water for injection. 
This would eliminate the need for a water reservoir that would decrease the overall aircraft performance.

These potential efficiency and emission improvements of aircraft engines can be cheaply and efficiently evaluated by using one-dimensional cycle analysis. 
One-dimensional cycle analysis uses a first-principles approach with simplifying assumptions to provide a low-fidelity model for engine analysis. 
This can be used to understand the general trends and design constraints of a engine cycle and evaluate potential improvements in design. Current tools that exist for engine cycle analysis include Numerical Propulsion System Simulation (NPSS) and pyCycle. 
NPSS utilizes a modular object-oriented framework in which individual engine components are connected and thermodynamic properties are evaluated using Chemical Equilibrium with Applications (CEA) to determine performance metrics of a given design. 
pyCycle improves on this modular architecture by introducing efficient analytic gradients to allow gradient-based multidisciplinary optimization \cite{Hendricks2019}.

% Message 3: Introduce the extension of the HBTF and propose novel contributions
In this work, we will analyze the potential propulsion benefits of closed-loop water vapor recovery with water injection in a high-bypass turbofan engine by optimizing the thrust-specific fuel consumption (TSFC) with a NOx emission constraint. 
This will be accomplished by developing new pyCycle components for water injection and vapor recovery and will use empirical NOx formation correlations to evaluate NOx emissions.
Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the maximum improvement of engine performance over current technologies.

In Section \ref{sec:epModel} we introduce the turbofan model and explain how we will introduce the water injection and water recovery components within the model.
Section \ref{sec:imp} explains how the multidisciplinary optimization will be implemented to take into account the different operating conditions of the engine model and the associated NOx emissions.

\section{Emission-Propulsion Model Description}
\label{sec:epModel}
% Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
We will use a next-generation high-bypass turbofan engine configuration for this work.
Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Hendricks2019}. The N+3 reference cycle represents a notional high bypass ratio geared turbofan that could be available in the 2030–2040 time frame. 
This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements that were mentioned before such as a large bypass ratio, high pressure ratio, and high combustion temperature. 
This model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, and ends in a bypass nozzle and core nozzle. The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft. 
Similarly, the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft. Along the axial flow path, a the one-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied. 
We then introduce a water injection component directly before the HPC. 
This will inject pure water vapor into the core stream to reduce the flame combustion temperature. 
The water vapor recovery component is then introduced directly before the core nozzle to recover water vapor from the core stream. 
While in practice this component would require a technical analysis of a condenser in the core stream, this work is only looking at the potential benefit of extracting water vapor and not the recovery method specifically. 
With these components integrated into the N+3 engine, the coupled water inject and water recovery presents a implicit relationship which would need to be iterative solver to match the flow rate entering the engine and exiting the engine. 
The flow and mechanical connections within the engine model with the water injector and water extractor are visualized in Figure \ref{fig:hbtf_cycle}.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{turbofan_wvr.pdf}
	\caption{Configuration of the original high-bypass turbofan model.}
	\label{fig:hbtf_cycle}
\end{figure}

% Subsystem Models: Explain the subsystem modeling and coupling in moderate detail

\section{Implementation}
\label{sec:imp}
% Fully coupled model
The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{openmdao_2019}. 
For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity (CITE P3T3). 
This method uses the pressure and temperature of the flow before the combustor to determine NOx formation from a reference design condition of the engine. 
Since not many NOx correlations exist for the NOx formation for the liquid hydrogen fuel, we will use a surrogate model using data computed using Cantera to approximately model the NOx emissions.

% Briefly discuss the optimization problem
We will perform gradient-based emission-propulsion design optimization of the engine model with a multipoint architecture that considers the common flight conditions experienced by commercial aircraft. And XDSM diagram of the optimization problem is shown in Figure \ref{fig:opt_prob}.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{N3_inject.pdf}
	\caption{}
	\label{fig:opt_prob}
\end{figure}

The objective is to minimize the thrust specific energy consumption at a cruise condition subject to NOx formation, thrust, engine diameter.
Following this study, we will conduct a multi-objective optimization problem considering thrust specific fuel consumption and NOx formation. 
This will define a pareto front of different thrust specific fuel consumption and NOx formation designs to show trade-offs in the design space.

\section{Conclusion}
% Message 1: Re-state the problem
In this work, we will model, analyze, and optimize a high-bypass turbofan propulsion cycle using a novel closed-loop water vapor recovery to improve cycle efficiency and NOx emissions. We 
% Message 2: Summarize the HBTF model
The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with two newly developed water injection and water vapor recovery components to accurately compute the thermodynamic response of the engine. 
Two fuels, Jet-A and liquid hydrogen, will be compared with and without the closed-loop water vapor recovery system to determine the benefits of the implementation. 
NOx formation will be modeled using common industry methods and a novel reactor model in Cantera for hydrogen combustion NOx formation.
% Message 3: Expected results
The results will include a full propulsion-emission analysis of the novel systems with multipoint design optimizations of the entire flight envelope.
This work will build off of current industry research into NOx emission reduction methods and provide a first principles analysis of the potential benefits of closed-loop water vapor recover and injection for commercial aviation applications.

\section{Contact Author Email Address}
mailto: patma@umich.edu

\section{Copyright Statement} % update for Aviation instead of ICAS
\begin{small}
	The authors confirm that they, and/or their company or organization, hold copyright on all of the original material included in this paper. The authors also confirm that they have obtained permission, from the copyright holder of any third party material included in this paper, to publish it as part of their paper. The authors confirm that they give permission, or have obtained permission from the copyright holder of this paper, for the publication and distribution of this paper as part of the ICAS proceedings or as individual off-prints from the proceedings.
\end{small}

\bibliographystyle{new-aiaa}
\bibliography{mdolab}

\end{document}

### 2022-11-10 conference-abstract/main.tex
updated figures

@@
-\documentclass[]{icas2022}
+\RequirePackage{fix-cm}
+\documentclass[conf]{new-aiaa}
 
+\usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{siunitx}
+\sisetup{group-separator = {,}}
+\usepackage{booktabs}
+\usepackage{enumitem}
 \usepackage{float}
-
+\usepackage{amsmath}
+\usepackage[version=4]{mhchem}
+\usepackage{longtable,tabularx}
+\usepackage{placeins}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{latexsym}
+\usepackage{subcaption}
+\usepackage{latexsym}
 \usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
@@
 
+\hypersetup{
+    pdfauthor={Peter Atma}, % insert author here
+	pdftitle={Aviation 2022 Abstract}, % insert title here
+	pdfsubject={}, % insert keywords here
+}
+
 \graphicspath{{../figures/}}
 
-\TitlePaper{Coupled Low-Emission Propulsion Analysis and Optimization of a High Bypass Turbofan Engine}
-\AuthorPaper[1]{Peter N. Atma}
-\AuthorPaper[2]{Andrew H.~R.~Lamkin}
-\AuthorPaper[3]{Joaquim R.~R.~A.~Martins}
-\affil[1]{MSE Student, Department of Aerospace Engineering, University of Michigan}
-\affil[2]{Ph.D.~Candidate, Department of Aerospace Engineering, University of Michigan}
-\affil[3]{Professor, Department of Aerospace Engineering, University of Michigan}
+\title{Multi-point Aeropropulsive Design Optimization of a High-Bypass Turbofan Engine} % change
+
+\author{Peter Atma\footnote{MS Student, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Andrew H.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
+\affil{University of Michigan, Ann Arbor, MI, 48109}
 
@@
 % ==================================================
-\abstractEnglish{
+
+% ==================================================
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
 	Advances in commercial propulsion technology has lead to the development of larger and more advanced high-bypass turbofan engines with larger bypass ratios, pressure ratios, and internal temperatures.
@@
 These developments will accelerate and validate current research into the next generation of fuel-efficient, low emission high-bypass turbofan engines.
-
-}
-\keywords{Propulsion, Optimization, Emissions}
-
-% ==================================================
-\begin{document}
-
-% ==================================================
-%	Body of Document
-% ==================================================
-\body  %%% Do not remove
+\end{abstract}
 
@@
 We will use a next-generation high-bypass turbofan engine configuration for this work.
-Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Hendricks2019}.
+Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite[]{Hendricks2019}.
 The N+3 reference cycle represents a notional high bypass ratio geared turbofan that could be available in the 2030–2040 time frame.
@@
 
-% Subsystem Models: Explain the subsystem modeling and coupling in moderate detail
+% Preliminary Results
+This model has been tested using Jet-A and liquid hydrogen fuels to determine the improvements in efficiency with injecting water into the core stream.
+Preliminary results are shown in Figure \ref{fig:results} and show the relative improvement in thrust specfic energy consumption with water injection for the same engine design with each type of fuel.
+We can already see great improvements in the cruise engine efficiency which may be able to be further improved with a full engine optimization.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.png.pdf}
+	\caption{Relative improvement in .}
+	\label{fig:results}
+\end{figure}
 
@@
 % Fully coupled model
-The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{openmdao_2019}.
+The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
 For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity (CITE P3T3).
@@
 
-\section{Contact Author Email Address}
-mailto: patma@umich.edu
-
-\section{Copyright Statement} % update for Aviation instead of ICAS
-\begin{small}
-	The authors confirm that they, and/or their company or organization, hold copyright on all of the original material included in this paper.
-The authors also confirm that they have obtained permission, from the copyright holder of any third party material included in this paper, to publish it as part of their paper.
-The authors confirm that they give permission, or have obtained permission from the copyright holder of this paper, for the publication and distribution of this paper as part of the ICAS proceedings or as individual off-prints from the proceedings.
-\end{small}
-
-\bibliographystyle{new-aiaa}
-\bibliography{mdolab}
+\bibliography{mdolab,references}
 

### 2022-11-10 conference-abstract/main.tex
fixed obvious issues

@@
 	pdftitle={Aviation 2022 Abstract}, % insert title here
-	pdfsubject={}, % insert keywords here
+	pdfsubject={Propulsion Analysis and Optimization of a High Bypass Turbofan Engine}, % insert keywords here
 }
@@
 
-\title{Multi-point Aeropropulsive Design Optimization of a High-Bypass Turbofan Engine} % change
+\title{Multi-point Low-Emission Propulsion Analysis and Optimization of a High Bypass Turbofan Engine} % change
 
-\author{Peter Atma\footnote{MS Student, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Peter Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
 \author{Andrew H.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
@@
 	\includegraphics[width=0.8\textwidth]{turbofan_wvr.pdf}
-	\caption{Configuration of the original high-bypass turbofan model.}
+	\caption{Configuration of the high-bypass turbofan model with vapor recovery and injection.}
 	\label{fig:hbtf_cycle}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.png.pdf}
-	\caption{Relative improvement in .}
+	\includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.png}
+	\caption{Relative improvement in TSEC from water injection.}
 	\label{fig:results}
@@
 The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
-For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity (CITE P3T3).
+For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity \cite[]{Dubois2006}.
 This method uses the pressure and temperature of the flow before the combustor to determine NOx formation from a reference design condition of the engine.
@@
 	\includegraphics[width=0.8\textwidth]{N3_inject.pdf}
-	\caption{}
+	\caption{XDSM diagram of the multi-point optimization problem with constraints.}
 	\label{fig:opt_prob}

### 2022-11-10 conference-abstract/main.tex
minor grammatical and structure  fixes

@@
 % Message 2: Background and references to support using H2 and water injection in HBTF engines
-Therefore, a potential solution to these downsides is to inject finely atomized water droplets into the core air stream of a high-bypass turbofan engine.
+A potential solution to these drawbacks to improve fuel efficiency is to inject finely atomized water droplets into the core air stream of a high-bypass turbofan engine.
 While water injection is generally an old technology, studies conducted by NASA, Boeing, and Rolls-Royce suggest that this technique can be used to reduce the NOx emissions in high-bypass turbofan engines by as much as 47\%.
@@
 % Message 3: Introduce the extension of the HBTF and propose novel contributions
-In this work, we will analyze the potential propulsion benefits of closed-loop water vapor recovery with water injection in a high-bypass turbofan engine by optimizing the thrust-specific fuel consumption (TSFC) with a NOx emission constraint.
-This will be accomplished by developing new pyCycle components for water injection and vapor recovery and will use empirical NOx formation correlations to evaluate NOx emissions.
-Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the maximum improvement of engine performance over current technologies.
+In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recovery with water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
+TSEC is the thrust specfic fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuels.
+The optimization problem will be accomplished by developing new pyCycle components for water injection and vapor recovery and will use empirical NOx formation correlations to evaluate NOx emissions.
+Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the how these improvements vary with fuel type and how they compare to current technologies.
 
 In Section \ref{sec:epModel} we introduce the turbofan model and explain how we will introduce the water injection and water recovery components within the model.
+Additionally, preliminary data is provided as a motivation for studying these methods.
 Section \ref{sec:imp} explains how the multidisciplinary optimization will be implemented to take into account the different operating conditions of the engine model and the associated NOx emissions.
@@
 The N+3 reference cycle represents a notional high bypass ratio geared turbofan that could be available in the 2030–2040 time frame.
-This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements that were mentioned before such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-This model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, and ends in a bypass nozzle and core nozzle.
-The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft.
-Similarly, the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
+This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
+This high-bypass turbofan model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
+The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
 Along the axial flow path, a the one-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
-We then introduce a water injection component directly before the HPC.
-This will inject pure water vapor into the core stream to reduce the flame combustion temperature.
-The water vapor recovery component is then introduced directly before the core nozzle to recover water vapor from the core stream.
-While in practice this component would require a technical analysis of a condenser in the core stream, this work is only looking at the potential benefit of extracting water vapor and not the recovery method specifically.
-With these components integrated into the N+3 engine, the coupled water inject and water recovery presents a implicit relationship which would need to be iterative solver to match the flow rate entering the engine and exiting the engine.
+The closed-loop water recovery system is integrated by placing a water injection component directly before the HPC.
+This component will inject pure water vapor into the core stream which will reduce the combustion temperature.
+The water vapor recovery component is then placed directly before the core nozzle to recover water vapor from the core stream and recycle it back to the water injector component.
+While in practice the water vapor recovery component would require a technical analysis of a condenser in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
 The flow and mechanical connections within the engine model with the water injector and water extractor are visualized in Figure \ref{fig:hbtf_cycle}.
@@
 % Preliminary Results
-This model has been tested using Jet-A and liquid hydrogen fuels to determine the improvements in efficiency with injecting water into the core stream.
-Preliminary results are shown in Figure \ref{fig:results} and show the relative improvement in thrust specfic energy consumption with water injection for the same engine design with each type of fuel.
+This model has been tested using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency with injecting water into the core stream.
+The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in thrust specfic energy consumption with water injection for the same engine design with each type of fuel.
 We can already see great improvements in the cruise engine efficiency which may be able to be further improved with a full engine optimization.
@@
 This method uses the pressure and temperature of the flow before the combustor to determine NOx formation from a reference design condition of the engine.
-Since not many NOx correlations exist for the NOx formation for the liquid hydrogen fuel, we will use a surrogate model using data computed using Cantera to approximately model the NOx emissions.
+Since not many accurate NOx formation correlations exist for full-sized turbofan engines running on liquid hydrogen, we will use a surrogate model using data computed using Cantera to model the NOx emissions \cite[]{cantera}.
 
@@
 We will perform gradient-based emission-propulsion design optimization of the engine model with a multipoint architecture that considers the common flight conditions experienced by commercial aircraft.
-And XDSM diagram of the optimization problem is shown in Figure \ref{fig:opt_prob}.
+An XDSM diagram of the optimization problem is shown in Figure \ref{fig:opt_prob}.
 
@@
 
-The objective is to minimize the thrust specific energy consumption at a cruise condition subject to NOx formation, thrust, engine diameter.
-Following this study, we will conduct a multi-objective optimization problem considering thrust specific fuel consumption and NOx formation.
-This will define a pareto front of different thrust specific fuel consumption and NOx formation designs to show trade-offs in the design space.
+The objective is to minimize the thrust specific energy consumption at a cruise condition subject to NOx formation, thrust, engine diameter and explore the design space of the model formulation.
+Following this study, we will conduct a multi-objective optimization problem considering thrust specific energy consumption and NOx formation.
+This will define a pareto front of different thrust specific energy consumption and NOx formation designs to show trade-offs in the design space.
 
@@
 % Message 1: Re-state the problem
-In this work, we will model, analyze, and optimize a high-bypass turbofan propulsion cycle using a novel closed-loop water vapor recovery to improve cycle efficiency and NOx emissions. We
+In this work, we will model, analyze, and optimize a high-bypass turbofan propulsion cycle using a novel closed-loop water vapor recovery to improve cycle efficiency and NOx emissions.
 % Message 2: Summarize the HBTF model
-The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with two newly developed water injection and water vapor recovery components to accurately compute the thermodynamic response of the engine.
-Two fuels, Jet-A and liquid hydrogen, will be compared with and without the closed-loop water vapor recovery system to determine the benefits of the implementation.
+The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with two newly developed novel components to model water recovery and injection to accurately establish the performance and emissions improvements.
+Two fuels, Jet-A and liquid hydrogen, will be compared with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
 NOx formation will be modeled using common industry methods and a novel reactor model in Cantera for hydrogen combustion NOx formation.
@@
 The results will include a full propulsion-emission analysis of the novel systems with multipoint design optimizations of the entire flight envelope.
-This work will build off of current industry research into NOx emission reduction methods and provide a first principles analysis of the potential benefits of closed-loop water vapor recover and injection for commercial aviation applications.
+This work will build off of current industry research into emission reduction methods and provide a first principles analysis of the potential benefits of closed-loop water vapor recover and injection for commercial aviation applications.
 

### 2022-11-10 conference-abstract/main.tex
My changes for the first draft

@@
 
+% TODO: AL-PA: Change the title to something like "Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation"
+% Current title doesn't really describe the biggest aspects of the paper
+% N+3 engine is a Ultra high-bypass engine...BPR > 20 for most designs
 \title{Multi-point Low-Emission Propulsion Analysis and Optimization of a High Bypass Turbofan Engine} % change
@@
 \begin{abstract}
+	% TODO: AL-PA: Rephrase this sentence. You say 'larger' twice in the same context.
+	% REPHRASE: Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
 	Advances in commercial propulsion technology has lead to the development of larger and more advanced high-bypass turbofan engines with larger bypass ratios, pressure ratios, and internal temperatures.
+	% TODO: AL-PA: I wouldn't say 'impending climate crisis'.  Maybe change to 'With the focus on reducing aircraft emissions'
+	% TODO: AL-PA: Change from 'greener fuels' to say just 'Hydrogen'.  Drive home the point that we are studying the transition to H2.
+	% TODO: AL-PA: Just say carbon dioxide and NOx emissions, we don't consider all greenhouse emissions in this work.
 	With the impending climate crisis, aircraft and engine manufacturers have been pushing for greener fuels and more efficient engines to lower greenhouse and NOx emissions.
+	% TODO: AL-PA: Previous sentence already says we want to use greener fuels.
+	% REPHRASE: Using Hydrogen introduces complexity and weight penalties that we need to offset by using all the advantageous properties of the fuel.
 	This has revitalized research into using liquid hydrogen as a fuel for aircraft turbine engines in addition to using known thrust augmentation techniques to reduce NOx emissions and improve fuel efficiency.
+	% TODO: AL-PA: Rephrase this to be more clear
+	% REPHRASE: In this study we investigate the benefits of using Hydrogen versus Jet-A fuel with a closed-loop water recirculation system within a high-bypass turbofan.
 	The high-bypass turbofan study investigates the industry-proposed benefits of using a closed-loop water injection and water vapor recovery system with two types of fuels.
+	% TODO: AL-PA: I would stick to just saying we are going to leverage gradient-based optimization to do a paramter sweep.
+	%REPHRASE: We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and Hydrogen fuels.
 	We will perform a single point analysis to explore the design space and a multi-point gradient-based optimization to determine and validate the efficiency and emission improvements associated with the proposed engine model.
-	Finally, we will present the results from the design space analysis and multi-point optimization from this model.
+	% TODO: AL-PA: We don't need this sentence so I commented it out.
+	% Finally, we will present the results from the design space analysis and multi-point optimization from this model.
+	% TODO: AL-PA: This doesn't do a great job summarizing our effort and stating the benefit
+	% REPHRASE: This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to use the properties of hydrogen for improved performance and reduced emissions.
 	These developments will accelerate and validate current research into the next generation of fuel-efficient, low emission high-bypass turbofan engines.
@@
 % Message 1: Motivation to incorporate low-emission fuels and techniques
+% TODO: AL-PA: Rephrase this.
+% REPHRASE: The effects of climate change are pushing the aviation industry towards hydrogen fueled propulsion systems as a solution to reduce emissions.
 In the commercial aviation industry today, the global effects of climate change and high gas prices have motivated the development of more efficient and cleaner propulsion systems.
+% TODO: AL-PA: Rephrase this.
+% REPHRASE: N+3 technology estimates for turbofans burning hydrocarbon fuels point to ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
+%			Higher OPR and smaller core designs are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
 Most development so far has been targeted at making existing engine architectures more efficient with the fuels and technologies we currently have to reduce fuel consumption and thus release fewer carbon and NOx emissions.
+% TODO: AL-PA: Rephrase this.
+% REPHRASE: Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
+%			However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
+%			In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A or hydrogen considering UHB ratio turbofan engines.
+%			We will look at new ideas with water recirculation to squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
 By continuing this trend of development, high-bypass turbofan engines can be improved by lowering the pressure ratio of the fan to enable a higher bypass ratio of the engine.
-Furthermore, higher overall pressure ratios and more advanced metals with higher melting temperatures can allow larger burner temperatures both of which improve thermal efficiency.
+% TODO: AL-PA: We don't need this sentence until later.
+% Furthermore, higher overall pressure ratios and more advanced metals with higher melting temperatures can allow larger burner temperatures both of which improve thermal efficiency.
 
-Additionally, greener fuels can be used that have fewer products that are harmful to the environment and human health.
-Liquid hydrogen has been proposed as a possible replacement fuel for hydrocarbon fuel such as Jet-A due to the fact that hydrogen has zero carbon emissions and the combustion products mainly consist of water vapor.
-A consequence of using hydrogen as a fuel and designing higher pressure ratios is that hydrogen burns at higher temperatures than hydrocarbon fuels and higher pressure ratios result in higher combustion pressures.
-High combustion temperatures and pressures tend to increase NOx formation and emissions in aircraft engines.
+% TODO: AL-PA: We are saying upfront that we are using hydrogen so there is no reason to beat a dead horse here.
+% Additionally, greener fuels can be used that have fewer products that are harmful to the environment and human health.
+% Liquid hydrogen has been proposed as a possible replacement fuel for hydrocarbon fuel such as Jet-A due to the fact that hydrogen has zero carbon emissions and the combustion products mainly consist of water vapor.
+% A consequence of using hydrogen as a fuel and designing higher pressure ratios is that hydrogen burns at higher temperatures than hydrocarbon fuels and higher pressure ratios result in higher combustion pressures.
+% High combustion temperatures and pressures tend to increase NOx formation and emissions in aircraft engines.
 
 % Message 2: Background and references to support using H2 and water injection in HBTF engines
+% TODO: AL-PA: rephrase
+% REPHRASE: Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
 A potential solution to these drawbacks to improve fuel efficiency is to inject finely atomized water droplets into the core air stream of a high-bypass turbofan engine.
+% TODO: AL-PA: rephrase
+% REPHRASE: NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent.
 While water injection is generally an old technology, studies conducted by NASA, Boeing, and Rolls-Royce suggest that this technique can be used to reduce the NOx emissions in high-bypass turbofan engines by as much as 47\%.
+% TODO: AL-PA: rephrase
+% REPHRASE: Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
 Additional benefits include improvements in fuel efficiency and thrust, lower burner temperatures to improve the lifetime of high-temperature components, and engine noise reduction \cite{nasa_inject}.
+% TODO: AL-PA: rephrase
+% REPHRASE: Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
+%			The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
 While water injection may provide all of these benefits, water would still have to be stored on the aircraft and increase the weight of the aircraft.
+% TODO: AL-PA: rephrase
+% REPHRASE: If we switch to hydrogen fuels, the main product of hydrogen combustion is water vapor.
 Therefore, a method currently being investigated in industry is to use a closed-loop system that uses water vapor recovery from the exhaust to provide the water for injection.
+% TODO: AL-PA: rephrase
+% REPHRASE: The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
 This would eliminate the need for a water reservoir that would decrease the overall aircraft performance.
 
+% TODO: AL-PA: We are using a zero-dimensional approach because we scale maps.  If we did meanline turbomachinery analysis it would be one-dim
+% REPHRASE: Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
 These potential efficiency and emission improvements of aircraft engines can be cheaply and efficiently evaluated by using one-dimensional cycle analysis.
-One-dimensional cycle analysis uses a first-principles approach with simplifying assumptions to provide a low-fidelity model for engine analysis.
-This can be used to understand the general trends and design constraints of a engine cycle and evaluate potential improvements in design.
-Current tools that exist for engine cycle analysis include Numerical Propulsion System Simulation (NPSS) and pyCycle.
-NPSS utilizes a modular object-oriented framework in which individual engine components are connected and thermodynamic properties are evaluated using Chemical Equilibrium with Applications (CEA) to determine performance metrics of a given design.
-pyCycle improves on this modular architecture by introducing efficient analytic gradients to allow gradient-based multidisciplinary optimization \cite{Hendricks2019}.
+Zero-dimensional cycle analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver that considers the molecular species of different fuels.
+This can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
+The industry standard for zero and one-dimensional cycle analysis is the Numerical Proprulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
+NPSS is a modular object-oriented framework in that models engine components as individual blocks with several thermodynamic solvers.
+% pyCycle improves on this modular architecture by introducing efficient analytic gradients to allow gradient-based multidisciplinary optimization \cite{Hendricks2019}.
+\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but including analytical derivatives for every engine component and thermodynamic solver.
+We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures to improve robustness.
 
 % Message 3: Introduce the extension of the HBTF and propose novel contributions
-In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recovery with water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
-TSEC is the thrust specfic fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuels.
-The optimization problem will be accomplished by developing new pyCycle components for water injection and vapor recovery and will use empirical NOx formation correlations to evaluate NOx emissions.
-Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the how these improvements vary with fuel type and how they compare to current technologies.
+In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recirculation with a water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
+TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel, and is a metric for comparing the efficiency of different fuel choices.
+We will develop new pyCycle components for water injection and vapor recovery within pyCycle to understand the benefit of a closed loop recirculation system.
+In addition, we will apply existing empirical models as well as develop new surrogate models to estimate NOx emissions using chemical reactor networks and steady-state combustion analyses.
+Finally, we will present a comparison between Jet-A and hydrogen combustion with and without water recirculation in terms of improvement of TSEC and emissions.
+% Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the how these improvements vary with fuel type and how they compare to current technologies.
 
-In Section \ref{sec:epModel} we introduce the turbofan model and explain how we will introduce the water injection and water recovery components within the model.
-Additionally, preliminary data is provided as a motivation for studying these methods.
-Section \ref{sec:imp} explains how the multidisciplinary optimization will be implemented to take into account the different operating conditions of the engine model and the associated NOx emissions.
+In Section \ref{sec:epModel} we introduce the turbofan model and explain how we will implement the water injection and water recovery components in pyCycle.
+Section \ref{sec:imp} explains the implementation of the multi-point optimization problem and the conditions limiting the engine model.
 
@@
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-We will use a next-generation high-bypass turbofan engine configuration for this work.
-Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite[]{Hendricks2019}.
-The N+3 reference cycle represents a notional high bypass ratio geared turbofan that could be available in the 2030–2040 time frame.
-This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-This high-bypass turbofan model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
+We will use a next-generation UHB turbofan engine configuration for this work.
+% TODO: AL-PA: The pyCycle paper is not the original reference for the N+3 engine.  Use this instead: Jones2017a
+Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Hendricks2019}.
+The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame.
+% TODO: AL-PA: Rephrase
+% This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
+This propulsion cycle includes state of the art concepts such as a small core, high OPR, and advance turbine cooling technology.
+% This high-bypass turbofan model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
+The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
 The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-Along the axial flow path, a the one-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
+Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
 The closed-loop water recovery system is integrated by placing a water injection component directly before the HPC.
+% TODO: AL-PA: How will the water vapor reduce the combustion temperature? Need to be specific here.
 This component will inject pure water vapor into the core stream which will reduce the combustion temperature.
-The water vapor recovery component is then placed directly before the core nozzle to recover water vapor from the core stream and recycle it back to the water injector component.
-While in practice the water vapor recovery component would require a technical analysis of a condenser in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
-The flow and mechanical connections within the engine model with the water injector and water extractor are visualized in Figure \ref{fig:hbtf_cycle}.
+The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
+In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
+The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.
 
+% TODO: AL-PA: You need to add more description to the caption.  The figure and caption should stand alone in the paper.
+% i.e The reader should be able to look at the figure and caption and understand without reading the paper.
+% It's okay for the caption to be 3-4 sentences long if necessary.
 \begin{figure}[H]
@@
 % Preliminary Results
-This model has been tested using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency with injecting water into the core stream.
-The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in thrust specfic energy consumption with water injection for the same engine design with each type of fuel.
-We can already see great improvements in the cruise engine efficiency which may be able to be further improved with a full engine optimization.
+We tested the N+3 propulsion model with water recovery using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency.
+The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in TESC with water injection for the same engine design with each type of fuel.
+We see improvements in the cruise engine efficiency using a baseline analysis and will be further improved using design optimization.
 
+% TODO: AL-PA: Again, this needs a much better caption.
 \begin{figure}[H]
@@
 % Fully coupled model
+% TODO: AL-PA: One of my earlier changes already has this in the intro, but I think it's OK to keep it here as well if you agree.
 The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
-For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity \cite[]{Dubois2006}.
-This method uses the pressure and temperature of the flow before the combustor to determine NOx formation from a reference design condition of the engine.
-Since not many accurate NOx formation correlations exist for full-sized turbofan engines running on liquid hydrogen, we will use a surrogate model using data computed using Cantera to model the NOx emissions \cite[]{cantera}.
+% TODO: AL-PA: The Dubois2006 reference is missing
+% REPHRASE: The NOx model for Jet-A fuel will use the P3-T3 method~\cite{Dubois2006}, a common technique in academia and industry for determing NOx formation in aircraft engines.
+For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity \cite{Dubois2006}.
+This method uses the pressure and temperature of the flow before the combustor to determine NOx formation.
+% NOTE: AL: I removed the reference to Cantera.  We can cite it in the paper, but for now lets stick with combustor reactor network models
+Since not many accurate NOx formation correlations exist for full-sized turbofan engines running on liquid hydrogen, we will use a surrogate model using data from combustor reactor network models to accurately predict NOx emissions.
 
 % Briefly discuss the optimization problem
-We will perform gradient-based emission-propulsion design optimization of the engine model with a multipoint architecture that considers the common flight conditions experienced by commercial aircraft.
-An XDSM diagram of the optimization problem is shown in Figure \ref{fig:opt_prob}.
+We will perform gradient-based emission-propulsion design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
+An XDSM diagram of the optimization problem with the multi-point formulation is shown in Figure \ref{fig:opt_prob}.
 
@@
 
-The objective is to minimize the thrust specific energy consumption at a cruise condition subject to NOx formation, thrust, engine diameter and explore the design space of the model formulation.
-Following this study, we will conduct a multi-objective optimization problem considering thrust specific energy consumption and NOx formation.
-This will define a pareto front of different thrust specific energy consumption and NOx formation designs to show trade-offs in the design space.
+The objective is to minimize the thrust specific energy consumption at a cruise condition subject to constraints on NOx formation, thrust, max temperature, and engine diameter.
+We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
+With an understanding of the design space, we will construct a multi-objective optimization problem to generate a pareto front for the trade-space between TESC and NOx emissions.
 
@@
 % Message 1: Re-state the problem
-In this work, we will model, analyze, and optimize a high-bypass turbofan propulsion cycle using a novel closed-loop water vapor recovery to improve cycle efficiency and NOx emissions.
+In this work, we will model, analyze, and optimize a UHB next-generation turbofan model considering Jet-A and hydrogen fuel using a novel closed-loop water vapor recovery to improve cycle efficiency and NOx emissions.
 % Message 2: Summarize the HBTF model
-The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with two newly developed novel components to model water recovery and injection to accurately establish the performance and emissions improvements.
-Two fuels, Jet-A and liquid hydrogen, will be compared with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
-NOx formation will be modeled using common industry methods and a novel reactor model in Cantera for hydrogen combustion NOx formation.
+The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with the new water recovery and injection capability to asses the performance and emissions improvements.
+We will compare Jet-A and liquid hydrogen with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
+% AL: I added this line
+The results will show a quantitative comparison at the propulsion system level, with a qualitative assessment of the feasibility of water recirculation for both Jet-A and hydrogen fuels.
+We will use existing P3-T3 methods in addition to new surrogate based NOx prediction models to predict the emissions impact of each fuel with and without water recirculation.
 % Message 3: Expected results
-The results will include a full propulsion-emission analysis of the novel systems with multipoint design optimizations of the entire flight envelope.
-This work will build off of current industry research into emission reduction methods and provide a first principles analysis of the potential benefits of closed-loop water vapor recover and injection for commercial aviation applications.
+% The results will include a full propulsion-emission analysis of the novel systems with multipoint design optimizations of the entire flight envelope.
+We will develop a multi-objective optimization problem to find a pareto-front between TESC and NOx emissions for all fuel and water recovery architectures proposed in this work.
+Finally, this work will demonstrate the ability of gradient-based optimization with zero-dimensional cycle analysis to explore the potential benefits of hydrogen combustion with a closed-loop water vapor recover and injection.
 

### 2022-11-10 conference-abstract/main.tex
fixed AL's comments

@@
 	pdftitle={Aviation 2022 Abstract}, % insert title here
-	pdfsubject={Propulsion Analysis and Optimization of a High Bypass Turbofan Engine}, % insert keywords here
+	pdfsubject={Propulsion Analysis and Optimization of an Ultra Bypass Turbofan Engine}, % insert keywords here
 }
@@
 
-% TODO: AL-PA: Change the title to something like "Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation"
-% Current title doesn't really describe the biggest aspects of the paper
-% N+3 engine is a Ultra high-bypass engine...BPR > 20 for most designs
-\title{Multi-point Low-Emission Propulsion Analysis and Optimization of a High Bypass Turbofan Engine} % change
+\title{Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation} % change
 
@@
 \begin{abstract}
-	% TODO: AL-PA: Rephrase this sentence. You say 'larger' twice in the same context.
-	% REPHRASE: Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
-	Advances in commercial propulsion technology has lead to the development of larger and more advanced high-bypass turbofan engines with larger bypass ratios, pressure ratios, and internal temperatures.
-	% TODO: AL-PA: I wouldn't say 'impending climate crisis'.  Maybe change to 'With the focus on reducing aircraft emissions'
-	% TODO: AL-PA: Change from 'greener fuels' to say just 'Hydrogen'.  Drive home the point that we are studying the transition to H2.
-	% TODO: AL-PA: Just say carbon dioxide and NOx emissions, we don't consider all greenhouse emissions in this work.
-	With the impending climate crisis, aircraft and engine manufacturers have been pushing for greener fuels and more efficient engines to lower greenhouse and NOx emissions.
-	% TODO: AL-PA: Previous sentence already says we want to use greener fuels.
-	% REPHRASE: Using Hydrogen introduces complexity and weight penalties that we need to offset by using all the advantageous properties of the fuel.
-	This has revitalized research into using liquid hydrogen as a fuel for aircraft turbine engines in addition to using known thrust augmentation techniques to reduce NOx emissions and improve fuel efficiency.
-	% TODO: AL-PA: Rephrase this to be more clear
-	% REPHRASE: In this study we investigate the benefits of using Hydrogen versus Jet-A fuel with a closed-loop water recirculation system within a high-bypass turbofan.
-	The high-bypass turbofan study investigates the industry-proposed benefits of using a closed-loop water injection and water vapor recovery system with two types of fuels.
-	% TODO: AL-PA: I would stick to just saying we are going to leverage gradient-based optimization to do a paramter sweep.
-	%REPHRASE: We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and Hydrogen fuels.
-	We will perform a single point analysis to explore the design space and a multi-point gradient-based optimization to determine and validate the efficiency and emission improvements associated with the proposed engine model.
-	% TODO: AL-PA: We don't need this sentence so I commented it out.
-	% Finally, we will present the results from the design space analysis and multi-point optimization from this model.
-	% TODO: AL-PA: This doesn't do a great job summarizing our effort and stating the benefit
-	% REPHRASE: This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to use the properties of hydrogen for improved performance and reduced emissions.
-	These developments will accelerate and validate current research into the next generation of fuel-efficient, low emission high-bypass turbofan engines.
+	Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
+	With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for Hydrogen as a fuel and more efficient engines to lower carbon dioxide and NOx emissions.
+	Using Hydrogen introduces complexity and weight penalties that we need to offset by using all the advantageous properties of the fuel.
+	In this study we investigate the benefits of using Hydrogen versus Jet-A fuel with a closed-loop water recirculation system within a high-bypass turbofan.
+	We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and Hydrogen fuels.
+	This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to use the properties of hydrogen for improved performance and reduced emissions.
 \end{abstract}
@@
 % Message 1: Motivation to incorporate low-emission fuels and techniques
-% TODO: AL-PA: Rephrase this.
-% REPHRASE: The effects of climate change are pushing the aviation industry towards hydrogen fueled propulsion systems as a solution to reduce emissions.
-In the commercial aviation industry today, the global effects of climate change and high gas prices have motivated the development of more efficient and cleaner propulsion systems.
-% TODO: AL-PA: Rephrase this.
-% REPHRASE: N+3 technology estimates for turbofans burning hydrocarbon fuels point to ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
-%			Higher OPR and smaller core designs are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
-Most development so far has been targeted at making existing engine architectures more efficient with the fuels and technologies we currently have to reduce fuel consumption and thus release fewer carbon and NOx emissions.
-% TODO: AL-PA: Rephrase this.
-% REPHRASE: Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
-%			However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
-%			In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A or hydrogen considering UHB ratio turbofan engines.
-%			We will look at new ideas with water recirculation to squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
-By continuing this trend of development, high-bypass turbofan engines can be improved by lowering the pressure ratio of the fan to enable a higher bypass ratio of the engine.
+The effects of climate change are pushing the aviation industry towards Hydrogen-fueled propulsion systems as a solution to reduce emissions.
+N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
+Higher OPR and smaller core designs are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
+Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
+However, Hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
+In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A or Hydrogen considering UHB ratio turbofan engines.
+We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and Hydrogen combustion using gradient-based design optimization.
 % TODO: AL-PA: We don't need this sentence until later.
@@
 
-% TODO: AL-PA: We are saying upfront that we are using hydrogen so there is no reason to beat a dead horse here.
-% Additionally, greener fuels can be used that have fewer products that are harmful to the environment and human health.
-% Liquid hydrogen has been proposed as a possible replacement fuel for hydrocarbon fuel such as Jet-A due to the fact that hydrogen has zero carbon emissions and the combustion products mainly consist of water vapor.
-% A consequence of using hydrogen as a fuel and designing higher pressure ratios is that hydrogen burns at higher temperatures than hydrocarbon fuels and higher pressure ratios result in higher combustion pressures.
-% High combustion temperatures and pressures tend to increase NOx formation and emissions in aircraft engines.
+% Message 2: Background and references to support using H2 and water injection in HBTF engines
+Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
+NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent.
+Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
+Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
+The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
+However, if Hydrogen fuels are used, the main product of Hydrogen combustion is water vapor and can thus be recovered.
+The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
 
-% Message 2: Background and references to support using H2 and water injection in HBTF engines
-% TODO: AL-PA: rephrase
-% REPHRASE: Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
-A potential solution to these drawbacks to improve fuel efficiency is to inject finely atomized water droplets into the core air stream of a high-bypass turbofan engine.
-% TODO: AL-PA: rephrase
-% REPHRASE: NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent.
-While water injection is generally an old technology, studies conducted by NASA, Boeing, and Rolls-Royce suggest that this technique can be used to reduce the NOx emissions in high-bypass turbofan engines by as much as 47\%.
-% TODO: AL-PA: rephrase
-% REPHRASE: Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
-Additional benefits include improvements in fuel efficiency and thrust, lower burner temperatures to improve the lifetime of high-temperature components, and engine noise reduction \cite{nasa_inject}.
-% TODO: AL-PA: rephrase
-% REPHRASE: Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
-%			The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-While water injection may provide all of these benefits, water would still have to be stored on the aircraft and increase the weight of the aircraft.
-% TODO: AL-PA: rephrase
-% REPHRASE: If we switch to hydrogen fuels, the main product of hydrogen combustion is water vapor.
-Therefore, a method currently being investigated in industry is to use a closed-loop system that uses water vapor recovery from the exhaust to provide the water for injection.
-% TODO: AL-PA: rephrase
-% REPHRASE: The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
-This would eliminate the need for a water reservoir that would decrease the overall aircraft performance.
-
-% TODO: AL-PA: We are using a zero-dimensional approach because we scale maps.  If we did meanline turbomachinery analysis it would be one-dim
-% REPHRASE: Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
-These potential efficiency and emission improvements of aircraft engines can be cheaply and efficiently evaluated by using one-dimensional cycle analysis.
+Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
 Zero-dimensional cycle analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver that considers the molecular species of different fuels.
@@
 NPSS is a modular object-oriented framework in that models engine components as individual blocks with several thermodynamic solvers.
-% pyCycle improves on this modular architecture by introducing efficient analytic gradients to allow gradient-based multidisciplinary optimization \cite{Hendricks2019}.
 \citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but including analytical derivatives for every engine component and thermodynamic solver.
@@
 In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recirculation with a water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
-TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel, and is a metric for comparing the efficiency of different fuel choices.
+TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuel choices.
 We will develop new pyCycle components for water injection and vapor recovery within pyCycle to understand the benefit of a closed loop recirculation system.
@@
 Finally, we will present a comparison between Jet-A and hydrogen combustion with and without water recirculation in terms of improvement of TSEC and emissions.
-% Furthermore, two fuel types will be evaluated, Jet-A and liquid hydrogen to determine the how these improvements vary with fuel type and how they compare to current technologies.
 
@@
 We will use a next-generation UHB turbofan engine configuration for this work.
-% TODO: AL-PA: The pyCycle paper is not the original reference for the N+3 engine.  Use this instead: Jones2017a
-Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Hendricks2019}.
+Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Jones2017a}.
 The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame.
-% TODO: AL-PA: Rephrase
-% This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-This propulsion cycle includes state of the art concepts such as a small core, high OPR, and advance turbine cooling technology.
-% This high-bypass turbofan model consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
+This engine was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
 The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
@@
 Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
-The closed-loop water recovery system is integrated by placing a water injection component directly before the HPC.
-% TODO: AL-PA: How will the water vapor reduce the combustion temperature? Need to be specific here.
-This component will inject pure water vapor into the core stream which will reduce the combustion temperature.
+The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
+This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
 The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
@@
 	\includegraphics[width=0.8\textwidth]{turbofan_wvr.pdf}
-	\caption{Configuration of the high-bypass turbofan model with vapor recovery and injection.}
+	\caption{The configuration of a high-bypass turbofan model with an integrated closed-loop vapor recovery and injection system.
+		Water vapor is recovered from the core stream of the engine before the nozzle and is re-injected into the core stream before the LPC.}
 	\label{fig:hbtf_cycle}
@@
 % Preliminary Results
-We tested the N+3 propulsion model with water recovery using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency.
-The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in TESC with water injection for the same engine design with each type of fuel.
+We tested the N+3 propulsion model with water injection using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency.
+The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in TSEC with water injection for the same engine design with each type of fuel.
 We see improvements in the cruise engine efficiency using a baseline analysis and will be further improved using design optimization.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.png}
-	\caption{Relative improvement in TSEC from water injection.}
+	\includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.pdf}
+	\caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
+		Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
 	\label{fig:results}
@@
 % Fully coupled model
-% TODO: AL-PA: One of my earlier changes already has this in the intro, but I think it's OK to keep it here as well if you agree.
 The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
-% TODO: AL-PA: The Dubois2006 reference is missing
-% REPHRASE: The NOx model for Jet-A fuel will use the P3-T3 method~\cite{Dubois2006}, a common technique in academia and industry for determing NOx formation in aircraft engines.
-For the Jet-A fuel, the NOx correlation will use the P3-T3 method which is commonly a used technique in industry to determine NOx formation in aircraft engines while considering humidity \cite{Dubois2006}.
+The NOx model for Jet-A fuel will use the P3-T3 method~\cite{Dubois2006}, a common technique in academia and industry for determing NOx formation in aircraft engines.
 This method uses the pressure and temperature of the flow before the combustor to determine NOx formation.
-% NOTE: AL: I removed the reference to Cantera.  We can cite it in the paper, but for now lets stick with combustor reactor network models
 Since not many accurate NOx formation correlations exist for full-sized turbofan engines running on liquid hydrogen, we will use a surrogate model using data from combustor reactor network models to accurately predict NOx emissions.
@@
 	\includegraphics[width=0.8\textwidth]{N3_inject.pdf}
-	\caption{XDSM diagram of the multi-point optimization problem with constraints.}
+	\caption{XDSM diagram of the multi-point optimization problem with constraints.
+		The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
 	\label{fig:opt_prob}
@@
 
-The objective is to minimize the thrust specific energy consumption at a cruise condition subject to constraints on NOx formation, thrust, max temperature, and engine diameter.
+The objective is to minimize the TSEC at a cruise condition subject to constraints on NOx formation, thrust, max temperature, and engine diameter.
 We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
-With an understanding of the design space, we will construct a multi-objective optimization problem to generate a pareto front for the trade-space between TESC and NOx emissions.
+With an understanding of the design space, we will construct a multi-objective optimization problem to generate a pareto-front for the trade-space between TESC and NOx emissions.
 
@@
 % Message 2: Summarize the HBTF model
-The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with the new water recovery and injection capability to asses the performance and emissions improvements.
+The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with the new water recovery and injection capability to assess the performance and emissions improvements.
 We will compare Jet-A and liquid hydrogen with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
-% AL: I added this line
 The results will show a quantitative comparison at the propulsion system level, with a qualitative assessment of the feasibility of water recirculation for both Jet-A and hydrogen fuels.
@@
 % Message 3: Expected results
-% The results will include a full propulsion-emission analysis of the novel systems with multipoint design optimizations of the entire flight envelope.
 We will develop a multi-objective optimization problem to find a pareto-front between TESC and NOx emissions for all fuel and water recovery architectures proposed in this work.

### 2022-11-10 conference-abstract/main.tex
Adding my last round of changes

@@
 	Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
-	With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for Hydrogen as a fuel and more efficient engines to lower carbon dioxide and NOx emissions.
-	Using Hydrogen introduces complexity and weight penalties that we need to offset by using all the advantageous properties of the fuel.
-	In this study we investigate the benefits of using Hydrogen versus Jet-A fuel with a closed-loop water recirculation system within a high-bypass turbofan.
-	We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and Hydrogen fuels.
-	This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to use the properties of hydrogen for improved performance and reduced emissions.
+	With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for hydrogen as a fuel and more efficient engines to lower carbon dioxide and NOx emissions.
+	Carrying and burning hydrogen introduces complexity and weight penalties that can be partially offset by taking advantage of the fuel's thermodynamic and chemical properties.
+	In this study, we compare the benefits of using hydrogen against Jet-A fuel in a high-bypass turbofan with a closed-loop water recirculation system.
+	We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and hydrogen fuels.
+	This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to exploit the properties of hydrogen for improved performance and reduced emissions.
 \end{abstract}
@@
 % Message 1: Motivation to incorporate low-emission fuels and techniques
-The effects of climate change are pushing the aviation industry towards Hydrogen-fueled propulsion systems as a solution to reduce emissions.
+The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
 N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
-Higher OPR and smaller core designs are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
+Higher OPR and smaller cores are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
 Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
-However, Hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
-In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A or Hydrogen considering UHB ratio turbofan engines.
-We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and Hydrogen combustion using gradient-based design optimization.
-% TODO: AL-PA: We don't need this sentence until later.
-% Furthermore, higher overall pressure ratios and more advanced metals with higher melting temperatures can allow larger burner temperatures both of which improve thermal efficiency.
+However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
+In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHB ratio turbofan engines.
+We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
 
@@
 Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
+% TODO: AL-PM: This needs a citation.  If its the 'nasa_inject' citation we should add it in both lines.
 NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent.
@@
 The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-However, if Hydrogen fuels are used, the main product of Hydrogen combustion is water vapor and can thus be recovered.
+However, if hydrogen fuels are used, the main product of hydrogen combustion is water vapor and can thus be recovered.
 The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
@@
 NPSS is a modular object-oriented framework in that models engine components as individual blocks with several thermodynamic solvers.
-\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but including analytical derivatives for every engine component and thermodynamic solver.
-We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures to improve robustness.
+\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but includes analytical derivatives for each engine component and thermodynamic solver.
+We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
 
 % Message 3: Introduce the extension of the HBTF and propose novel contributions
-In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recirculation with a water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
+In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recovery and water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC) with a NOx emission constraint.
 TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuel choices.
@@
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
+% TODO: AL-PM: I think the follow three sentences can be reduced into one or two sentences.
 We will use a next-generation UHB turbofan engine configuration for this work.
-Specifically, the NASA advanced technology high bypass geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Jones2017a}.
+Specifically, the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine, was selected for this research \cite{Jones2017a}.
 The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame.
@@
 % It's okay for the caption to be 3-4 sentences long if necessary.
-\begin{figure}[H]
+\begin{figure}[!hbt]
 	\centering
-	\includegraphics[width=0.8\textwidth]{turbofan_wvr.pdf}
+	\includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
 	\caption{The configuration of a high-bypass turbofan model with an integrated closed-loop vapor recovery and injection system.
@@
 % TODO: AL-PA: Again, this needs a much better caption.
-\begin{figure}[H]
+\begin{figure}[!hbt]
 	\centering
@@
 % Fully coupled model
-The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and allows the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
+The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
 The NOx model for Jet-A fuel will use the P3-T3 method~\cite{Dubois2006}, a common technique in academia and industry for determing NOx formation in aircraft engines.
 This method uses the pressure and temperature of the flow before the combustor to determine NOx formation.
-Since not many accurate NOx formation correlations exist for full-sized turbofan engines running on liquid hydrogen, we will use a surrogate model using data from combustor reactor network models to accurately predict NOx emissions.
+Since not many accurate NOx correlations exist for full-sized turbofan engines burning liquid hydrogen, we will create a surrogate model using data from combustor reactor network models to accurately predict NOx emissions.
 
 % Briefly discuss the optimization problem
-We will perform gradient-based emission-propulsion design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
-An XDSM diagram of the optimization problem with the multi-point formulation is shown in Figure \ref{fig:opt_prob}.
+We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
+An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:opt_prob}.
 
-\begin{figure}[H]
+\begin{figure}[!hbt]
 	\centering
-	\includegraphics[width=0.8\textwidth]{N3_inject.pdf}
+	\includegraphics[width=0.75\textwidth]{N3_inject.pdf}
 	\caption{XDSM diagram of the multi-point optimization problem with constraints.

### 2022-12-21 AE590_report/main.tex
added 590 report and figures

\documentclass[12pt]{article}
% \documentclass[12pt]{new-aiaa}

% Formatting
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{siunitx}
\sisetup{group-separator = {,}}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{float}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{longtable,tabularx}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{latexsym}
\usepackage{subcaption}
\usepackage{latexsym}
\usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
\usepackage{hypernat} % To get natbib to play nicely with hyperref
\usepackage{doi} % For getting hyperlinked DOI in the references

\graphicspath{{../figures/}}

% Title content
\title{AERO 590: Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation}
\author{Peter Atma}
% \affil{University of Michigan, AERO 590}

\begin{document}

\maketitle

\section{Introduction}
The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
Higher OPR and smaller cores are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHB ratio turbofan engines.
We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.

Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
NASA, Boeing, and Rolls-Royce studied injectiong water into the airstream and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{nasa_inject}.
Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
However, if hydrogen fuels are used, the main product of hydrogen combustion is water vapor and can thus be recovered.
The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
Additionally, Pratt and Whitney are currently looking at closed-loop water vapor recovery for impementation in their Hydrogen Steam-Injected, Inter‐Cooled Turbine Engine (HySIITE) as part of the US Departement of Energy's Advanced Research Projects Agency-Energy (ARPA-E) program (CITE).
Pratt and Whitney suggest that this type of hydrogen-powered engine could achieve zero-carbon emissions and reduce NOx emissions by as much as 80\%.

Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
Zero-dimensional cycle analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver that considers the molecular species of different fuels.
This can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
The industry standard for zero and one-dimensional cycle analysis is the Numerical Proprulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
NPSS is a modular object-oriented framework that models engine components as individual blocks with several thermodynamic solvers.
\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but includes analytical derivatives for each engine component and thermodynamic solver.
We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.

In this work, the potential propulsion benefits of a closed-loop water vapor recovery and water injection system are analyzed in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC).
TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuel choices.
New pyCycle components are developed for water injection and vapor recovery within pyCycle to understand the benefit of a closed loop recirculation system.

\section{Model}

\subsection{Engine Model Overview}
The engine model that was selected for this project is the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_diagram.pdf}
    \caption{N+3 cycle layout.}
    \label{fig:N3_original}
\end{figure}

\noindent
The N3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
These operating conditions are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
To account for each of these operating conditions, the N3 model uses a technique called Multipoint Design Point (MDP) modeling to converge to an engine design that satisfies the requirements at each of these operation conditions.
One of the operation conditions is specified as the design point which in this case is TOC and the other operating conditions are the off-design points.
The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables to the off-design points and similarly converges those.
Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each point.
An XDSM diagram of the nominal N3 engine model is shown in Figure \ref{fig:N3_xdsm}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
    \caption{N+3 Multipoint XDSM diagram.}
    \label{fig:N3_xdsm}
\end{figure}

\subsection{Water Recovery Model}
The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
This location was chosen as it was one of the configurations chosen by the afformetioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{nasa_inject}.
The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
    \caption{The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.}
    \label{fig:hbtf_cycle}
\end{figure}

\noindent
To model this complicated water recirculation loop in pyCycle new components had to be developed.
The two new components that were developed are a water injector to add water to the flow and a water extractor to divert a fraction of the water in the flow back upstream.
The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
This new mixture combination is then used to compute the various chemical species present in the flow at the given thermodynamic state which is determined by the incoming flow.
The new species composition and thermodynamic variables are then determined using a Gibbs Free Energy minization approach called Chemical Equilibrium with Applications (CEA).
Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
The water injector component was created to work similarly to the combustor but would instead inject water as a reactant instead of the fuel.
The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
A simple schematic of the injector is shown in Figure \ref{fig:injector}

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{injector.png}
    \caption{Injector component schematic.}
    \label{fig:injector}
\end{figure}

\noindent
The water extractor component is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
This extractor component works by first determining the water content of the incoming flow and extracting a given fraction of that water flow.
The water content of the incoming flow is determined by solving a CEA analysis of the incoming flow.
This water content in the incoming flow is then used with a given fraction of the water to extract to determine the how much mass flow to remove from the stream.
At the some time, the atomic mixture is updated to represent the mixture that would be left if a number of hydrogen and oxygen atoms corresponding to the amount of water were removed.
The outputs of the extractor component are the flow rate of the main flow and the corresponding properties in addition to a water mass flow rate.
While this process certainly would have pressure loss penalties in terms of condensing water in a condersor, this project looks to just look at the effects of water recovery since there are no current models for nozzle exhaust condensors.
A simple schematic of the extractor is shown in Figure \ref{fig:extractor}

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{extractor.png}
    \caption{Extractor component schematic.}
    \label{fig:extractor}
\end{figure}

\noindent
Unlike other flow streams in the N3 model, the vapor recovery loop would be adding a mass flow rate at the injector and extracting a mass flow rate at the extractor, the loop would have a feedback effect.
This is because the pyCycle model is solved sequentially during each Newton iteration.
So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
However, the N3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
These connections can be seen in Figure \ref{fig:N3_xdsm_full}

\subsection{NOx Model}
To compute the Nitrogen Oxide (NOx) emissions from the engine model when using JetA as a fuel, the P3T3 NOx correlation was used (CITE).
The P3T3 method computes the NOx emission index (EINOx) of an engine at a specific operation condition as a function of the combustor pressure ($P_3$) and FAR.
The P3T3 method uses the EINOx level at sea-level operating condition as a reference point to scale the desired operating condition EINOx.
Finally, the EINOx level is scaled by a humidity factor based on the water content of the specific operating condition compared to the sea-level water content.
The P3T3 method is give below:

\begin{equation}
    EINOx_{alt} = EINOx_{SLS} \left(\frac{P_{3,alt}}{P_{3,SLS}}\right)^n \left(\frac{FAR_{alt}}{FAR_{SLS}}\right)^m e^{H}
\end{equation}

\begin{equation}
    H = 19 (h_{SLS} - h_{alt})
\end{equation}

\noindent
Experiments have shown that $n=0.4$ and $m=0$ so the FAR essentially drops out (CITE).
The sea-level EINOx level is determined using a curve-fit based on combustor inlet temperature ($T_3)$ (CITE).
The EINOx level is based on the CFM56-5B3 engine and is assumed to be proportional to $P_3^{0.4}$.

\begin{equation}
    EINOx = P_3^{0.4} (6.26 \times 10^{-8}T_3^3 - 0.000117 T_3^2 + 0.074 T_3 - 15.04)
\end{equation}

\noindent
Since the experimental data for these curve-fits are based on the CFM56-5B3 engine which runs on Jet-A fuel, this EINOx correlation will only be valid for Jet-A NOx emissions modeling.
Note, the curve-fit found in the above paper has a typo in that the factor on $T_3^2$ was $0.00117$.
However, inserting a 0 seems to fit the data curve-fit included in the paper relatively well.

\subsection{Performance Metrics}
For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since is a metric of how low the fuel burn is for a given level of thrust.
However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC):

\begin{equation}
    TSFC = \frac{\Dot{m}_{fuel}}{F_{thrust}}
\end{equation}

\begin{equation}
    TSEC = \frac{\Dot{m}_{fuel} LHV}{F_{thrust}} = TSFC \times LHV
\end{equation}

\noindent
With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full} and a N2 diagram of the model shown in Figure \ref{fig:N3_n2}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm_full.pdf}
    \caption{Full project N+3 XDSM diagram.}
    \label{fig:N3_xdsm_full}
\end{figure}

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_CLVR_n2.pdf}
    \caption{N2 diagram of the model.}
    \label{fig:N3_n2}
\end{figure}

\subsection{Model Parametric Studies}
To understand the coupling between the various operation conditions and design point, some simple parametric studies of the water recovery fraction were run.
The constant parameters for the engine and NOx model are shown in the table below.

\begin{table}[H]
    \centering
    \caption{atmosphere parameters for the parametric study.}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Parameter             & Value    & Units                 & Comments \\
        \hline
        $W_{TOC}$             & 820.441  & $lbm/s$               &          \\
        $BPR_{TOC}$           & 23.945   & $-$                   &          \\
        $PR_{HPC,TOC}$        & 53.633   & $-$                   &          \\
        $PR_{LPC,TOC}$        & 3.00     & $-$                   &          \\
        $PR_{fan,TOC}$        & 1.30     & $-$                   &          \\
        $F_{net,SLS}$         & 28620.84 & $lbf$                 &          \\
        $F_{net,CRZ}$         & 5510.72  & $lbf$                 &          \\
        $T_{4,TOC}/T_{4,RTO}$ & 0.926    & $-$                   &          \\
        $T_{4,RTO}$           & 3400.0   & $R$                   &          \\
        $h_TOC$               & 0.007    & $kg_{water}/kg_{air}$ &          \\
        $h_RTO$               & 0.001    & $kg_{water}/kg_{air}$ &          \\
        $h_SLS$               & 0.001    & $kg_{water}/kg_{air}$ &          \\
        $h_CRZ$               & 0.007    & $kg_{water}/kg_{air}$ &          \\
        $n$                   & 0.4      & $-$                   &          \\
        $m$                   & 0.0      & $-$                   &          \\
        \hline
    \end{tabular}
    \label{hx_params}
\end{table}

\noindent
Each of the 4 water recovery fractions was varied independently of the other 3 to gain an understanding of how that particular point was coupled with the rest.
The results are shown in Figure \ref{fig:para_study}.

\begin{figure}[!hbt]
    \centering
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{TSEC_N3-CLVR-H2-0-7-TOC.pdf}
        {TOC}
    \end{minipage}
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{TSEC_N3-CLVR-H2-0-5-RTO.pdf}
        {RTO}
    \end{minipage}
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{TSEC_N3-CLVR-H2-0-5-SLS.pdf}
        {SLS}
    \end{minipage}
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{TSEC_N3-CLVR-H2-0-10-CRZ.pdf}
        {CRZ}
    \end{minipage}
    \caption{}
    \label{fig:para_study}
\end{figure}

\noindent
From these figures we can see that the water fraction at TOC has a large impact on all of the off-design points. This makes sense since the design point sets the sizing of the engine and therefore dictates the performance of the off-design conditions. We also see that the water fraction at RTO has an impact on all of the operating conditions. This is due to the fact that the maximum temperature in the engine at TOC, $T_{4,TOC}$, is set by conditions at RTO. Therefore, the design point is affected by the water recovery at RTO. We see that the SLS condition has no impact on any other operating condition since its design has no impact on the other operating conditions. This is also true for the CRZ condition. The difference we see is that it is likely that the optimal water fraction at SLS will trend towards zero and the CRZ optimal water fraction will likely be non-zero.

\subsection{Optimization Problem}
The optimization problem of the N3 engine and the vapor recovery loop are shown in Figure \ref{fig:N3_xdsm_opt}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm_opt.pdf}
    \caption{Optimization XDSM diagram.}
    \label{fig:N3_xdsm_opt}
\end{figure}

\noindent
This optimization problem was run for both JetA and H2 fuels using the parameters given in the parametric study.
The optimization problem for each fuel was specified as:

\begin{equation*}
    \begin{aligned}
         & {\text{minimize}}
         &                     & TSEC_{CRZ}                                         \\
         & {\text{by varying}}
         &                     & x_{H2O,TOC}, x_{H2O,RTO}, x_{H2O,SLS}, x_{H2O,CRZ} \\
         & \text{subject to}
         &                     & F_{net,TOC} \geq 5800 lbf                          \\
    \end{aligned}
\end{equation*}

\subsection{Optimization Results}
The SNOPT optimizations for both fuels successfully finished with a 0/1 exit code and the optimal solution is given below. Note that the water recovery fraction, $x_{H2O,CRZ}$, had to be bounded above by a specific value. This value was determined by running the optimziation until the optimizer ran into numerical issues in the model where the engine would not resolve the amount of water in the engine at the CRZ condition. The optimizer wants to keep pushing through more and more water but this eventually breaks the model. Therefore an upper bound just below the breaking point is used.

\begin{table}[H]
    \centering
    \caption{Vapor recovery loop water fraction optimization for JetA fuel.}
    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Category    & Name          & Value   & Lower & Upper  & Units                 \\
        \hline
        Objective   & $TSEC_{CRZ}$  & 7886.58 & -     & -      & $\frac{BTU}{hr-lb_f}$ \\
        \hline
        Variables   & $x_{H2O,TOC}$ & 0.0699  & 0.0   & -      & -                     \\
                    & $x_{H2O,RTO}$ & 0.0     & 0.0   & -      & -                     \\
                    & $x_{H2O,SLS}$ & 0.0     & 0.0   & -      & -                     \\
                    & $x_{H2O,CRZ}$ & 0.27    & 0.0   & 0.27   & -                     \\
        \hline
        Constraints & $F_{net,TOC}$ & 5800.0  & -     & 5800.0 & $lbf$                 \\
        \hline
    \end{tabular}
    \label{tab_jeta_opt}
\end{table}

\begin{table}[H]
    \centering
    \caption{Vapor recovery loop water fraction optimization for H2 fuel.}
    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Category    & Name          & Value   & Lower & Upper  & Units                 \\
        \hline
        Objective   & $TSEC_{CRZ}$  & 7840.04 & -     & -      & $\frac{BTU}{hr-lb_f}$ \\
        \hline
        Variables   & $x_{H2O,TOC}$ & 0.105   & 0.0   & -      & -                     \\
                    & $x_{H2O,RTO}$ & 0.0     & 0.0   & -      & -                     \\
                    & $x_{H2O,SLS}$ & 0.0     & 0.0   & -      & -                     \\
                    & $x_{H2O,CRZ}$ & 0.19    & 0.0   & 0.19   & -                     \\
        \hline
        Constraints & $F_{net,TOC}$ & 5800.0  & -     & 5800.0 & $lbf$                 \\
        \hline
    \end{tabular}
    \label{tab_h2_opt}
\end{table}

\noindent
The convergence plot for the JetA optimzation is shown in Figure \ref{fig:conv_opt}. The plot for H2 is similar in shape.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{opt_summary.pdf}
    \caption{Optimality and feasibility convergence plots for JetA.}
    \label{fig:conv_opt}
\end{figure}

\noindent
From these optimization problems, we can see that the in both cases the CRZ condition water recovery fraction goes all the way to the upper bound.
We also see that the TOC condtion water recovery fraction finds a non-zero point that minimizes the objective whereas the RTO and SLS conditions find the smallest possible fraction.
While we saw in the parametric studies that a non-zero $x_{H2O,RTO}$ could improve efficiency, the $x_{H2O,TOC}$ takes this into account in how it resized parts of the engine.
These optimizations show the tight coupling between the different design points.
The off-design points do not have any impact on the performance of the design point (TOC) with the exception of RTO in how it handles maximum temperatures.
When the objective is the performance of the off-design CRZ condition, then the main two tuning variables are the water fractions at TOC and CRZ since those are the only two that directly impact the objective.
Finally, we see that the H2 fuel results in a slight improvement in TSEC.
Even this slight improvement is impactful since slight improvements in fuel economy result in large carbon and cost savings, with the added bonus of the hydrogen engine producing no carbon.

\section{Conclusions}
A novel water vapor recovery loop was developed, studied, and optimized for two different types of fuel.
New pyCycle components, a water injector and water extractor, were developed for this project and implmented in the NASA N3 ultra-high bypass turbofan engine.
Additionally, nitrogen oxide emission models were introduced and implemented to allow for NOx emission constraints on the engine model.
The parametric studies that were performed show a strong coupling between the on-design and off-design operation conditions of the N3 engine.
Furthermore, the simple optimizations that were performed for each fuel show an improvement in performance with water injection and recovery.
The different fuels ended up having very similar thrust-specific energy consumption metrics with a slight improvement when using hydrogen as a fuel as opposed to the traditional JetA fuel.
These results are promising as they indicate that the efficiency improvement that has been seen in empirical results can be modeled in zero-dimensional modeling software packages such as pyCycle, allowing multidisciplinary design and analysis for future high-efficiency engine and aircraft design.
Future plans for this project are to use this model to run large parallel sweeps of the model design space and to eventually create a surrogate model of this engine for use in other optimization libraries such as OpenConcept.
Additionally, water condensor models may be researched in the future so that a fairly accurate condensor and pressure loss model can be implemented for the extractor to determine how severe the pressure loss penalties are.
Finally, a pareto front will be computed to determine the tradeoffs between TSEC and NOx emissions for the JetA fuel.

\bibliography{mdolab,references}

% \newpage

% \section*{Appendix: Compressor and Turbine Maps}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.75\linewidth]{TOC.fan.pdf}
%     \caption{Optimized engine location on the fan map (black dot).}
%     \label{}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.75\linewidth]{TOC.lpc.pdf}
%     \caption{Optimized engine location on the low pressure compressor map (black dot).}
%     \label{}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.75\linewidth]{TOC.hpc.pdf}
%     \caption{Optimized engine location on the high pressure compressor map (black dot).}
%     \label{}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.75\linewidth]{TOC.lpt.pdf}
%     \caption{Optimized engine location on the low pressure turbine map (black dot).}
%     \label{}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.75\linewidth]{TOC.hpt.pdf}
%     \caption{Optimized engine location on the high pressure turbine map (black dot).}
%     \label{}
% \end{figure}

\end{document}

### 2022-12-21 AE590_report/main.tex
updated report

@@
-\documentclass[12pt]{article}
-% \documentclass[12pt]{new-aiaa}
+\RequirePackage{fix-cm}
+% \documentclass[12pt]{article}
+\documentclass[12pt]{new-aiaa}
 
@@
 The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
-Additionally, Pratt and Whitney are currently looking at closed-loop water vapor recovery for impementation in their Hydrogen Steam-Injected, Inter‐Cooled Turbine Engine (HySIITE) as part of the US Departement of Energy's Advanced Research Projects Agency-Energy (ARPA-E) program (CITE).
+Additionally, Pratt and Whitney are currently looking at closed-loop water vapor recovery for impementation in their Hydrogen Steam-Injected, Inter‐Cooled Turbine Engine (HySIITE) as part of the US Departement of Energy's Advanced Research Projects Agency-Energy (ARPA-E) program \cite{hysiite}.
 Pratt and Whitney suggest that this type of hydrogen-powered engine could achieve zero-carbon emissions and reduce NOx emissions by as much as 80\%.
@@
 The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
-A simple schematic of the injector is shown in Figure \ref{fig:injector}
+A simple schematic of the injector is shown in Figure \ref{fig:injector} where $Y_{H_2O}$ is the mole fraction of water molecules.
 
@@
 While this process certainly would have pressure loss penalties in terms of condensing water in a condersor, this project looks to just look at the effects of water recovery since there are no current models for nozzle exhaust condensors.
-A simple schematic of the extractor is shown in Figure \ref{fig:extractor}
+A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream of operating condition, $k$.
 
@@
 \subsection{NOx Model}
-To compute the Nitrogen Oxide (NOx) emissions from the engine model when using JetA as a fuel, the P3T3 NOx correlation was used (CITE).
+To compute the Nitrogen Oxide (NOx) emissions from the engine model when using JetA as a fuel, the P3T3 NOx correlation was used \cite{Voet2021}.
 The P3T3 method computes the NOx emission index (EINOx) of an engine at a specific operation condition as a function of the combustor pressure ($P_3$) and FAR.
@@
         \hline
-        Constraints & $F_{net,TOC}$ & 5800.0  & -     & 5800.0 & $lbf$                 \\
+        Constraints & $F_{net,TOC}$ & 5800.0  & 5800.0 & -     & $lbf$                 \\
         \hline
@@
 Finally, a pareto front will be computed to determine the tradeoffs between TSEC and NOx emissions for the JetA fuel.
+All of these future studies will help determine if the claims of performance enhancements and emission reductions of water recovery and hydrogen engines that are promoted by industy are within the realm of possibliy.
 

### 2023-04-22 conference-paper/paper_main.tex
Added conference paper tex file and started writing

\RequirePackage{fix-cm}
\documentclass[conf]{new-aiaa}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{siunitx}
\sisetup{group-separator = {,}}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{float}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{longtable,tabularx}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{latexsym}
\usepackage{subcaption}
\usepackage{latexsym}
\usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
\usepackage{hypernat} % To get natbib to play nicely with hyperref
\usepackage{doi} % For getting hyperlinked DOI in the references

\hypersetup{
    pdfauthor={Peter Atma}, % insert author here
	pdftitle={Aviation 2022 Abstract}, % insert title here
	pdfsubject={Propulsion Analysis and Optimization of an Ultra Bypass Turbofan Engine}, % insert keywords here
}

\graphicspath{{../figures/}}

\title{Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation} % change

\author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
\author{Andrew H.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
\author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
\affil{University of Michigan, Ann Arbor, MI, 48109}

% ==================================================
%	Abstract
% ==================================================

% ==================================================
\begin{document}

\maketitle

\begin{abstract}
    Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
    With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for hydrogen as a fuel and more efficient engines to lower carbon emissions.
    Carrying and burning hydrogen introduces complexity and weight penalties that can be partially offset by taking advantage of the fuel's thermodynamic and chemical properties.
    In this study, we compare the benefits of using hydrogen against Jet-A fuel in a high-bypass turbofan with a closed-loop water recirculation system.
    We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and hydrogen fuels.
    This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to exploit the properties of hydrogen for improved performance and reduced emissions.
\end{abstract}

\section{Introduction}
% Message 1: Motivation to incorporate low-emission fuels and techniques
The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
Higher OPR and smaller cores are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHB ratio turbofan engines.
We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.

% Message 2: Background and references to support using H2 and water injection in HBTF engines
Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{nasa_inject}.
Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
However, if hydrogen fuels are used, the main product of hydrogen combustion is water vapor and can thus be recovered.
The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.

Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
Zero-dimensional cycle analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver that considers the molecular species of different fuels.
This can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
The industry standard for zero and one-dimensional cycle analysis is the Numerical Proprulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
NPSS is a modular object-oriented framework that models engine components as individual blocks with several thermodynamic solvers.
\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but includes analytical derivatives for each engine component and thermodynamic solver.
We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.

% Message 3: Introduce the extension of the HBTF and propose novel contributions
In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recovery and water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC).
TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuel choices.
We will develop new pyCycle components for water injection and vapor recovery within pyCycle to understand the benefit of a closed loop recirculation system.
Finally, we will present a comparison between Jet-A and hydrogen combustion with and without water recirculation in terms of improvement of TSEC.

This work is organized as follows. First, in Section \ref{sec:method}, we introduce the turbofan model and explain how we will implement the water injection and water recovery components in pyCycle.
In section \ref{sec:results} explains the implementation of the multi-point optimization problem and the conditions limiting the engine model.

% \section{Model Description}
% \label{sec:epModel}
% % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
% We will use the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a} for this work.
% The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
% The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
% The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
% Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
% This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
% The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
% The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.

% \begin{figure}[!hbt]
%     \centering
%     \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
%     \caption{The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
%         Water vapor is recovered from the core stream of the engine before the nozzle and is re-injected into the core stream before the HPC.}
%     \label{fig:hbtf_cycle}
% \end{figure}

% % Preliminary Results
% We tested the N+3 propulsion model with water injection using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency.
% The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in TSEC with water injection for the same engine design with each type of fuel.
% We see improvements in the cruise engine efficiency using a baseline analysis and will be further improved using design optimization.

% \begin{figure}[!hbt]
%     \centering
%     \includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.pdf}
%     \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
%         Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
%     \label{fig:results}
% \end{figure}

\section{Methodology}
\label{sec:method}
\subsection{Engine Model Overview}
The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
The engine model that was selected for this project is the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure the first principle governing equations are satisfied.
Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_diagram.pdf}
    \caption{
        N+3 engine cycle layout that shows how each of the pyCycle components are connected and how performance metrics are computed.
        The fluid flow connections are shown in blue, the mechanical connections are shown in red, and the performance connections are shown in green.
    }
    \label{fig:N3_original}
\end{figure}

\noindent
The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
These operating conditions are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design that satisfies the requirements at each of these operation conditions.
One of the operation conditions is specified as the design point, which in this case is TOC, and the other operating conditions are the off-design points.
The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
    \caption{
        N+3 engine multipoint setup XDSM diagram.
        This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
    }
    \label{fig:N3_xdsm}
\end{figure}

\subsection{Water Recovery Model}
The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
This location was chosen as it was one of the configurations chosen by the afformetioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{nasa_inject}.
The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
    \caption{
        The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
        The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and reinjects it upstream of the high-pressure compressor.
        This diagram illustrates the feedback effect that this implementation has on the overall core flow.}
    \label{fig:hbtf_cycle}
\end{figure}

\noindent
To model this complicated water recirculation loop in pyCycle new components had to be developed.
The two new components that were developed are a water injector to add water to the flow and a water extractor to divert a fraction of the water in the flow back upstream.
The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
This new mixture combination is then used to compute the various chemical species present in the flow at the given thermodynamic state which is determined by the incoming flow.
The new species composition and thermodynamic variables are then determined using a Gibbs Free Energy minization approach called Chemical Equilibrium with Applications (CEA).
Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
The water injector component was created to work similarly to the combustor but would instead inject water as a reactant instead of the fuel.
The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
A simple schematic of the injector is shown in Figure \ref{fig:injector} where $Y_{H_2O}$ is the mole fraction of water molecules.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{injector.pdf}
    \caption{
        Injector component schematic.
        Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
    }
    \label{fig:injector}
\end{figure}

\noindent
The water extractor component is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
This extractor component works by first determining the water content of the incoming flow and extracting a given fraction of that water flow.
The water content of the incoming flow is determined by solving a CEA analysis of the incoming flow.
This water content in the incoming flow is then used with a given fraction of the water to extract to determine the how much water mass flow to remove from the stream.
At the same time, the atomic mixture of the core stream is updated to represent the mixture that would be left if a number of hydrogen and oxygen atoms corresponding to the amount of water extracted were removed.
The outputs of the extractor component are the flow rate of the core flow and the corresponding flow properties in addition to the extracted water mass flow rate.
While this process certainly would have pressure loss penalties in terms of condensing water in a condersor, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensors available.
A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream of operating condition, $k$.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{extractor.pdf}
    \caption{
        Extractor component schematic.
        A certain mole fraction of the flow coming out of duct5 is comprised of water of which a certain specified fraction is extracted.
        The extracted water is routed back upstream to the injector and the rest is simply exhausted out the nozzle.
    }
    \label{fig:extractor}
\end{figure}

\noindent
Unlike other flow streams in the N+3 model, the vapor recovery loop has a feedback effect since it is adding a mass flow rate at the injector and extracting a mass flow rate at the extractor.
This is because the pyCycle model is solved sequentially during each Newton iteration.
So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
However, the N+3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
These connections can be seen in Figure \ref{fig:N3_xdsm_full}

% Talk about how areas are connected in pyCycle (injector/extractor set at CRZ everything else at TOC)

\subsection{Performance Metrics}
For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since is a metric of how low the fuel burn is for a given level of thrust.
However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel \cite{Adler2022d}.

\begin{equation}
    TSFC = \frac{\Dot{m}_{fuel}}{F_{thrust}}
\end{equation}

\begin{equation}
    TSEC = \frac{\Dot{m}_{fuel} LHV}{F_{thrust}} = TSFC \times LHV
\end{equation}

\noindent
With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm_full.pdf}
    \caption{
        Full model N+3 XDSM diagram.
        This XDSM diagram shows the multipoint coupling between the different operation conditions and shows how the water recovery fractions are used to solve for water mass flow rates.
    }
    \label{fig:N3_xdsm_full}
\end{figure}

\subsection{Model Parametric Studies}
To understand the coupling between the various operation conditions and design point, a few simple parametric studies of the water recovery fractions were run.
The design parameters for the engine are shown in the table below.
Additionally, the humidity conditions listed below are used in the flight conditions component in the N+3 engine to ensure that the humidity of the air entering the engine is equal to the humidity of the atmosphere at a given operating condition.

\begin{table}[H]
    \centering
    \caption{
        N3 engine model parameters.
        These parameters specify the engine design used for analysis in this report.
        Atmospheric parameters are presented that specify the flight conditions and humidity of the atmosphere.}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Parameter             & Value    & Units                 & Comments                                       \\
        \hline
        $W_{TOC}$             & 820.441  & $lbm/s$               & TOC total mass flow rate of air                \\
        $BPR_{TOC}$           & 23.945   & $-$                   & TOC bypass Ratio                               \\
        $PR_{HPC,TOC}$        & 53.633   & $-$                   & TOC high-pressure compressor pressure ratio    \\
        $PR_{LPC,TOC}$        & 3.00     & $-$                   & TOC low-pressure compressor pressure ratio     \\
        $PR_{fan,TOC}$        & 1.30     & $-$                   & TOC fan pressure ratio                         \\
        $F_{net,SLS}$         & 28620.84 & $lbf$                 & SLS net thrust                                 \\
        $F_{net,CRZ}$         & 5510.72  & $lbf$                 & CRZ net thrust                                 \\
        $T_{4,TOC}/T_{4,RTO}$ & 0.926    & $-$                   & TOC-to-RTO temperature ratio                   \\
        $T_{4,RTO}$           & 3400.0   & $^{\circ}R$           & RTO combustor temperature                      \\
        $h_{TOC}$             & 0.001    & $kg_{water}/kg_{air}$ & humidity raio at TOC                           \\
        $h_{RTO}$             & 0.007    & $kg_{water}/kg_{air}$ & humidity raio at RTO                           \\
        $h_{SLS}$             & 0.007    & $kg_{water}/kg_{air}$ & humidity raio at SLS                           \\
        $h_{CRZ}$             & 0.001    & $kg_{water}/kg_{air}$ & humidity raio at CRZ                           \\
        $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A \cite{boeingJetA} \\
        $LHV_{H2}$            & 51591.0  & $BTU/lbm$             & Lower heating value of H2 \cite{engtoolboxH2}  \\
        \hline
    \end{tabular}
    \label{engine_params}
\end{table}

\subsection{Optimization Problem}
The optimization problem of the N3 engine and the vapor recovery loop are shown in Figure \ref{fig:N3_xdsm_opt}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_xdsm_opt.pdf}
    \caption{
        XDSM diagram of the multipoint optimization problem with constraints.
        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
    \label{fig:N3_xdsm_opt}
\end{figure}

\noindent
This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
The optimization problem for each fuel was specified as:

\begin{table}[h]
    \centering
    \caption{
        Multipoint optimization problem definition.
        The 4 design variables are the water recovery fractions of the core exhaust stream at each operation condition.
        The objective function is the thrust specific energy consumption at the cruise condition with a net thrust constraint at the design point, TOC.
    }
    \small
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{r l l l l}
        \toprule
                        & Variable/Function           & Description                                                & Units                 & Quantity \\
        \hline
        minimize        & $ \text{TSEC}_{CRZ} $       & Thrust specific energy consumption at the cruise condition & $\frac{BTU}{hr-lb_f}$ & 1        \\
                        &                             &                                                            &                       &          \\
        with respect to & $x_{H2O,TOC}$               & Water recovery fraction at TOC                             & -                     & 1        \\
                        & $x_{H2O,RTO}$               & Water recovery fraction at RTO                             & -                     & 1        \\
                        & $x_{H2O,SLS}$               & Water recovery fraction at SLS                             & -                     & 1        \\
                        & $x_{H2O,CRZ}$               & Water recovery fraction at CRZ                             & -                     & 1        \\
                        & $PR_{HPC,TOC}$              & TOC high-pressure compressor pressure ratio                & -                     & 1        \\
                        & $PR_{LPC,TOC}$              & TOC low-pressure compressor pressure ratio                 & -                     & 1        \\
                        & $PR_{fan,TOC}$              & TOC fan pressure ratio                                     & -                     & 1        \\
                        & $T_{4,TOC}/T_{4,RTO}$       & TOC-to-RTO temperature ratio                               & -                     & 1        \\
                        & $T_{4,RTO}$                 & RTO combustor temperature                                  & $^\circ$R             & 1        \\
        \cline{3-5}
                        &                             & Total                                                      &                       & 4        \\
                        &                             &                                                            &                       &          \\
        subject to      & $F_{net,TOC} \geq 5800$ lbf & Target net thrust at TOC                                   & lbf                   & 1        \\
                        & $D_{Fan} \leq 100$ $in^2$   & Maximum Fan Diameter                                       & $in^2$                & 1        \\
        \cline{3-5}
                        &                             & Total                                                      &                       & 1        \\
        \bottomrule
    \end{tabular}
    \label{tab:opt_problem}
\end{table}

% Briefly discuss the optimization problem
We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:opt_prob}.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=0.75\textwidth]{N3_inject.pdf}
    \caption{XDSM diagram of the multi-point optimization problem with constraints.
        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
    \label{fig:opt_prob}
\end{figure}

The objective is to minimize the TSEC at a cruise condition subject to constraints, thrust, max temperature, and engine diameter.
We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.

\section{Results}
\label{sec:results}

% results of parameter sweep
% results of parameter sweep
% results of optimization problems

\section{Conclusion}
\label{sec:conc}
% Message 1: Re-state the problem
In this work, we will model, analyze, and optimize a UHB next-generation turbofan model considering Jet-A and hydrogen fuel using a novel closed-loop water vapor recovery to improve cycle efficiency.
% Message 2: Summarize the HBTF model
The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with the new water recovery and injection capability to assess the performance and emissions improvements.
We will compare Jet-A and liquid hydrogen with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
The results will show a quantitative comparison at the propulsion system level, with a qualitative assessment of the feasibility of water recirculation for both Jet-A and hydrogen fuels.
% Message 3: Expected results
Finally, this work will demonstrate the ability of gradient-based optimization with zero-dimensional cycle analysis to explore the potential benefits of hydrogen combustion with a closed-loop water vapor recovery and injection.

\bibliography{mdolab,references}

\end{document}

### 2023-04-26 conference-paper/paper_main.tex
Draft sections Intro, Methods, Optimization problem completed

@@
 This work is organized as follows. First, in Section \ref{sec:method}, we introduce the turbofan model and explain how we will implement the water injection and water recovery components in pyCycle.
-In section \ref{sec:results} explains the implementation of the multi-point optimization problem and the conditions limiting the engine model.
-
-% \section{Model Description}
-% \label{sec:epModel}
-% % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-% We will use the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a} for this work.
-% The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-% The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
-% The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-% Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
-% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
-% This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
-% The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
-% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
-% The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.
-
-% \begin{figure}[!hbt]
-%     \centering
-%     \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
-%     \caption{The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
-%         Water vapor is recovered from the core stream of the engine before the nozzle and is re-injected into the core stream before the HPC.}
-%     \label{fig:hbtf_cycle}
-% \end{figure}
-
-% % Preliminary Results
-% We tested the N+3 propulsion model with water injection using Jet-A and liquid hydrogen fuels to determine if there are any immediate improvements in efficiency.
-% The preliminary results from this analysis are shown in Figure \ref{fig:results} and show the relative improvement in TSEC with water injection for the same engine design with each type of fuel.
-% We see improvements in the cruise engine efficiency using a baseline analysis and will be further improved using design optimization.
-
-% \begin{figure}[!hbt]
-%     \centering
-%     \includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.pdf}
-%     \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
-%         Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
-%     \label{fig:results}
-% \end{figure}
+In section \ref{sec:optprob} the implementation of the multi-point optimization problem is discussed. Finally, we present the results from the optimization problem in section \ref{sec:results}.
 
@@
 \subsection{Engine Model Overview}
-The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
-The engine model that was selected for this project is the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
+% Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
+In this work we use the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
 The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
@@
 The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure the first principle governing equations are satisfied.
-Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.
+Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
+The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
+This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
+The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
+In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
+The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:N3_original}.
+% The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
+% The engine model that was selected for this project is the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
+% The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
+% The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
+% The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
+% Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure the first principle governing equations are satisfied.
+% Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{N3_diagram.pdf}
+    \includegraphics[width=1.0\textwidth]{N3_cycle.pdf}
     \caption{
-        N+3 engine cycle layout that shows how each of the pyCycle components are connected and how performance metrics are computed.
-        The fluid flow connections are shown in blue, the mechanical connections are shown in red, and the performance connections are shown in green.
+        N+3 engine cycle layout that shows how each of the pyCycle components are connected and how performance metrics are computed. % Use Tiks
     }
@@
 
-\noindent
-The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
-These operating conditions are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design that satisfies the requirements at each of these operation conditions.
-One of the operation conditions is specified as the design point, which in this case is TOC, and the other operating conditions are the off-design points.
-The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
-Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
-An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
-    \caption{
-        N+3 engine multipoint setup XDSM diagram.
-        This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
-    }
-    \label{fig:N3_xdsm}
-\end{figure}
-
-\subsection{Water Recovery Model}
+\subsection{Water Recovery Loop Model}
 The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
@@
 In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
-The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:hbtf_cycle}.
+The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:n3_cycle}.
 
@@
         This diagram illustrates the feedback effect that this implementation has on the overall core flow.}
-    \label{fig:hbtf_cycle}
+    \label{fig:n3_cycle}
 \end{figure}
 
-\noindent
-To model this complicated water recirculation loop in pyCycle new components had to be developed.
-The two new components that were developed are a water injector to add water to the flow and a water extractor to divert a fraction of the water in the flow back upstream.
+Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
+To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
+This can be accomplished by using the $wet_air$ dataset in pyCycle.
+The $wet_air$ dataset simply uses the $Janaf$ dataset from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
+The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
+In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
+The WAR value is simply the specific humidity (g water/kg total) of the air expressed in equal units and separating out the total mass (kg water/kg air).
+The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.
+
+To model the complicated water recirculation loop in pyCycle new components had to be developed.
+The two new components that were developed are a water injector to add water to the flow and a water extractor to divert a fraction of the water in the flow away from the exhaust stream.
 The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
@@
 Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
-The water injector component was created to work similarly to the combustor but would instead inject water as a reactant instead of the fuel.
+The water injector component would inject water as a reactant instead of the fuel as the combustor would.
 The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
@@
 
-\noindent
 The water extractor component is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
@@
 
-\noindent
 Unlike other flow streams in the N+3 model, the vapor recovery loop has a feedback effect since it is adding a mass flow rate at the injector and extracting a mass flow rate at the extractor.
-This is because the pyCycle model is solved sequentially during each Newton iteration.
+This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
 So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
 However, the N+3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
-These connections can be seen in Figure \ref{fig:N3_xdsm_full}
+These connections can be seen in Figure \ref{fig:N3_xdsm_full}.
 
-% Talk about how areas are connected in pyCycle (injector/extractor set at CRZ everything else at TOC)
+\begin{figure}[!hbt]
+    \centering
+    \includegraphics[width=1.0\textwidth]{N3_CLVR_cycle.pdf}
+    \caption{
+        N+3 engine cycle layout that shows how each of the pyCycle components are connected with the closed-loop vapor recovery system. % Use Tiks
+    }
+    \label{fig:n3_clvr}
+\end{figure}
+
+In pyCycle, the Cycle block contains all of the governing thermodynamic equations needed to model an engine such as CEA analysis, compressor and turbine models, and equations of state.
+These equations allow any arbitrary engine design to be assembled using the modular cycle elements.
+The Cycle block itself may not result in a valid model of the engine since some physical dependencies may not match.
+These physical dependencies are handled by the Balance block which solves a set of implicit state variables and nonlinear physical residual equations in the form:
+
+\begin{equation}
+    \mathcal{R}_c = \sum_{i=1}^{n} x_i = 0
+\end{equation}
+
+\noindent
+where $x_i$ is some physical variable such as a mass or energy flow rate.
+These residuals represent the physical conservation laws such as mass flow rate are converged to zero by the Solver.
+In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which uilizes the analytic partial derivatives provided by each OpenMDAO component.
+All residuals within the engine model are converged at the Cycle level for a given operation condition since all of the parameters downstream do not directly effect those upstream.
+However, with introducing the extractor and injector components, we add a feedback loop into the model where mass is removed downstream and added upstream.
+Therefore, the mass flow rates residuals of the closed-loop vapor recovery system shown below would need to be converged in the Multipoint Cycle explained in the next section.
+
+\begin{equation}
+    \mathcal{R}_{c,\dot{m}} = \dot{m}_{extractor} - \dot{m}_{injector} = 0
+\end{equation}
+
+\subsection{Multipoint Model}
+The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
+Therefore, the N+3 enigne model computes the engine performance at 4 different operating conditions in order to resolve the complexities between each operating condition on the final design.
+The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+The SLS condition represents the static performance requirements for the engine, the RTO condition represents the performance and cooling requirements at the point of rotation during takeoff, the TOC operating condition represents the performance requirements during a climb, and the CRZ operation condition represents the criuse performance of the engine.
+To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design that satisfies the requirements at each of these operating conditions.
+One of these operating conditions is specified as the design point, which in this case is TOC, and the other operating conditions are considered the off-design points.
+The design point for the model generally sets all of the engine sizing such as areas and pressure ratios across components.
+The off-design points are essentially the size of the engine at the design point but operating at the corresponding required thrust, cooling, and environmental conditions.
+The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
+Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
+An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
+
+\begin{figure}[!hbt]
+    \centering
+    \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
+    \caption{
+        N+3 engine multipoint setup XDSM diagram.
+        This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
+    }
+    \label{fig:N3_xdsm}
+\end{figure}
+
+In the optimization problem described later, we set the mass flow rate of fuel, $\dot{m}_{fuel}$, as the objective fuction.
+Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+Therefore, the water mass fraction that will most impact the objective function the most is at the CRZ operating condition and we thus want to size the area of the injector and extractor at CRZ instead of TOC like the rest of the areas are.
+Normally, the cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
+To size the areas of the injector and extractor at CRZ, we only connect the state variables across these components at the corresponding operating condition and set the areas of both components at the CRZ point.
+These connections are shown graphically in the XDSM diagram in Figure \ref{fig:N3_xdsm_full}.
+
+% Explain Exit ratios and how BPR and OD net thrusts are set
+In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a Balance component.
+The Balance component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
+
+\begin{equation}
+    V_{ratio} = \frac{V_{core,ideal}C_{v,core}}{V_{bypass,ideal}C_{v,bypass}}
+\end{equation}
+
+\noindent
+where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient of the nozzle which represents non-ideal effects.
+This adds a constraint where the core exit velocity is higher than the bypass exit velocity.
 
 \subsection{Performance Metrics}
-For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since is a metric of how low the fuel burn is for a given level of thrust.
+Past implementations of engine cycles and example engine cycles in pyCycle generally have used either JetA or JP-7 as a fuel.
+However, in this work we are interested in comparing the performance of similar engines with different types of fuel, specifically hydrogen due to the many benefits it offers in terms of performance and thermal properties.
+Fortunatly, pyCycle comes ready to use hydrogen with cateloged exhaust products for hydrogen fuel.
+The fuel type is simply changed from Jet-A to H2 in the pyCycle model.
+
+For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since it is a represents how low the fuel burn is for a given level of thrust.
 However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
@@
 
-\noindent
 With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.
@@
 
+% Update with table from Andrew
 \begin{table}[H]
@@
         $BPR_{TOC}$           & 23.945   & $-$                   & TOC bypass Ratio                               \\
-        $PR_{HPC,TOC}$        & 53.633   & $-$                   & TOC high-pressure compressor pressure ratio    \\
+        $PR_{HPC,TOC}$        & 53.633   & $-$                   & TOC overall pressure ratio                     \\
         $PR_{LPC,TOC}$        & 3.00     & $-$                   & TOC low-pressure compressor pressure ratio     \\
@@
         $T_{4,RTO}$           & 3400.0   & $^{\circ}R$           & RTO combustor temperature                      \\
-        $h_{TOC}$             & 0.001    & $kg_{water}/kg_{air}$ & humidity raio at TOC                           \\
-        $h_{RTO}$             & 0.007    & $kg_{water}/kg_{air}$ & humidity raio at RTO                           \\
-        $h_{SLS}$             & 0.007    & $kg_{water}/kg_{air}$ & humidity raio at SLS                           \\
-        $h_{CRZ}$             & 0.001    & $kg_{water}/kg_{air}$ & humidity raio at CRZ                           \\
+        $h_{TOC}$             & 0.00017  & $kg_{water}/kg_{air}$ & humidity ratio at TOC \cite{Kalnay1996}        \\
+        $h_{CRZ}$             & 0.00017  & $kg_{water}/kg_{air}$ & humidity ratio at CRZ \cite{Kalnay1996}        \\
+        $h_{RTO}$             & 0.009    & $kg_{water}/kg_{air}$ & humidity ratio at RTO \cite{Kalnay1996}        \\
+        $h_{SLS}$             & 0.009    & $kg_{water}/kg_{air}$ & humidity ratio at SLS \cite{Kalnay1996}        \\
         $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A \cite{boeingJetA} \\
@@
 
-\subsection{Optimization Problem}
+\section{Optimization Problem}
+\label{sec:optprob}
+
+\subsection{Problem Statment}
 The optimization problem of the N3 engine and the vapor recovery loop are shown in Figure \ref{fig:N3_xdsm_opt}.
@@
 
-\noindent
 This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
@@
         \hline
-        minimize        & $ \text{TSEC}_{CRZ} $       & Thrust specific energy consumption at the cruise condition & $\frac{BTU}{hr-lb_f}$ & 1        \\
+        minimize        & $ \dot{m}_{fuel,CRZ} $      & Fuel flow rate at CRZ                       & $\frac{lbm}{s}$ & 1        \\
                         &                             &                                             &                 &          \\
@@
                         & $T_{4,RTO}$                 & RTO combustor temperature                   & $^\circ$R       & 1        \\
+                        & $V_{ratio,CRZ}$             & RTO combustor temperature                   & $^\circ$R       & 1        \\
         \cline{3-5}
@@
 
-The objective is to minimize the TSEC at a cruise condition subject to constraints, thrust, max temperature, and engine diameter.
+The objective is to minimize the TSEC at the cruise condition subject to constraints, thrust, max temperature, and engine diameter.
 We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
+
+% Blurb about PyOptSparse and SNOPT
+\subsection{Optimization Software}
+OpenMDAO supports the use of different optimization packages including Scipy and PyOptSparse.
+PyOptSparse is an object-oriented framework for formulating and solving nonlinear constrained optimization problems.
+PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with OpenMDAO.
+
+SNOPT (Sparse Nonlinear OPTimizer) was the optimizer chosen for this work.
+SNOPT is a state-of-the-art optimizer used to solve large-scale optimization problems (linear and nonlinear).
+The software uses a sparse SQP (sequential quadratic programming) algo- rithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
+SNOPT is particularly useful for nonlinear problems whose functions and derivatives are expensive compute.
+An augmented Lagrangian merit function ensures convergence from an arbitrary point.
+SNOPT allows the nonlinear constraints to be violated (if necessary) and minimizes the sum of these violations.
+Due to the robustness of the algorithm, SNOPT is a perfect candidate to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
+SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization.
 
@@
 
-% results of parameter sweep
+\begin{figure}[!hbt]
+    \centering
+    \includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.pdf}
+    \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
+        Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
+    \label{fig:results}
+\end{figure}
+
 % results of parameter sweep
 % results of optimization problems
+% Feasibility, Optimality, Merit Func (all 4 on same plot)
+% DV and Constraints over time
+% Thrust splits
+% TSEC as a function of dPqP
+% Motivation: space to work with hydrogen, benefits of water injection, benefits of H2
 
@@
 % Message 1: Re-state the problem
-In this work, we will model, analyze, and optimize a UHB next-generation turbofan model considering Jet-A and hydrogen fuel using a novel closed-loop water vapor recovery to improve cycle efficiency.
 % Message 2: Summarize the HBTF model
-The high-bypass turbofan engine will be composed of separate sub-components modeled in pyCycle with the new water recovery and injection capability to assess the performance and emissions improvements.
-We will compare Jet-A and liquid hydrogen with and without the closed-loop water vapor recovery system to determine the benefits of this technology implementation.
-The results will show a quantitative comparison at the propulsion system level, with a qualitative assessment of the feasibility of water recirculation for both Jet-A and hydrogen fuels.
 % Message 3: Expected results
-Finally, this work will demonstrate the ability of gradient-based optimization with zero-dimensional cycle analysis to explore the potential benefits of hydrogen combustion with a closed-loop water vapor recovery and injection.
+
+\section{Acknowledgements}
 

### 2023-04-26 conference-paper/paper_main.tex
Edits and comments for the abstract, intro, and methods setup

@@
 
-\title{Comparing Hydrogen and Jet-A for a Ultra High-Bypass Turbofan with Water Recirculation} % change
-
+% [ ] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
+\title{Comparing Hydrogen and Jet-A for an Ultra High Bypass Ratio Turbofan with Water Recirculation} % change
 \author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
-\author{Andrew H.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Andrew hbt!.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
 \author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
 \affil{University of Michigan, Ann Arbor, MI, 48109}
+
+\begin{document}
+
+\maketitle
 
@@
 % ==================================================
-
-% ==================================================
-\begin{document}
-
-\maketitle
-
 \begin{abstract}
-    Advances in commercial propulsion technology have resulted in the creation of larger and more advanced high-bypass turbofan engines with higher bypass ratios, pressure ratios, and internal temperatures.
-    With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for hydrogen as a fuel and more efficient engines to lower carbon emissions.
-    Carrying and burning hydrogen introduces complexity and weight penalties that can be partially offset by taking advantage of the fuel's thermodynamic and chemical properties.
-    In this study, we compare the benefits of using hydrogen against Jet-A fuel in a high-bypass turbofan with a closed-loop water recirculation system.
-    We will setup and perform a gradient-based optimization parameter sweep to understand the performance and emissions benefits of water recirculation using Jet-A and hydrogen fuels.
-    This study will demonstrate the benefits of hydrogen combustion with water recirculation in order to encourage next-generation propulsion systems to exploit the properties of hydrogen for improved performance and reduced emissions.
+    Advances in commercial propulsion technology led to the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
+    Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
+    Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
+    %   With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for hydrogen as a fuel and more efficient engines to lower carbon emissions.
+    Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
+    In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between jet-A and hydrogen fuels.
+    We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
+    The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
 \end{abstract}
@@
 The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
-N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high-bypass (UHB) engines with small cores and high overall pressure ratios (OPR).
-Higher OPR and smaller cores are pushing the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
+N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) engines with small cores and high overall pressure ratios (OPR).
+Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
 Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
-However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be leveraged to further increase the performance and emission reduction of the propulsion system.
-In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHB ratio turbofan engines.
-We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
+However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
+We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
+% In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHBR ratio turbofan engines.
+% We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
 
 % Message 2: Background and references to support using H2 and water injection in HBTF engines
+% [ ] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
 Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
-NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{nasa_inject}.
-Additionally, water recirculation improves fuel efficiency and thrust output with lower burner temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{nasa_inject}.
+NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{Daggett2010}.
+Additionally, water recirculation improves fuel efficiency and thrust output with lower combustion temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{Daggett2010}.
+% [ ]TODO: AL-PA, Should try to find a citation for this if one exists.
 Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
 The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-However, if hydrogen fuels are used, the main product of hydrogen combustion is water vapor and can thus be recovered.
-The ability to recirculate water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
+The main product of hydrogen combustion is water vapor and can thus be recovered from the exhaust stream.
+Recirculating water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
 
 Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
-Zero-dimensional cycle analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver that considers the molecular species of different fuels.
-This can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
-The industry standard for zero and one-dimensional cycle analysis is the Numerical Proprulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
-NPSS is a modular object-oriented framework that models engine components as individual blocks with several thermodynamic solvers.
-\citet{Hendricks2019} and \citet{Gray2017b} created a tool called pyCycle with the same functionality as NPSS, but includes analytical derivatives for each engine component and thermodynamic solver.
-We use pyCycle because it is built on top of the OpenMDAO framework~\cite{Gray2019a} to simplify gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
+% [x] TODO: AL-AL, Need to cite CEA paper.
+Zero-dimensional analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver~\cite{Gordon1994} that considers the molecular species of different fuels.
+% CEA can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
+The industry standard for thermodynamic cycle analysis is the Numerical Propulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
+NPSS is a modular object-oriented library that models engine components as individual blocks with several thermodynamic solvers.
+\citet{Hendricks2019} created a new tool called pyCycle with the same functionality as NPSS with analytical derivatives for each engine component and thermodynamic solver~\cite{Gray2017b}.
+pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to enable gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
 
 % Message 3: Introduce the extension of the HBTF and propose novel contributions
-In this work, we will analyze the potential propulsion benefits of a closed-loop water vapor recovery and water injection system in a high-bypass turbofan engine by optimizing the thrust-specific energy consumption (TSEC).
-TSEC is the thrust specific fuel consumption multiplied by the lower heating value of the fuel and is a metric for comparing the efficiency of different fuel choices.
-We will develop new pyCycle components for water injection and vapor recovery within pyCycle to understand the benefit of a closed loop recirculation system.
-Finally, we will present a comparison between Jet-A and hydrogen combustion with and without water recirculation in terms of improvement of TSEC.
+In this work, we analyze the thermodynamic benefits of a closed-loop water vapor recovery and water injection system in a high-bypass turbofan engine.
+We develop pyCycle components for water injection and vapor recovery to quantify the benefit of a closed loop recirculation system.
+We use gradient-based optimization to minimize fuel burn subject to performance requirements using both jet-A and hydrogen at a range of flight conditions.
+The optimized results show the trade-off between complexity, performance, and efficiency for jet-A and hydrogen fuels.
 
-This work is organized as follows. First, in Section \ref{sec:method}, we introduce the turbofan model and explain how we will implement the water injection and water recovery components in pyCycle.
-In section \ref{sec:optprob} the implementation of the multi-point optimization problem is discussed. Finally, we present the results from the optimization problem in section \ref{sec:results}.
+This work is organized as follows. First, in Section \ref{sec:method}, we introduce the turbofan model and explain the water injection and water recovery components.
+In section \ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
+Finally, we present the optimized results and discuss the design space in section \ref{sec:results}.
 
@@
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-In this work we use the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
-The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
-The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure first the principle governing equations are satisfied.
-The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
-This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
-The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
-In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
+The UHB turbfan model is the NASA advanced technology "N+3" engine \cite{Jones2017a}.
+The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
+% We selected the N+3 model because it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
+The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core and a bypass stream, each ending in a core and bypass nozzle, respectively.
+The low pressure system is split into two mechanical subsystems.
+First, the fan is connected to the gearbox that reduces the shaft speed to decrease the fan tip speeds.
+Second, the gearbox attaches to the low-pressure shaft that connects to the low-pressure compressor (LPC) and low-pressure turbine (LPT).
+% The low pressure system consists of a fan connected to a gearbox that attaches to the lo and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft.
+The high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
+
+% [ ] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
+% Thermodynamic equations of state are solved using CEA at the interface between components, shown as black arrows in Figure~\ref{fig:n3_cycle}.
+We introduce the closed-loop water recovery system as a feedback loop that transports water from the exhaust to upstream of the compressors.
+% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
+The recovery system injects vaporized water into the core stream that reduces the combustion temperature due to heat absorption.
+The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycle it back to the injector.
+% NOTE: AL-PA, don't discredit your work before you even explain the model and methods.  We can make this point in the results or conclusion.
+% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
+
+In this section we explain the implementation and assumptions of the water recovery model.
+We present the full engine layout and provide details on the multipoint zero-dimensional modeling approach.
 The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:N3_original}.
@@
 
-\begin{figure}[!hbt]
+% [ ] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
+% [ ] TODO: AL-PA, Add the description of the figure elements to the caption.
+% [ ] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
+% [ ] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
+\begin{figure}[hbt!]
     \centering
@@
 This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
-This location was chosen as it was one of the configurations chosen by the afformetioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{nasa_inject}.
+This location was chosen as it was one of the configurations chosen by the aforementioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{Daggett2010}.
 The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
@@
 
-\begin{figure}[!hbt]
+\begin{figure}[hbt!]
     \centering
@@
 This new mixture combination is then used to compute the various chemical species present in the flow at the given thermodynamic state which is determined by the incoming flow.
-The new species composition and thermodynamic variables are then determined using a Gibbs Free Energy minization approach called Chemical Equilibrium with Applications (CEA).
+The new species composition and thermodynamic variables are then determined using a Gibbs Free Energy minimization approach called Chemical Equilibrium with Applications (CEA).
 Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
@@
 The outputs of the extractor component are the flow rate of the core flow and the corresponding flow properties in addition to the extracted water mass flow rate.
-While this process certainly would have pressure loss penalties in terms of condensing water in a condersor, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensors available.
+While this process certainly would have pressure loss penalties in terms of condensing water in a condenser, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensers available.
 A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream of operating condition, $k$.
 
-\begin{figure}[!hbt]
+\begin{figure}[hbt!]
     \centering
@@
 These residuals represent the physical conservation laws such as mass flow rate are converged to zero by the Solver.
-In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which uilizes the analytic partial derivatives provided by each OpenMDAO component.
+In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which utilizes the analytic partial derivatives provided by each OpenMDAO component.
 All residuals within the engine model are converged at the Cycle level for a given operation condition since all of the parameters downstream do not directly effect those upstream.
@@
 The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
-Therefore, the N+3 enigne model computes the engine performance at 4 different operating conditions in order to resolve the complexities between each operating condition on the final design.
+Therefore, the N+3 engine model computes the engine performance at 4 different operating conditions in order to resolve the complexities between each operating condition on the final design.
 The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
@@
 
-In the optimization problem described later, we set the mass flow rate of fuel, $\dot{m}_{fuel}$, as the objective fuction.
+In the optimization problem described later, we set the mass flow rate of fuel, $\dot{m}_{fuel}$, as the objective function.
 Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
@@
 However, in this work we are interested in comparing the performance of similar engines with different types of fuel, specifically hydrogen due to the many benefits it offers in terms of performance and thermal properties.
-Fortunatly, pyCycle comes ready to use hydrogen with cateloged exhaust products for hydrogen fuel.
+Fortunately, pyCycle comes ready to use hydrogen with cataloged exhaust products for hydrogen fuel.
 The fuel type is simply changed from Jet-A to H2 in the pyCycle model.
@@
 However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
-Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel \cite{Adler2022d}.
+Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel \cite{Adler2023}.
 
@@
 % Update with table from Andrew
-\begin{table}[H]
+% TODO: AL - PA, What is the citation key "Kalnay1996"?  It's not in the MDOLab Bib or references.bib
+\begin{table}[hbt!]
     \centering
@@
         Atmospheric parameters are presented that specify the flight conditions and humidity of the atmosphere.}
-    \begin{tabular}{|c|c|c|c|}
+    \begin{tabular}{c c c c}
         \hline
@@
         $h_{SLS}$             & 0.009    & $kg_{water}/kg_{air}$ & humidity ratio at SLS \cite{Kalnay1996}    \\
-        $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A \cite{boeingJetA} \\
-        $LHV_{H2}$            & 51591.0  & $BTU/lbm$             & Lower heating value of H2 \cite{engtoolboxH2}  \\
+        $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A               \\
+        $LHV_{H2}$            & 51591.0  & $BTU/lbm$             & Lower heating value of H2                  \\
         \hline

### 2023-04-27 conference-paper/paper_main.tex
Initial edits to the water recovery section

@@
 
+% ==================================================
+%	OVERALL COMMENTS
+% ==================================================
+% 1. AL-PA, Fix the citation for Kalnay1996
+
 \begin{document}
@@
 Additionally, water recirculation improves fuel efficiency and thrust output with lower combustion temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{Daggett2010}.
-% [ ]TODO: AL-PA, Should try to find a citation for this if one exists.
+% [ ] TODO: AL-PA, Should try to find a citation for this if one exists.
 Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
@@
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-The UHB turbfan model is the NASA advanced technology "N+3" engine \cite{Jones2017a}.
+The UHB turbofan model is the NASA advanced technology "N+3" engine \cite{Jones2017a}.
 The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
@@
 \subsection{Water Recovery Loop Model}
-The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
-This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
-This location was chosen as it was one of the configurations chosen by the aforementioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{Daggett2010}.
-The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
-Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
-In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
+We implemented the closed-loop water recovery system as a feedback system that extracts water from the exhaust stream and injects it upstream of the HPC.
+% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
+% This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
+We chose this injection location based on claims from a study by NASA, Boeing, and Rolls-Royce~\cite{Daggett2010} that water injection directly into the combustor is unnecessary.
+% This location was chosen as it was one of the configurations chosen by the aforementioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{Daggett2010}.
+The water vapor recovery component sits downstream of the LPT and extracts water from the flow before it exits the core nozzle.
+% The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
+% Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
+% [ ] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
+% NOTE: AL-PA, we will talk about the condenser when we discuss the results of the pressure recovery parameter sweep.
+% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
 The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:n3_cycle}.

### 2023-04-27 conference-paper/paper_main.tex
Initial results section

--- 2023-04-26 conference-paper/paper_main.tex
@@
     \caption{
-        N3 engine model parameters.
+        N+3 engine model parameters.
         These parameters specify the engine design used for analysis in this report.
@@
 \subsection{Problem Statment}
+% Briefly discuss the optimization problem
+We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
+An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_xdsm_opt}.
+The objective is to minimize the TSEC at the cruise condition subject to constraints, thrust, max temperature, and engine diameter.
+We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
 The optimization problem of the N3 engine and the vapor recovery loop are shown in Figure \ref{fig:N3_xdsm_opt}.
@@
 This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
-The optimization problem for each fuel was specified as:
+% The optimization problem for each fuel was specified as:
 
@@
         The 4 design variables are the water recovery fractions of the core exhaust stream at each operation condition.
-        The objective function is the thrust specific energy consumption at the cruise condition with a net thrust constraint at the design point, TOC.
+        The objective function is the fuel flow rate at the CRZ condition with a net thrust and fan diameter constraint at the design point, TOC.
     }
@@
                         & $x_{H2O,CRZ}$               & Water recovery fraction at CRZ             & -               & 1        \\
-                        & $PR_{HPC,TOC}$              & TOC high-pressure compressor pressure ratio & -               & 1        \\
+                        & $PR_{fan,TOC}$              & TOC fan pressure ratio                     & -               & 1        \\
                         & $PR_{LPC,TOC}$              & TOC low-pressure compressor pressure ratio & -               & 1        \\
-                        & $PR_{fan,TOC}$              & TOC fan pressure ratio                      & -               & 1        \\
+                        & $PR_{OPR,TOC}$              & TOC overall pressure ratio                 & -               & 1        \\
                         & $T_{4,TOC}/T_{4,RTO}$       & TOC-to-RTO temperature ratio               & -               & 1        \\
                         & $T_{4,RTO}$                 & RTO combustor temperature                  & $^\circ$R       & 1        \\
-                        & $V_{ratio,CRZ}$             & RTO combustor temperature                   & $^\circ$R       & 1        \\
+                        & $V_{ratio,CRZ}$             & Velocity exit ratio at CRZ                 &                 & 1        \\
         \cline{3-5}
@@
 \end{table}
-
-% Briefly discuss the optimization problem
-We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
-An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:opt_prob}.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=0.75\textwidth]{N3_inject.pdf}
-    \caption{XDSM diagram of the multi-point optimization problem with constraints.
-        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
-    \label{fig:opt_prob}
-\end{figure}
-
-The objective is to minimize the TSEC at the cruise condition subject to constraints, thrust, max temperature, and engine diameter.
-We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{JetA-H2_bar_chart_diff.pdf}
+    \includegraphics[width=0.8\textwidth]{JetA-H2_TSEC_diff.pdf}
     \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
         Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
-    \label{fig:results}
+    \label{fig:barchart}
 \end{figure}

### 2023-04-27 conference-paper/main.tex
renamed files to main to be consistent

--- 2023-04-27 conference-paper/paper_main.tex
@@
 
-% [ ] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
-\title{Comparing Hydrogen and Jet-A for an Ultra High Bypass Ratio Turbofan with Water Recirculation} % change
+% [x] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
+\title{Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization} % change
 \author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
@@
 % ==================================================
-% 1. AL-PA, Fix the citation for Kalnay1996
 
@@
 However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
-Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel \cite{Adler2023}.
+% TODO: Update mdolab.bib
+Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel %\cite{Adler2023}.
 
@@
 % Update with table from Andrew
-% TODO: AL - PA, What is the citation key "Kalnay1996"?  It's not in the MDOLab Bib or references.bib
 \begin{table}[hbt!]
@@
     $BPR_{TOC}$           & 23.945   & $-$                   & TOC bypass Ratio                                \\
-        $PR_{HPC,TOC}$        & 53.633   & $-$                   & TOC overall pressure ratio                 \\
+    $OPR_{TOC}$           & 53.633   & $-$                   & TOC overall pressure ratio                      \\
     $PR_{LPC,TOC}$        & 3.00     & $-$                   & TOC low-pressure compressor pressure ratio      \\
@@
     $h_{SLS}$             & 0.009    & $kg_{water}/kg_{air}$ & humidity ratio at SLS \cite{Kalnay1996}         \\
-        $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A               \\
-        $LHV_{H2}$            & 51591.0  & $BTU/lbm$             & Lower heating value of H2                  \\
+    $LHV_{JetA}$          & 18564.0  & $BTU/lbm$             & Lower heating value of Jet-A \cite{Lawicki2002} \\
+    $LHV_{H2}$            & 51591.0  & $BTU/lbm$             & Lower heating value of H2 \cite{toolbox2003}    \\
     \hline
@@
 % Briefly discuss the optimization problem
+% TODO: PA - PA, Condense this and remove repeated parts
 We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
@@
 
-% Briefly discuss the optimization problem
-We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
-An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:opt_prob}.
-
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.75\textwidth]{N3_inject.pdf}
-    \caption{XDSM diagram of the multi-point optimization problem with constraints.
-        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
-    \label{fig:opt_prob}
-\end{figure}
-
-The objective is to minimize the TSEC at the cruise condition subject to constraints, thrust, max temperature, and engine diameter.
-We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
-
 % Blurb about PyOptSparse and SNOPT
@@
 SNOPT is a state-of-the-art optimizer used to solve large-scale optimization problems (linear and nonlinear).
-The software uses a sparse SQP (sequential quadratic programming) algo- rithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
+The software uses a sparse SQP (sequential quadratic programming) algorithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
 SNOPT is particularly useful for nonlinear problems whose functions and derivatives are expensive compute.
@@
 SNOPT allows the nonlinear constraints to be violated (if necessary) and minimizes the sum of these violations.
-Due to the robustness of the algorithm, SNOPT is a perfect candidate to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
+Due to the robustness of the algorithm, SNOPT is a perfect optimizer to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
 SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization.
@@
 \label{sec:results}
+
+\begin{table}[h]
+  \centering
+  \caption{
+  }
+  \small
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{r l l l l l}
+                & Variable/Function     & Value  & Lower  & Upper & Units           \\
+    \toprule
+    objective   & $\dot{m}_{fuel,CRZ}$  & _      & -      & -     & $\frac{lbm}{s}$ \\
+    \hline
+    variables   & $x_{H2O,TOC}$         & 0.053  & 0.0    & -     & -               \\
+                & $x_{H2O,RTO}$         & 0.0    & 0.0    & -     & -               \\
+                & $x_{H2O,SLS}$         & 0.0    & 0.0    & -     & -               \\
+                & $x_{H2O,CRZ}$         & 0.3    & 0.0    & 0.3   & -               \\
+                & $PR_{fan,TOC}$        & _      & _      & -     & -               \\
+                & $PR_{LPC,TOC}$        & _      & _      & -     & -               \\
+                & $PR_{OPR,TOC}$        & _      & _      & -     & -               \\
+                & $T_{4,TOC}/T_{4,RTO}$ & _      & _      & -     & -               \\
+                & $T_{4,RTO}$           & _      & _      & -     & $^\circ$R       \\
+                & $V_{ratio,CRZ}$       & _      & _      & -     &                 \\
+    \cline{3-5}
+    constraints & $F_{net,TOC}$         & 5800.0 & 5800.0 & -     & lbf             \\
+                & $D_{Fan}$             & 100.0  & 100    & -     & $in^2$          \\
+    \cline{3-5}
+                &                       & Total  &                                  \\
+    \bottomrule
+  \end{tabular}
+  \label{tab:opt_res_JetA}
+\end{table}
 

### 2023-04-27 conference-paper/main.tex
Started results section and added preliminary figures and tables

@@
 % We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
+% [ ] TODO: PA-PA, add section about MAUD and cite.
 
@@
 % [ ] TODO: AL-PA, Add the description of the figure elements to the caption.
-% [ ] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
-% [ ] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
+% [x] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
+% [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
 \begin{figure}[hbt!]
@@
     \caption{
-    N+3 engine cycle layout that shows how each of the pyCycle components are connected and how performance metrics are computed. % Use Tiks
+        Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}.
+        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
     }
@@
     \caption{
-    N+3 engine cycle layout that shows how each of the pyCycle components are connected with the closed-loop vapor recovery system. % Use Tiks
+        Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
+        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
     }
@@
         N+3 engine model parameters.
-    These parameters specify the engine design used for analysis in this report.
-    Atmospheric parameters are presented that specify the flight conditions and humidity of the atmosphere.}
+        Atmospheric parameters specify the flight conditions and humidity of the atmosphere and Lower Heating Values are given for each fuel to compute TSEC.}
     \begin{tabular}{c c c c}
@@
         \hline
-    $W_{TOC}$             & 820.441  & $lbm/s$               & TOC total mass flow rate of air                 \\
-    $BPR_{TOC}$           & 23.945   & $-$                   & TOC bypass Ratio                                \\
-    $OPR_{TOC}$           & 53.633   & $-$                   & TOC overall pressure ratio                      \\
-    $PR_{LPC,TOC}$        & 3.00     & $-$                   & TOC low-pressure compressor pressure ratio      \\
-    $PR_{fan,TOC}$        & 1.30     & $-$                   & TOC fan pressure ratio                          \\
-    $F_{net,SLS}$         & 28620.84 & $lbf$                 & SLS net thrust                                  \\
-    $F_{net,CRZ}$         & 5510.72  & $lbf$                 & CRZ net thrust                                  \\
-    $T_{4,TOC}/T_{4,RTO}$ & 0.926    & $-$                   & TOC-to-RTO temperature ratio                    \\
-    $T_{4,RTO}$           & 3400.0   & $^{\circ}R$           & RTO combustor temperature                       \\
         $h_{TOC}$    & 0.00017 & $kg_{water}/kg_{air}$ & humidity ratio at TOC \cite{Kalnay1996}         \\
@@
 % Briefly discuss the optimization problem
-% TODO: PA - PA, Condense this and remove repeated parts
-We will perform gradient-based design optimization of the engine model with a multi-point architecture that considers several flight conditions experienced by commercial aircraft.
+We will perform gradient-based design optimization of the engine model with the multipoint architecture that considers each of the flight conditions experienced by commercial aircraft.
+% We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
+The objective is to minimize the TSEC since that is our performance metric for comparing the two types of fuels.
+However, since we are constraining net thrust at each operating condition this optimization problem becomes ill-posed.
+Therefore, we will minimize fuel flow rate, $W_{fuel}$ at the cruise condition subject to net thrust and engine diameter constraints since this will accomplish the same goal with a better posed problem.
 An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_xdsm_opt}.
-The objective is to minimize the TSEC at the cruise condition subject to constraints, thrust, max temperature, and engine diameter.
-We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
-The optimization problem of the N3 engine and the vapor recovery loop are shown in Figure \ref{fig:N3_xdsm_opt}.
 
-\begin{figure}[hbt!]
+\begin{figure}[!hbt]
     \centering
@@
 This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
-% The optimization problem for each fuel was specified as:
+The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
 
@@
         \hline
-    minimize        & $ \dot{m}_{fuel,CRZ} $      & Fuel flow rate at CRZ                      & $\frac{lbm}{s}$ & 1        \\
+        minimize        & $W_{fuel,CRZ}$              & Fuel flow rate at CRZ                      & $\frac{lbm}{s}$ & 1        \\
                         &                             &                                            &                 &          \\
@@
 PyOptSparse is an object-oriented framework for formulating and solving nonlinear constrained optimization problems.
-PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with OpenMDAO.
+PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with  \cite{Wu2020a}.
 
@@
 Due to the robustness of the algorithm, SNOPT is a perfect optimizer to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
-SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization.
+SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization \cite{Gill2005a}.
 
@@
 \label{sec:results}
+The 4 optimizations mentioned in the optimation problem section were run and solved.
+The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_clvr}.
 
+% results of parameter sweep
+
+% Feasibility, Optimality, Merit Func (all 4 on same plot)
+% NOTE: need to clean up this plot
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{opt_summary.pdf}
+    \caption{The optimality, feasibility, and merit fuction for each optimization problem.
+        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
+    \label{fig:history_clvr}
+\end{figure}
+
+From this plot we can visually check that each optimization achieved optimality and feasibility, and that the merit function reached a steady-state value.
+
+% DV and Constraints over each iteration
+
+% Results of optimization problems
+The optimization problems with both types of fuel but no water recovery ran smoothly and finished with 0/1 SNOPT exit codes meaning that the optimization finished successfully and met the optimiality conditions.
+The resulting values of the optimization problem for Jet-A and hydrogen without water recovery are shown in Tables \ref{tab:res_thermo_opt_JetA} and \ref{tab:res_thermo_opt_H2}, respectively.
+Similarly, the resulting values of the optimization problem for Jet-A and hydrogen with water recovery are shown in Tables \ref{tab:res_full_opt_JetA} and \ref{tab:res_full_opt_H2}, respectively.
+
+% NOTE: PA - PA/AL replace this with a parallel axis plot?
 \begin{table}[h]
     \centering
-  \caption{
+    \caption{Optimization results of the N+3 engine with no water recovery using Jet-A as the fuel.
     }
@@
         \toprule
-    objective   & $\dot{m}_{fuel,CRZ}$  & _      & -      & -     & $\frac{lbm}{s}$ \\
+        objective   & $W_{fuel,CRZ}$        & 0.6394   & -      & -     & $\frac{lbm}{s}$ \\
         \hline
-    variables   & $x_{H2O,TOC}$         & 0.053  & 0.0    & -     & -               \\
+        variables   & $PR_{fan,TOC}$        & 1.285    & 1.2    & 1.4   & -               \\
+                    & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
+                    & $PR_{OPR,TOC}$        & 59.495   & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.913    & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3220.570 & -      & -     & $^\circ$R       \\
+                    & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
+        \hline
+        constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
+                    & $D_{Fan}$             & 100.0    & 100    & -     & $in^2$          \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:res_thermo_opt_JetA}
+\end{table}
+
+\begin{table}[h]
+    \centering
+    \caption{Optimization results of the N+3 engine with no water recovery using hydrogen as the fuel.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l l l l}
+                    & Variable/Function     & Value   & Lower  & Upper & Units           \\
+        \toprule
+        objective   & $W_{fuel,CRZ}$        & 0.2331  & -      & -     & $\frac{lbm}{s}$ \\
+        \hline
+        variables   & $PR_{fan,TOC}$        & 1.288   & 1.2    & 1.4   & -               \\
+                    & $PR_{LPC,TOC}$        & 4.000   & 2.5    & 4.0   & -               \\
+                    & $PR_{OPR,TOC}$        & 59.153  & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.918   & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3204.07 & -      & -     & $^\circ$R       \\
+                    & $V_{ratio,CRZ}$       & 1.35    & 1.35   & 1.45  &                 \\
+        \hline
+        constraints & $F_{net,TOC}$         & 5800.0  & 5800.0 & -     & lbf             \\
+                    & $D_{Fan}$             & 100.0   & 100    & -     & $in^2$          \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:res_thermo_opt_H2}
+\end{table}
+
+\begin{table}[h] % need to run for T4 = 3220.570
+    \centering
+    \caption{Optimization results of the N+3 engine with water recovery using Jet-A as the fuel.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l l l l}
+                    & Variable/Function     & Value  & Lower  & Upper & Units           \\
+        \toprule
+        objective   & $W_{fuel,CRZ}$        & 0.6037 & -      & -     & $\frac{lbm}{s}$ \\
+        \hline
+        variables   & $x_{H2O,TOC}$         & 0.115  & 0.0    & -     & -               \\
                     & $x_{H2O,RTO}$         & 0.0    & 0.0    & -     & -               \\
@@
                     & $x_{H2O,CRZ}$         & 0.3    & 0.0    & 0.3   & -               \\
-                & $PR_{fan,TOC}$        & _      & _      & -     & -               \\
-                & $PR_{LPC,TOC}$        & _      & _      & -     & -               \\
-                & $PR_{OPR,TOC}$        & _      & _      & -     & -               \\
-                & $T_{4,TOC}/T_{4,RTO}$ & _      & _      & -     & -               \\
-                & $T_{4,RTO}$           & _      & _      & -     & $^\circ$R       \\
-                & $V_{ratio,CRZ}$       & _      & _      & -     &                 \\
-    \cline{3-5}
+                    & $PR_{fan,TOC}$        & 1.291  & 1.2    & 1.4   & -               \\
+                    & $PR_{LPC,TOC}$        & 4.0    & 2.5    & 4.0   & -               \\
+                    & $PR_{OPR,TOC}$        & 54.218 & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.923  & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3400.0 & -      & -     & $^\circ$R       \\
+                    & $V_{ratio,CRZ}$       & 1.35   & 1.35   & 1.45  &                 \\
+        \hline
         constraints & $F_{net,TOC}$         & 5800.0 & 5800.0 & -     & lbf             \\
                     & $D_{Fan}$             & 100.0  & 100    & -     & $in^2$          \\
-    \cline{3-5}
-                &                       & Total  &                                  \\
         \bottomrule
     \end{tabular}
-  \label{tab:opt_res_JetA}
+    \label{tab:res_full_opt_JetA}
+\end{table}
+
+\begin{table}[h]
+    \centering
+    \caption{Optimization results of the N+3 engine with water recovery using hydrogen as the fuel.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l l l l}
+                    & Variable/Function     & Value   & Lower  & Upper & Units           \\
+        \toprule
+        objective   & $W_{fuel,CRZ}$        & -       & -      & -     & $\frac{lbm}{s}$ \\
+        \hline
+        variables   & $x_{H2O,TOC}$         & 0.066   & 0.0    & -     & -               \\
+                    & $x_{H2O,RTO}$         & 0.0     & 0.0    & -     & -               \\
+                    & $x_{H2O,SLS}$         & 0.0     & 0.0    & -     & -               \\
+                    & $x_{H2O,CRZ}$         & 0.17    & 0.0    & 0.17  & -               \\
+                    & $PR_{fan,TOC}$        & 1.291   & 1.2    & 1.4   & -               \\
+                    & $PR_{LPC,TOC}$        & 4.0     & 2.5    & 4.0   & -               \\
+                    & $PR_{OPR,TOC}$        & 55.132  & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.927   & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3204.07 & -      & -     & $^\circ$R       \\
+                    & $V_{ratio,CRZ}$       & 1.35    & 1.35   & 1.45  &                 \\
+        \hline
+        constraints & $F_{net,TOC}$         & 5800.0  & 5800.0 & -     & lbf             \\
+                    & $D_{Fan}$             & 100.0   & 100    & -     & $in^2$          \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:res_full_opt_H2}
 \end{table}
@@
     \includegraphics[width=0.8\textwidth]{JetA-H2_TSEC_diff.pdf}
-  \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of an ultra-high bypass turbofan engine from water injection.
-    Data was collected with and without water injected into the core stream of the engine for Jet-A and hydrogen fuels.}
+    \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
+        This plot compares the relative improvement of the two optimziation problems with water recovery compared to the optimzation problems without water recovery.}
     \label{fig:barchart}
@@
 
-% results of parameter sweep
-% results of optimization problems
-% Feasibility, Optimality, Merit Func (all 4 on same plot)
-% DV and Constraints over time
 % Thrust splits
+% TODO PA - PA: Add thrust splits for each opt
+
 % TSEC as a function of dPqP
+% NOTE: need to clean up this plot
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
+        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
+    \label{fig:dpqp_sweep}
+\end{figure}
+
 % Motivation: space to work with hydrogen, benefits of water injection, benefits of H2

### 2023-04-27 figures/N3_CLVR_cycle.tex
Started results section and added preliminary figures and tables

\documentclass[landscape]{article}

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows, positioning, calc, matrix}
\usepackage{xcolor}

%%%<
\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{5pt}%
%%%>

\begin{document}
\pagestyle{empty}

% define colors
\definecolor{shaftcolor}{RGB}{255,0,0}
\definecolor{elementcolor}{RGB}{46, 187, 242}

% Define block styles

\tikzstyle{element} = [rectangle, draw, fill=elementcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{shaft_element} = [rectangle, draw, fill=shaftcolor!20,
text width=10em, text centered, font=\LARGE, rounded corners, minimum height=4em]
\tikzstyle{heat_element} = [rectangle, draw, fill=heatcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
\tikzstyle{heat_flow} = [draw, -latex', ultra thick, color=heatcolor]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    \node [element] (inlet) {Inlet};
    \node [element, right=4em of inlet] (fan) {Fan};
    \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (injector) {Water Injector};
    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (extractor) {Water Extractor};
    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
    \node [element, below=12em of burner] (bypduct) {Bypass Duct};
    \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};

    % Add shaft elements
    \node [shaft_element, above=8em of $(hpc)!0.5!(hpt)$] (hpshaft) {High Pressure Shaft};
    \node [shaft_element, above=16em of $(lpc)!0.5!(lpt)$] (lpshaft) {Low Pressure Shaft};
    \node [shaft_element, above=16em of $(fan)!0.28!(lpc)$] (fanshaft) {Fan Shaft};
    \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};

    % Draw element connections
    % \path [connection] (fc) -- (inlet);
    \path [connection] (inlet) -- (fan);
    \path [connection] (fan) -- (splitter);
    \path [connection] (splitter) -- (lpc);
    \path [connection] (splitter) |- (bypduct);
    \path [connection] (bypduct) -- (bypnozzle);
    \path [connection] (lpc) -- (injector);
    \path [connection] (injector) -- (hpc);
    \path [connection] (hpc) -- (burner);
    \path [connection] (burner) -- (hpt);
    \path [connection] (hpt) -- (lpt);
    \path [connection] (lpt) -- (extractor);
    \path [connection] (extractor) -- (corenozzle);
    \path [connection] (extractor) |- (vrl);
    \path [connection] (vrl) -| (injector);

    % Draw Shaft Connections
    \path [shaft] (fan) |- (fanshaft) -- (gearbox);
    \path [shaft] (gearbox) -| (lpc);
    \path [shaft] (lpc) |- (lpshaft) -| (lpt);
    \path [shaft] (hpc) |- (hpshaft) -| (hpt);

    % \matrix[draw, ultra thick, rounded corners, matrix of nodes, text width=30em, font=\LARGE, row sep=3mm, below=25em of current page.south west, anchor=west] (key) {
    %     $\bullet$ Black arrows are flow connections    \\
    %     $\bullet$ Red lines are mechanical connections \\
    %     $\bullet$ Blue boxes are cycle elements        \\
    %     $\bullet$ Red boxes are shaft elements         \\
    % };

\end{tikzpicture}

\end{document}

### 2023-04-27 figures/N3_cycle.tex
Started results section and added preliminary figures and tables

--- 2023-04-27 figures/N3_CLVR_cycle.tex
@@
     \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
-    \node [element, right=4em of lpc ] (injector) {Water Injector};
-    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
+    \node [element, right=4em of lpc ] (hpc) {High Pressure Compressor};
     \node [element, right=4em of hpc] (burner) {Burner};
@@
     \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
-    \node [element, right=4em of lpt] (extractor) {Water Extractor};
-    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
-    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
-    \node [element, below=12em of burner] (bypduct) {Bypass Duct};
-    \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};
+    \node [element, right=4em of lpt] (corenozzle) {Core Nozzle};
+    \node [element, below=4em of burner] (bypduct) {Bypass Duct};
+    \node [element, below=4em of corenozzle] (bypnozzle) {Bypass Nozzle};
 
@@
     \path [connection] (bypduct) -- (bypnozzle);
-    \path [connection] (lpc) -- (injector);
-    \path [connection] (injector) -- (hpc);
+    \path [connection] (lpc) -- (hpc);
     \path [connection] (hpc) -- (burner);
@@
     \path [connection] (hpt) -- (lpt);
-    \path [connection] (lpt) -- (extractor);
-    \path [connection] (extractor) -- (corenozzle);
-    \path [connection] (extractor) |- (vrl);
-    \path [connection] (vrl) -| (injector);
+    \path [connection] (lpt) -- (corenozzle);
 

### 2023-04-27 conference-paper/main.tex
Adding more comments and changes

@@
 \author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
-\author{Andrew hbt!.R. Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Andrew H~.R.~Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
 \author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
@@
 
-\subsection{Water Recovery Loop Model}
+\subsection{Water Recovery Model}
 We implemented the closed-loop water recovery system as a feedback system that extracts water from the exhaust stream and injects it upstream of the HPC.
@@
 
-Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
-To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
-This can be accomplished by using the $wet_air$ dataset in pyCycle.
-The $wet_air$ dataset simply uses the $Janaf$ dataset from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
-The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
-In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
-The WAR value is simply the specific humidity (g water/kg total) of the air expressed in equal units and separating out the total mass (kg water/kg air).
-The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.
+We modified the composition of the air mixture upstream of the combustor to account for humidity.
+% Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
+% To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
+pyCycle provides a \texttt{wet-air} dataset that introduces $\mathrm{H_2O}$ molecules to the composition of air.
+% The \texttt{wet-air} dataset inherits the NPSS \texttt{JANAF} data from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
+% The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
+We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of $\mathrm{H_2O}$ to air in the reactants of the inflow mixture.
+% In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
+% The WAR is the sp of the air expressed in equal units and separating out the total mass (kg water/kg air).
+\citet{Kalnay1996} give the humidity values for each flight condition.
+% The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.
 
-To model the complicated water recirculation loop in pyCycle new components had to be developed.
-The two new components that were developed are a water injector to add water to the flow and a water extractor to divert a fraction of the water in the flow away from the exhaust stream.
-The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
-This new mixture combination is then used to compute the various chemical species present in the flow at the given thermodynamic state which is determined by the incoming flow.
-The new species composition and thermodynamic variables are then determined using a Gibbs Free Energy minimization approach called Chemical Equilibrium with Applications (CEA).
-Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
-The water injector component would inject water as a reactant instead of the fuel as the combustor would.
-The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
-A simple schematic of the injector is shown in Figure \ref{fig:injector} where $Y_{H_2O}$ is the mole fraction of water molecules.
+We introduce two new thermodynamic models for water recirculation in pyCycle.
+% To model the complicated water recirculation loop in pyCycle new components had to be developed.
+A water injector adds water to the flow upstream of the HPC, while a water extractor diverts a portion of the water in the flow away from the exhaust stream.
+% The two models are a water injector that adds water to the flow upstream of the HPC and a water extractor to divert a fraction of the water in the flow away from the exhaust stream.
+The injector operates similarly to fuel injection in the combustor.
+We determine a WAR that is analogous to the fuel-to-air (FAR) ratio in the combustor.
+% The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
+This WAR is used to compute the chemical species present in the flow at the current thermodynamic state, determined by the incoming flow.
+The new species composition and thermodynamic state are determined using the pyCycle CEA solver~\cite{Gray2017b}.
+% Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
+% The water injector component would inject water as a reactant instead of the fuel as the combustor would.
+The water injector inputs are the mass flow rate and mass fraction of water.
+We can solve for the mass flow rate on a mixture basis using the WAR, or directly by specifying the mass flow rate of water.
+% The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
+A schematic of the injector is shown in Figure \ref{fig:injector} where $Y_{H_2O}$ is the mole fraction of water molecules.
 
@@
 
-The water extractor component is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
-This extractor component works by first determining the water content of the incoming flow and extracting a given fraction of that water flow.
-The water content of the incoming flow is determined by solving a CEA analysis of the incoming flow.
-This water content in the incoming flow is then used with a given fraction of the water to extract to determine the how much water mass flow to remove from the stream.
-At the same time, the atomic mixture of the core stream is updated to represent the mixture that would be left if a number of hydrogen and oxygen atoms corresponding to the amount of water extracted were removed.
-The outputs of the extractor component are the flow rate of the core flow and the corresponding flow properties in addition to the extracted water mass flow rate.
-While this process certainly would have pressure loss penalties in terms of condensing water in a condenser, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensers available.
-A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream of operating condition, $k$.
+The water extractor model diverts a fraction of a specific species from one flow path to another.
+% The water extractor model is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
+The CEA solver calculates the inflow composition and the extractor separates a specific species based on a mass fraction input.
+The composition of the core stream is updated to represent the remaining mixture after the extractor model removes the desired species from the incoming flow.
+We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
+% The extraction determines the water content of the incoming flow and extracting a given fraction of that water flow.
+% The water content of the incoming flow is determined by solving a CEA analysis of the incoming flow.
+% This water content in the incoming flow is then used with a given fraction of the water to extract to determine the how much water mass flow to remove from the stream.
+% The outputs of the extractor component are the flow rate of the core flow and the corresponding flow properties in addition to the extracted water mass flow rate.
+% While this process certainly would have pressure loss penalties in terms of condensing water in a condenser, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensers available.
+A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream.
 
@@
 
-Unlike other flow streams in the N+3 model, the vapor recovery loop has a feedback effect since it is adding a mass flow rate at the injector and extracting a mass flow rate at the extractor.
-This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
-So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
-However, the N+3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
-These connections can be seen in Figure \ref{fig:N3_xdsm_full}.
+We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.
+The model results in a mismatch between the mass flow rate upstream of the HPC and the mass flow rate exiting the core nozzle.
+To preserve conservation of mass, we treat the water recirculation as a nonlinear cycle that must converge before the engine calculation is physically balanced.
+% This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
+% So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
+% However, the N+3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
+We illustrate the water recirculation loop and the nonlinear solver connections in Figure \ref{fig:N3_xdsm_full}.
 
@@
 
-\subsection{Model Parametric Studies}
-To understand the coupling between the various operation conditions and design point, a few simple parametric studies of the water recovery fractions were run.
-The design parameters for the engine are shown in the table below.
-Additionally, the humidity conditions listed below are used in the flight conditions component in the N+3 engine to ensure that the humidity of the air entering the engine is equal to the humidity of the atmosphere at a given operating condition.
-
 % Update with table from Andrew
@@
         \hline
-        $h_{TOC}$    & 0.00017 & $kg_{water}/kg_{air}$ & humidity ratio at TOC \cite{Kalnay1996}         \\
-        $h_{CRZ}$    & 0.00017 & $kg_{water}/kg_{air}$ & humidity ratio at CRZ \cite{Kalnay1996}         \\
-        $h_{RTO}$    & 0.009   & $kg_{water}/kg_{air}$ & humidity ratio at RTO \cite{Kalnay1996}         \\
-        $h_{SLS}$    & 0.009   & $kg_{water}/kg_{air}$ & humidity ratio at SLS \cite{Kalnay1996}         \\
-        $LHV_{JetA}$ & 18564.0 & $BTU/lbm$             & Lower heating value of Jet-A \cite{Lawicki2002} \\
-        $LHV_{H2}$   & 51591.0 & $BTU/lbm$             & Lower heating value of H2 \cite{toolbox2003}    \\
+        $h_{\rm{TOC}}$         & 0.00017 & -              & humidity ratio at TOC \cite{Kalnay1996}         \\
+        $h_{\rm{CRZ}}$         & 0.00017 & -              & humidity ratio at CRZ \cite{Kalnay1996}         \\
+        $h_{\rm{RTO}}$         & 0.009   & -              & humidity ratio at RTO \cite{Kalnay1996}         \\
+        $h_{\rm{SLS}}$         & 0.009   & -              & humidity ratio at SLS \cite{Kalnay1996}         \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \unit{BTU/lbm} & Lower heating value of Jet-A \cite{Lawicki2002} \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \unit{BTU/lbm} & Lower heating value of H2 \cite{toolbox2003}    \\
         \hline
@@
 
-\begin{table}[h]
+% [ ] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
+% [ ] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
+\begin{table}[hbt!]
     \centering
@@
         The 4 design variables are the water recovery fractions of the core exhaust stream at each operation condition.
-        The objective function is the fuel flow rate at the CRZ condition with a net thrust and fan diameter constraint at the design point, TOC.
+        The objective function is the thrust specific energy consumption at the cruise condition with a net thrust constraint at the design point, TOC.
     }
@@
         \hline
-        minimize        & $W_{fuel,CRZ}$              & Fuel flow rate at CRZ                      & $\frac{lbm}{s}$ & 1        \\
+        minimize        & $ \dot{m}_{\rm{fuel,CRZ}} $    & Fuel flow rate at CRZ                       & \unit{lbm/s}     & 1        \\
                         &                                &                                             &                  &          \\
-        with respect to & $x_{H2O,TOC}$               & Water recovery fraction at TOC             & -               & 1        \\
-                        & $x_{H2O,RTO}$               & Water recovery fraction at RTO             & -               & 1        \\
-                        & $x_{H2O,SLS}$               & Water recovery fraction at SLS             & -               & 1        \\
-                        & $x_{H2O,CRZ}$               & Water recovery fraction at CRZ             & -               & 1        \\
-                        & $PR_{fan,TOC}$              & TOC fan pressure ratio                     & -               & 1        \\
-                        & $PR_{LPC,TOC}$              & TOC low-pressure compressor pressure ratio & -               & 1        \\
-                        & $PR_{OPR,TOC}$              & TOC overall pressure ratio                 & -               & 1        \\
-                        & $T_{4,TOC}/T_{4,RTO}$       & TOC-to-RTO temperature ratio               & -               & 1        \\
-                        & $T_{4,RTO}$                 & RTO combustor temperature                  & $^\circ$R       & 1        \\
-                        & $V_{ratio,CRZ}$             & Velocity exit ratio at CRZ                 &                 & 1        \\
+        with respect to & $X_{\rm{H2O,TOC}}$             & Water recovery fraction at TOC              & -                & 1        \\
+                        & $X_{\rm{H2O,RTO}}$             & Water recovery fraction at RTO              & -                & 1        \\
+                        & $X_{\rm{H2O,SLS}}$             & Water recovery fraction at SLS              & -                & 1        \\
+                        & $X_{\rm{H2O,CRZ}}$             & Water recovery fraction at CRZ              & -                & 1        \\
+                        & $\rm{PR}_{\rm{HPC,TOC}}$       & TOC high-pressure compressor pressure ratio & -                & 1        \\
+                        & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio  & -                & 1        \\
+                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                      & -                & 1        \\
+                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio                & -                & 1        \\
+                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                   & \unit{\degree R} & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & RTO combustor temperature                   & \unit{\degree R} & 1        \\
         \cline{3-5}
-                        &                             & Total                                      &                 & 4        \\
+                        &                                & Total                                       &                  & 10       \\
                         &                                &                                             &                  &          \\
-        subject to      & $F_{net,TOC} \geq 5800$ lbf & Target net thrust at TOC                   & lbf             & 1        \\
-                        & $D_{Fan} \leq 100$ $in^2$   & Maximum Fan Diameter                       & $in^2$          & 1        \\
+        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                    & \unit{lbf}       & 1        \\
+                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                        & \unit{inch^2}    & 1        \\
         \cline{3-5}
-                        &                             & Total                                      &                 & 1        \\
+                        &                                & Total                                       &                  & 2        \\
         \bottomrule
@@
 % NOTE: PA - PA/AL replace this with a parallel axis plot?
-\begin{table}[h]
+% [ ] TODO: AL-PA, Yeah let's do the parallel axis plot for the basic thermodynamic parameters
+% AL-PA, We can make another plot for the water fractions and the dpQp study.
+\begin{table}[hbt!]
     \centering
@@
 
-\begin{table}[h]
+\begin{table}[hbt!]
     \centering
@@
 
-\begin{table}[h] % need to run for T4 = 3220.570
+\begin{table}[hbt!] % need to run for T4 = 3220.570
     \centering

### 2023-04-28 conference-paper/main.tex
Added comments to the methodology section

@@
 \label{sec:method}
-\subsection{Engine Model Overview}
+
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
@@
 
-In this section we explain the implementation and assumptions of the water recovery model.
-We present the full engine layout and provide details on the multipoint zero-dimensional modeling approach.
-The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:N3_original}.
+In this section we present the full engine layout and provide details on the multipoint zero-dimensional modeling approach.
+We explain the implementation and assumptions of the water recovery model and the coupling with the thermodynamic cycle.
+% The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:N3_original}.
 % The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
@@
 % Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.
+
+\subsection{Propulsion Model}
+The N+3 model is implemented in pyCycle~\cite{Hendricks2019}, a zero-dimensional thermodynamic cycle modeling library with analytical gradients.
+Zero-dimensional models are a collection of components that combine to form a unified thermodynamic cycle.
+The N+3 UHB geared turbofan model consists of twenty-five different elements that define the flow path and the mechanical systems.
+Thermodynamic quantities are exchanged at flow path boundaries represented by black arrows between blue flow path components in Figure~\ref{fig:N3_original}.
+The fan, gearbox, low pressure, and high pressure systems are connected by three mechanical shafts depicted in red in Figure~\ref{fig:N3_original}.
+% Three mechanical shafts, depicted in red in Figure~\ref{fig:N3_original}, connect the fan, low pressure, and high pressure systems.
+
+We impose \emph{balance} equations on the cycle to satisfy the physical governing equations, conservation laws, and design rules.
+\emph{Balance} relationships are formulated as equations in the form $r(u)=0$ where $r$ is a residual function and $u$ is an implicit state variable.
+We use Newton based solvers to find the value of the state variables that drive the set of balance residuals to zero.
+\citeauthor{Hendricks2019} provide the balance equations for the N+3 engine model and further detail the cycle setup.
 
@@
 \end{figure}
+
+% In pyCycle, the Cycle block contains all of the governing thermodynamic equations needed to model an engine such as CEA analysis, compressor and turbine models, and equations of state.
+% These equations allow any arbitrary engine design to be assembled using the modular cycle elements.
+% The Cycle block itself may not result in a valid model of the engine since some physical dependencies may not match.
+% These physical dependencies are handled by the Balance block which solves a set of implicit state variables and nonlinear physical residual equations in the form:
+
+% \noindent
+% where $x_i$ is some physical variable such as a mass or energy flow rate.
+% These residuals represent the physical conservation laws such as mass flow rate are converged to zero by the Solver.
+% In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which utilizes the analytic partial derivatives provided by each OpenMDAO component.
+% All residuals within the engine model are converged at the Cycle level for a given operation condition since all of the parameters downstream do not directly effect those upstream.
+% However, with introducing the extractor and injector components, we add a feedback loop into the model where mass is removed downstream and added upstream.
+% Therefore, the mass flow rates residuals of the closed-loop vapor recovery system shown below would need to be converged in the Multipoint Cycle explained in the next section.
+
+% \begin{equation}
+%     \mathcal{R}_{c,\dot{m}} = \dot{m}_{extractor} - \dot{m}_{injector} = 0
+% \end{equation}
 
@@
 
-In pyCycle, the Cycle block contains all of the governing thermodynamic equations needed to model an engine such as CEA analysis, compressor and turbine models, and equations of state.
-These equations allow any arbitrary engine design to be assembled using the modular cycle elements.
-The Cycle block itself may not result in a valid model of the engine since some physical dependencies may not match.
-These physical dependencies are handled by the Balance block which solves a set of implicit state variables and nonlinear physical residual equations in the form:
+\subsection{Multipoint Model}
+We operate the engine cycle in different modes depending on the desired conservation relationships, design rules, and flight conditions.
+In ``on-design'' mode, we prescribe important cycle inputs such as turbo machinery efficiencies, pressure ratios, and combustion temperatures.
+The ``off-design'' mode inherits the flow path areas and turbo machinery map scalars from the ``on-design'' analysis.
+We enforce design rules as balance equations between different design points to consider the performance of the engine cycle at limiting flight conditions.
 
-\begin{equation}
-    \mathcal{R}_c = \sum_{i=1}^{n} x_i = 0
-\end{equation}
+% [ ] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
+The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+Each flight condition is either critical to the performance or limits the design of the engine.
+% [ ] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
+%   - For example, the SLS point is important for making sure the turbomachinery and flow paths are designed to meet a static thrust target
+%   - The RTO point is limiting for temperature, etc...
 
-\noindent
-where $x_i$ is some physical variable such as a mass or energy flow rate.
-These residuals represent the physical conservation laws such as mass flow rate are converged to zero by the Solver.
-In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which utilizes the analytic partial derivatives provided by each OpenMDAO component.
-All residuals within the engine model are converged at the Cycle level for a given operation condition since all of the parameters downstream do not directly effect those upstream.
-However, with introducing the extractor and injector components, we add a feedback loop into the model where mass is removed downstream and added upstream.
-Therefore, the mass flow rates residuals of the closed-loop vapor recovery system shown below would need to be converged in the Multipoint Cycle explained in the next section.
-
-\begin{equation}
-    \mathcal{R}_{c,\dot{m}} = \dot{m}_{extractor} - \dot{m}_{injector} = 0
-\end{equation}
-
-\subsection{Multipoint Model}
+% [ ] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
 The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
@@
 One of these operating conditions is specified as the design point, which in this case is TOC, and the other operating conditions are considered the off-design points.
+% NOTE: AL-PA, The design point sizes the flow paths and scales the turbomachinery.
+The off-design has the exact same flow path as the design mode cycle.
+The turbo machinery maps are scaled using scalar quantities for off-design performance.
 The design point for the model generally sets all of the engine sizing such as areas and pressure ratios across components.
 The off-design points are essentially the size of the engine at the design point but operating at the corresponding required thrust, cooling, and environmental conditions.
-The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
-Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
+% [ ] TODO: AL-PA, We don't need to talk about the Newton or linear solver details.  Just explain the multipoint model structure with the Newton solver added for context.
+% The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
+% Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
 An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
@@
 
+% [ ] TODO: AL-PA, Don't talk about the objective function until the optimization problem section.
 In the optimization problem described later, we set the mass flow rate of fuel, $\dot{m}_{fuel}$, as the objective function.
+% [ ] TODO: AL-PA, Move the discussion about TSEC to the results.  You don't need to introduce the equation here because it has nothing to do with the details of the multipoint model.
 Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+% [ ] TODO: AL-PA, Again, move this to the optimization problem section.  You should also try to make this sentence more concise.
 Therefore, the water mass fraction that will most impact the objective function the most is at the CRZ operating condition and we thus want to size the area of the injector and extractor at CRZ instead of TOC like the rest of the areas are.
+% [ ] TODO: You shouldn't say things "normally" occur.  Just tell the reader what you did.
+% I suggest re-writing this to plainly explain why we size the water recirculation at cruise instead of TOC
+% Example: We size the water recovery system at cruise because it is the most important phase for fuel burn reduction. etc...
 Normally, the cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
@@
 % Explain Exit ratios and how BPR and OD net thrusts are set
+% [ ] TODO: AL-PA, consider removing this stuff and just direct the reader to the pyCycle paper.
 In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a Balance component.

### 2023-04-28 conference-paper/main.tex
Comments for the optimization problem and multipoint sections

@@
     pdfauthor={Peter Atma}, % insert author here
-	pdftitle={Aviation 2022 Abstract}, % insert title here
-	pdfsubject={Propulsion Analysis and Optimization of an Ultra Bypass Turbofan Engine}, % insert keywords here
+	pdftitle={Aviation 2023 Paper}, % insert title here
+	pdfsubject={Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization}, % insert keywords here
 }
@@
 % ==================================================
-%	OVERALL COMMENTS
+%	OVERALL TODOS
 % ==================================================
+% [ ] TODO: AL-PA, Need to add equation labels
+% [ ] TODO: AL-PA, When you are citing things you should include a "~" to link the citation to the text.  i.e, "OpenMDAO~\cite{Gray2019a}" (See my edits in the introduction)
+% [ ] TODO: AL-PA, You should also use the "~" to link all equation, figure, and table references to the text.
+% [ ] TODO: AL-PA, Make sure all acronyms and subscripts that are longer than a single letter or represent words are shown as text using \rm{} in math mode
 
@@
 
-This work is organized as follows. First, in Section \ref{sec:method}, we introduce the turbofan model and explain the water injection and water recovery components.
-In section \ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
-Finally, we present the optimized results and discuss the design space in section \ref{sec:results}.
+This work is organized as follows. First, in Section~\ref{sec:method}, we introduce the turbofan model and explain the water injection and water recovery components.
+In section~\ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
+Finally, we present the optimized results and discuss the design space in section~\ref{sec:results}.
 
@@
 \subsection{Multipoint Model}
+% NOTE: AL-PA, I added this blurb to introduce multipoint
 We operate the engine cycle in different modes depending on the desired conservation relationships, design rules, and flight conditions.
@@
 % [ ] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
-%   - For example, the SLS point is important for making sure the turbomachinery and flow paths are designed to meet a static thrust target
+%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
 %   - The RTO point is limiting for temperature, etc...
@@
 The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+% [ ] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
 The SLS condition represents the static performance requirements for the engine, the RTO condition represents the performance and cooling requirements at the point of rotation during takeoff, the TOC operating condition represents the performance requirements during a climb, and the CRZ operation condition represents the criuse performance of the engine.
 To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design that satisfies the requirements at each of these operating conditions.
+% NOTE: AL-PA, Using a lot of extra words to say: "The TOC point is the on-design condition."
 One of these operating conditions is specified as the design point, which in this case is TOC, and the other operating conditions are considered the off-design points.
-% NOTE: AL-PA, The design point sizes the flow paths and scales the turbomachinery.
+% NOTE: AL-PA, The design point sizes the flow paths and scales the turbo machinery.
 The off-design has the exact same flow path as the design mode cycle.
 The turbo machinery maps are scaled using scalar quantities for off-design performance.
+% TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
 The design point for the model generally sets all of the engine sizing such as areas and pressure ratios across components.
@@
 
+% [ ] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
 \begin{figure}[hbt!]
@@
 % Explain Exit ratios and how BPR and OD net thrusts are set
-% [ ] TODO: AL-PA, consider removing this stuff and just direct the reader to the pyCycle paper.
+% [ ] TODO: AL-PA, I would include all four of the balance components here and explain how they effectively act as constraints on the multipoint model.
+% NOTE: AL-PA, See the pyCycle paper, they explain how using the balance residuals creates a reduced design space for the optimization problem.
+% NOTE: AL-PA, You can discuss how this makes the multipoint nonlinear solution more challenging, but improves the optimization problem conditioning.
 In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a Balance component.
@@
 
+% [ ] TODO: AL-PA, I'm not sure this subsection is necessary.  We will describe the performance metrics in the optimization problem section.  Consider moving it there.
 \subsection{Performance Metrics}
@@
 
+% [ ] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
+% [ ] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
 \begin{figure}[hbt!]
@@
 % Update with table from Andrew
+% [ ] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
+% [ ] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
 \begin{table}[hbt!]
@@
         Atmospheric parameters specify the flight conditions and humidity of the atmosphere and Lower Heating Values are given for each fuel to compute TSEC.}
-    \begin{tabular}{c c c c}
+    \begin{tabular}{r r r l}
         \hline
-        Parameter              & Value   & Units          & Comments                                        \\
+        Parameter              & Value   & Units          & Description                                     \\
         \hline
@@
 
-\subsection{Problem Statment}
+% NOTE: AL-PA, No reason to have an extra subsection here so I removed it
+% \subsection{Problem Statment}
 % Briefly discuss the optimization problem
-We will perform gradient-based design optimization of the engine model with the multipoint architecture that considers each of the flight conditions experienced by commercial aircraft.
+% NOTE: AL-PA, "We will perform" makes it seem like we haven't done the work yet.
+We performed multipoint gradient-based design optimization of the N+3 engine model considering TOC, RTO, SLS, and CRZ flight conditions.
+% We will perform gradient-based design optimization of the engine model with the multipoint architecture that considers each of the flight conditions experienced by commercial aircraft.
 % We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
-The objective is to minimize the TSEC since that is our performance metric for comparing the two types of fuels.
-However, since we are constraining net thrust at each operating condition this optimization problem becomes ill-posed.
-Therefore, we will minimize fuel flow rate, $W_{fuel}$ at the cruise condition subject to net thrust and engine diameter constraints since this will accomplish the same goal with a better posed problem.
+% NOTE: AL-PA, I re-wrote this to be more direct
+The objective is to minimize fuel burn subject to design and performance constraints at each flight condition.
+% The objective is to minimize the TSEC since that is our performance metric for comparing the two types of fuels.
+% However, since we are constraining net thrust at each operating condition this optimization problem becomes ill-posed.
+% Therefore, we will minimize fuel flow rate, $W_{fuel}$ at the cruise condition subject to net thrust and engine diameter constraints since this will accomplish the same goal with a better posed problem.
+% [ ] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
 An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_xdsm_opt}.
 
+% [ ] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
 \begin{figure}[!hbt]
@@
 
+% [ ] TODO: AL-PA, I would elaborate on this a bit more.  Are these the on-design parameters?  Are they constraints?
+% [ ] TODO: AL-PA, The N+3 model has a bunch of constraints imposed on the multipoint problem via balance comps.  This is a good place to talk about those.
+% [ ] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
 This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
@@
 % [ ] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
+% [ ] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
 \begin{table}[hbt!]
@@
                         & $T_{4,\rm{RTO}}$               & RTO combustor temperature                   & \unit{\degree R} & 1        \\
-                        & $V_{\rm{ratio,CRZ}}$           & RTO combustor temperature                   & \unit{\degree R} & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ & \unit{\degree R} & 1        \\
         \cline{3-5}
@@
 % Blurb about PyOptSparse and SNOPT
-\subsection{Optimization Software}
-OpenMDAO supports the use of different optimization packages including Scipy and PyOptSparse.
-PyOptSparse is an object-oriented framework for formulating and solving nonlinear constrained optimization problems.
-PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with  \cite{Wu2020a}.
+% NOTE: AL-PA, This can all be part of the optimization problem section you don't need a new subsection
+% \subsection{Optimization Software}
+% NOTE: AL-PA, "pyOptSparse" not "PyOptSparse", i.e the first "p" is not capitalized.
+% [x] TODO: AL-AL, need to cite pyOptSparse, SNOPT, and OpenMDAO
+% NOTE: AL-PA, I re-wrote most of this to be more concise.
+OpenMDAO~\cite{Gray2019a} is a modular framework that enables multidisciplinary gradient-based optimization with analytic coupled derivatives.
+We use pyOptSparse~\cite{Wu2020a} to facilitate the use of state-of-the-art optimization software through a unified python interface.
+We solve the optimization problem listed in Table~\ref{tab:opt_problem} with SNOPT~\cite{Gill2005a}, a gradient-based sequential quadratic programming (SQP) algorithm for large-scale constrained problems.
 
-SNOPT (Sparse Nonlinear OPTimizer) was the optimizer chosen for this work.
-SNOPT is a state-of-the-art optimizer used to solve large-scale optimization problems (linear and nonlinear).
-The software uses a sparse SQP (sequential quadratic programming) algorithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
-SNOPT is particularly useful for nonlinear problems whose functions and derivatives are expensive compute.
-An augmented Lagrangian merit function ensures convergence from an arbitrary point.
-SNOPT allows the nonlinear constraints to be violated (if necessary) and minimizes the sum of these violations.
-Due to the robustness of the algorithm, SNOPT is a perfect optimizer to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
-SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization \cite{Gill2005a}.
+% OpenMDAO supports the use of different optimization packages including Scipy and PyOptSparse.
+% PyOptSparse is an object-oriented framework for formulating and solving nonlinear constrained optimization problems.
+% PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with  \cite{Wu2020a}.
+
+% SNOPT (Sparse Nonlinear OPTimizer) was the optimizer chosen for this work.
+% SNOPT is a state-of-the-art optimizer used to solve large-scale optimization problems (linear and nonlinear).
+% The software uses a sparse SQP (sequential quadratic programming) algorithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
+% SNOPT is particularly useful for nonlinear problems whose functions and derivatives are expensive compute.
+% An augmented Lagrangian merit function ensures convergence from an arbitrary point.
+% SNOPT allows the nonlinear constraints to be violated (if necessary) and minimizes the sum of these violations.
+% Due to the robustness of the algorithm, SNOPT is a perfect optimizer to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
+% SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization \cite{Gill2005a}.
 

### 2023-04-29 conference-paper/main.tex
Updates 4/27
Peter's fixes 4/28

@@
 
-% [ ] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
+% [x] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
 % Thermodynamic equations of state are solved using CEA at the interface between components, shown as black arrows in Figure~\ref{fig:n3_cycle}.
@@
 The N+3 UHB geared turbofan model consists of twenty-five different elements that define the flow path and the mechanical systems.
-Thermodynamic quantities are exchanged at flow path boundaries represented by black arrows between blue flow path components in Figure~\ref{fig:N3_original}.
+Thermodynamic quantities are solved and exchanged using CEA at flow path boundaries represented by black arrows between blue flow path components in Figure~\ref{fig:N3_original}.
 The fan, gearbox, low pressure, and high pressure systems are connected by three mechanical shafts depicted in red in Figure~\ref{fig:N3_original}.
+
 % Three mechanical shafts, depicted in red in Figure~\ref{fig:N3_original}, connect the fan, low pressure, and high pressure systems.
@@
 
-% [ ] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
-% [ ] TODO: AL-PA, Add the description of the figure elements to the caption.
+% [x] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
+% [x] TODO: AL-PA, Add the description of the figure elements to the caption.
 % [x] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
@@
 % Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
-% [ ] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
+% [x] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
+In the model of the extractor, we are assuming that a fraction of the total water available in the exhaust stream is recovered and that there are no pressure or temperature losses associated with this process.
 % NOTE: AL-PA, we will talk about the condenser when we discuss the results of the pressure recovery parameter sweep.
@@
 
-We modified the composition of the air mixture upstream of the combustor to account for humidity.
+To account for the humidity of the inlet air as well as the increased humidity after water injection, we modified the composition of the air mixture upstream of the combustor.
 % Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
@@
 % The two models are a water injector that adds water to the flow upstream of the HPC and a water extractor to divert a fraction of the water in the flow away from the exhaust stream.
-The injector operates similarly to fuel injection in the combustor.
+The injector operates similarly to fuel injection in the pyCycle combustor component.
 We determine a WAR that is analogous to the fuel-to-air (FAR) ratio in the combustor.
@@
 We enforce design rules as balance equations between different design points to consider the performance of the engine cycle at limiting flight conditions.
+Table
 
-% [ ] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
+% [x] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
+\begin{table}[hbt!]
+    \centering
+    \caption{Altitude and mach numbers at each of the flight conditions considered in the multipoint formulation.
+    }
+    \begin{tabular}{l r r r r l}
+        \hline
+        Parameter & TOC   & RTO  & SLS & CRZ   & Units   \\
+        \hline
+        Altitude  & 35000 & 0    & 0   & 35000 & \si{ft} \\
+        Mach      & 0.8   & 0.25 & 0.0 & 0.8   & -       \\
+        % Humidity      & 0.00017   & 0.009 & 0.009 & 0.00017   & -     \\
+        \hline
+    \end{tabular}
+    \label{flight_levels}
+\end{table}
+
 The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
@@
 The turbo machinery maps are scaled using scalar quantities for off-design performance.
-% TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
+% [ ] TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
 The design point for the model generally sets all of the engine sizing such as areas and pressure ratios across components.
@@
 
-% [ ] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
-    \caption{
-        N+3 engine multipoint setup XDSM diagram.
-        This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
-    }
-    \label{fig:N3_xdsm}
-\end{figure}
+% [x] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
+% \begin{figure}[hbt!]
+%     \centering
+%     \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
+%     \caption{
+%         N+3 engine multipoint setup XDSM diagram.
+%         This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
+%     }
+%     \label{fig:N3_xdsm}
+% \end{figure}
 
@@
 
-% [ ] TODO: AL-PA, I'm not sure this subsection is necessary.  We will describe the performance metrics in the optimization problem section.  Consider moving it there.
-\subsection{Performance Metrics}
-Past implementations of engine cycles and example engine cycles in pyCycle generally have used either JetA or JP-7 as a fuel.
-However, in this work we are interested in comparing the performance of similar engines with different types of fuel, specifically hydrogen due to the many benefits it offers in terms of performance and thermal properties.
-Fortunately, pyCycle comes ready to use hydrogen with cataloged exhaust products for hydrogen fuel.
-The fuel type is simply changed from Jet-A to H2 in the pyCycle model.
-
-For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since it is a represents how low the fuel burn is for a given level of thrust.
-However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
-% TODO: Update mdolab.bib
-Therefore, a new metric for comparing the relative efficiencies of engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) which multiplies TSFC by the lower heating value (LHV) of the fuel %\cite{Adler2023}.
-
-\begin{equation}
-    TSFC = \frac{\Dot{m}_{fuel}}{F_{thrust}}
-\end{equation}
-
-\begin{equation}
-    TSEC = \frac{\Dot{m}_{fuel} LHV}{F_{thrust}} = TSFC \times LHV
-\end{equation}
+% [x] TODO: AL-PA, I'm not sure this subsection is necessary.  We will describe the performance metrics in the optimization problem section.  Consider moving it there.
 
@@
 % Update with table from Andrew
-% [ ] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
-% [ ] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
+% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
+% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
 \begin{table}[hbt!]
@@
         N+3 engine model parameters.
-        Atmospheric parameters specify the flight conditions and humidity of the atmosphere and Lower Heating Values are given for each fuel to compute TSEC.}
+        Atmospheric parameters specify the flight conditions and humidity of the atmosphere and lower heating values are given for each fuel to compute TSEC.}
     \begin{tabular}{r r r l}
@@
         \hline
-        $h_{\rm{TOC}}$         & 0.00017 & -              & humidity ratio at TOC \cite{Kalnay1996}         \\
-        $h_{\rm{CRZ}}$         & 0.00017 & -              & humidity ratio at CRZ \cite{Kalnay1996}         \\
-        $h_{\rm{RTO}}$         & 0.009   & -              & humidity ratio at RTO \cite{Kalnay1996}         \\
-        $h_{\rm{SLS}}$         & 0.009   & -              & humidity ratio at SLS \cite{Kalnay1996}         \\
-        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \unit{BTU/lbm} & Lower heating value of Jet-A \cite{Lawicki2002} \\
-        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \unit{BTU/lbm} & Lower heating value of H2 \cite{toolbox2003}    \\
+        $HR_{\rm{TOC}}$        & 0.00017 & -            & humidity ratio at TOC \cite{Kalnay1996}                                                                                \\
+        $HR_{\rm{CRZ}}$        & 0.00017 & -            & humidity ratio at CRZ \cite{Kalnay1996}                                                                                \\
+        $HR_{\rm{RTO}}$        & 0.009   & -            & humidity ratio at RTO \cite{Kalnay1996}                                                                                \\
+        $HR_{\rm{SLS}}$        & 0.009   & -            & humidity ratio at SLS \cite{Kalnay1996}                                                                                \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
         \hline
@@
 % Therefore, we will minimize fuel flow rate, $W_{fuel}$ at the cruise condition subject to net thrust and engine diameter constraints since this will accomplish the same goal with a better posed problem.
-% [ ] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
+% [x] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
+
+For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since it is a represents how much fuel is burned at a given thrust level.
+However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
+% TODO: Update mdolab.bib
+A better metric for comparing the relative efficiencies of an engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) %\cite{Adler2023}.
+TSEC is TSFC multipied by the lower heating value (LHV) of the fuel shown in Equation~\eqref{eq:tsec}.
+
+\begin{equation}
+    TSFC = \frac{\Dot{m}_{fuel}}{F_{thrust}}
+    \label{eq:tsfc}
+\end{equation}
+
+\begin{equation}
+    TSEC = \frac{\Dot{m}_{fuel} LHV}{F_{thrust}} = TSFC \times LHV
+    \label{eq:tsec}
+\end{equation}
+
+Therefore, TSEC is the objective function we are minimizing in the optimzation problem.
 An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_xdsm_opt}.
@@
     \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l}
+    \begin{tabular}{r l l r l}
         \toprule
@@
         \hline
-        minimize        & $ \dot{m}_{\rm{fuel,CRZ}} $    & Fuel flow rate at CRZ                       & \unit{lbm/s}     & 1        \\
+        minimize        & $ \dot{m}_{\rm{fuel,CRZ}} $    & Fuel flow rate at CRZ                       & \si{lbm/s}     & 1        \\
                         &                                &                                             &                &          \\
@@
                         & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio                & -              & 1        \\
-                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                   & \unit{\degree R} & 1        \\
-                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ & \unit{\degree R} & 1        \\
+                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                   & \si{\degree R} & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ & \si{\degree R} & 1        \\
         \cline{3-5}
@@
                         &                                &                                             &                &          \\
-        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                    & \unit{lbf}       & 1        \\
-                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                        & \unit{inch^2}    & 1        \\
+        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                    & \si{lbf}       & 1        \\
+                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                        & \si{inch^2}    & 1        \\
         \cline{3-5}

### 2023-04-29 figures/N3_CLVR_cycle.tex
Peter's fixes 4/28

@@
     % \node [element] (fc) {Flight Conditions};
-    \node [element] (inlet) {Inlet};
-    \node [element, right=4em of inlet] (fan) {Fan};
-    \node [element, right=4em of fan] (splitter) {Splitter};
-    \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
+    % \node [element] (inlet) {Inlet};
+    % \node [element, right=4em of inlet] (fan) {Fan};
+    % \node [element, right=4em of fan] (splitter) {Splitter};
+    \node [element] (lpc) {Low Pressure Compressor};
     \node [element, right=4em of lpc ] (injector) {Water Injector};
@@
     \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
-    \node [element, below=12em of burner] (bypduct) {Bypass Duct};
-    \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};
+    % \node [element, below=12em of burner] (bypduct) {Bypass Duct};
+    % \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};
 
     % Add shaft elements
-    \node [shaft_element, above=8em of $(hpc)!0.5!(hpt)$] (hpshaft) {High Pressure Shaft};
-    \node [shaft_element, above=16em of $(lpc)!0.5!(lpt)$] (lpshaft) {Low Pressure Shaft};
-    \node [shaft_element, above=16em of $(fan)!0.28!(lpc)$] (fanshaft) {Fan Shaft};
-    \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};
+    % \node [shaft_element, above=8em of $(hpc)!0.5!(hpt)$] (hpshaft) {High Pressure Shaft};
+    % \node [shaft_element, above=16em of $(lpc)!0.5!(lpt)$] (lpshaft) {Low Pressure Shaft};
+    % \node [shaft_element, above=16em of $(fan)!0.28!(lpc)$] (fanshaft) {Fan Shaft};
+    % \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};
 
@@
     % \path [connection] (fc) -- (inlet);
-    \path [connection] (inlet) -- (fan);
-    \path [connection] (fan) -- (splitter);
-    \path [connection] (splitter) -- (lpc);
-    \path [connection] (splitter) |- (bypduct);
-    \path [connection] (bypduct) -- (bypnozzle);
+    % \path [connection] (inlet) -- (fan);
+    % \path [connection] (fan) -- (splitter);
+    % \path [connection] (splitter) -- (lpc);
+    % \path [connection] (splitter) |- (bypduct);
+    % \path [connection] (bypduct) -- (bypnozzle);
     \path [connection] (lpc) -- (injector);
@@
     % Draw Shaft Connections
-    \path [shaft] (fan) |- (fanshaft) -- (gearbox);
-    \path [shaft] (gearbox) -| (lpc);
-    \path [shaft] (lpc) |- (lpshaft) -| (lpt);
-    \path [shaft] (hpc) |- (hpshaft) -| (hpt);
+    % \path [shaft] (fan) |- (fanshaft) -- (gearbox);
+    % \path [shaft] (gearbox) -| (lpc);
+    % \path [shaft] (lpc) |- (lpshaft) -| (lpt);
+    % \path [shaft] (hpc) |- (hpshaft) -| (hpt);
 

### 2023-04-30 conference-paper/main.tex
Addressed most comments up to Results, added Results figures

@@
 We enforce design rules as balance equations between different design points to consider the performance of the engine cycle at limiting flight conditions.
-Table
+Table \ref{flight_conds} shows the different altitudes and mach numbers at each flight condition.
+
+The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+Each flight condition is either critical to the performance or limits the design of the engine.
+% [x] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
+%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
+%   - The RTO point is limiting for temperature, etc...
+
+% [x] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
+The N+3 engine model has many complex thermodynamic and performance connections between the different operating conditions such as temperature ratios and cooling requirements.
+Therefore, the N+3 engine model computes the engine performance at the four different operating conditions in order to resolve these connections.
+% The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+% [x] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
+The SLS operating condition is important for ensuring that the turbomachinery and flow paths are designed to a meet static thrust target.
+The RTO operating condition is important for specifying the upper limit of the combustor temperature and cooling requirements for a thrust target during take-off.
+The TOC operating condition is important for specifying the required thrust during the climb at the design altitude.
+Finally, the CRZ operation condition is important for specifying that the turbomachinery and flow paths are designed to meet cruise target thrust.
+To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
+This final design must satisfies the requirements at each of these operating conditions.
+The altitude and mach number of each of the operating conditions is shown in Table \ref{flight_conds}.
 
@@
         Mach           & 0.8     & 0.25  & 0.0   & 0.8     & -          \\
-        % Humidity      & 0.00017   & 0.009 & 0.009 & 0.00017   & -     \\
+        Humidity Ratio & 0.00017 & 0.009 & 0.009 & 0.00017 & \si{kg/kg} \\
         \hline
     \end{tabular}
-    \label{flight_levels}
+    \label{flight_conds}
 \end{table}
 
-The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-Each flight condition is either critical to the performance or limits the design of the engine.
-% [ ] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
-%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
-%   - The RTO point is limiting for temperature, etc...
-
-% [ ] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
-The N+3 engine model as it is implemented in pyCycle has many complex thermodynamic and performance connections between different operating conditions.
-Therefore, the N+3 engine model computes the engine performance at 4 different operating conditions in order to resolve the complexities between each operating condition on the final design.
-The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-% [ ] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
-The SLS condition represents the static performance requirements for the engine, the RTO condition represents the performance and cooling requirements at the point of rotation during takeoff, the TOC operating condition represents the performance requirements during a climb, and the CRZ operation condition represents the criuse performance of the engine.
-To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design that satisfies the requirements at each of these operating conditions.
 % NOTE: AL-PA, Using a lot of extra words to say: "The TOC point is the on-design condition."
-One of these operating conditions is specified as the design point, which in this case is TOC, and the other operating conditions are considered the off-design points.
+The TOC point is the ``on-design'' condition since it is desireable to specify combustor temperatures and pressure ratios at this point.
 % NOTE: AL-PA, The design point sizes the flow paths and scales the turbo machinery.
@@
 The turbo machinery maps are scaled using scalar quantities for off-design performance.
-% [ ] TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
-The design point for the model generally sets all of the engine sizing such as areas and pressure ratios across components.
-The off-design points are essentially the size of the engine at the design point but operating at the corresponding required thrust, cooling, and environmental conditions.
+% [x] TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
+The design point for the model sets all of the engine sizing such as areas and pressure ratios across components.
+The off-design points inherit the size of the engine in terms of the cross-sectional areas from the design point but operate at the corresponding required thrust, cooling, and environmental conditions.
 % [ ] TODO: AL-PA, We don't need to talk about the Newton or linear solver details.  Just explain the multipoint model structure with the Newton solver added for context.
@@
 % Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
-An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
+% An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
 
 % [x] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
-% \begin{figure}[hbt!]
-%     \centering
-%     \includegraphics[width=0.75\textwidth]{N3_xdsm.pdf}
-%     \caption{
-%         N+3 engine multipoint setup XDSM diagram.
-%         This XDSM diagram shows how each of the operating conditions is coupled with each other and how the outputs are computed.
-%     }
-%     \label{fig:N3_xdsm}
-% \end{figure}
 
-% [ ] TODO: AL-PA, Don't talk about the objective function until the optimization problem section.
-In the optimization problem described later, we set the mass flow rate of fuel, $\dot{m}_{fuel}$, as the objective function.
-% [ ] TODO: AL-PA, Move the discussion about TSEC to the results.  You don't need to introduce the equation here because it has nothing to do with the details of the multipoint model.
-Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
-% [ ] TODO: AL-PA, Again, move this to the optimization problem section.  You should also try to make this sentence more concise.
-Therefore, the water mass fraction that will most impact the objective function the most is at the CRZ operating condition and we thus want to size the area of the injector and extractor at CRZ instead of TOC like the rest of the areas are.
-% [ ] TODO: You shouldn't say things "normally" occur.  Just tell the reader what you did.
+% [x] TODO: AL-PA, Don't talk about the objective function until the optimization problem section.
+% [x] TODO: AL-PA, Move the discussion about TSEC to the results.  You don't need to introduce the equation here because it has nothing to do with the details of the multipoint model.
+% Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+% [x] TODO: AL-PA, Again, move this to the optimization problem section.  You should also try to make this sentence more concise.
+% Therefore, the water mass fraction that will most impact the objective function the most is at the CRZ operating condition and we thus want to size the area of the injector and extractor at CRZ instead of TOC like the rest of the areas are.
+% [x] TODO: You shouldn't say things "normally" occur.  Just tell the reader what you did.
 % I suggest re-writing this to plainly explain why we size the water recirculation at cruise instead of TOC
 % Example: We size the water recovery system at cruise because it is the most important phase for fuel burn reduction. etc...
-Normally, the cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
-To size the areas of the injector and extractor at CRZ, we only connect the state variables across these components at the corresponding operating condition and set the areas of both components at the CRZ point.
+% The cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
+We size the water recovery system at the cruise condition because it is the longest and most important phase of flight for fuel burn reduction.
+To size the areas of the injector and extractor at CRZ, we only connect the thermodynamic state variables across these components at the corresponding operating condition and set the areas of both components at the CRZ point.
 These connections are shown graphically in the XDSM diagram in Figure \ref{fig:N3_xdsm_full}.
@@
 % Explain Exit ratios and how BPR and OD net thrusts are set
-% [ ] TODO: AL-PA, I would include all four of the balance components here and explain how they effectively act as constraints on the multipoint model.
+% [x] TODO: AL-PA, I would include all four of the balance components here and explain how they effectively act as constraints on the multipoint model.
 % NOTE: AL-PA, See the pyCycle paper, they explain how using the balance residuals creates a reduced design space for the optimization problem.
 % NOTE: AL-PA, You can discuss how this makes the multipoint nonlinear solution more challenging, but improves the optimization problem conditioning.
-In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a Balance component.
-The Balance component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
+The N+3 multipoint model has many constraints on the model that set conservation and design values using \emph{balance} components.
+A Newton solver is used to converge these conservation an design values such $r=0$.
+The conservation \emph{balance} residuals are associated with each of the three shafts at each design condition.
+The state variables that set the shaft conservation residuals are the turbomachinery pressure ratios ($PR_{Fan}$, $PR_{LPC}$, $PR_{HPC}$) at TOC and shaft speeds ($N_{Fan}$, $N_{LPC}$, $N_{HPC}$) and engine mass flow rate ($\dot{m}$) at the ``off-design'' points.
+The design constraints are also set using \emph{balance} residuals.
+For the TOC point, $T_{4}$ is set by the fuel-to-air ratio (FAR) of the burner and $OPR$ is set by $HPC_{PR}$.
+Additionally, a constraint on the turbomachinery polytropic efficiency is set based on technological assumptions.
+These TOC balance residuals are summarized in Equation \eqref{des_resid} \cite{Hendricks2019}.
+
+\begin{equation}
+    r_{des} \rightarrow
+    \begin{cases}
+        T_{4,TOC} = T_{4,des}                 \\
+        OPR_{TOC} = OPR_{des}                 \\
+        \eta_{poly,i,TOC} = \eta_{poly,i,des} \\
+    \end{cases}
+    \label{des_resid}
+\end{equation}
+
+The outputs for the TOC point based on these design constraints are TSFC and $F_{net}$.
+For the ``off-design'' points, the target fan stall margin is set by the bypass ratio (BPR) and target net thrust is mainly set by FAR.
+Additionally, the engine cooling mass flow rate residuals are set by cooling needs at RTO using a perscibed value.
+These ``off-design'' residuals are summarized in Equation \eqref{od_resid} \cite{Hendricks2019}.
+
+\begin{equation}
+    r_{od} \rightarrow
+    \begin{cases}
+        R_{Fan} = R_{Fan,target}      \\
+        F_{net} = F_{net,target}      \\
+        \dot{m}_{cooling, err, k} = 0 \\
+    \end{cases}
+    \label{od_resid}
+\end{equation}
+
+Solving for all of the state and design variables while satisfying constraints could be accomplish with only an optimizer to simplify the problem.
+However, using a solver to converge constraints using \emph{balance} components creates a reduced-space problem with few design variables for the optimizer.
+This increases the complexity of the multipoint nonlinear solution but simplifies the problem for the optimizer and is the preferred method in cycle analysis.
+
+In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a \emph{balance} component.
+The \emph{balance} component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
 
@@
     V_{ratio} = \frac{V_{core,ideal}C_{v,core}}{V_{bypass,ideal}C_{v,bypass}}
+    \label{vratio}
 \end{equation}
@@
 
-% [ ] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
+% [x] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
 % [ ] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
@@
 \end{figure}
-
-% Update with table from Andrew
-% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
-% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
-\begin{table}[hbt!]
-    \centering
-    \caption{
-        N+3 engine model parameters.
-        Atmospheric parameters specify the flight conditions and humidity of the atmosphere and lower heating values are given for each fuel to compute TSEC.}
-    \begin{tabular}{r r r l}
-        \hline
-        Parameter              & Value   & Units        & Description                                                                                                            \\
-        \hline
-        $HR_{\rm{TOC}}$        & 0.00017 & -            & humidity ratio at TOC \cite{Kalnay1996}                                                                                \\
-        $HR_{\rm{CRZ}}$        & 0.00017 & -            & humidity ratio at CRZ \cite{Kalnay1996}                                                                                \\
-        $HR_{\rm{RTO}}$        & 0.009   & -            & humidity ratio at RTO \cite{Kalnay1996}                                                                                \\
-        $HR_{\rm{SLS}}$        & 0.009   & -            & humidity ratio at SLS \cite{Kalnay1996}                                                                                \\
-        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
-        \hline
-    \end{tabular}
-    \label{engine_params}
-\end{table}
 
@@
 % TODO: Update mdolab.bib
-A better metric for comparing the relative efficiencies of an engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC) %\cite{Adler2023}.
+A better metric for comparing the relative efficiencies of an engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC). %\cite{Adler2023}.
 TSEC is TSFC multipied by the lower heating value (LHV) of the fuel shown in Equation~\eqref{eq:tsec}.
@@
 
-Therefore, TSEC is the objective function we are minimizing in the optimzation problem.
-An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_xdsm_opt}.
+Therefore, TSEC at the cruise condition is the objective function in the optimzation problem.
+An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{N3_xdsm_opt.pdf}
+    \includegraphics[width=0.75\textwidth]{N3_opt_XDSM.pdf}
     \caption{
@@
         The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
-    \label{fig:N3_xdsm_opt}
+    \label{fig:N3_opt_xdsm}
 \end{figure}
 
-% [ ] TODO: AL-PA, I would elaborate on this a bit more.  Are these the on-design parameters?  Are they constraints?
-% [ ] TODO: AL-PA, The N+3 model has a bunch of constraints imposed on the multipoint problem via balance comps.  This is a good place to talk about those.
-% [ ] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
-This optimization problem was run for both Jet-A and H2 fuels using the parameters given in Table \ref{engine_params}.
+% [x] TODO: AL-PA, I would elaborate on this a bit more.  Are these the on-design parameters?  Are they constraints?
+% [x] TODO: AL-PA, The N+3 model has a bunch of constraints imposed on the multipoint problem via balance comps.  This is a good place to talk about those.
+% [x] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
+The TOC point constraints shown in Figure \ref{fig:N3_opt_xdsm} are only the constraints imposed on the model at optimizer level.
+
+The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
+Only the water recovery fraction at CRZ is a design variable since we are optimizing $TSEC_{\rm{CRZ}}$.
+TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
+\begin{equation}
+    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
+    \label{t4ratio}
+\end{equation}
+
+This optimization problem was run for both Jet-A and H2 fuels using the fuel properties in \ref{fuel_props} and flight conditions in Table \ref{flight_conds}.
+
+% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
+% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
+\begin{table}[hbt!]
+    \centering
+    \caption{
+        N+3 model fuel properties.
+        The lower heating values are given for each fuel used to compute TSEC.}
+    \begin{tabular}{r r r l}
+        \hline
+        Parameter              & Value   & Units        & Description                                                                                                            \\
+        \hline                                                                                                                                                                   \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+        \hline
+    \end{tabular}
+    \label{fuel_props}
+\end{table}
+
 The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
 
-% [ ] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
-% [ ] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
+% [x] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
+% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
 % [ ] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
@@
         \hline
-        minimize        & $ \dot{m}_{\rm{fuel,CRZ}} $    & Fuel flow rate at CRZ                       & \si{lbm/s}     & 1        \\
+        minimize        & $TSEC_{\rm{CRZ}} $             & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
                         &                                &                                                                       &                &          \\
-        with respect to & $X_{\rm{H2O,TOC}}$             & Water recovery fraction at TOC              & -              & 1        \\
-                        & $X_{\rm{H2O,RTO}}$             & Water recovery fraction at RTO              & -              & 1        \\
-                        & $X_{\rm{H2O,SLS}}$             & Water recovery fraction at SLS              & -              & 1        \\
-                        & $X_{\rm{H2O,CRZ}}$             & Water recovery fraction at CRZ              & -              & 1        \\
-                        & $\rm{PR}_{\rm{HPC,TOC}}$       & TOC high-pressure compressor pressure ratio & -              & 1        \\
+        with respect to & $X_{\rm{H2O,CRZ}}$             & Water recovery fraction at CRZ                                        & -              & 1        \\
+                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                & -              & 1        \\
                         & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                            & -              & 1        \\
-                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                      & -              & 1        \\
-                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio                & -              & 1        \\
+                        & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                            & -              & 1        \\
                         & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                             & \si{\degree R} & 1        \\
-                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ & \si{\degree R} & 1        \\
+                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation \eqref{t4ratio})               & -              & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation \eqref{vratio}) & -              & 1        \\
         \cline{3-5}
-                        &                                & Total                                       &                & 10       \\
+                        &                                & Total                                                                 &                & 7        \\
                         &                                &                                                                       &                &          \\
@@
 \label{sec:results}
+
+Our comparison metric is $TSEC$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.
+
+When $T4_{RTO}$ and $X_{\rm{H2O,CRZ}}$ are design variables at the same time it was found that the optimizer pushes $T4_{RTO}$ down and $X_{\rm{H2O,CRZ}}$ up.
+Since these two variables are at odds with each other and the upper limit for $X_{\rm{H2O,CRZ}}$ is where the model breaks, $T4_{RTO}$ was set as the optimal value from the optimizations with no water recirulation.
+
 The 4 optimizations mentioned in the optimation problem section were run and solved.
-The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_clvr}.
+The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_summary}.
 
-% results of parameter sweep
-
-% Feasibility, Optimality, Merit Func (all 4 on same plot)
-% NOTE: need to clean up this plot
+% Feasibility, Optimality, Merit Func history
 \begin{figure}[hbt!]
@@
     \includegraphics[width=0.8\textwidth]{opt_summary.pdf}
-    \caption{The optimality, feasibility, and merit fuction for each optimization problem.
+    \caption{The optimality, feasibility, and merit fuction history for each optimization problem.
         Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
-    \label{fig:history_clvr}
+    \label{fig:history_summary}
 \end{figure}
@@
 
-% DV and Constraints over each iteration
+% DV history
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{dvs.pdf}
+    \caption{The design variable history for each optimization problem.
+        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
+    \label{fig:history_dvs}
+\end{figure}
+
+% Constraint history
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{cons.pdf}
+    \caption{The constraint history for each optimization problem.
+        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
+    \label{fig:history_cons}
+\end{figure}
 
@@
         \toprule
-        objective   & $W_{fuel,CRZ}$        & 0.6394   & -      & -     & $\frac{lbm}{s}$ \\
+        objective   & $TSEC_{\rm{CRZ}} $    & 8186.255 & -      & -     & $\frac{lbm}{s}$ \\
         \hline
@@
                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 59.495   & 40.0   & 70.0  & -               \\
+                    & $PR_{OPR,TOC}$        & 61.012   & 40.0   & 70.0  & -               \\
                     & $T_{4,TOC}/T_{4,RTO}$ & 0.913    & 0.8    & 0.95  & -               \\
@@
         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0    & 100    & -     & $in^2$          \\
+                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
         \bottomrule
@@
         \toprule
-        objective   & $W_{fuel,CRZ}$        & 0.2331  & -      & -     & $\frac{lbm}{s}$ \\
+        objective   & $TSEC_{\rm{CRZ}} $    & 8295.236 & -      & -     & $\frac{lbm}{s}$ \\
         \hline
@@
                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 59.153  & 40.0   & 70.0  & -               \\
+                    & $PR_{OPR,TOC}$        & 60.660   & 40.0   & 70.0  & -               \\
                     & $T_{4,TOC}/T_{4,RTO}$ & 0.918    & 0.8    & 0.95  & -               \\
@@
         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0   & 100    & -     & $in^2$          \\
+                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
         \bottomrule
@@
 
-\begin{table}[hbt!] % need to run for T4 = 3220.570
+\begin{table}[hbt!]
     \centering
@@
         \toprule
-        objective   & $W_{fuel,CRZ}$        & 0.6037 & -      & -     & $\frac{lbm}{s}$ \\
+        objective   & $TSEC_{\rm{CRZ}} $    & 7766.339 & -      & -     & $\frac{lbm}{s}$ \\
         \hline
-        variables   & $x_{H2O,TOC}$         & 0.115  & 0.0    & -     & -               \\
-                    & $x_{H2O,RTO}$         & 0.0    & 0.0    & -     & -               \\
-                    & $x_{H2O,SLS}$         & 0.0    & 0.0    & -     & -               \\
-                    & $x_{H2O,CRZ}$         & 0.3    & 0.0    & 0.3   & -               \\
-                    & $PR_{fan,TOC}$        & 1.291  & 1.2    & 1.4   & -               \\
+        variables   & $x_{H2O,CRZ}$         & 0.3      & 0.0    & 0.3   & -               \\
+                    & $PR_{fan,TOC}$        & 1.292    & 1.2    & 1.4   & -               \\
                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 54.218 & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.923  & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3400.0 & -      & -     & $^\circ$R       \\
+                    & $PR_{OPR,TOC}$        & 61.188   & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.911    & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3220.574 & -      & -     & $^\circ$R       \\
                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
@@
         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0  & 100    & -     & $in^2$          \\
+                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
         \bottomrule
@@
         \toprule
-        objective   & $W_{fuel,CRZ}$        & -       & -      & -     & $\frac{lbm}{s}$ \\
+        objective   & $TSEC_{\rm{CRZ}} $    & 7859.635 & -      & -     & $\frac{lbm}{s}$ \\
         \hline
-        variables   & $x_{H2O,TOC}$         & 0.066   & 0.0    & -     & -               \\
-                    & $x_{H2O,RTO}$         & 0.0     & 0.0    & -     & -               \\
-                    & $x_{H2O,SLS}$         & 0.0     & 0.0    & -     & -               \\
-                    & $x_{H2O,CRZ}$         & 0.17    & 0.0    & 0.17  & -               \\
-                    & $PR_{fan,TOC}$        & 1.291   & 1.2    & 1.4   & -               \\
+        variables   & $x_{H2O,CRZ}$         & 0.17     & 0.0    & 0.17  & -               \\
+                    & $PR_{fan,TOC}$        & 1.297    & 1.2    & 1.4   & -               \\
                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 55.132  & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.927   & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3204.07 & -      & -     & $^\circ$R       \\
+                    & $PR_{OPR,TOC}$        & 61.952   & 40.0   & 70.0  & -               \\
+                    & $T_{4,TOC}/T_{4,RTO}$ & 0.916    & 0.8    & 0.95  & -               \\
+                    & $T_{4,RTO}$           & 3204.071 & -      & -     & $^\circ$R       \\
                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
@@
 
+The breakdown of thrust for each point is shown in Table \ref{tab:thrust}.
+This table shows the resulting net thrust, gross thrust, and ram drag of each engine design for the four optimizations performed.
+
 % Thrust splits
-% TODO PA - PA: Add thrust splits for each opt
+% [x] TODO: PA-PA: Add thrust splits for each opt
+\begin{table}[hbt!]
+    \centering
+    \caption{Thrust breakdown for each flight operating condition.
+        The net thrust, gross thrust, and ram drag are shown for each optimization result.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l l l l}
+        Point & Parameter              & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
+        \toprule
+              & Net Thrust, \si{lbf}   & 5800.0    & 5800.0    & 5800.0  & 5800.0  \\
+        TOC   & Ram Drag, \si{lbf}     & 19623.4   & 19623.4   & 19623.4 & 19623.4 \\
+              & Gross Thrust, \si{lbf} & 25423.4   & 25423.4   & 25423.4 & 25423.4 \\
+        \hline
+              & Net Thrust, \si{lbf}   & 22800.0   & 22800.0   & 22800.0 & 22800.0 \\
+        RTO   & Ram Drag, \si{lbf}     & 17089.7   & 17043.5   & 17070.8 & 17014.6 \\
+              & Gross Thrust, \si{lbf} & 39889.7   & 39843.5   & 39870.8 & 39814.6 \\
+        \hline
+              & Net Thrust, \si{lbf}   & 28620.8   & 28620.8   & 28620.8 & 28620.8 \\
+        SLS   & Ram Drag, \si{lbf}     & 61.8      & 61.7      & 61.8    & 61.6    \\
+              & Gross Thrust, \si{lbf} & 28682.7   & 28682.5   & 28682.6 & 28682.4 \\
+        \hline
+              & Net Thrust, \si{lbf}   & 5220.0    & 5220.0    & 5220.0  & 5220.0  \\
+        CRZ   & Ram Drag, \si{lbf}     & 19194.0   & 19152.9   & 19190.3 & 19144.1 \\
+              & Gross Thrust, \si{lbf} & 24414.0   & 24372.9   & 24410.3 & 24364.1 \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:thrust}
+\end{table}
 
 % TSEC as a function of dPqP
-% NOTE: need to clean up this plot
 \begin{figure}[hbt!]
@@
 % Motivation: space to work with hydrogen, benefits of water injection, benefits of H2
-
 \section{Conclusion}

### 2023-04-30 conference-paper/main.tex
Additional comments addressed 4/30

@@
 To preserve conservation of mass, we treat the water recirculation as a nonlinear cycle that must converge before the engine calculation is physically balanced.
+In this model, we are assuming the water molelues are removed from the exhaust stream with no pressure or temperature losses.
+Additionlly, the model assumes the injected water molecules are at the same pressure and temperature as the air flow just before the HPC.
+Therefore, we are just capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
 % This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
@@
 With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.
+This is the multidisciplinary design analysis block of the model.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{N3_xdsm_full.pdf}
+    \includegraphics[width=1.0\textwidth]{N3_xdsm_full.pdf}
     \caption{
-        Full model N+3 XDSM diagram.
+        Full multidisciplinary design analysis (MDA) model N+3 XDSM diagram.
         This XDSM diagram shows the multipoint coupling between the different operation conditions and shows how the water recovery fractions are used to solve for water mass flow rates.
@@
 % NOTE: AL-PA, "We will perform" makes it seem like we haven't done the work yet.
-We performed multipoint gradient-based design optimization of the N+3 engine model considering TOC, RTO, SLS, and CRZ flight conditions.
+We performed multipoint gradient-based design optimization of the N+3 engine model considering the TOC, RTO, SLS, and CRZ flight conditions.
 % We will perform gradient-based design optimization of the engine model with the multipoint architecture that considers each of the flight conditions experienced by commercial aircraft.
@@
 
-For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is generally used since it is a represents how much fuel is burned at a given thrust level.
+For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
 However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
@@
 
-% [ ] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
+% [x] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
 \begin{figure}[!hbt]
     \centering
-    \includegraphics[width=0.75\textwidth]{N3_opt_XDSM.pdf}
+    \includegraphics[width=1.0\textwidth]{N3_opt_XDSM.pdf}
     \caption{
-        XDSM diagram of the multipoint optimization problem with constraints.
-        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and design points.}
+        XDSM diagram of the multipoint optimization problem with objective, constraints, and MDA block.
+        The XDSM diagram shows the variables and outputs within the optimization model and how each of these values is connected to the optimizer and MDA block.}
     \label{fig:N3_opt_xdsm}
@@
 % [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
-% [ ] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
+% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
 \begin{table}[hbt!]
@@
         Multipoint optimization problem definition.
-        The 4 design variables are the water recovery fractions of the core exhaust stream at each operation condition.
-        The objective function is the thrust specific energy consumption at the cruise condition with a net thrust constraint at the design point, TOC.
+        The objective function is the thrust specific energy consumption at the cruise condition.
+        The constraints are net thrust and engine diameter constraint at the design point, TOC.
     }
@@
 % AL-PA, We can make another plot for the water fractions and the dpQp study.
+% PA-AL, currently working on this plot, Matplotlib scaling between parameters is being troublesome
 \begin{table}[hbt!]
@@
 
-% Motivation: space to work with hydrogen, benefits of water injection, benefits of H2
+% Motivation: space to work with hydrogen, benefits of water injection, benefits of H2 (a lot of water, no tanks, de-mineralized water)
 \section{Conclusion}

### 2023-04-30 conference-paper/main.tex
More figure additions 4/30

@@
 The optimization problems with both types of fuel but no water recovery ran smoothly and finished with 0/1 SNOPT exit codes meaning that the optimization finished successfully and met the optimiality conditions.
-The resulting values of the optimization problem for Jet-A and hydrogen without water recovery are shown in Tables \ref{tab:res_thermo_opt_JetA} and \ref{tab:res_thermo_opt_H2}, respectively.
-Similarly, the resulting values of the optimization problem for Jet-A and hydrogen with water recovery are shown in Tables \ref{tab:res_full_opt_JetA} and \ref{tab:res_full_opt_H2}, respectively.
+The resulting values of the optimization problems is shown in Figure \ref{fig:parallel_coords}.
+% The resulting values of the optimization problem for Jet-A and hydrogen without water recovery are shown in Tables \ref{tab:res_thermo_opt_JetA} and \ref{tab:res_thermo_opt_H2}, respectively.
+% Similarly, the resulting values of the optimization problem for Jet-A and hydrogen with water recovery are shown in Tables \ref{tab:res_full_opt_JetA} and \ref{tab:res_full_opt_H2}, respectively.
 
@@
 % AL-PA, We can make another plot for the water fractions and the dpQp study.
-% PA-AL, currently working on this plot, Matplotlib scaling between parameters is being troublesome
-\begin{table}[hbt!]
+% NOTE: PA-AL, currently working on this plot, Matplotlib scaling between parameters is being troublesome. Tried using Plotly but formatting documentation is scarce.
+\begin{figure}[hbt!]
     \centering
-    \caption{Optimization results of the N+3 engine with no water recovery using Jet-A as the fuel.
-    }
-    \small
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l l}
-                    & Variable/Function     & Value    & Lower  & Upper & Units           \\
-        \toprule
-        objective   & $TSEC_{\rm{CRZ}} $    & 8186.255 & -      & -     & $\frac{lbm}{s}$ \\
-        \hline
-        variables   & $PR_{fan,TOC}$        & 1.285    & 1.2    & 1.4   & -               \\
-                    & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 61.012   & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.913    & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3220.570 & -      & -     & $^\circ$R       \\
-                    & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-        \hline
-        constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-        \bottomrule
-    \end{tabular}
-    \label{tab:res_thermo_opt_JetA}
-\end{table}
+    \includegraphics[width=0.8\textwidth]{N3_parallel_coords.pdf}
+    \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
+        The red lines show Jet-A fuel and the blue lines show H2 fuel.
+        The solid lines show the models without water recovery and the dashed lines show the models with water recovery.}
+    \label{fig:parallel_coords}
+\end{figure}
 
-\begin{table}[hbt!]
-    \centering
-    \caption{Optimization results of the N+3 engine with no water recovery using hydrogen as the fuel.
-    }
-    \small
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l l}
-                    & Variable/Function     & Value    & Lower  & Upper & Units           \\
-        \toprule
-        objective   & $TSEC_{\rm{CRZ}} $    & 8295.236 & -      & -     & $\frac{lbm}{s}$ \\
-        \hline
-        variables   & $PR_{fan,TOC}$        & 1.288    & 1.2    & 1.4   & -               \\
-                    & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 60.660   & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.918    & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3204.07  & -      & -     & $^\circ$R       \\
-                    & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-        \hline
-        constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-        \bottomrule
-    \end{tabular}
-    \label{tab:res_thermo_opt_H2}
-\end{table}
+% \begin{table}[hbt!]
+%     \centering
+%     \caption{Optimization results of the N+3 engine with no water recovery using Jet-A as the fuel.
+%     }
+%     \small
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{r l l l l l}
+%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
+%         \toprule
+%         objective   & $TSEC_{\rm{CRZ}} $    & 8186.255 & -      & -     & $\frac{lbm}{s}$ \\
+%         \hline
+%         variables   & $PR_{fan,TOC}$        & 1.285    & 1.2    & 1.4   & -               \\
+%                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
+%                     & $PR_{OPR,TOC}$        & 61.012   & 40.0   & 70.0  & -               \\
+%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.913    & 0.8    & 0.95  & -               \\
+%                     & $T_{4,RTO}$           & 3220.570 & -      & -     & $^\circ$R       \\
+%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
+%         \hline
+%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
+%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
+%         \bottomrule
+%     \end{tabular}
+%     \label{tab:res_thermo_opt_JetA}
+% \end{table}
 
-\begin{table}[hbt!]
-    \centering
-    \caption{Optimization results of the N+3 engine with water recovery using Jet-A as the fuel.
-    }
-    \small
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l l}
-                    & Variable/Function     & Value    & Lower  & Upper & Units           \\
-        \toprule
-        objective   & $TSEC_{\rm{CRZ}} $    & 7766.339 & -      & -     & $\frac{lbm}{s}$ \\
-        \hline
-        variables   & $x_{H2O,CRZ}$         & 0.3      & 0.0    & 0.3   & -               \\
-                    & $PR_{fan,TOC}$        & 1.292    & 1.2    & 1.4   & -               \\
-                    & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 61.188   & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.911    & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3220.574 & -      & -     & $^\circ$R       \\
-                    & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-        \hline
-        constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-        \bottomrule
-    \end{tabular}
-    \label{tab:res_full_opt_JetA}
-\end{table}
+% \begin{table}[hbt!]
+%     \centering
+%     \caption{Optimization results of the N+3 engine with no water recovery using hydrogen as the fuel.
+%     }
+%     \small
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{r l l l l l}
+%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
+%         \toprule
+%         objective   & $TSEC_{\rm{CRZ}} $    & 8295.236 & -      & -     & $\frac{lbm}{s}$ \\
+%         \hline
+%         variables   & $PR_{fan,TOC}$        & 1.288    & 1.2    & 1.4   & -               \\
+%                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
+%                     & $PR_{OPR,TOC}$        & 60.660   & 40.0   & 70.0  & -               \\
+%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.918    & 0.8    & 0.95  & -               \\
+%                     & $T_{4,RTO}$           & 3204.07  & -      & -     & $^\circ$R       \\
+%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
+%         \hline
+%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
+%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
+%         \bottomrule
+%     \end{tabular}
+%     \label{tab:res_thermo_opt_H2}
+% \end{table}
 
-\begin{table}[hbt!]
-    \centering
-    \caption{Optimization results of the N+3 engine with water recovery using hydrogen as the fuel.
-    }
-    \small
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l l}
-                    & Variable/Function     & Value    & Lower  & Upper & Units           \\
-        \toprule
-        objective   & $TSEC_{\rm{CRZ}} $    & 7859.635 & -      & -     & $\frac{lbm}{s}$ \\
-        \hline
-        variables   & $x_{H2O,CRZ}$         & 0.17     & 0.0    & 0.17  & -               \\
-                    & $PR_{fan,TOC}$        & 1.297    & 1.2    & 1.4   & -               \\
-                    & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-                    & $PR_{OPR,TOC}$        & 61.952   & 40.0   & 70.0  & -               \\
-                    & $T_{4,TOC}/T_{4,RTO}$ & 0.916    & 0.8    & 0.95  & -               \\
-                    & $T_{4,RTO}$           & 3204.071 & -      & -     & $^\circ$R       \\
-                    & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-        \hline
-        constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-                    & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-        \bottomrule
-    \end{tabular}
-    \label{tab:res_full_opt_H2}
-\end{table}
+% \begin{table}[hbt!]
+%     \centering
+%     \caption{Optimization results of the N+3 engine with water recovery using Jet-A as the fuel.
+%     }
+%     \small
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{r l l l l l}
+%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
+%         \toprule
+%         objective   & $TSEC_{\rm{CRZ}} $    & 7766.339 & -      & -     & $\frac{lbm}{s}$ \\
+%         \hline
+%         variables   & $x_{H2O,CRZ}$         & 0.3      & 0.0    & 0.3   & -               \\
+%                     & $PR_{fan,TOC}$        & 1.292    & 1.2    & 1.4   & -               \\
+%                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
+%                     & $PR_{OPR,TOC}$        & 61.188   & 40.0   & 70.0  & -               \\
+%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.911    & 0.8    & 0.95  & -               \\
+%                     & $T_{4,RTO}$           & 3220.574 & -      & -     & $^\circ$R       \\
+%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
+%         \hline
+%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
+%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
+%         \bottomrule
+%     \end{tabular}
+%     \label{tab:res_full_opt_JetA}
+% \end{table}
+
+% \begin{table}[hbt!]
+%     \centering
+%     \caption{Optimization results of the N+3 engine with water recovery using hydrogen as the fuel.
+%     }
+%     \small
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{r l l l l l}
+%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
+%         \toprule
+%         objective   & $TSEC_{\rm{CRZ}} $    & 7859.635 & -      & -     & $\frac{lbm}{s}$ \\
+%         \hline
+%         variables   & $x_{H2O,CRZ}$         & 0.17     & 0.0    & 0.17  & -               \\
+%                     & $PR_{fan,TOC}$        & 1.297    & 1.2    & 1.4   & -               \\
+%                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
+%                     & $PR_{OPR,TOC}$        & 61.952   & 40.0   & 70.0  & -               \\
+%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.916    & 0.8    & 0.95  & -               \\
+%                     & $T_{4,RTO}$           & 3204.071 & -      & -     & $^\circ$R       \\
+%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
+%         \hline
+%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
+%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
+%         \bottomrule
+%     \end{tabular}
+%     \label{tab:res_full_opt_H2}
+% \end{table}
 
@@
 
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
+    }
+    \label{fig:dpqp_wdot}
+\end{figure}
+
 % Motivation: space to work with hydrogen, benefits of water injection, benefits of H2 (a lot of water, no tanks, de-mineralized water)

### 2023-04-30 conference-paper/main.tex
Updated parallel coords plot
Finished initial results section draft

@@
 % ==================================================
-% [ ] TODO: AL-PA, Need to add equation labels
+% [x] TODO: AL-PA, Need to add equation labels
 % [ ] TODO: AL-PA, When you are citing things you should include a "~" to link the citation to the text.  i.e, "OpenMDAO~\cite{Gray2019a}" (See my edits in the introduction)
 % [ ] TODO: AL-PA, You should also use the "~" to link all equation, figure, and table references to the text.
-% [ ] TODO: AL-PA, Make sure all acronyms and subscripts that are longer than a single letter or represent words are shown as text using \rm{} in math mode
+% [x] TODO: AL-PA, Make sure all acronyms and subscripts that are longer than a single letter or represent words are shown as text using \rm{} in math mode
 
@@
 Additionlly, the model assumes the injected water molecules are at the same pressure and temperature as the air flow just before the HPC.
-Therefore, we are just capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
+Therefore, we are capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
 % This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
@@
         \hline
-        minimize        & $TSEC_{\rm{CRZ}} $             & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
+        minimize        & $\rm{TSEC}_{\rm{CRZ}} $        & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
                         &                                &                                                                       &                &          \\
@@
 
-Our comparison metric is $TSEC$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+Our comparison metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
 Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.
@@
 Since these two variables are at odds with each other and the upper limit for $X_{\rm{H2O,CRZ}}$ is where the model breaks, $T4_{RTO}$ was set as the optimal value from the optimizations with no water recirulation.
+The upper bound on $X_{\rm{H2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
 
-The 4 optimizations mentioned in the optimation problem section were run and solved.
+% Results of optimization problems
+The 4 optimizations mentioned in the section \ref{sec:optprob} were run and solved.
 The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_summary}.
 
-% Feasibility, Optimality, Merit Func history
+% Feasibility, Optimality, Merit history
 \begin{figure}[hbt!]
@@
 From this plot we can visually check that each optimization achieved optimality and feasibility, and that the merit function reached a steady-state value.
+Indeed, we see quadratic convergence in the optimiality of the problem near the optimal solution as expected.
+The design variable history for each optmization problem is shown in Figure \ref{fig:history_dvs}.
 
@@
 
+From this figure we see that the design variables start at their initial value and converge toward their optimal value.
+Note that the $RTO_{T4}$ variables are only present for the optimzations without water recovery and the $X_{\rm{H2O,CRZ}}$ variables are present only for the optimizations with water recovery.
+The constraint history for each optmization problem is shown in Figure \ref{fig:history_cons}.
+
 % Constraint history
@@
 
-% Results of optimization problems
-The optimization problems with both types of fuel but no water recovery ran smoothly and finished with 0/1 SNOPT exit codes meaning that the optimization finished successfully and met the optimiality conditions.
-The resulting values of the optimization problems is shown in Figure \ref{fig:parallel_coords}.
+From this figure we can see that the constraints are quickly satisfied and for the most part remain feasible for the duration of the optimization.
+The resulting optimal values from the optimization problems are shown in Figure \ref{fig:parallel_coords} on a parallel coordinate plot.
 % The resulting values of the optimization problem for Jet-A and hydrogen without water recovery are shown in Tables \ref{tab:res_thermo_opt_JetA} and \ref{tab:res_thermo_opt_H2}, respectively.
@@
 \end{figure}
+
+We can see that the resulting engine designs are all very similar.
+The main differences in the engine designs are the pressure ratios and temperatures.
+Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
+Given that more water is present in the exhaust stream of the H2 engine, the H2 engine can recover a smaller fraction of the water compared to the Jet-A engine.
+The water recovery flow rates for the Jet-A and H2 engines was 0.324 $\si{lbm/s}$ and 0.405 $\si{lbm/s}$, respectively.
+Therefore, the H2 has the benefit of being able to recover more water at a lower fraction of the overall core exhaust stream water.
+With water recovery, we see slightly higher pressure ratios across the fan and overall pressure ratio while the LPC pressure ratio is pushed to its technological upperbound.
+We only see differences in $RTO_{T4}$ without water recovery due to these values are fixed for water recovery.
+The $RTO_{T4}$ value for Jet-A is slightly higher than that of H2.
+Furthermore, adding water recovery slightly decreases the $T_{4,\rm{ratio}}$ value.
+Therefore, temperatures at cooler with the H2 fuel and barely cooler when adding water recovery.
+Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
+Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water injection.
+In fact, we can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure \ref{fig:barchart}.
 
@@
 
+Based on this analysis and model, we see an improvement greater than 5\% at CRZ for TSEC for both fuels.
+This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
+Due to the relatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser.
+This would incure larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
+Therefore, H2 is a much more appealing fuel to use with the proposed closed-loop water recovery system.
+Since no large-scale water condensers have been designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
+Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
+pyCycle handles pressure loss in a duct by specifyign a pressure loss coefficient, dPqP.
+This coefficient is the ratio of change in pressure to the inlet pressure of the engine duct.
+The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
+Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to no water recovery.
+
+% TSEC as a function of dPqP
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
+        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
+    \label{fig:dpqp_sweep}
+\end{figure}
+
+From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
+This model will offer efficiency benefits up until about $dPqP = 0.16$ which means a 16\% loss of pressure from the condenser.
+Furthermore, Figure \ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
+        The engine was optimized with the water recovery upperbound of 17\%.
+    }
+    \label{fig:dpqp_wdot}
+\end{figure}
+
+This figure shows that the optimizer finds designs that increase the available water in the core stream.
+Since the water recovery fraction is always pushed to 17\%, the water recovered is increased to overcome the pressure loss.
+This effect helps the engine increase the benefit area in Figure \ref{fig:dpqp_sweep}.
+
 The breakdown of thrust for each point is shown in Table \ref{tab:thrust}.
@@
 
-% TSEC as a function of dPqP
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
-    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
-        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
-    \label{fig:dpqp_sweep}
-\end{figure}
-
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
-    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
-    }
-    \label{fig:dpqp_wdot}
-\end{figure}
+% NOTE: PA-AL, any other plots to include?
 

### 2023-05-01 conference-paper/main.tex
Updated figures and citations

@@
 % We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
-% [ ] TODO: PA-PA, add section about MAUD and cite.
+% [x] TODO: PA-PA, add section about MAUD and cite.
 
@@
 % [ ] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
-Water recirculation is the process of extracting water from the exhaust stream of a propulsion system and injecting it upstream of the combustor as finely atomized droplets.
+Water injection is the process of injecting water upstream of the combustor as finely atomized droplets.
 NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{Daggett2010}.
-Additionally, water recirculation improves fuel efficiency and thrust output with lower combustion temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{Daggett2010}.
-% [ ] TODO: AL-PA, Should try to find a citation for this if one exists.
-Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft because they do not produce enough in the exhaust for recirculation.
+Additionally, water injection improves fuel efficiency and thrust output with lower combustion temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{Daggett2010}.
+% [x] TODO: AL-PA, Should try to find a citation for this if one exists.
+Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft for water injection~\cite{Mourouzidis2015}.
 The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-The main product of hydrogen combustion is water vapor and can thus be recovered from the exhaust stream.
-Recirculating water vapor from the exhaust of hydrogen combustion reduces the requirement for storage tanks and allows for the creation of a closed loop system inside the propulsion cycle.
+The main product of hydrogen combustion is water vapor and can thus be recovered from the exhaust stream~\cite{Strom2002}.
+Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it elimiates the requirement for storage tanks.
+This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
+Indeed, the aerospace industry is starting to look into this technology to make hydrogen-powered aircraft economical~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}{}.
 
@@
 pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to enable gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
+OpenMDAO provides a framework for computing coupled derivatives efficiently using the modular analysis and unified derivatives (MAUD) architecture which supports a large number of design variables~\cite{Hwang2018a}.
 
@@
 
-The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
+The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
 Only the water recovery fraction at CRZ is a design variable since we are optimizing $TSEC_{\rm{CRZ}}$.
@@
                         &                                &                                                                       &                &          \\
-        with respect to & $X_{\rm{H2O,CRZ}}$             & Water recovery fraction at CRZ                                        & -              & 1        \\
+        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery fraction at CRZ                                        & -              & 1        \\
                         & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                & -              & 1        \\
@@
 
-Our comparison metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
+Our fuel performance metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
 Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.
 
-When $T4_{RTO}$ and $X_{\rm{H2O,CRZ}}$ are design variables at the same time it was found that the optimizer pushes $T4_{RTO}$ down and $X_{\rm{H2O,CRZ}}$ up.
-Since these two variables are at odds with each other and the upper limit for $X_{\rm{H2O,CRZ}}$ is where the model breaks, $T4_{RTO}$ was set as the optimal value from the optimizations with no water recirulation.
-The upper bound on $X_{\rm{H2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
+When $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time it was found that the optimizer pushes $T_{4,\rm{RTO}}$ down and $X_{\rm{H_2O,CRZ}}$ up.
+Since these two variables are at odds with each other and the upper limit for $X_{\rm{H_2O,CRZ}}$ is where the model breaks, $T_{4,\rm{RTO}}$ was set as the optimal value from the optimizations with no water recirulation.
+The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
 
@@
 
-From this figure we see that the design variables start at their initial value and converge toward their optimal value.
-Note that the $RTO_{T4}$ variables are only present for the optimzations without water recovery and the $X_{\rm{H2O,CRZ}}$ variables are present only for the optimizations with water recovery.
+From this figure we see that the design variables start at the initial values and converge toward their optimal value.
+Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimzations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
 The constraint history for each optmization problem is shown in Figure \ref{fig:history_cons}.
@@
 % NOTE: PA - PA/AL replace this with a parallel axis plot?
-% [ ] TODO: AL-PA, Yeah let's do the parallel axis plot for the basic thermodynamic parameters
+% [x] TODO: AL-PA, Yeah let's do the parallel axis plot for the basic thermodynamic parameters
 % AL-PA, We can make another plot for the water fractions and the dpQp study.
-% NOTE: PA-AL, currently working on this plot, Matplotlib scaling between parameters is being troublesome. Tried using Plotly but formatting documentation is scarce.
 \begin{figure}[hbt!]
     \centering
-    \includegraphics[width=0.8\textwidth]{N3_parallel_coords.pdf}
+    \includegraphics[width=1.0\textwidth]{N3_parallel_coords.pdf}
     \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
         The red lines show Jet-A fuel and the blue lines show H2 fuel.
-        The solid lines show the models without water recovery and the dashed lines show the models with water recovery.}
+        The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.}
     \label{fig:parallel_coords}
@@
 With water recovery, we see slightly higher pressure ratios across the fan and overall pressure ratio while the LPC pressure ratio is pushed to its technological upperbound.
-We only see differences in $RTO_{T4}$ without water recovery due to these values are fixed for water recovery.
-The $RTO_{T4}$ value for Jet-A is slightly higher than that of H2.
+We only see differences in $T_{4,\rm{RTO}}$ without water recovery due to these values are fixed for water recovery.
+The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of H2.
 Furthermore, adding water recovery slightly decreases the $T_{4,\rm{ratio}}$ value.
@@
 In fact, we can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure \ref{fig:barchart}.
-
-% \begin{table}[hbt!]
-%     \centering
-%     \caption{Optimization results of the N+3 engine with no water recovery using Jet-A as the fuel.
-%     }
-%     \small
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}{r l l l l l}
-%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
-%         \toprule
-%         objective   & $TSEC_{\rm{CRZ}} $    & 8186.255 & -      & -     & $\frac{lbm}{s}$ \\
-%         \hline
-%         variables   & $PR_{fan,TOC}$        & 1.285    & 1.2    & 1.4   & -               \\
-%                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-%                     & $PR_{OPR,TOC}$        & 61.012   & 40.0   & 70.0  & -               \\
-%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.913    & 0.8    & 0.95  & -               \\
-%                     & $T_{4,RTO}$           & 3220.570 & -      & -     & $^\circ$R       \\
-%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-%         \hline
-%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-%         \bottomrule
-%     \end{tabular}
-%     \label{tab:res_thermo_opt_JetA}
-% \end{table}
-
-% \begin{table}[hbt!]
-%     \centering
-%     \caption{Optimization results of the N+3 engine with no water recovery using hydrogen as the fuel.
-%     }
-%     \small
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}{r l l l l l}
-%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
-%         \toprule
-%         objective   & $TSEC_{\rm{CRZ}} $    & 8295.236 & -      & -     & $\frac{lbm}{s}$ \\
-%         \hline
-%         variables   & $PR_{fan,TOC}$        & 1.288    & 1.2    & 1.4   & -               \\
-%                     & $PR_{LPC,TOC}$        & 4.000    & 2.5    & 4.0   & -               \\
-%                     & $PR_{OPR,TOC}$        & 60.660   & 40.0   & 70.0  & -               \\
-%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.918    & 0.8    & 0.95  & -               \\
-%                     & $T_{4,RTO}$           & 3204.07  & -      & -     & $^\circ$R       \\
-%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-%         \hline
-%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-%         \bottomrule
-%     \end{tabular}
-%     \label{tab:res_thermo_opt_H2}
-% \end{table}
-
-% \begin{table}[hbt!]
-%     \centering
-%     \caption{Optimization results of the N+3 engine with water recovery using Jet-A as the fuel.
-%     }
-%     \small
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}{r l l l l l}
-%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
-%         \toprule
-%         objective   & $TSEC_{\rm{CRZ}} $    & 7766.339 & -      & -     & $\frac{lbm}{s}$ \\
-%         \hline
-%         variables   & $x_{H2O,CRZ}$         & 0.3      & 0.0    & 0.3   & -               \\
-%                     & $PR_{fan,TOC}$        & 1.292    & 1.2    & 1.4   & -               \\
-%                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-%                     & $PR_{OPR,TOC}$        & 61.188   & 40.0   & 70.0  & -               \\
-%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.911    & 0.8    & 0.95  & -               \\
-%                     & $T_{4,RTO}$           & 3220.574 & -      & -     & $^\circ$R       \\
-%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-%         \hline
-%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-%         \bottomrule
-%     \end{tabular}
-%     \label{tab:res_full_opt_JetA}
-% \end{table}
-
-% \begin{table}[hbt!]
-%     \centering
-%     \caption{Optimization results of the N+3 engine with water recovery using hydrogen as the fuel.
-%     }
-%     \small
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}{r l l l l l}
-%                     & Variable/Function     & Value    & Lower  & Upper & Units           \\
-%         \toprule
-%         objective   & $TSEC_{\rm{CRZ}} $    & 7859.635 & -      & -     & $\frac{lbm}{s}$ \\
-%         \hline
-%         variables   & $x_{H2O,CRZ}$         & 0.17     & 0.0    & 0.17  & -               \\
-%                     & $PR_{fan,TOC}$        & 1.297    & 1.2    & 1.4   & -               \\
-%                     & $PR_{LPC,TOC}$        & 4.0      & 2.5    & 4.0   & -               \\
-%                     & $PR_{OPR,TOC}$        & 61.952   & 40.0   & 70.0  & -               \\
-%                     & $T_{4,TOC}/T_{4,RTO}$ & 0.916    & 0.8    & 0.95  & -               \\
-%                     & $T_{4,RTO}$           & 3204.071 & -      & -     & $^\circ$R       \\
-%                     & $V_{ratio,CRZ}$       & 1.35     & 1.35   & 1.45  &                 \\
-%         \hline
-%         constraints & $F_{net,TOC}$         & 5800.0   & 5800.0 & -     & lbf             \\
-%                     & $D_{Fan}$             & 100.0    & -      & 100   & $in^2$          \\
-%         \bottomrule
-%     \end{tabular}
-%     \label{tab:res_full_opt_H2}
-% \end{table}
 
@@
 This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
-Due to the relatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser.
+Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser~\cite{Strom2002}.
 This would incure larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
@@
 Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
-pyCycle handles pressure loss in a duct by specifyign a pressure loss coefficient, dPqP.
-This coefficient is the ratio of change in pressure to the inlet pressure of the engine duct.
+pyCycle handles pressure losses in ducts by specifyign a pressure loss coefficient, dPqP.
+This coefficient is the ratio of change in pressure normalized by the inlet pressure of the duct.
 The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
-Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to no water recovery.
+Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
 
@@
 From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
-This model will offer efficiency benefits up until about $dPqP = 0.16$ which means a 16\% loss of pressure from the condenser.
+This model will offer efficiency benefits up until about $\rm{dPqP} = 0.16$ which means a 16\% loss of pressure from the condenser.
 Furthermore, Figure \ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.

### 2023-05-01 conference-paper/main.tex
Added conclusion, other minor changes

@@
 This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
-Indeed, the aerospace industry is starting to look into this technology to make hydrogen-powered aircraft economical~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}{}.
+Indeed, the aerospace industry is starting to look into this technology to make hydrogen-powered aircraft economical~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}.
 
@@
 % [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
+% [ ] TODO: PA-PA, explain variable ranges
 \begin{table}[hbt!]
@@
     \label{tab:opt_problem}
+\end{table}
+
+\begin{table}[hbt!]
+    \centering
+    \caption{Design variable ranges for the optimization problem.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{l l l l}
+        Design Variable       & Lower  & Upper  & Units     \\
+        \toprule
+        $x_{H2O,CRZ}$         & 0.0    & -      & -         \\
+        $PR_{fan,TOC}$        & 1.2    & 1.4    & -         \\
+        $PR_{LPC,TOC}$        & 2.5    & 4.0    & -         \\
+        $PR_{OPR,TOC}$        & 40.0   & 70.0   & -         \\
+        $T_{4,TOC}/T_{4,RTO}$ & 0.5    & 0.95   & -         \\
+        $T_{4,RTO}$           & 3000.0 & 3600.0 & $^\circ$R \\
+        $V_{ratio,CRZ}$       & 1.35   & 1.45   &           \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:res_full_opt_H2}
 \end{table}
@@
 From this plot we can visually check that each optimization achieved optimality and feasibility, and that the merit function reached a steady-state value.
-Indeed, we see quadratic convergence in the optimiality of the problem near the optimal solution as expected.
+Indeed, we observe quadratic convergence in the optimiality of the problem near the optimal solution as expected.
 The design variable history for each optmization problem is shown in Figure \ref{fig:history_dvs}.
@@
 
-% NOTE: PA - PA/AL replace this with a parallel axis plot?
+% NOTE: PA-PA/AL replace this with a parallel axis plot?
 % [x] TODO: AL-PA, Yeah let's do the parallel axis plot for the basic thermodynamic parameters
@@
 Furthermore, adding water recovery slightly decreases the $T_{4,\rm{ratio}}$ value.
-Therefore, temperatures at cooler with the H2 fuel and barely cooler when adding water recovery.
-Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
-Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water injection.
-In fact, we can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure \ref{fig:barchart}.
-
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{JetA-H2_TSEC_diff.pdf}
-    \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
-        This plot compares the relative improvement of the two optimziation problems with water recovery compared to the optimzation problems without water recovery.}
-    \label{fig:barchart}
-\end{figure}
-
-Based on this analysis and model, we see an improvement greater than 5\% at CRZ for TSEC for both fuels.
-This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
-Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser~\cite{Strom2002}.
-This would incure larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
-Therefore, H2 is a much more appealing fuel to use with the proposed closed-loop water recovery system.
-Since no large-scale water condensers have been designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
-Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
-pyCycle handles pressure losses in ducts by specifyign a pressure loss coefficient, dPqP.
-This coefficient is the ratio of change in pressure normalized by the inlet pressure of the duct.
-The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
-Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
-
-% TSEC as a function of dPqP
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
-    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
-        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
-    \label{fig:dpqp_sweep}
-\end{figure}
-
-From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
-This model will offer efficiency benefits up until about $\rm{dPqP} = 0.16$ which means a 16\% loss of pressure from the condenser.
-Furthermore, Figure \ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
-
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
-    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
-        The engine was optimized with the water recovery upperbound of 17\%.
-    }
-    \label{fig:dpqp_wdot}
-\end{figure}
-
-This figure shows that the optimizer finds designs that increase the available water in the core stream.
-Since the water recovery fraction is always pushed to 17\%, the water recovered is increased to overcome the pressure loss.
-This effect helps the engine increase the benefit area in Figure \ref{fig:dpqp_sweep}.
-
+Therefore, temperatures are cooler with the H2 fuel and even slightly cooler when adding water recovery.
+It is noted that with more water recovery the farther the optimizer would push the value of $T_{4,\rm{RTO}}$ down.
+Therefore, there are temperature-related advantages of using water recovery to maintain a certain effenciency and thrust.
 The breakdown of thrust for each point is shown in Table \ref{tab:thrust}.
@@
 
+From this table we can see that the net thrust is constrained at values set by \emph{balance} components or optimization constraints.
+We see the largest thrust differences at the RTO and CRZ points.
+Since net thrust is constrainted, the optimizer sizes the engine to reduce ram drag slightly from Jet-A to H2.
+Water recirculation provides an even more significant improvement in ram drag for both Jet-A and H2 at CRZ with reductions of 0.21\% and 0.24\%, respectively.
+Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
+Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water injection.
+In fact, we can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure \ref{fig:barchart}.
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{JetA-H2_TSEC_diff.pdf}
+    \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
+        This plot compares the relative improvement of the two optimziation problems with water recovery compared to the optimzation problems without water recovery.}
+    \label{fig:barchart}
+\end{figure}
+
+Based on this analysis and model, we see an improvement greater than 5\% at CRZ for TSEC for both fuels.
+This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
+Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser~\cite{Strom2002}.
+This would incure larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
+Therefore, H2 is a much more appealing fuel to use with the proposed closed-loop water recovery system.
+Since there a lack of literature on large-scale water condensers that are designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
+Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
+pyCycle handles pressure losses in ducts by specifyign a pressure loss coefficient, dPqP.
+This coefficient is the ratio of change in pressure normalized by the inlet pressure of the duct.
+The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
+Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
+
+% TSEC as a function of dPqP
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
+        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
+    \label{fig:dpqp_sweep}
+\end{figure}
+
+From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
+This model will offer efficiency benefits up until about $\rm{dPqP} = 0.16$ which means a 16\% loss of pressure from the condenser.
+This benefit area would be reduced if a smaller fraction of water recovered could be obtained.
+Figure \ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
+        The engine was optimized with the water recovery upperbound of 17\%.
+    }
+    \label{fig:dpqp_wdot}
+\end{figure}
+
+This figure shows that the optimizer finds designs that increase the available water in the core stream.
+Since the water recovery fraction is always pushed to 17\%, the water recovered is increased to overcome the pressure loss.
+This effect helps the engine increase the benefit area in Figure \ref{fig:dpqp_sweep}.
+
 % NOTE: PA-AL, any other plots to include?
@@
 \label{sec:conc}
-% Message 1: Re-state the problem
-% Message 2: Summarize the HBTF model
-% Message 3: Expected results
+In this paper, we describe a how a novel closed-loop water recirculation system would be integrated in a commercial aviation setting.
+The water recirculation system comprised was designed and implemented into the N+3 ultra-high bypass engine model.
+We have presented the results of four optimization problems demonstrating the use of this technology using the pyCycle cycle modeling tool for Jet-A and hydrogen fuel.
+
+The recirculation system is implemented by introducing two new custom pyCycle components, the water extractor and injector, which form a continuous closed-loop feedback water flow in the engine.
+We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
+System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
+The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, presusres and velocities within the engine.
+An additional design variable controlling how much water is recirulated is added at the CRZ point to improve the fuel burn.
+
+The results from the optimization problems show temperature, thrust, and efficiency improvements when using hydrogen as a fuel with water circulation.
+Thermal reductions will improve the lifetime of the engine which impact maintanence and overall costs.
+Between the two fuels, we see similar values of TSEC.
+Significant energy efficiency gains are seen with water recirculation and injection.
+This would lead to lower operating costs over the lifetime of the engine.
+
+Technological problems do exist such as how to design a condensor that can recover a large portion of the exhaust water without large pressure losses.
+However, the thermal properties of hydrogen provide a heat sink and thus a readily available resource for condensation.
+Furthermore, using the exhaust stream to heat the hydrogen fuel has been proposed as an additional avenue to improve engine efficiency%~\cite{}.
+The results from this work outline the working space available for the design of such a condenser.
+% heavier engine due to condensor, but less fuel needed
 

### 2023-05-01 conference-paper/main.tex
Adding more feedback

@@
 The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
-N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) engines with small cores and high overall pressure ratios (OPR).
+N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR).
 Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
 Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
-However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
+However, hydrogen is a versatile fuel with advantageous molecular and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
 We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
@@
 % [ ] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
-Water injection is the process of injecting water upstream of the combustor as finely atomized droplets.
+Water injection is the process of introducing water upstream of the combustor as finely atomized droplets.
 NASA, Boeing, and Rolls-Royce studied this concept and suggested that this technique reduces the NOx emissions as much as 47 percent~\cite{Daggett2010}.
@@
 The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-The main product of hydrogen combustion is water vapor and can thus be recovered from the exhaust stream~\cite{Strom2002}.
-Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it elimiates the requirement for storage tanks.
+The main product of hydrogen combustion is water vapor that we can recover from the exhaust stream~\cite{Strom2002}.
+Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
 This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
-Indeed, the aerospace industry is starting to look into this technology to make hydrogen-powered aircraft economical~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}.
+Pratt and Whitney are actively researching this technology to improve the feasibility of hydrogen-powered propulsion~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}.
 
@@
 NPSS is a modular object-oriented library that models engine components as individual blocks with several thermodynamic solvers.
-\citet{Hendricks2019} created a new tool called pyCycle with the same functionality as NPSS with analytical derivatives for each engine component and thermodynamic solver~\cite{Gray2017b}.
+\citet{Hendricks2019} created a new tool called pyCycle with the same functionality as NPSS with analytical derivatives~\cite{Gray2017b}.
 pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to enable gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
-OpenMDAO provides a framework for computing coupled derivatives efficiently using the modular analysis and unified derivatives (MAUD) architecture which supports a large number of design variables~\cite{Hwang2018a}.
+% NOTE: AL-PA, I removed the MAUD sentence because it's a wormhole that you probably don't want to enter lol.
+% OpenMDAO provides a framework for computing coupled derivatives efficiently using the modular analysis and unified derivatives (MAUD) architecture which supports a large number of design variables~\cite{Hwang2018a}.
 
@@
 The UHB turbofan model is the NASA advanced technology "N+3" engine \cite{Jones2017a}.
-The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
+The N+3 reference cycle is a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
 % We selected the N+3 model because it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
@@
 The low pressure system is split into two mechanical subsystems.
-First, the fan is connected to the gearbox that reduces the shaft speed to decrease the fan tip speeds.
+First, the fan is connected to the gearbox that reduces the shaft speed to decrease fan tip speeds.
 Second, the gearbox attaches to the low-pressure shaft that connects to the low-pressure compressor (LPC) and low-pressure turbine (LPT).
@@
 The high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
+% [ ] TODO: AL-PA, I think we need to reference the engine diagram figure here so the reader can visualize all this text.
 
@@
 % Thermodynamic equations of state are solved using CEA at the interface between components, shown as black arrows in Figure~\ref{fig:n3_cycle}.
-We introduce the closed-loop water recovery system as a feedback loop that transports water from the exhaust to upstream of the compressors.
+We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to upstream of the compressors.
 % The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
@@
 The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycle it back to the injector.
+% [ ] TODO: AL-PA, Again, probably should reference a figure to give context to the water recovery layout.
 % NOTE: AL-PA, don't discredit your work before you even explain the model and methods.  We can make this point in the results or conclusion.
@@
 % Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.
-
-\subsection{Propulsion Model}
-The N+3 model is implemented in pyCycle~\cite{Hendricks2019}, a zero-dimensional thermodynamic cycle modeling library with analytical gradients.
-Zero-dimensional models are a collection of components that combine to form a unified thermodynamic cycle.
-The N+3 UHB geared turbofan model consists of twenty-five different elements that define the flow path and the mechanical systems.
-Thermodynamic quantities are solved and exchanged using CEA at flow path boundaries represented by black arrows between blue flow path components in Figure~\ref{fig:N3_original}.
-The fan, gearbox, low pressure, and high pressure systems are connected by three mechanical shafts depicted in red in Figure~\ref{fig:N3_original}.
-
-% Three mechanical shafts, depicted in red in Figure~\ref{fig:N3_original}, connect the fan, low pressure, and high pressure systems.
-
-We impose \emph{balance} equations on the cycle to satisfy the physical governing equations, conservation laws, and design rules.
-\emph{Balance} relationships are formulated as equations in the form $r(u)=0$ where $r$ is a residual function and $u$ is an implicit state variable.
-We use Newton based solvers to find the value of the state variables that drive the set of balance residuals to zero.
-\citeauthor{Hendricks2019} provide the balance equations for the N+3 engine model and further detail the cycle setup.
 
@@
 \subsection{Water Recovery Model}
-We implemented the closed-loop water recovery system as a feedback system that extracts water from the exhaust stream and injects it upstream of the HPC.
+We implemented the closed-loop water recovery system as a feedback cycle that extracts water from the exhaust stream and injects it upstream of the HPC.
 % The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
@@
 % This location was chosen as it was one of the configurations chosen by the aforementioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{Daggett2010}.
-The water vapor recovery component sits downstream of the LPT and extracts water from the flow before it exits the core nozzle.
+The water vapor recovery component sits downstream of the LPT and extracts water from the flow before exiting the core nozzle.
 % The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
@@
 % [x] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
-In the model of the extractor, we are assuming that a fraction of the total water available in the exhaust stream is recovered and that there are no pressure or temperature losses associated with this process.
+We assume that a fraction of the total water available in the exhaust stream is recovered and that there are no pressure or temperature losses associated with this process.
 % NOTE: AL-PA, we will talk about the condenser when we discuss the results of the pressure recovery parameter sweep.
@@
 % To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
-pyCycle provides a \texttt{wet-air} dataset that introduces $\mathrm{H_2O}$ molecules to the composition of air.
+pyCycle provides a \texttt{wet-air} dataset that introduces \ce{H2O} molecules to the composition of air.
 % The \texttt{wet-air} dataset inherits the NPSS \texttt{JANAF} data from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
 % The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
-We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of $\mathrm{H_2O}$ to air in the reactants of the inflow mixture.
+We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of \ce{H2O} to air in the reactants of the inflow mixture.
 % In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
 % The WAR is the sp of the air expressed in equal units and separating out the total mass (kg water/kg air).
+% [ ] TODO: AL-PA, Reference Table 1 with humidity values as well.
 \citet{Kalnay1996} give the humidity values for each flight condition.
@@
 % The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
-A schematic of the injector is shown in Figure \ref{fig:injector} where $Y_{H_2O}$ is the mole fraction of water molecules.
+A schematic of the injector is shown in Figure \ref{fig:injector} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules.
 
+% NOTE: AL-PA, I turned this into a subfigure to save some space
 \begin{figure}[hbt!]
     \centering
-    \includegraphics[width=0.75\textwidth]{injector.pdf}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{injector.pdf}
         \caption{
-        Injector component schematic.
             Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
@@
         \label{fig:injector}
+    \end{subfigure}
+    \hspace{2pt}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{extractor.pdf}
+        \caption{
+            We extract a fraction of the moles of water from the out flow of duct 5.
+            % A certain mole fraction of the flow coming out of duct 5 is comprised of water of which a certain specified fraction is extracted.
+            The extracted water is routed back upstream to the injector and the rest is exhausted out the nozzle.
+        }
+        \label{fig:extractor}
+    \end{subfigure}
+    % [ ] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
+    \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.}
+    \label{fig:extract_inject}
 \end{figure}
+
+% \begin{figure}[hbt!]
+%     \centering
+%     \includegraphics[width=0.75\textwidth]{injector.pdf}
+%     \caption{
+%         Injector component schematic.
+%         Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
+%     }
+%     \label{fig:injector}
+% \end{figure}
 
@@
 The CEA solver calculates the inflow composition and the extractor separates a specific species based on a mass fraction input.
-The composition of the core stream is updated to represent the remaining mixture after the extractor model removes the desired species from the incoming flow.
+The composition of the core stream is updated to represent the remaining mixture after the extractor model removes the species from the incoming flow.
 We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
@@
 % While this process certainly would have pressure loss penalties in terms of condensing water in a condenser, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensers available.
-A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where $Y_{H_2O}$ is the mole fraction of water molecules and $X_{H_2O,k}$ is the fraction of water that is recovered from the core stream.
+A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the fraction of water that is recovered from the core stream.
 
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.75\textwidth]{extractor.pdf}
-    \caption{
-        Extractor component schematic.
-        A certain mole fraction of the flow coming out of duct5 is comprised of water of which a certain specified fraction is extracted.
-        The extracted water is routed back upstream to the injector and the rest is simply exhausted out the nozzle.
-    }
-    \label{fig:extractor}
-\end{figure}
+% \begin{figure}[hbt!]
+%     \centering
+%     \includegraphics[width=0.75\textwidth]{extractor.pdf}
+%     \caption{
+%         Extractor component schematic.
+%         A certain mole fraction of the flow coming out of duct5 is comprised of water of which a certain specified fraction is extracted.
+%         The extracted water is routed back upstream to the injector and the rest is simply exhausted out the nozzle.
+%     }
+%     \label{fig:extractor}
+% \end{figure}
 
@@
 To preserve conservation of mass, we treat the water recirculation as a nonlinear cycle that must converge before the engine calculation is physically balanced.
-In this model, we are assuming the water molelues are removed from the exhaust stream with no pressure or temperature losses.
-Additionlly, the model assumes the injected water molecules are at the same pressure and temperature as the air flow just before the HPC.
-Therefore, we are capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
+In this model, we are assuming the water molecules are removed from the exhaust stream with no pressure or temperature losses.
+We also assume the injected water molecules are at the same pressure and temperature as the air flow just before the HPC.
+% NOTE: AL-PA, I removed this because I don't think the reader will understand the phase-change nuances with 0D cycle and CEA
+% Therefore, we are capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
 % This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
@@
 
-\subsection{Multipoint Model}
+\subsection{Multipoint Propulsion Model}
+The N+3 model is a collection of components that combine to form a unified zero-dimensional cycle.
+% Zero-dimensional models are a collection of components that combine to form a unified thermodynamic cycle.
+The model consists of twenty-five different elements that define the flow path and the mechanical systems.
+Thermodynamic quantities are solved and exchanged using CEA at flow path boundaries represented by black arrows between blue flow path components in Figure~\ref{fig:N3_original}.
+The fan, gearbox, low pressure, and high pressure systems are connected by three mechanical shafts depicted in red in Figure~\ref{fig:N3_original}.
+
+% Three mechanical shafts, depicted in red in Figure~\ref{fig:N3_original}, connect the fan, low pressure, and high pressure systems.
+
 % NOTE: AL-PA, I added this blurb to introduce multipoint
 We operate the engine cycle in different modes depending on the desired conservation relationships, design rules, and flight conditions.
-In ``on-design'' mode, we prescribe important cycle inputs such as turbo machinery efficiencies, pressure ratios, and combustion temperatures.
+In ``on-design'' mode, we prescribe cycle inputs such as turbo machinery efficiencies, pressure ratios, and combustion temperatures.
 The ``off-design'' mode inherits the flow path areas and turbo machinery map scalars from the ``on-design'' analysis.
-We enforce design rules as balance equations between different design points to consider the performance of the engine cycle at limiting flight conditions.
-Table \ref{flight_conds} shows the different altitudes and mach numbers at each flight condition.
 
-The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-Each flight condition is either critical to the performance or limits the design of the engine.
-% [x] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
-%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
-%   - The RTO point is limiting for temperature, etc...
-
-% [x] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
-The N+3 engine model has many complex thermodynamic and performance connections between the different operating conditions such as temperature ratios and cooling requirements.
-Therefore, the N+3 engine model computes the engine performance at the four different operating conditions in order to resolve these connections.
-% The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-% [x] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
-The SLS operating condition is important for ensuring that the turbomachinery and flow paths are designed to a meet static thrust target.
-The RTO operating condition is important for specifying the upper limit of the combustor temperature and cooling requirements for a thrust target during take-off.
-The TOC operating condition is important for specifying the required thrust during the climb at the design altitude.
-Finally, the CRZ operation condition is important for specifying that the turbomachinery and flow paths are designed to meet cruise target thrust.
-To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
-This final design must satisfies the requirements at each of these operating conditions.
-The altitude and mach number of each of the operating conditions is shown in Table \ref{flight_conds}.
+% NOTE: AL-PA, this ended up a bit choppy, but I think it's better than before.  If you want to adjust things a bit go ahead.
+We impose \emph{balance} equations to satisfy the physical governing equations, conservation laws, and design rules.
+\emph{Balance} relationships are formulated as equations in the form $r(u)=0$ where $r$ is a residual function and $u$ is an implicit state variable.
+We use Newton based solvers to find the value of the state variables that drive the set of balance residuals to zero.
+\citeauthor{Hendricks2019} provide the extensive set of balance equations with further details on the construction of the nonlinear system for the N+3 model.
+% We enforce design rules as balance equations between different flight conditions to consider the limitations on performance across the flight envelope.
+% \citeauthor{Hendricks2019} provide the balance equations for the N+3 engine model and further detail the cycle setup.
 
@@
 
+The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+Table \ref{flight_conds} shows the different altitudes and mach numbers for each flight condition.
+We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
+% [x] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
+%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
+%   - The RTO point is limiting for temperature, etc...
+% [x] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
+% The N+3 engine model has complex thermodynamic and performance connections between the different operating conditions.
+% Therefore, the N+3 engine model computes the engine performance at the four different operating conditions in order to resolve these connections.
+% The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+% [x] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
+The design rules at SLS ensure that the turbo machinery and flow paths meet the static thrust target.
+Rolling takeoff limitations constrain the upper limit of the combustor temperature and subsequently the cooling requirements of the turbines.
+The cooling mass flow rates ($\dot{m}_{\rm{cool},k}$) are passed from the RTO point to all other flight conditions creating a cyclic connection.
+We add a fuel burn objective at cruise to optimize the engine performance during the longest flight segment.
+We size the water recovery system at the CRZ condition because it has the greatest impact on fuel burn over the flight envelope.
+Similarly to $\dot{m}_{\rm{cool},k}$, the water recovery mass flow rates ($\dot{m}_{\rm{water},k}$) are connected back to the other operating points.
+The interconnections between flight conditions create a complex nonlinear loop, shown in Figure~\ref{fig:N3_xdsm_full}.
+The converged model represents a feasible multipoint engine that accounts for design considerations at all four operating conditions.
+% [ ] TODO: AL-PA, I removed a lot of stuff here to simplify this section.
+%                  - Ultimately I think we need to reference the pyCycle paper to prevent duplicating a bunch of math/text
+%                  - If you are okay with this check off this TODO.  If not feel free to add a bit more and then check it off.
+We direct the reader to the N+3 multipoint model definition in the paper by \citet{Hendricks2019} for the detailed description of the balance relationships.
+
+% To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
+% The final design must satisfies the requirements at each of these operating conditions.
+% The altitude and mach number of each of the operating conditions is shown in Table \ref{flight_conds}.
+
 % NOTE: AL-PA, Using a lot of extra words to say: "The TOC point is the on-design condition."
-The TOC point is the ``on-design'' condition since it is desireable to specify combustor temperatures and pressure ratios at this point.
+% The TOC point determines the flow path areas and turbo machinery properties.
 % NOTE: AL-PA, The design point sizes the flow paths and scales the turbo machinery.
@@
 % [x] TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
-The design point for the model sets all of the engine sizing such as areas and pressure ratios across components.
-The off-design points inherit the size of the engine in terms of the cross-sectional areas from the design point but operate at the corresponding required thrust, cooling, and environmental conditions.
+% The design point for the model sets all of the engine sizing such as areas and pressure ratios across components.
+% The off-design points inherit the cross-sectional areas and turbo machinery scalars from the design point.
 % [ ] TODO: AL-PA, We don't need to talk about the Newton or linear solver details.  Just explain the multipoint model structure with the Newton solver added for context.
@@
 % An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
-
 % [x] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
-
 % [x] TODO: AL-PA, Don't talk about the objective function until the optimization problem section.
@@
 % The cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
-We size the water recovery system at the cruise condition because it is the longest and most important phase of flight for fuel burn reduction.
-To size the areas of the injector and extractor at CRZ, we only connect the thermodynamic state variables across these components at the corresponding operating condition and set the areas of both components at the CRZ point.
-These connections are shown graphically in the XDSM diagram in Figure \ref{fig:N3_xdsm_full}.
 
@@
 % NOTE: AL-PA, You can discuss how this makes the multipoint nonlinear solution more challenging, but improves the optimization problem conditioning.
-The N+3 multipoint model has many constraints on the model that set conservation and design values using \emph{balance} components.
-A Newton solver is used to converge these conservation an design values such $r=0$.
-The conservation \emph{balance} residuals are associated with each of the three shafts at each design condition.
-The state variables that set the shaft conservation residuals are the turbomachinery pressure ratios ($PR_{Fan}$, $PR_{LPC}$, $PR_{HPC}$) at TOC and shaft speeds ($N_{Fan}$, $N_{LPC}$, $N_{HPC}$) and engine mass flow rate ($\dot{m}$) at the ``off-design'' points.
-The design constraints are also set using \emph{balance} residuals.
-For the TOC point, $T_{4}$ is set by the fuel-to-air ratio (FAR) of the burner and $OPR$ is set by $HPC_{PR}$.
-Additionally, a constraint on the turbomachinery polytropic efficiency is set based on technological assumptions.
-These TOC balance residuals are summarized in Equation \eqref{des_resid} \cite{Hendricks2019}.
+% We implement conservation and design constraints in the multipoint model using \emph{balance} residuals.
+% A Newton solver is used to converge these conservation an design values such $r=0$.
+% The conservation balances match the shaft power on the low and high-pressure systems respectively by varying the turbine pressure ratios.
+% The conservation \emph{balance} residuals are associated with each of the three shafts at each design condition.
+% The state variables that set the shaft conservation residuals are the turbomachinery pressure ratios ($PR_{Fan}$, $PR_{LPC}$, $PR_{HPC}$) at TOC and shaft speeds ($N_{Fan}$, $N_{LPC}$, $N_{HPC}$) and engine mass flow rate ($\dot{m}$) at the ``off-design'' points.
+% The design constraints are also set using \emph{balance} residuals.
+% For the TOC point, $T_{4}$ is set by the fuel-to-air ratio (FAR) of the burner and $OPR$ is set by $HPC_{PR}$.
+% Additionally, a constraint on the turbomachinery polytropic efficiency is set based on technological assumptions.
+% These TOC balance residuals are summarized in Equation \eqref{des_resid} \cite{Hendricks2019}.
 
-\begin{equation}
-    r_{des} \rightarrow
-    \begin{cases}
-        T_{4,TOC} = T_{4,des}                 \\
-        OPR_{TOC} = OPR_{des}                 \\
-        \eta_{poly,i,TOC} = \eta_{poly,i,des} \\
-    \end{cases}
-    \label{des_resid}
-\end{equation}
+% \begin{equation}
+%     r_{des} \rightarrow
+%     \begin{cases}
+%         T_{4,TOC} = T_{4,des}                 \\
+%         OPR_{TOC} = OPR_{des}                 \\
+%         \eta_{poly,i,TOC} = \eta_{poly,i,des} \\
+%     \end{cases}
+%     \label{des_resid}
+% \end{equation}
 
-The outputs for the TOC point based on these design constraints are TSFC and $F_{net}$.
-For the ``off-design'' points, the target fan stall margin is set by the bypass ratio (BPR) and target net thrust is mainly set by FAR.
-Additionally, the engine cooling mass flow rate residuals are set by cooling needs at RTO using a perscibed value.
-These ``off-design'' residuals are summarized in Equation \eqref{od_resid} \cite{Hendricks2019}.
+% The outputs for the TOC point based on these design constraints are TSFC and $F_{net}$.
+% For the ``off-design'' points, the target fan stall margin is set by the bypass ratio (BPR) and target net thrust is set by FAR.
+% Additionally, the engine cooling mass flow rate residuals are set by cooling needs at RTO using a perscibed value.
+% These ``off-design'' residuals are summarized in Equation \eqref{od_resid} \cite{Hendricks2019}.
 
-\begin{equation}
-    r_{od} \rightarrow
-    \begin{cases}
-        R_{Fan} = R_{Fan,target}      \\
-        F_{net} = F_{net,target}      \\
-        \dot{m}_{cooling, err, k} = 0 \\
-    \end{cases}
-    \label{od_resid}
-\end{equation}
+% \begin{equation}
+%     r_{od} \rightarrow
+%     \begin{cases}
+%         R_{Fan} = R_{Fan,target}      \\
+%         F_{net} = F_{net,target}      \\
+%         \dot{m}_{cooling, err, k} = 0 \\
+%     \end{cases}
+%     \label{od_resid}
+% \end{equation}
 
-Solving for all of the state and design variables while satisfying constraints could be accomplish with only an optimizer to simplify the problem.
-However, using a solver to converge constraints using \emph{balance} components creates a reduced-space problem with few design variables for the optimizer.
-This increases the complexity of the multipoint nonlinear solution but simplifies the problem for the optimizer and is the preferred method in cycle analysis.
+% \citet{Hendricks2019} implemented four additional balance residuals for the multipoint N+3 model.
+% These balances operate as constraints and create a reduced design space for the optimization problem.
+% The first balance varies the bypass ratio (BPR) at TOC to match a given nozzle velocity ratio.
+% The nozzle velocity ratio is defined as,
+% \begin{equation}
+%     V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
+%     \label{eq:vratio}
+% \end{equation}
 
-In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a \emph{balance} component.
-The \emph{balance} component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
+% Solving for all of the state and design variables while satisfying constraints could be accomplish with only an optimizer to simplify the problem.
+% However, using a solver to converge constraints using \emph{balance} components creates a reduced-space problem with few design variables for the optimizer.
+% This increases the complexity of the multipoint nonlinear solution but simplifies the problem for the optimizer and is the preferred method in cycle analysis.
 
-\begin{equation}
-    V_{ratio} = \frac{V_{core,ideal}C_{v,core}}{V_{bypass,ideal}C_{v,bypass}}
-    \label{vratio}
-\end{equation}
+% In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a \emph{balance} component.
+% The \emph{balance} component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
 
-\noindent
-where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient of the nozzle which represents non-ideal effects.
-This adds a constraint where the core exit velocity is higher than the bypass exit velocity.
+% \noindent
+% where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient of the nozzle which represents non-ideal effects.
+% This adds a constraint where the core exit velocity is higher than the bypass exit velocity.
 
@@
 
-With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.
-This is the multidisciplinary design analysis block of the model.
+% With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.
+% This is the multidisciplinary design analysis block of the model.
 
 % [x] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
-% [ ] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
+% [x] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
+% [ ] TODO: AL-PA, Remove the mdot_inject and mdot_extract stuff, just call it mdot_water
+% [ ] TODO: AL-PA, copy the format of the cooling flow connections for the water mass flow rates
+% [ ] TODO: AL-PA, "Area" should be abbreviated to just the letter "A"
+% [ ] TODO: AL-PA, Change the component types for TOC, RTO, SLS, CRZ, and BALANCE to be implicit groups. They should show up as red polygons.
 \begin{figure}[hbt!]
     \centering
-    \includegraphics[width=1.0\textwidth]{N3_xdsm_full.pdf}
+    \includegraphics[width=\textwidth]{N3_xdsm_full.pdf}
     \caption{
@@
 % NOTE: AL-PA, I re-wrote this to be more direct
-The objective is to minimize fuel burn subject to design and performance constraints at each flight condition.
+The objective is to minimize fuel burn subject to design and performance constraints.
 % The objective is to minimize the TSEC since that is our performance metric for comparing the two types of fuels.
@@
 
-For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
-However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
+Typical gas-turbine analysis measures the efficiency using the thrust-specific fuel consumption (TSFC).
+% For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
+However, this metric is not useful in the comparison of efficiency between jet-A and hydrogen fueled cycle models because of the differences in fuel density and energy capacity.
+% However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
 % TODO: Update mdolab.bib
-A better metric for comparing the relative efficiencies of an engine running on Jet-A versus hydrogen is thrust-specific energy consumption (TSEC). %\cite{Adler2023}.
+A better metric for comparing Jet-A versus hydrogen is thrust-specific energy consumption (TSEC). %\cite{Adler2023}.
 TSEC is TSFC multipied by the lower heating value (LHV) of the fuel shown in Equation~\eqref{eq:tsec}.
@@
 \begin{equation}
-    TSFC = \frac{\Dot{m}_{fuel}}{F_{thrust}}
+    \mathrm{TSFC} = \frac{\dot{m}_{\mathrm{fuel}}}{F_{\mathrm{thrust}}}
     \label{eq:tsfc}
@@
 \begin{equation}
-    TSEC = \frac{\Dot{m}_{fuel} LHV}{F_{thrust}} = TSFC \times LHV
+    \mathrm{TSEC} = \frac{\dot{m}_{\mathrm{fuel}} \mathrm{LHV}}{F_{\mathrm{thrust}}} = \mathrm{TSFC} \times \mathrm{LHV}
     \label{eq:tsec}
@@
 
-Therefore, TSEC at the cruise condition is the objective function in the optimzation problem.
+% [ ] TODO: AL-PA, TSEC is not the objective.  Fuel burn is the objective.  TSEC is the efficiency metric of interest.
+Therefore, TSEC at the cruise condition is the objective function in the optimization problem.
+% [ ] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
 An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{N3_opt_XDSM.pdf}
+    \includegraphics[width=0.5\textwidth]{N3_opt_XDSM.pdf}
     \caption{
@@
 % [x] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
-The TOC point constraints shown in Figure \ref{fig:N3_opt_xdsm} are only the constraints imposed on the model at optimizer level.
+% [ ] TODO: AL-AL, I decided this is no longer necessary
+% The TOC point constraints shown in Figure \ref{fig:N3_opt_xdsm} are only the constraints imposed on the model at optimizer level.
 
+% [ ] TODO: AL-PA, I would break this up into two or more sentences.
 The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
-Only the water recovery fraction at CRZ is a design variable since we are optimizing $TSEC_{\rm{CRZ}}$.
+% [ ] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
+% [ ] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
+Only the water recovery fraction at CRZ is a design variable since we are optimizing $\rm{TSEC}_{\rm{CRZ}}$.
 TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
@@
 
+% [ ] TODO: AL-PA, You already explained the flight conditions in the multipoint section so not necessary here
+% [ ] TODO: AL-PA, Combine these into a single sentence.
+% [ ] TODO: AL-PA, I would describe the constraints in more detail here.  This might be a good spot to talk about the constraints imposed by the balance comps at the top level.
+%                  - i.e the SLS and CRZ net thrust constraints
+%                  - i.e how the BPR is set by the nozzle velocity ratio
+%                  - i.e The interdependence of the TOC mass flow rate and the RTO temperature
 This optimization problem was run for both Jet-A and H2 fuels using the fuel properties in \ref{fuel_props} and flight conditions in Table \ref{flight_conds}.
+The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
 
@@
         \hline                                                                                                                                                                   \\
-        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
         \hline
@@
 \end{table}
-
-The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
 
@@
 % NOTE: AL-PA, I re-wrote most of this to be more concise.
-OpenMDAO~\cite{Gray2019a} is a modular framework that enables multidisciplinary gradient-based optimization with analytic coupled derivatives.
+The N+3 pyCycle model is implemented in OpenMDAO~\cite{Gray2019a} to enable multidisciplinary gradient-based optimization with analytic coupled derivatives.
 We use pyOptSparse~\cite{Wu2020a} to facilitate the use of state-of-the-art optimization software through a unified python interface.
@@
 \label{sec:results}
-
+% [ ] TODO: AL-PA, I would move the following two lines into the optimization problem section and re-write them to be a single concise sentence.
 Our fuel performance metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
@@
 
+% [ ] TODO: AL-PA, This is confusing.  You have two different optimization problem formulations and that is not clear here.
+%                  - I think you need to add information to the previous section about the optimization problem that explains all of this information.
+%                    Introducing this at the beginning of the results does not make sense.
 When $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time it was found that the optimizer pushes $T_{4,\rm{RTO}}$ down and $X_{\rm{H_2O,CRZ}}$ up.
@@
 % Results of optimization problems
+% [ ] TODO: AL-PA, Include the optimization and feasibility targets and talk about the number of iterations for each optimization.
+% [ ] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
 The 4 optimizations mentioned in the section \ref{sec:optprob} were run and solved.
@@
 
+% [ ] TODO: AL-PA, Stretch the aspect ratio of this figure and squeeze the height in matplotlib.  You don't need this many values on the y-axis for the summary plots.
 % Feasibility, Optimality, Merit history
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{opt_summary.pdf}
+    \includegraphics[width=0.65\textwidth]{opt_summary.pdf}
     \caption{The optimality, feasibility, and merit fuction history for each optimization problem.
@@
 
+% [ ] TODO: AL-PA, No need to explain this and then answer your own observation from the plot.  Just tell the reader what the plot shows.
+% [ ] TODO: AL-PA, Be cognizant that latex will not always put the figure right above a paragraph.  So saying "From this plot" might not make sense.  Need to directly reference the figure.
+% NOTE: AL-PA, The merit function is not a time-dependent quantity, so there's no "steady state".  Its enough to just say the merit function was reduced by X amount in X number of iterations...
 From this plot we can visually check that each optimization achieved optimality and feasibility, and that the merit function reached a steady-state value.
-Indeed, we observe quadratic convergence in the optimiality of the problem near the optimal solution as expected.
-The design variable history for each optmization problem is shown in Figure \ref{fig:history_dvs}.
+Indeed, we observe quadratic convergence in the optimality of the problem near the optimal solution as expected.
+The design variable history for each optimization problem is shown in Figure \ref{fig:history_dvs}.
 
+% [ ] TODO: AL-PA, Convert this to a table so it takes up less space.  Just show that final DV values for each optimization.
 % DV history
@@
 
+% [ ] TODO: AL-PA, You should explain the plot before it's introduced to the reader.  Stating what's on the figure after it appears doesn't provide any insight.
 From this figure we see that the design variables start at the initial values and converge toward their optimal value.
-Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimzations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
-The constraint history for each optmization problem is shown in Figure \ref{fig:history_cons}.
+% [ ] TODO: AL-PA, See my previous TODOs but this needs some more explanation in the optimization problem section.
+Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
+The constraint history for each optimization problem is shown in Figure \ref{fig:history_cons}.
 
+% [ ] TODO: AL-PA, This is unnecessary because you already show that the optimization is feasible.  Just write out these values in a description of the constraints in the paper.
 % Constraint history
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{cons.pdf}
+    \includegraphics[width=0.75\textwidth]{cons.pdf}
     \caption{The constraint history for each optimization problem.
@@
 
+% [ ] TODO: AL-PA, Constraints are either feasible or they aren't, can't be "for the most part"
 From this figure we can see that the constraints are quickly satisfied and for the most part remain feasible for the duration of the optimization.
+% [ ] TODO: AL-PA, Elaborate on why we include this parallel axis plot.  Why is it important?  What insight does it provide to the reader?  Compare and contrast the optimization results!
 The resulting optimal values from the optimization problems are shown in Figure \ref{fig:parallel_coords} on a parallel coordinate plot.
@@
     \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
-        The red lines show Jet-A fuel and the blue lines show H2 fuel.
+        The red lines show Jet-A fuel and the blue lines show \ce{H2} fuel.
         The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.}
@@
 
+% [ ] TODO: AL-PA, I would move a lot of this up to when you introduce the parallel axis plot.
+% [ ] TODO: AL-PA, How are they similar? Be specific.
 We can see that the resulting engine designs are all very similar.
+% [ ] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
 The main differences in the engine designs are the pressure ratios and temperatures.
+% [ ] TODO: AL-PA, Why is pushed to the upper limit?  Explain how it improves the combustion characteristics.
 Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
-Given that more water is present in the exhaust stream of the H2 engine, the H2 engine can recover a smaller fraction of the water compared to the Jet-A engine.
-The water recovery flow rates for the Jet-A and H2 engines was 0.324 $\si{lbm/s}$ and 0.405 $\si{lbm/s}$, respectively.
-Therefore, the H2 has the benefit of being able to recover more water at a lower fraction of the overall core exhaust stream water.
-With water recovery, we see slightly higher pressure ratios across the fan and overall pressure ratio while the LPC pressure ratio is pushed to its technological upperbound.
-We only see differences in $T_{4,\rm{RTO}}$ without water recovery due to these values are fixed for water recovery.
+The recovery fraction does not directly relate to the mass flow rate of recirculated water.
+The recovery fraction for \ce{H2} is smaller than the recovery fraction for jet-A because there is more water produced in the combustion process.
+However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for jet-A.
+% Given that more water is present in the exhaust stream of the H2 engine, the H2 engine can recover a smaller fraction of the water compared to the Jet-A engine.
+% The water recovery flow rates for the Jet-A and H2 engines was 0.324 $\si{lbm/s}$ and 0.405 $\si{lbm/s}$, respectively.
+The \ce{H2} has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
+We see slightly higher pressure ratios across the fan with water recovery leading to a larger overall pressure ratio.
+The LPC pressure ratio tend to the upper bound for each optimization with and without water recovery enabled.
+% [ ] TODO: AL-PA, I'm beating a dead horse here but you don't need to say this if you mention it earlier
+% We only see differences in $T_{4,\rm{RTO}}$ without water recovery due to these values are fixed for water recovery.
+% [ ] TODO: AL-PA, Why is the T4 ratio higher?  Explain it in terms of the fuel properties.  The reader can look at the plot themselves and see that it's higher.
 The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of H2.
 Furthermore, adding water recovery slightly decreases the $T_{4,\rm{ratio}}$ value.
-Therefore, temperatures are cooler with the H2 fuel and even slightly cooler when adding water recovery.
+% [ ] TODO: AL-PA, Why are the temperatures colder with the H2 fuel?  Why does water recovery make them even lower?
+% [ ] TODO: AL-PA, I wouldn't say "cooler" I would say "less than" or "colder"
+Therefore, temperatures are cooler with the \ce{H2} fuel and even slightly cooler when adding water recovery.
+% [ ] TODO: AL-PA, Why did the optimizer push the value of T4 down with water recovery?  Dig into this more.
 It is noted that with more water recovery the farther the optimizer would push the value of $T_{4,\rm{RTO}}$ down.
 Therefore, there are temperature-related advantages of using water recovery to maintain a certain effenciency and thrust.
+% [ ] TODO: AL-PA, We want to discuss how the thrust from the fan/core changes when we introduce water recovery.
+% NOTE: AL-PA, The idea here is to communicate the effect of water recovery on the core power vs. the fan power.
 The breakdown of thrust for each point is shown in Table \ref{tab:thrust}.
@@
 % [x] TODO: PA-PA: Add thrust splits for each opt
+% [ ] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
+%                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
 \begin{table}[hbt!]
@@
 
+% [ ] TODO: AL-PA, Again, this table might not be directly above this text in the PDF so you need to use \ref{tab:thrust}.
+% [ ] TODO: AL-PA, You already showed the constraint values and that the design is feasible, the reader knows what the net thrust should be from that information.
 From this table we can see that the net thrust is constrained at values set by \emph{balance} components or optimization constraints.
-We see the largest thrust differences at the RTO and CRZ points.
-Since net thrust is constrainted, the optimizer sizes the engine to reduce ram drag slightly from Jet-A to H2.
-Water recirculation provides an even more significant improvement in ram drag for both Jet-A and H2 at CRZ with reductions of 0.21\% and 0.24\%, respectively.
-Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
+% [x] TODO: AL-PA, Thrust differences?  These values change with mass flow rate which we know is affected by water recovery.  Probably need to remove the following stuff discussing this.
+% NOTE: AL-PA, I think you misunderstood what happens in the ram drag/gross thrust calculations.  They are just simple control volume thrust equations.
+%              If your mass flow rate changes with water recirculation these will change, but that is expected and not super informative in terms of a comparison.
+
+% We see the largest thrust differences at the RTO and CRZ points.
+% Since net thrust is constrainted, the optimizer sizes the engine to reduce ram drag slightly from Jet-A to H2.
+% Water recirculation provides an even more significant improvement in ram drag for both Jet-A and H2 at CRZ with reductions of 0.21\% and 0.24\%, respectively.
+% Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
+
+% [ ] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
 Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water injection.
@@
 
+% [ ] TODO: I would change this to the horizontal bar chart and plot both H2 and Jet-A on the same axis
+% See this example in niceplots: https://github.com/mdolab/niceplots/blob/main/examples/plot_bar_chart.py and https://github.com/mdolab/niceplots/blob/main/examples/ref/bar_chart.png
 \begin{figure}[hbt!]
@@
     \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
-        This plot compares the relative improvement of the two optimziation problems with water recovery compared to the optimzation problems without water recovery.}
+        This plot compares the relative improvement of the two optimization problems with water recovery compared to the optimization problems without water recovery.}
     \label{fig:barchart}
@@
 This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
+% [ ] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
 Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser~\cite{Strom2002}.
-This would incure larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
-Therefore, H2 is a much more appealing fuel to use with the proposed closed-loop water recovery system.
-Since there a lack of literature on large-scale water condensers that are designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
+% This would incur larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
+Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
+% [ ] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
+%                  Might be worth moving this into a new subsection.
+% [ ] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
+Since there is a lack of literature on large-scale water condensers that are designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
 Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
-pyCycle handles pressure losses in ducts by specifyign a pressure loss coefficient, dPqP.
-This coefficient is the ratio of change in pressure normalized by the inlet pressure of the duct.
+% [ ] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"
+pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
+This coefficient is the ratio of change in total pressure normalized by the inlet pressure of the duct.
+% [ ] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
+% [ ] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
 The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
@@
 
-% TSEC as a function of dPqP
 \begin{figure}[hbt!]
     \centering
-    \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
+    \begin{subfigure}[t]{0.49\textwidth}
+        % [ ] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
+        \includegraphics[width=\textwidth]{N3_dpqp.pdf}
         \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
-        This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
+            The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery.
+            This shows the working space available for designing a water condenser while still gaining the benefits of water recovery.}
         \label{fig:dpqp_sweep}
+    \end{subfigure}
+    \hspace{2pt}
+    \begin{subfigure}[t]{0.49\textwidth}
+        % [ ] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
+        \includegraphics[width=\textwidth]{N3_wdot.pdf}
+        \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+            The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
+            The engine was optimized with the water recovery upper bound of 17\%.
+        }
+        \label{fig:dpqp_wdot}
+    \end{subfigure}
+    \caption{}
+    \label{fig:dpqp_study}
 \end{figure}
+
+% TSEC as a function of dPqP
+% \begin{figure}[hbt!]
+%     \centering
+%     \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
+%     \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+%         The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
+%         This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
+%     \label{fig:dpqp_sweep}
+% \end{figure}
 
@@
 
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
-    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-        The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
-        The engine was optimized with the water recovery upperbound of 17\%.
-    }
-    \label{fig:dpqp_wdot}
-\end{figure}
+% \begin{figure}[hbt!]
+%     \centering
+%     \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
+%     \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+%         The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
+%         The engine was optimized with the water recovery upperbound of 17\%.
+%     }
+%     \label{fig:dpqp_wdot}
+% \end{figure}
 

### 2023-05-01 conference-paper/main.tex
Fixed some formating and scentence issues

--- 2023-05-01 conference-paper/main.tex
@@
 Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
-Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
+Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits%~\cite{Adler2023}.
 However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
@@
         Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
+        Flow stations are identified with bubble text
     }
@@
         The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
-        The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and reinjects it upstream of the high-pressure compressor.
+        The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and re-injects it upstream of the high-pressure compressor.
         This diagram illustrates the feedback effect that this implementation has on the overall core flow.}
@@
 % Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
-% To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
+% To utilize water engine section in front of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
 pyCycle provides a \texttt{wet-air} dataset that introduces $\mathrm{H_2O}$ molecules to the composition of air.
@@
         Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
-        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
+        Black arrows are flow connections, blue boxes are cycle elements
+        Flow stations are identified with bubble text.
     }
@@
 
-Therefore, TSEC at the cruise condition is the objective function in the optimzation problem.
+For this work we are concerned with minimizing fuel burn of the engine subject to known thrust constraints.
+Therefore, we will use TSEC at the cruise condition to compare the two fuels but will use $\dot{m}_{\rm{fuel,CRZ}}$ as the objective function in the optimzation problem.
 An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.
@@
 The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
-Only the water recovery fraction at CRZ is a design variable since we are optimizing $TSEC_{\rm{CRZ}}$.
+Only the water recovery fraction at CRZ is a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}} $.
 TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
@@
 The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
+The thermodynamic cycle design variable ranges are determined from the expected N+3 technology limits~\cite{Hendricks2019}.
+Additionally, the design variable ranges are shown in Table \ref{tab:dv_table}.
 
-% [x] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
+% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
 % [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
 % [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
-% [ ] TODO: PA-PA, explain variable ranges
+% [x] TODO: PA-PA, explain variable ranges
 \begin{table}[hbt!]
@@
         \hline
-        minimize        & $\rm{TSEC}_{\rm{CRZ}} $        & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
+        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/hr/lbf} & 1        \\
                         &                                &                                                                       &                 &          \\
@@
         \toprule
-        $x_{H2O,CRZ}$         & 0.0    & -      & -         \\
-        $PR_{fan,TOC}$        & 1.2    & 1.4    & -         \\
-        $PR_{LPC,TOC}$        & 2.5    & 4.0    & -         \\
-        $PR_{OPR,TOC}$        & 40.0   & 70.0   & -         \\
-        $T_{4,TOC}/T_{4,RTO}$ & 0.5    & 0.95   & -         \\
+        $X_{\rm{H_2O,CRZ}}$      & 0.0    & 1.0    & -         \\
+        $\rm{PR}_{\rm{fan,TOC}}$ & 1.2    & 1.4    & -         \\
+        $\rm{PR}_{\rm{LPC,TOC}}$ & 2.5    & 4.0    & -         \\
+        $\rm{OPR}_{\rm{TOC}}$    & 40.0   & 70.0   & -         \\
+        $T_{4,\rm{ratio}}$       & 0.5    & 0.95   & -         \\
         $T_{4,RTO}$              & 3000.0 & 3600.0 & $^\circ$R \\
-        $V_{ratio,CRZ}$       & 1.35   & 1.45   &           \\
+        $V_{ratio,CRZ}$          & 1.35   & 1.45   & -         \\
         \bottomrule
     \end{tabular}
-    \label{tab:res_full_opt_H2}
+    \label{tab:dv_table}
 \end{table}
@@
 
-Our fuel performance metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
-Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.
+Our fuel performance metric is TSEC but minimizing $\dot{m}_{\rm{fuel}}$ is a more relavent problem since we will have known thrust constraints and want to compare fuel economy.
+Therefore, the fuel flow rate at CRZ, $\dot{m}_{\rm{fuel,CRZ}}$, was set as the objective function.
 
@@
 System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
-The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, presusres and velocities within the engine.
+The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
 An additional design variable controlling how much water is recirulated is added at the CRZ point to improve the fuel burn.
+The optimization problem is then solved for four cases: with Jet-A or hydrogen fuel and with and without water recirculation.
 
@@
 \section{Acknowledgements}
+We would like to thank Justin Grey for his help with the pyCycle components of this work.
+Since there is very little pyCycle documentation, his expertise and knowledge of the tool helped make the development of the custom pyCycle components possible.
 

### 2023-05-01 figures/N3_CLVR_cycle.tex
Fixed some formating and scentence issues

@@
 \tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
-\tikzstyle{heat_flow} = [draw, -latex', ultra thick, color=heatcolor]
+\tikzstyle{station_label} = [circle, draw, text width=2em, text centered, font=\LARGE]
+\tikzstyle{connection} = [draw, -latex', ultra thick]
+\tikzstyle{line} = [draw]
 
@@
     \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
-    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
+    \node [element, below=8em of burner] (vrl) {Vapor Recovery Loop};
     % \node [element, below=12em of burner] (bypduct) {Bypass Duct};
@@
     % \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};
+
+    % Create station labels
+    % \node [station_label, below=8em of inlet.west] (1) {1};
+    % \node [station_label, below=6em of fan.west] (1) {1};
+    % \node [station_label, below=8em of splitter.west] (13) {13};
+    \node [station_label, below=6em of lpc.west] (2) {2};
+    \node [station_label, below=6em of hpc.west] (25) {25};
+    \node [station_label, below=6em of burner.west] (3) {3};
+    \node [station_label, below=6em of hpt.west] (4) {4};
+    \node [station_label, below=6em of lpt.west] (45) {45};
+    \node [station_label, below=6em of corenozzle.west] (5) {5};
+    % \node [station_label, below=6em of bypnozzle.west] (17) {17};
 
@@
 
+    % Draw station label connections
+    % \path [line] (inlet.west) -- (1.north);
+    % \path [line] (fan.west) -- (1.north);
+    % \path [line] (splitter.west) -- (13.north);
+    \path [line] (lpc.west) -- (2.north);
+    \path [line] (hpc.west) -- (25.north);
+    \path [line] (burner.west) -- (3.north);
+    \path [line] (hpt.west) -- (4.north);
+    \path [line] (lpt.west) -- (45.north);
+    \path [line] (corenozzle.west) -- (5.north);
+    % \path [line] (bypnozzle.west) -- (17.north);
+
     % Draw Shaft Connections

### 2023-05-01 figures/N3_cycle.tex
Peter's fixes 4/28
Fixed some formating and scentence issues

@@
 \tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
-\tikzstyle{heat_flow} = [draw, -latex', ultra thick, color=heatcolor]
+\tikzstyle{station_label} = [circle, draw, text width=2em, text centered, font=\LARGE]
+\tikzstyle{line} = [draw]
 
@@
     \node [element, right=4em of lpt] (corenozzle) {Core Nozzle};
-    \node [element, below=4em of burner] (bypduct) {Bypass Duct};
-    \node [element, below=4em of corenozzle] (bypnozzle) {Bypass Nozzle};
+    \node [element, below=8em of burner] (bypduct) {Bypass Duct};
+    \node [element, below=8em of corenozzle] (bypnozzle) {Bypass Nozzle};
 
@@
     \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};
+
+    % Create station labels
+    % \node [station_label, below=8em of inlet.west] (1) {1};
+    \node [station_label, below=6em of fan.west] (1) {1};
+    % \node [station_label, below=8em of splitter.west] (13) {13};
+    \node [station_label, below=6em of lpc.west] (2) {2};
+    \node [station_label, below=6em of hpc.west] (25) {25};
+    \node [station_label, below=6em of burner.west] (3) {3};
+    \node [station_label, below=6em of hpt.west] (4) {4};
+    \node [station_label, below=6em of lpt.west] (45) {45};
+    \node [station_label, below=6em of corenozzle.west] (5) {5};
+    \node [station_label, below=6em of bypnozzle.west] (17) {17};
 
@@
     \path [connection] (lpt) -- (corenozzle);
+
+    % Draw station label connections
+    % \path [line] (inlet.west) -- (1.north);
+    \path [line] (fan.west) -- (1.north);
+    % \path [line] (splitter.west) -- (13.north);
+    \path [line] (lpc.west) -- (2.north);
+    \path [line] (hpc.west) -- (25.north);
+    \path [line] (burner.west) -- (3.north);
+    \path [line] (hpt.west) -- (4.north);
+    \path [line] (lpt.west) -- (45.north);
+    \path [line] (corenozzle.west) -- (5.north);
+    \path [line] (bypnozzle.west) -- (17.north);
 

### 2023-05-03 conference-paper/main.tex

--- 2023-05-01 conference-paper/main.tex
@@
 % [x] TODO: AL-PA, Need to add equation labels
-% [ ] TODO: AL-PA, When you are citing things you should include a "~" to link the citation to the text.  i.e, "OpenMDAO~\cite{Gray2019a}" (See my edits in the introduction)
-% [ ] TODO: AL-PA, You should also use the "~" to link all equation, figure, and table references to the text.
+% [x] TODO: AL-PA, When you are citing things you should include a "~" to link the citation to the text.  i.e, "OpenMDAO~\cite{Gray2019a}" (See my edits in the introduction)
+% [x] TODO: AL-PA, You should also use the "~" to link all equation, figure, and table references to the text.
 % [x] TODO: AL-PA, Make sure all acronyms and subscripts that are longer than a single letter or represent words are shown as text using \rm{} in math mode
@@
     Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
-    % With the focus on reducing aircraft emissions, aircraft and engine manufacturers have been pushing for hydrogen as a fuel and more efficient engines to lower carbon emissions.
     Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
@@
 Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
-Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
+Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits~\cite{Adler2023}.
 However, hydrogen is a versatile fuel with advantageous molecular and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
 We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
-% In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHBR ratio turbofan engines.
-% We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
 % [x] TODO: PA-PA, add section about MAUD and cite.
@@
 % Message 2: Background and references to support using H2 and water injection in HBTF engines
-% [ ] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
+% [x] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
 Water injection is the process of introducing water upstream of the combustor as finely atomized droplets.
@@
 This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
-Pratt and Whitney are actively researching this technology to improve the feasibility of hydrogen-powered propulsion~\footnote{https://arpa-e.energy.gov/technologies/projects/hydrogen-steam-and-inter-cooled-turbine-engine-hysite}.
+Pratt and Whitney are actively researching this technology to improve the feasibility of hydrogen-powered propulsion~\cite{arpa-e_2021}.
+They suggest that water vapor can be recovered by utilizing the thermal properties of hydrogen to condense some of the water in the turbofan exhaust.
 
@@
 Zero-dimensional analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver~\cite{Gordon1994} that considers the molecular species of different fuels.
-% CEA can be used to understand the trends and design limitations of an engine cycle and study potential improvements in design using optimization.
 The industry standard for thermodynamic cycle analysis is the Numerical Propulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
@@
 % NOTE: AL-PA, I removed the MAUD sentence because it's a wormhole that you probably don't want to enter lol.
-% OpenMDAO provides a framework for computing coupled derivatives efficiently using the modular analysis and unified derivatives (MAUD) architecture which supports a large number of design variables~\cite{Hwang2018a}.
 
@@
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-The UHB turbofan model is the NASA advanced technology "N+3" engine \cite{Jones2017a}.
+The UHB turbofan model is the NASA advanced technology "N+3" engine~\cite{Jones2017a}.
 The N+3 reference cycle is a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
-% We selected the N+3 model because it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
 The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core and a bypass stream, each ending in a core and bypass nozzle, respectively.
@@
 Second, the gearbox attaches to the low-pressure shaft that connects to the low-pressure compressor (LPC) and low-pressure turbine (LPT).
-% The low pressure system consists of a fan connected to a gearbox that attaches to the lo and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft.
 The high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-% [ ] TODO: AL-PA, I think we need to reference the engine diagram figure here so the reader can visualize all this text.
-
+% [x] TODO: AL-PA, I think we need to reference the engine diagram figure here so the reader can visualize all this text.
+Figure~\ref{fig:n3_cycle} shows a standard high bypass turbofan engine flow connections.
 % [x] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
-% Thermodynamic equations of state are solved using CEA at the interface between components, shown as black arrows in Figure~\ref{fig:n3_cycle}.
 We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to upstream of the compressors.
-% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
 The recovery system injects vaporized water into the core stream that reduces the combustion temperature due to heat absorption.
 The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycle it back to the injector.
-% [ ] TODO: AL-PA, Again, probably should reference a figure to give context to the water recovery layout.
+Figure~\ref{fig:n3_clvr} shows the water vapor recovery loop implemented in a turbofan engine.
+% [x] TODO: AL-PA, Again, probably should reference a figure to give context to the water recovery layout.
 % NOTE: AL-PA, don't discredit your work before you even explain the model and methods.  We can make this point in the results or conclusion.
-% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
 
@@
 We explain the implementation and assumptions of the water recovery model and the coupling with the thermodynamic cycle.
-% The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:N3_original}.
-% The propulsion model is constructed in pyCycle which is built on top of OpenMDAO to allow a modular design of the engine components and the coupling of other engineering disciplines for analysis \cite{Gray2019a}.
-% The engine model that was selected for this project is the NASA advanced technology UHB geared turbofan engine cycle, referred to as the "N+3" engine \cite{Jones2017a}.
-% The N+3 reference cycle represents a UHB ratio geared turbofan that could be available in the 2030–2040 time frame and was selected since it has already been modeled in pyCycle as a robust example cycle and includes the advanced engine cycle improvements such as a large bypass ratio, high pressure ratio, and high combustion temperature.
-% The flow path consists of an inlet that directs ambient air through a fan, followed by a duct that splits the flow into a core flow and a bypass flow, each of which ends in a bypass nozzle and core nozzle, respectively.
-% The fan and low pressure compressor (LPC) are connected to the low pressure turbine (LPT) by the low pressure shaft and the high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-% Along the axial flow path, the zero-dimensional thermodynamic connections are solved using CEA to ensure the first principle governing equations are satisfied.
-% Figure \ref{fig:N3_original} shows how the 25 elements in the N+3 cycle are connected together with the fluid flows in blue, the mechanical connections in red, and the performance elements in green \cite{Hendricks2019}.
 
@@
 
-% In pyCycle, the Cycle block contains all of the governing thermodynamic equations needed to model an engine such as CEA analysis, compressor and turbine models, and equations of state.
-% These equations allow any arbitrary engine design to be assembled using the modular cycle elements.
-% The Cycle block itself may not result in a valid model of the engine since some physical dependencies may not match.
-% These physical dependencies are handled by the Balance block which solves a set of implicit state variables and nonlinear physical residual equations in the form:
-
-% \noindent
-% where $x_i$ is some physical variable such as a mass or energy flow rate.
-% These residuals represent the physical conservation laws such as mass flow rate are converged to zero by the Solver.
-% In pyCycle, a direct solver is used for linear equations and a Newton solver is used for nonlinear equations which utilizes the analytic partial derivatives provided by each OpenMDAO component.
-% All residuals within the engine model are converged at the Cycle level for a given operation condition since all of the parameters downstream do not directly effect those upstream.
-% However, with introducing the extractor and injector components, we add a feedback loop into the model where mass is removed downstream and added upstream.
-% Therefore, the mass flow rates residuals of the closed-loop vapor recovery system shown below would need to be converged in the Multipoint Cycle explained in the next section.
-
-% \begin{equation}
-%     \mathcal{R}_{c,\dot{m}} = \dot{m}_{extractor} - \dot{m}_{injector} = 0
-% \end{equation}
-
 \subsection{Water Recovery Model}
 We implemented the closed-loop water recovery system as a feedback cycle that extracts water from the exhaust stream and injects it upstream of the HPC.
-% The closed-loop water recovery system is implemented into the cycle by placing a water injection component directly before the HPC.
-% This component will inject pure water into the core stream which will reduce the combustion temperature due to heat absorption from vaporization.
 We chose this injection location based on claims from a study by NASA, Boeing, and Rolls-Royce~\cite{Daggett2010} that water injection directly into the combustor is unnecessary.
-% This location was chosen as it was one of the configurations chosen by the aforementioned NASA, Boeing, and Rolls-Royce study that did not require direct combustor injection \cite{Daggett2010}.
 The water vapor recovery component sits downstream of the LPT and extracts water from the flow before exiting the core nozzle.
-% The water vapor recovery component is placed directly before the core nozzle to extract water from the core stream and recycle it back to the water injector.
-% Water is recovered from this location as it is the last possible location before the nozzle in which water can be extracted.
 % [x] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
@@
 % NOTE: AL-PA, we will talk about the condenser when we discuss the results of the pressure recovery parameter sweep.
-% In practice a water vapor recovery component requires a complex condenser model in the core stream, this work will only look at the potential benefits of extracting water vapor and not the recovery method specifically.
-The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure \ref{fig:n3_cycle}.
+The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure~\ref{fig:n3_cycle}.
 
@@
 To account for the humidity of the inlet air as well as the increased humidity after water injection, we modified the composition of the air mixture upstream of the combustor.
-% Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
-% To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
 pyCycle provides a \texttt{wet-air} dataset that introduces \ce{H2O} molecules to the composition of air.
-% The \texttt{wet-air} dataset inherits the NPSS \texttt{JANAF} data from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
-% The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
 We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of \ce{H2O} to air in the reactants of the inflow mixture.
-% In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
-% The WAR is the sp of the air expressed in equal units and separating out the total mass (kg water/kg air).
-% [ ] TODO: AL-PA, Reference Table 1 with humidity values as well.
-\citet{Kalnay1996} give the humidity values for each flight condition.
-% The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.
+% [x] TODO: AL-PA, Reference Table 1 with humidity values as well.
+\citet{Kalnay1996} give the humidity values for each flight condition and are shown in Table~\ref{tab:flight_conds}.
 
 We introduce two new thermodynamic models for water recirculation in pyCycle.
-% To model the complicated water recirculation loop in pyCycle new components had to be developed.
 A water injector adds water to the flow upstream of the HPC, while a water extractor diverts a portion of the water in the flow away from the exhaust stream.
-% The two models are a water injector that adds water to the flow upstream of the HPC and a water extractor to divert a fraction of the water in the flow away from the exhaust stream.
 The injector operates similarly to fuel injection in the pyCycle combustor component.
 We determine a WAR that is analogous to the fuel-to-air (FAR) ratio in the combustor.
-% The injector component is based on the combustor component already included in pyCycle which operates by injecting a given fuel-to-air ratio (FAR) or fuel flow rate to determine the mass of fuel added to the incoming flow.
 This WAR is used to compute the chemical species present in the flow at the current thermodynamic state, determined by the incoming flow.
 The new species composition and thermodynamic state are determined using the pyCycle CEA solver~\cite{Gray2017b}.
-% Once the new composition is determined, the various thermodynamic variables are passed to the next component in the engine.
-% The water injector component would inject water as a reactant instead of the fuel as the combustor would.
 The water injector inputs are the mass flow rate and mass fraction of water.
 We can solve for the mass flow rate on a mixture basis using the WAR, or directly by specifying the mass flow rate of water.
-% The water injector can take either water-to-air ratio (WAR) or water mass flow rate to determine how much water is added to the flow.
-A schematic of the injector is shown in Figure \ref{fig:injector} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules.
+A schematic of the injector is shown in Figure~\ref{fig:injector} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules.
 
@@
             We extract a fraction of the moles of water from the out flow of duct 5.
-            % A certain mole fraction of the flow coming out of duct 5 is comprised of water of which a certain specified fraction is extracted.
             The extracted water is routed back upstream to the injector and the rest is exhausted out the nozzle.
@@
     \end{subfigure}
-    % [ ] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
-    \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.}
+    % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
+    \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
+        The inputs and outputs show which flow values are used to compute the amount of recirculated water.}
     \label{fig:extract_inject}
@@
 
-% \begin{figure}[hbt!]
-%     \centering
-%     \includegraphics[width=0.75\textwidth]{injector.pdf}
-%     \caption{
-%         Injector component schematic.
-%         Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
-%     }
-%     \label{fig:injector}
-% \end{figure}
-
 The water extractor model diverts a fraction of a specific species from one flow path to another.
-% The water extractor model is based on an air-bleed component in pyCycle with the added complexity of extracting a fraction of a specific species within the flow.
 The CEA solver calculates the inflow composition and the extractor separates a specific species based on a mass fraction input.
@@
 We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
-% The extraction determines the water content of the incoming flow and extracting a given fraction of that water flow.
-% The water content of the incoming flow is determined by solving a CEA analysis of the incoming flow.
-% This water content in the incoming flow is then used with a given fraction of the water to extract to determine the how much water mass flow to remove from the stream.
-% The outputs of the extractor component are the flow rate of the core flow and the corresponding flow properties in addition to the extracted water mass flow rate.
-% While this process certainly would have pressure loss penalties in terms of condensing water in a condenser, this project just looks at the effects of water recovery since there are no current models for nozzle exhaust condensers available.
-A simple schematic of the extractor is shown in Figure \ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the fraction of water that is recovered from the core stream.
-
-% \begin{figure}[hbt!]
-%     \centering
-%     \includegraphics[width=0.75\textwidth]{extractor.pdf}
-%     \caption{
-%         Extractor component schematic.
-%         A certain mole fraction of the flow coming out of duct5 is comprised of water of which a certain specified fraction is extracted.
-%         The extracted water is routed back upstream to the injector and the rest is simply exhausted out the nozzle.
-%     }
-%     \label{fig:extractor}
-% \end{figure}
-
+A simple schematic of the extractor is shown in Figure~\ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the fraction of water that is recovered from the core stream.
 We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.
@@
 % NOTE: AL-PA, I removed this because I don't think the reader will understand the phase-change nuances with 0D cycle and CEA
-% Therefore, we are capturing the effect of adding pure water to the stream since zero-dimentional analysis cannot reproduce the effect of evaporation.
-% This is because the pyCycle model is solved sequentially component to component during each Newton iteration.
-% So a Nonlinear Block Gauss-Seidel solver would be sufficient to solve this feedback loop.
-% However, the N+3 model already has a nonlinear Newton solver at the Multipoint Design level, so the extractor mass flow rate and injector mass flow rate variables are connected for each design point and use this nonlinear solver to converge the water streams.
-We illustrate the water recirculation loop and the nonlinear solver connections in Figure \ref{fig:N3_xdsm_full}.
+We illustrate the water recirculation loop and the nonlinear solver connections in Figure~\ref{fig:N3_xdsm_full}.
 
@@
 The N+3 model is a collection of components that combine to form a unified zero-dimensional cycle.
-% Zero-dimensional models are a collection of components that combine to form a unified thermodynamic cycle.
 The model consists of twenty-five different elements that define the flow path and the mechanical systems.
@@
 The fan, gearbox, low pressure, and high pressure systems are connected by three mechanical shafts depicted in red in Figure~\ref{fig:N3_original}.
-
-% Three mechanical shafts, depicted in red in Figure~\ref{fig:N3_original}, connect the fan, low pressure, and high pressure systems.
 
@@
 \citeauthor{Hendricks2019} provide the extensive set of balance equations with further details on the construction of the nonlinear system for the N+3 model.
-% We enforce design rules as balance equations between different flight conditions to consider the limitations on performance across the flight envelope.
-% \citeauthor{Hendricks2019} provide the balance equations for the N+3 engine model and further detail the cycle setup.
 
+The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
+To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
+Table~\ref{tab:flight_conds} shows the different altitudes and mach numbers for each flight condition.
+We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
 % [x] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
@@
     \caption{Altitude and mach numbers at each of the flight conditions considered in the multipoint formulation.
+        The humidity ratios were computed from humidity data~\cite{Kalnay1996}.
     }
@@
     \end{tabular}
-    \label{flight_conds}
+    \label{tab:flight_conds}
 \end{table}
-
-The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-Table \ref{flight_conds} shows the different altitudes and mach numbers for each flight condition.
-We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
 % [x] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
@@
 % [x] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
-% The N+3 engine model has complex thermodynamic and performance connections between the different operating conditions.
-% Therefore, the N+3 engine model computes the engine performance at the four different operating conditions in order to resolve these connections.
-% The operating conditions that considered are top-of-climb (TOC), rotating takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
 % [x] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
@@
 The converged model represents a feasible multipoint engine that accounts for design considerations at all four operating conditions.
-% [ ] TODO: AL-PA, I removed a lot of stuff here to simplify this section.
+% [x] TODO: AL-PA, I removed a lot of stuff here to simplify this section.
 %                  - Ultimately I think we need to reference the pyCycle paper to prevent duplicating a bunch of math/text
@@
 
-% To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
-% The final design must satisfies the requirements at each of these operating conditions.
-% The altitude and mach number of each of the operating conditions is shown in Table \ref{flight_conds}.
-
-% NOTE: AL-PA, Using a lot of extra words to say: "The TOC point is the on-design condition."
-% The TOC point determines the flow path areas and turbo machinery properties.
-% NOTE: AL-PA, The design point sizes the flow paths and scales the turbo machinery.
-The off-design has the exact same flow path as the design mode cycle.
-The turbo machinery maps are scaled using scalar quantities for off-design performance.
-% [x] TODO: AL-PA, Don't say "generally" or "essentially" because it makes the method appear ambiguous.
-% The design point for the model sets all of the engine sizing such as areas and pressure ratios across components.
-% The off-design points inherit the cross-sectional areas and turbo machinery scalars from the design point.
-% [ ] TODO: AL-PA, We don't need to talk about the Newton or linear solver details.  Just explain the multipoint model structure with the Newton solver added for context.
-% The design point of the engine model is converged using a linear Newton solver which then passes the geometric sizing variables such as cross-sectional areas and map scalars to the off-design points and similarly converges those.
-% Then, a nonlinear Newton solver is used to converge the overall model with respect to the variable connections between each operating condition.
-% An XDSM diagram of the nominal N+3 engine model is shown in Figure \ref{fig:N3_xdsm} \cite{Hendricks2019}.
-% [x] TODO: AL-PA, I would remove this figure.  Not adding anything more than the detailed XDSM you provide later.
-% [x] TODO: AL-PA, Don't talk about the objective function until the optimization problem section.
-% [x] TODO: AL-PA, Move the discussion about TSEC to the results.  You don't need to introduce the equation here because it has nothing to do with the details of the multipoint model.
-% Our comparison metric is $TSEC_{CRZ}$ but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
-% [x] TODO: AL-PA, Again, move this to the optimization problem section.  You should also try to make this sentence more concise.
-% Therefore, the water mass fraction that will most impact the objective function the most is at the CRZ operating condition and we thus want to size the area of the injector and extractor at CRZ instead of TOC like the rest of the areas are.
-% [x] TODO: You shouldn't say things "normally" occur.  Just tell the reader what you did.
-% I suggest re-writing this to plainly explain why we size the water recirculation at cruise instead of TOC
-% Example: We size the water recovery system at cruise because it is the most important phase for fuel burn reduction. etc...
-% The cross-sectional areas are set at the design point (TOC) and are connected to the off-design points.
-
-% Explain Exit ratios and how BPR and OD net thrusts are set
-% [x] TODO: AL-PA, I would include all four of the balance components here and explain how they effectively act as constraints on the multipoint model.
-% NOTE: AL-PA, See the pyCycle paper, they explain how using the balance residuals creates a reduced design space for the optimization problem.
-% NOTE: AL-PA, You can discuss how this makes the multipoint nonlinear solution more challenging, but improves the optimization problem conditioning.
-% We implement conservation and design constraints in the multipoint model using \emph{balance} residuals.
-% A Newton solver is used to converge these conservation an design values such $r=0$.
-% The conservation balances match the shaft power on the low and high-pressure systems respectively by varying the turbine pressure ratios.
-% The conservation \emph{balance} residuals are associated with each of the three shafts at each design condition.
-% The state variables that set the shaft conservation residuals are the turbomachinery pressure ratios ($PR_{Fan}$, $PR_{LPC}$, $PR_{HPC}$) at TOC and shaft speeds ($N_{Fan}$, $N_{LPC}$, $N_{HPC}$) and engine mass flow rate ($\dot{m}$) at the ``off-design'' points.
-% The design constraints are also set using \emph{balance} residuals.
-% For the TOC point, $T_{4}$ is set by the fuel-to-air ratio (FAR) of the burner and $OPR$ is set by $HPC_{PR}$.
-% Additionally, a constraint on the turbomachinery polytropic efficiency is set based on technological assumptions.
-% These TOC balance residuals are summarized in Equation \eqref{des_resid} \cite{Hendricks2019}.
-
-% \begin{equation}
-%     r_{des} \rightarrow
-%     \begin{cases}
-%         T_{4,TOC} = T_{4,des}                 \\
-%         OPR_{TOC} = OPR_{des}                 \\
-%         \eta_{poly,i,TOC} = \eta_{poly,i,des} \\
-%     \end{cases}
-%     \label{des_resid}
-% \end{equation}
-
-% The outputs for the TOC point based on these design constraints are TSFC and $F_{net}$.
-% For the ``off-design'' points, the target fan stall margin is set by the bypass ratio (BPR) and target net thrust is set by FAR.
-% Additionally, the engine cooling mass flow rate residuals are set by cooling needs at RTO using a perscibed value.
-% These ``off-design'' residuals are summarized in Equation \eqref{od_resid} \cite{Hendricks2019}.
-
-% \begin{equation}
-%     r_{od} \rightarrow
-%     \begin{cases}
-%         R_{Fan} = R_{Fan,target}      \\
-%         F_{net} = F_{net,target}      \\
-%         \dot{m}_{cooling, err, k} = 0 \\
-%     \end{cases}
-%     \label{od_resid}
-% \end{equation}
-
-% \citet{Hendricks2019} implemented four additional balance residuals for the multipoint N+3 model.
-% These balances operate as constraints and create a reduced design space for the optimization problem.
-% The first balance varies the bypass ratio (BPR) at TOC to match a given nozzle velocity ratio.
-% The nozzle velocity ratio is defined as,
-% \begin{equation}
-%     V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
-%     \label{eq:vratio}
-% \end{equation}
-
-% Solving for all of the state and design variables while satisfying constraints could be accomplish with only an optimizer to simplify the problem.
-% However, using a solver to converge constraints using \emph{balance} components creates a reduced-space problem with few design variables for the optimizer.
-% This increases the complexity of the multipoint nonlinear solution but simplifies the problem for the optimizer and is the preferred method in cycle analysis.
-
-% In the N+3 model implementation presented in the pyCycle paper, the bypass ratio (BPR) at TOC is computed using a \emph{balance} component.
-% The \emph{balance} component for $BPR_{TOC}$ uses the exit velocity ratio of the core and bypass nozzles which is given as:
-
-% \noindent
-% where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient of the nozzle which represents non-ideal effects.
-% This adds a constraint where the core exit velocity is higher than the bypass exit velocity.
-
-% [x] TODO: AL-PA, I'm not sure this subsection is necessary.  We will describe the performance metrics in the optimization problem section.  Consider moving it there.
-
-% With all of the sub-models of the N3 engine presented, the complete engine cycle XDSM diagram is shown in Figure \ref{fig:N3_xdsm_full}.
-% This is the multidisciplinary design analysis block of the model.
-
 % [x] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
 % [x] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
-% [ ] TODO: AL-PA, Remove the mdot_inject and mdot_extract stuff, just call it mdot_water
-% [ ] TODO: AL-PA, copy the format of the cooling flow connections for the water mass flow rates
-% [ ] TODO: AL-PA, "Area" should be abbreviated to just the letter "A"
-% [ ] TODO: AL-PA, Change the component types for TOC, RTO, SLS, CRZ, and BALANCE to be implicit groups. They should show up as red polygons.
+% [x] TODO: AL-PA, Remove the mdot_inject and mdot_extract stuff, just call it mdot_water
+% [x] TODO: AL-PA, copy the format of the cooling flow connections for the water mass flow rates
+% [x] TODO: AL-PA, "Area" should be abbreviated to just the letter "A"
+% [x] TODO: AL-PA, Change the component types for TOC, RTO, SLS, CRZ, and BALANCE to be implicit groups. They should show up as red polygons.
 \begin{figure}[hbt!]
@@
 % NOTE: AL-PA, No reason to have an extra subsection here so I removed it
-% \subsection{Problem Statment}
+% \subsection{Problem Statement}
 % Briefly discuss the optimization problem
@@
 We performed multipoint gradient-based design optimization of the N+3 engine model considering the TOC, RTO, SLS, and CRZ flight conditions.
-% We will perform gradient-based design optimization of the engine model with the multipoint architecture that considers each of the flight conditions experienced by commercial aircraft.
-% We will perform a parameter sweep of the limiting constraint to understand the impact of different emissions and performance requirements on the design space.
 % NOTE: AL-PA, I re-wrote this to be more direct
 The objective is to minimize fuel burn subject to design and performance constraints.
-% The objective is to minimize the TSEC since that is our performance metric for comparing the two types of fuels.
-% However, since we are constraining net thrust at each operating condition this optimization problem becomes ill-posed.
-% Therefore, we will minimize fuel flow rate, $W_{fuel}$ at the cruise condition subject to net thrust and engine diameter constraints since this will accomplish the same goal with a better posed problem.
 % [x] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
@@
 % However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
-% TODO: Update mdolab.bib
-A better metric for comparing Jet-A versus hydrogen is thrust-specific energy consumption (TSEC). %\cite{Adler2023}.
-TSEC is TSFC multipied by the lower heating value (LHV) of the fuel shown in Equation~\eqref{eq:tsec}.
+A better metric for comparing Jet-A versus hydrogen is thrust-specific energy consumption (TSEC)~\cite{Adler2023}.
+TSEC is TSFC multiplied by the lower heating value (LHV) of the fuel shown in Equation~\eqref{eq:tsec}.
 
@@
 
-% [ ] TODO: AL-PA, TSEC is not the objective.  Fuel burn is the objective.  TSEC is the efficiency metric of interest.
-Therefore, TSEC at the cruise condition is the objective function in the optimization problem.
-% [ ] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
-An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.
+For this work we are concerned with minimizing fuel burn of the engine subject to known thrust constraints.
+% [x] TODO: AL-PA, TSEC is not the objective.  Fuel burn is the objective.  TSEC is the efficiency metric of interest.
+TSEC will be used as a efficiency metric at the cruise condition to compare the two fuels in the results.
+% [x] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
+Large multidisciplinary optimization problems are commonly represented with extended design structure matrix (XDSM) diagrams.
+XDSM diagrams are used to visualize the complex implicit and explicit relationships between functions, the solver, and optimizer.
+An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure~\ref{fig:N3_opt_xdsm}.
 
@@
 % [x] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
-% [ ] TODO: AL-AL, I decided this is no longer necessary
-% The TOC point constraints shown in Figure \ref{fig:N3_opt_xdsm} are only the constraints imposed on the model at optimizer level.
+% [x] TODO: AL-AL, I decided this is no longer necessary
 
-% [ ] TODO: AL-PA, I would break this up into two or more sentences.
-The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
-% [ ] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
-% [ ] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
-Only the water recovery fraction at CRZ is a design variable since we are optimizing $\rm{TSEC}_{\rm{CRZ}}$.
-TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
+% [x] TODO: AL-PA, I would break this up into two or more sentences.
+The design variables for this problem are pressure controls such as fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$).
+Other design variables are temperature controls such as burner temperature at RTO ($T_{4,\rm{RTO}}$) and the TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$).
+The nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$) is also added as a design variable to control the bypass ratio and mass flow rate through the engine.
+Finally, the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$) is added as a design variable in order to take advantage of water recirculation.
+% [x] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
+% [x] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
+We only add the water recovery fraction at CRZ as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.
+The CRZ operating condition is also the longest flight segment and therefore contributes the most to long-term performance.
+TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
 \begin{equation}
@@
 
-% [ ] TODO: AL-PA, You already explained the flight conditions in the multipoint section so not necessary here
-% [ ] TODO: AL-PA, Combine these into a single sentence.
-% [ ] TODO: AL-PA, I would describe the constraints in more detail here.  This might be a good spot to talk about the constraints imposed by the balance comps at the top level.
+% [x] TODO: AL-PA, You already explained the flight conditions in the multipoint section so not necessary here
+% [x] TODO: AL-PA, I would describe the constraints in more detail here.  This might be a good spot to talk about the constraints imposed by the balance comps at the top level.
 %                  - i.e the SLS and CRZ net thrust constraints
@@
 %                  - i.e The interdependence of the TOC mass flow rate and the RTO temperature
-This optimization problem was run for both Jet-A and H2 fuels using the fuel properties in \ref{fuel_props} and flight conditions in Table \ref{flight_conds}.
-The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
+
+The net thrust for the SLS and CRZ conditions are set using \emph{balance} components.
+Net thrust for SLS is constrained to be about 1.2335 times the net thrust at RTO.
+Similarly, the net thrust at CRZ is constrained to be 0.9 times the net thrust at TOC.
+The bypass ratio (BPR) at TOC is set by the \emph{balance} component such that the CRZ nozzle velocity ratio meets a given target value.
+The nozzle velocity ratio is defined as,
+\begin{equation}
+    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
+    \label{eq:vratio}
+\end{equation}
+
+\noindent
+where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient which accounts for non-ideal effects.
+This adds a constraint to ensure that the core exit velocity is higher than the bypass exit velocity.
+The TOC engine mass flow rate is set by the \emph{balance} component using the combustor temperature at RTO, $T_{4,\rm{RTO}}$.
+
+% [x] TODO: AL-PA, Combine these into a single sentence.
+The fuel properties used in the engine model are given in~\ref{fuel_props}.
 
@@
 
-% [x] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
+The optimization problem objective function, design variables, and constraints are shown in Table~\ref{tab:opt_problem}.
+The thermodynamic cycle design variable ranges are determined from the expected N+3 technology limits~\cite{Hendricks2019}.
+Additionally, the design variable ranges are shown in Table~\ref{tab:dv_table}.
+
+% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
 % [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
 % [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
-% [ ] TODO: PA-PA, explain variable ranges
+% [x] TODO: PA-PA, explain variable ranges
 \begin{table}[hbt!]
@@
         \hline
-        minimize        & $\rm{TSEC}_{\rm{CRZ}} $        & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
+        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Thrust-specific energy consumption at CRZ (Equation~\eqref{eq:tsec})     & \si{lbm/hr/lbf} & 1        \\
                         &                                &                                                                          &                 &          \\
@@
                         & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R}  & 1        \\
-                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation \eqref{t4ratio})               & -              & 1        \\
-                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation \eqref{vratio}) & -              & 1        \\
+                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -               & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -               & 1        \\
         \cline{3-5}
@@
 
-% OpenMDAO supports the use of different optimization packages including Scipy and PyOptSparse.
-% PyOptSparse is an object-oriented framework for formulating and solving nonlinear constrained optimization problems.
-% PyOptSparse was chosen as the main optimization package for this problem due to its wide range of open-source gradient-based optimizers and integration with  \cite{Wu2020a}.
-
-% SNOPT (Sparse Nonlinear OPTimizer) was the optimizer chosen for this work.
-% SNOPT is a state-of-the-art optimizer used to solve large-scale optimization problems (linear and nonlinear).
-% The software uses a sparse SQP (sequential quadratic programming) algorithm with a limited-memory quasi-Newton approximation to the Hessian of the lagrangian.
-% SNOPT is particularly useful for nonlinear problems whose functions and derivatives are expensive compute.
-% An augmented Lagrangian merit function ensures convergence from an arbitrary point.
-% SNOPT allows the nonlinear constraints to be violated (if necessary) and minimizes the sum of these violations.
-% Due to the robustness of the algorithm, SNOPT is a perfect optimizer to solve the highly complex Multipoint systek since the pyCycle engine cycle would occasionally reach a point that is non-physical and would thus cause the solver to fail.
-% SNOPT is able to respond to these solver failures and backtrack to a region in the design space that is physical and continue the optimization \cite{Gill2005a}.
+During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time, they had opposite effects on the design.
+The optimizer increases $X_{\rm{H_2O,CRZ}}$ which allows for a lower optimal $T_{4,\rm{RTO}}$.
+This is likely due to the interdependency between engine mass flow rate and $T_{4,\rm{RTO}}$.
+As the recovery water fraction increases less mass flow rate is required through the engine which lowers the required $T_{4,\rm{RTO}}$ for a required level of thrust.
+It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules.
+Since $T_{4,\rm{RTO}}$ would be pushed down to its lower limit, it was set as the optimal value from the optimizations with no water recovery.
+This allowed the optimizer to find the maximum $X_{\rm{H_2O,CRZ}}$ that would allow the most water to be recirculated.
+The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
 
@@
 \label{sec:results}
-% [ ] TODO: AL-PA, I would move the following two lines into the optimization problem section and re-write them to be a single concise sentence.
-Our fuel performance metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
-Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.
 
-% [ ] TODO: AL-PA, This is confusing.  You have two different optimization problem formulations and that is not clear here.
+\subsection{Optimization Results}
+\label{sub:opt_res}
+% [x] TODO: AL-PA, I would move the following two lines into the optimization problem section and re-write them to be a single concise sentence.
+
+% [x] TODO: AL-PA, This is confusing.  You have two different optimization problem formulations and that is not clear here.
 %                  - I think you need to add information to the previous section about the optimization problem that explains all of this information.
 %                    Introducing this at the beginning of the results does not make sense.
-When $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time it was found that the optimizer pushes $T_{4,\rm{RTO}}$ down and $X_{\rm{H_2O,CRZ}}$ up.
-Since these two variables are at odds with each other and the upper limit for $X_{\rm{H_2O,CRZ}}$ is where the model breaks, $T_{4,\rm{RTO}}$ was set as the optimal value from the optimizations with no water recirulation.
-The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
 
 % Results of optimization problems
-% [ ] TODO: AL-PA, Include the optimization and feasibility targets and talk about the number of iterations for each optimization.
-% [ ] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
-The 4 optimizations mentioned in the section \ref{sec:optprob} were run and solved.
+% [x] TODO: AL-PA, Include the optimization and feasibility targets and talk about the number of iterations for each optimization.
+% [x] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
+The 4 optimizations mentioned in the section~\ref{sec:optprob} were run and solved.
+The optimality and feasibility targets for the optimizations was $1e-6$.
+These optimizations took between 20-30 major SNOPT iterations to reach optimality and run in approximately 36-48 minutes on a standard laptop.
 The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_summary}.
+% [x] TODO: AL-PA, No need to explain this and then answer your own observation from the plot.  Just tell the reader what the plot shows.
+% [x] TODO: AL-PA, Be cognizant that latex will not always put the figure right above a paragraph.  So saying "From this plot" might not make sense.  Need to directly reference the figure.
+% NOTE: AL-PA, The merit function is not a time-dependent quantity, so there's no "steady state".  Its enough to just say the merit function was reduced by X amount in X number of iterations...
+From Figure~\ref{fig:history_summary} we observe quadratic convergence in the optimality of the problem near the optimal solution as expected.
+A feasible design is reached and the merit function is reduced to its final value in about 10 iterations for all cases.
 
-% [ ] TODO: AL-PA, Stretch the aspect ratio of this figure and squeeze the height in matplotlib.  You don't need this many values on the y-axis for the summary plots.
+% [x] TODO: AL-PA, Stretch the aspect ratio of this figure and squeeze the height in matplotlib.  You don't need this many values on the y-axis for the summary plots.
 % Feasibility, Optimality, Merit history
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{opt_summary.pdf}
-    \caption{The optimality, feasibility, and merit fuction history for each optimization problem.
+    \includegraphics[width=1.0\textwidth]{opt_summary.pdf}
+    \caption{The optimality, feasibility, and merit function history for each optimization problem.
         Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
@@
 
-% [ ] TODO: AL-PA, No need to explain this and then answer your own observation from the plot.  Just tell the reader what the plot shows.
-% [ ] TODO: AL-PA, Be cognizant that latex will not always put the figure right above a paragraph.  So saying "From this plot" might not make sense.  Need to directly reference the figure.
-% NOTE: AL-PA, The merit function is not a time-dependent quantity, so there's no "steady state".  Its enough to just say the merit function was reduced by X amount in X number of iterations...
-From this plot we can visually check that each optimization achieved optimality and feasibility, and that the merit function reached a steady-state value.
-Indeed, we observe quadratic convergence in the optimality of the problem near the optimal solution as expected.
-The design variable history for each optimization problem is shown in Figure \ref{fig:history_dvs}.
+The optimal design variables for each of the four optimizations is shown in Table~\ref{tab:dv_opt}.
+% [x] TODO: AL-PA, You should explain the plot before it's introduced to the reader.  Stating what's on the figure after it appears doesn't provide any insight.
+% [x] TODO: AL-PA, See my previous TODOs but this needs some more explanation in the optimization problem section.
+Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
 
-% [ ] TODO: AL-PA, Convert this to a table so it takes up less space.  Just show that final DV values for each optimization.
-% DV history
-\begin{figure}[hbt!]
+\begin{table}[hbt!]
     \centering
-    \includegraphics[width=0.8\textwidth]{dvs.pdf}
-    \caption{The design variable history for each optimization problem.
-        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
-    \label{fig:history_dvs}
-\end{figure}
+    \caption{Optimization results of the N+3 engine for four optimizations using jet-A and hydrogen fuel with and without water recirculation.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l l l l l}
+                    & Variable/Function         & Jet-A Dry & Jet-A Wet & \ce{H2} Dry & \ce{H2} Wet & Units           \\
+        \toprule
+        objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \si{lbm/s}      \\
+                    & $\rm{TSEC}_{\rm{CRZ}}$    & 8186.254  & 7766.338  & 8295.236    & 7859.635    & \si{lbm/hr/lbf} \\
+        \hline
+        variables   & $x_{H2O,CRZ}$             & -         & 0.3       & -           & 0.17        & -               \\
+                    & $\rm{PR}_{fan,TOC}$       & 1.285     & 1.292     & 1.288       & 1.297       & -               \\
+                    & $\rm{PR}_{LPC,TOC}$       & 4.0       & 4.0       & 4.0         & 4.0         & -               \\
+                    & $\rm{OPR}_{\rm{TOC}}$     & 61.012    & 61.188    & 60.660      & 61.952      & -               \\
+                    & $T_{4,ratio}$             & 0.913     & 0.911     & 0.918       & 0.915       & -               \\
+                    & $T_{4,RTO}$               & 3220.574  & -         & 3204.071    & -           & $^\circ$R       \\
+                    & $V_{ratio,CRZ}$           & 1.35      & 1.35      & 1.35        & 1.35        & -               \\
+        \hline
+        constraints & $F_{net,TOC}$             & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf             \\
+                    & $D_{Fan}$                 & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$          \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:dv_opt}
+\end{table}
 
-% [ ] TODO: AL-PA, You should explain the plot before it's introduced to the reader.  Stating what's on the figure after it appears doesn't provide any insight.
-From this figure we see that the design variables start at the initial values and converge toward their optimal value.
-% [ ] TODO: AL-PA, See my previous TODOs but this needs some more explanation in the optimization problem section.
-Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
-The constraint history for each optimization problem is shown in Figure \ref{fig:history_cons}.
-
-% [ ] TODO: AL-PA, This is unnecessary because you already show that the optimization is feasible.  Just write out these values in a description of the constraints in the paper.
-% Constraint history
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=0.75\textwidth]{cons.pdf}
-    \caption{The constraint history for each optimization problem.
-        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
-    \label{fig:history_cons}
-\end{figure}
-
-% [ ] TODO: AL-PA, Constraints are either feasible or they aren't, can't be "for the most part"
-From this figure we can see that the constraints are quickly satisfied and for the most part remain feasible for the duration of the optimization.
-% [ ] TODO: AL-PA, Elaborate on why we include this parallel axis plot.  Why is it important?  What insight does it provide to the reader?  Compare and contrast the optimization results!
-The resulting optimal values from the optimization problems are shown in Figure \ref{fig:parallel_coords} on a parallel coordinate plot.
-% The resulting values of the optimization problem for Jet-A and hydrogen without water recovery are shown in Tables \ref{tab:res_thermo_opt_JetA} and \ref{tab:res_thermo_opt_H2}, respectively.
-% Similarly, the resulting values of the optimization problem for Jet-A and hydrogen with water recovery are shown in Tables \ref{tab:res_full_opt_JetA} and \ref{tab:res_full_opt_H2}, respectively.
+% [x] TODO: AL-PA, Constraints are either feasible or they aren't, can't be "for the most part"
+% [x] TODO: AL-PA, Elaborate on why we include this parallel axis plot.  Why is it important?  What insight does it provide to the reader?  Compare and contrast the optimization results!
+The resulting optimal values from the optimization problems are shown in Figure~\ref{fig:parallel_coords} on a parallel coordinate plot.
+Figure~\ref{fig:parallel_coords} shows the how each of the optimal overall design of the engine compares across fuel type with and without water recovery.
+% [x] TODO: AL-PA, How are they similar? Be specific.
+% [x] TODO: AL-PA, I would move a lot of this up to when you introduce the parallel axis plot.
+We see that across the range of values that each optimal value is very similar with the exception of water recovery fraction.
+As noted earlier, the water recovery fractions are different because the optimizer pushes $X_{\rm{{H_2O},CRZ}}$ to the highest value it can attain.
+The $\rm{PR}_{fan,TOC}$ and $V_{ratio,CRZ}$ design variables go to their upper and lower limits, respectively.
 
@@
 
-% [ ] TODO: AL-PA, I would move a lot of this up to when you introduce the parallel axis plot.
-% [ ] TODO: AL-PA, How are they similar? Be specific.
-We can see that the resulting engine designs are all very similar.
-% [ ] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
+% [x] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
+$\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than the $\rm{OPR}_{\rm{TOC}}$.
+$V_{ratio,CRZ}$ goes toward its lower value since the engine is more efficient when the bypass stream is larger and has more mass flow through it.
 The main differences in the engine designs are the pressure ratios and temperatures.
-% [ ] TODO: AL-PA, Why is pushed to the upper limit?  Explain how it improves the combustion characteristics.
+% [x] TODO: AL-PA, Why is pushed to the upper limit?  Explain how it improves the combustion characteristics.
 Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
-The recovery fraction does not directly relate to the mass flow rate of recirculated water.
-The recovery fraction for \ce{H2} is smaller than the recovery fraction for jet-A because there is more water produced in the combustion process.
+One reason the water recovery fraction increases to its upper bound use to improve combustion characteristics of the core flow when fuel is injected.
+The same thrust output can be achieved with water recovery at a lower FAR, slightly lower temperature, and less total mass flow rate.
+The recovery fraction does not directly relate to the mass flow rate of recirculated water since more available water will increase the recirculation flow rate.
+It is noted that recovery fraction for \ce{H2} is smaller than the recovery fraction for Jet-A because there is more water produced in the combustion process.
 However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for jet-A.
-% Given that more water is present in the exhaust stream of the H2 engine, the H2 engine can recover a smaller fraction of the water compared to the Jet-A engine.
-% The water recovery flow rates for the Jet-A and H2 engines was 0.324 $\si{lbm/s}$ and 0.405 $\si{lbm/s}$, respectively.
-The \ce{H2} has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
+The \ce{H2} fuel has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
 We see slightly higher pressure ratios across the fan with water recovery leading to a larger overall pressure ratio.
-The LPC pressure ratio tend to the upper bound for each optimization with and without water recovery enabled.
-% [ ] TODO: AL-PA, I'm beating a dead horse here but you don't need to say this if you mention it earlier
-% We only see differences in $T_{4,\rm{RTO}}$ without water recovery due to these values are fixed for water recovery.
-% [ ] TODO: AL-PA, Why is the T4 ratio higher?  Explain it in terms of the fuel properties.  The reader can look at the plot themselves and see that it's higher.
-The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of H2.
-Furthermore, adding water recovery slightly decreases the $T_{4,\rm{ratio}}$ value.
-% [ ] TODO: AL-PA, Why are the temperatures colder with the H2 fuel?  Why does water recovery make them even lower?
-% [ ] TODO: AL-PA, I wouldn't say "cooler" I would say "less than" or "colder"
-Therefore, temperatures are cooler with the \ce{H2} fuel and even slightly cooler when adding water recovery.
-% [ ] TODO: AL-PA, Why did the optimizer push the value of T4 down with water recovery?  Dig into this more.
-It is noted that with more water recovery the farther the optimizer would push the value of $T_{4,\rm{RTO}}$ down.
-Therefore, there are temperature-related advantages of using water recovery to maintain a certain effenciency and thrust.
-% [ ] TODO: AL-PA, We want to discuss how the thrust from the fan/core changes when we introduce water recovery.
+% [x] TODO: AL-PA, I'm beating a dead horse here but you don't need to say this if you mention it earlier
+% [x] TODO: AL-PA, Why is the T4 ratio higher?  Explain it in terms of the fuel properties.  The reader can look at the plot themselves and see that it's higher.
+The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of \ce{H2}.
+This is most likely due to the properties of \ce{H2} compared to Jet-A.
+\ce{H2} can has a wider combustion flammability limit and allows the engine to burn at a lower equivalence ratio to attain the same thrust requirements.
+Burning leaner not only cools the engine but also reduces fuel consumption.
+% [x] TODO: AL-PA, Why are the temperatures colder with the H2 fuel?  Why does water recovery make them even lower?
+% [x] TODO: AL-PA, I wouldn't say "cooler" I would say "less than" or "colder"
+Therefore, TOC temperatures are colder with the \ce{H2} fuel and even slightly colder when adding water recovery.
+The engine is likely able to size the components with water recovery so that the same thrust is generated at a lower fuel-to-air ratio.
+Furthermore, adding water recovery at CRZ slightly decreases the $T_{4,\rm{ratio}}$ value.
+As noted earlier, the water recovery and injection allows the engine achieve the same level of thrust at a lower temperature.
+% [x] TODO: AL-PA, Why did the optimizer push the value of T4 down with water recovery?  Dig into this more.
+In terms of pressure ratios we see that the fan pressure ratio increases with hydrogen fuel and even more with water recovery.
+This is again likely due to using \ce{H2} and water recovery each resizing the engine to increase the amount of thrust generated by the fan.
+% [x] TODO: AL-PA, We want to discuss how the thrust from the fan/core changes when we introduce water recovery.
 % NOTE: AL-PA, The idea here is to communicate the effect of water recovery on the core power vs. the fan power.
-The breakdown of thrust for each point is shown in Table \ref{tab:thrust}.
-This table shows the resulting net thrust, gross thrust, and ram drag of each engine design for the four optimizations performed.
+The breakdown of the gross thrust fractions from the core and bypass nozzles for each point is shown in Table~\ref{tab:thrust}.
+Table~\ref{tab:thrust} shows that the fraction of gross thrust generated by the core nozzle is decrease when we use \ce{H2} and add water recovery.
+Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel.
+The increase in $\rm{OPR}_{\rm{TOC}}$ reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
 
@@
 % [x] TODO: PA-PA: Add thrust splits for each opt
-% [ ] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
+% [x] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
 %                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
@@
     \begin{tabular}{r l l l l l}
-        Point & Parameter              & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
+        Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
         \toprule
-              & Net Thrust, \si{lbf}   & 5800.0    & 5800.0    & 5800.0  & 5800.0  \\
-        TOC   & Ram Drag, \si{lbf}     & 19623.4   & 19623.4   & 19623.4 & 19623.4 \\
-              & Gross Thrust, \si{lbf} & 25423.4   & 25423.4   & 25423.4 & 25423.4 \\
+        TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
+              & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
         \hline
-              & Net Thrust, \si{lbf}   & 22800.0   & 22800.0   & 22800.0 & 22800.0 \\
-        RTO   & Ram Drag, \si{lbf}     & 17089.7   & 17043.5   & 17070.8 & 17014.6 \\
-              & Gross Thrust, \si{lbf} & 39889.7   & 39843.5   & 39870.8 & 39814.6 \\
+        RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
+              & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
         \hline
-              & Net Thrust, \si{lbf}   & 28620.8   & 28620.8   & 28620.8 & 28620.8 \\
-        SLS   & Ram Drag, \si{lbf}     & 61.8      & 61.7      & 61.8    & 61.6    \\
-              & Gross Thrust, \si{lbf} & 28682.7   & 28682.5   & 28682.6 & 28682.4 \\
+        SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
+              & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
         \hline
-              & Net Thrust, \si{lbf}   & 5220.0    & 5220.0    & 5220.0  & 5220.0  \\
-        CRZ   & Ram Drag, \si{lbf}     & 19194.0   & 19152.9   & 19190.3 & 19144.1 \\
-              & Gross Thrust, \si{lbf} & 24414.0   & 24372.9   & 24410.3 & 24364.1 \\
+        CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
+              & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
         \bottomrule
@@
 
-% [ ] TODO: AL-PA, Again, this table might not be directly above this text in the PDF so you need to use \ref{tab:thrust}.
-% [ ] TODO: AL-PA, You already showed the constraint values and that the design is feasible, the reader knows what the net thrust should be from that information.
-From this table we can see that the net thrust is constrained at values set by \emph{balance} components or optimization constraints.
+% [x] TODO: AL-PA, Again, this table might not be directly above this text in the PDF so you need to use \ref{tab:thrust}.
+% [x] TODO: AL-PA, You already showed the constraint values and that the design is feasible, the reader knows what the net thrust should be from that information.
 % [x] TODO: AL-PA, Thrust differences?  These values change with mass flow rate which we know is affected by water recovery.  Probably need to remove the following stuff discussing this.
@@
 
-% We see the largest thrust differences at the RTO and CRZ points.
-% Since net thrust is constrainted, the optimizer sizes the engine to reduce ram drag slightly from Jet-A to H2.
-% Water recirculation provides an even more significant improvement in ram drag for both Jet-A and H2 at CRZ with reductions of 0.21\% and 0.24\%, respectively.
-% Both fuels have similar efficiencies at the optimal design with Jet-A having a slight advantage in thems of TSEC.
+We can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure~\ref{fig:barchart}.
 
-% [ ] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
-Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water injection.
-In fact, we can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure \ref{fig:barchart}.
-
-% [ ] TODO: I would change this to the horizontal bar chart and plot both H2 and Jet-A on the same axis
+% [x] TODO: I would change this to the horizontal bar chart and plot both H2 and Jet-A on the same axis
 % See this example in niceplots: https://github.com/mdolab/niceplots/blob/main/examples/plot_bar_chart.py and https://github.com/mdolab/niceplots/blob/main/examples/ref/bar_chart.png
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{JetA-H2_TSEC_diff.pdf}
+    \includegraphics[width=0.65\textwidth]{bar_chart.pdf}
     \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
@@
 
-Based on this analysis and model, we see an improvement greater than 5\% at CRZ for TSEC for both fuels.
+We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
+% [x] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
+Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water recovery and injection.
 This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
-% [ ] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
-Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser~\cite{Strom2002}.
-% This would incur larger condenser mass and pressure penalties compared to the H2 engine which would have more water and requires a smaller fraction of that water.
+% [x] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
+As~\citeauthor{Strom2002} points out, the water in the exhaust of a \ce{H2}-powered engine would have close to 3 times the amount of a similar Jet-A engine.
+Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser.
 Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
-% [ ] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
+\subsection{Condenser Design Space Study}
+\label{sub:dpqp_sweep}
+% [x] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
 %                  Might be worth moving this into a new subsection.
-% [ ] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
-Since there is a lack of literature on large-scale water condensers that are designed to fit inside a turbofan engine, a relatively low pressure loss condenser would need to be developed for this system to work.
-Given the lack of knowledge of the type of condenser that would need to be require, we performed a pressure loss sweep of the H2 engine.
-% [ ] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"
+% [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
+The large efficiency improvement gained from water recirculation warrant a study of a condenser that could be developed to capture these gains.
+Companies that are developing engines with water recirculation suggest that hydrogen can be used to as a heat sink in a water condenser~\cite{arpa-e_2021}.
+To motivate water recirculation technology it of interest to explore the design space for a condenser designed to fit inside the exhaust stream of a turbofan engine.
+A relatively low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
+% [x] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"
 pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
-This coefficient is the ratio of change in total pressure normalized by the inlet pressure of the duct.
-% [ ] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
-% [ ] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
-The pressure loss of the duct just upstream of the extractor was varied while the rest of the engine design variables were optimized.
-Figure \ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
+This coefficient is the pressure loss relative to the inlet pressure of the duct.
+% [x] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
+% [x] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
+We varied the total pressure loss across the extraction model to simulate drag from an increasingly large condenser.
+The rest of the engine design variables were optimized during this pressure loss sweep to determine the how the optimal amount of water recovery changed based on drag losses from the condenser.
+Figure~\ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
 
@@
     \begin{subfigure}[t]{0.49\textwidth}
-        % [ ] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
+        % [x] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
         \includegraphics[width=\textwidth]{N3_dpqp.pdf}
@@
     \begin{subfigure}[t]{0.49\textwidth}
-        % [ ] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
+        % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
         \includegraphics[width=\textwidth]{N3_wdot.pdf}
@@
 
-% TSEC as a function of dPqP
-% \begin{figure}[hbt!]
-%     \centering
-%     \includegraphics[width=0.8\textwidth]{N3_dpqp.pdf}
-%     \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-%         The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimzation problem without water recovery.
-%         This shows the working space available for designing a water condensor while still gaining the benefits of water recovery.}
-%     \label{fig:dpqp_sweep}
-% \end{figure}
-
 From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
@@
 This benefit area would be reduced if a smaller fraction of water recovered could be obtained.
-Figure \ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
-
-% \begin{figure}[hbt!]
-%     \centering
-%     \includegraphics[width=0.8\textwidth]{N3_wdot.pdf}
-%     \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-%         The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
-%         The engine was optimized with the water recovery upperbound of 17\%.
-%     }
-%     \label{fig:dpqp_wdot}
-% \end{figure}
+Figure~\ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
 
@@
 Since the water recovery fraction is always pushed to 17\%, the water recovered is increased to overcome the pressure loss.
-This effect helps the engine increase the benefit area in Figure \ref{fig:dpqp_sweep}.
+This effect helps the engine increase the benefit area in Figure~\ref{fig:dpqp_sweep}.
 
@@
 System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
-The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, presusres and velocities within the engine.
-An additional design variable controlling how much water is recirulated is added at the CRZ point to improve the fuel burn.
+The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
+An additional design variable controlling how much water is recirculated is added at the CRZ point to improve the fuel burn.
+The optimization problem is then solved for four cases: with Jet-A or hydrogen fuel and with and without water recirculation.
 
 The results from the optimization problems show temperature, thrust, and efficiency improvements when using hydrogen as a fuel with water circulation.
-Thermal reductions will improve the lifetime of the engine which impact maintanence and overall costs.
+Thermal reductions will improve the lifetime of the engine which impact maintenance and overall costs.
 Between the two fuels, we see similar values of TSEC.
@@
 
-Technological problems do exist such as how to design a condensor that can recover a large portion of the exhaust water without large pressure losses.
+Technological problems do exist such as how to design a condenser that can recover a large portion of the exhaust water without large pressure losses.
 However, the thermal properties of hydrogen provide a heat sink and thus a readily available resource for condensation.
@@
 The results from this work outline the working space available for the design of such a condenser.
-% heavier engine due to condensor, but less fuel needed
+% heavier engine due to condenser, but less fuel needed
 
 \section{Acknowledgements}
+We would like to thank Justin Grey for his help with the pyCycle components of this work.
+Since there is very little pyCycle documentation, his expertise and knowledge of the tool helped make the development of the custom pyCycle components possible.
 

### 2023-05-06 conference-paper/main.tex
added revision edits and fixed plots

@@
     Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
-    In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between jet-A and hydrogen fuels.
+    In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
     We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
@@
 The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
-N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR).
+N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiencies can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR).
 Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
-Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits~\cite{Adler2023}.
+Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that can offset the benefits~\cite{Adler2023}.
 However, hydrogen is a versatile fuel with advantageous molecular and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
@@
 % [x] TODO: AL-PA, Should try to find a citation for this if one exists.
-Traditional propulsion systems that burn hydrocarbon fuels would require external water storage on the aircraft for water injection~\cite{Mourouzidis2015}.
-The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
+Traditional propulsion systems that burn hydrocarbon fuels would require external demineralized water storage on the aircraft for water injection~\cite{Mourouzidis2015}.
+The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft over the entire flight.
 The main product of hydrogen combustion is water vapor that we can recover from the exhaust stream~\cite{Strom2002}.
@@
 We develop pyCycle components for water injection and vapor recovery to quantify the benefit of a closed loop recirculation system.
-We use gradient-based optimization to minimize fuel burn subject to performance requirements using both jet-A and hydrogen at a range of flight conditions.
-The optimized results show the trade-off between complexity, performance, and efficiency for jet-A and hydrogen fuels.
+We use gradient-based optimization to minimize fuel burn subject to performance requirements using both Jet-A and hydrogen at a range of flight conditions.
+The optimized results show the trade-off between complexity, performance, and efficiency for Jet-A and hydrogen fuels.
 
@@
 % [x] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
-We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to upstream of the compressors.
+We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to a point upstream of the compressors.
 The recovery system injects vaporized water into the core stream that reduces the combustion temperature due to heat absorption.
-The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycle it back to the injector.
+The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycles it back to the injector.
 Figure~\ref{fig:n3_clvr} shows the water vapor recovery loop implemented in a turbofan engine.
@@
         Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
-        Flow stations are identified with bubble text
+        Flow stations are identified with bubble text.
     }
@@
         Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
-        Black arrows are flow connections, blue boxes are cycle elements
+        Black arrows are flow connections, blue boxes are cycle elements.
         Flow stations are identified with bubble text.
@@
 The interconnections between flight conditions create a complex nonlinear loop, shown in Figure~\ref{fig:N3_xdsm_full}.
-The converged model represents a feasible multipoint engine that accounts for design considerations at all four operating conditions.
+The converged model represents a feasible multipoint engine that accounts for design considerations and conservation laws at all four operating conditions.
 % [x] TODO: AL-PA, I removed a lot of stuff here to simplify this section.
@@
 Typical gas-turbine analysis measures the efficiency using the thrust-specific fuel consumption (TSFC).
-% For measuring the efficiency of jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
-However, this metric is not useful in the comparison of efficiency between jet-A and hydrogen fueled cycle models because of the differences in fuel density and energy capacity.
+% For measuring the efficiency of Jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
+However, this metric is not useful in the comparison of efficiency between Jet-A and hydrogen fueled cycle models because of the differences in fuel density and energy capacity.
 % However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
@@
 % [x] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
+The fuel properties used in the engine model are given in~\ref{fuel_props}.
+
+% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
+% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
+\begin{table}[hbt!]
+    \centering
+    \caption{
+        N+3 model fuel properties.
+        The lower heating values are given for each fuel used to compute TSEC.}
+    \begin{tabular}{r r r l}
+        \hline
+        Parameter              & Value   & Units        & Description                                                                                                            \\
+        \hline                                                                                                                                                                   \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+        \hline
+    \end{tabular}
+    \label{fuel_props}
+\end{table}
+
 Large multidisciplinary optimization problems are commonly represented with extended design structure matrix (XDSM) diagrams.
@@
 Other design variables are temperature controls such as burner temperature at RTO ($T_{4,\rm{RTO}}$) and the TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$).
+TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
+
+\begin{equation}
+    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
+    \label{t4ratio}
+\end{equation}
+
+\noindent
 The nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$) is also added as a design variable to control the bypass ratio and mass flow rate through the engine.
+The nozzle velocity ratio is defined as,
+
+\begin{equation}
+    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
+    \label{eq:vratio}
+\end{equation}
+
+\noindent
+where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient which accounts for non-ideal effects.
 Finally, the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$) is added as a design variable in order to take advantage of water recirculation.
@@
 The CRZ operating condition is also the longest flight segment and therefore contributes the most to long-term performance.
-TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
-\begin{equation}
-    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
-    \label{t4ratio}
-\end{equation}
 
@@
 The net thrust for the SLS and CRZ conditions are set using \emph{balance} components.
-Net thrust for SLS is constrained to be about 1.2335 times the net thrust at RTO.
+Net thrust for SLS is constrained to be 1.2335 times the net thrust at RTO which itself is constrained to 22800 \si{lbf}.
 Similarly, the net thrust at CRZ is constrained to be 0.9 times the net thrust at TOC.
 The bypass ratio (BPR) at TOC is set by the \emph{balance} component such that the CRZ nozzle velocity ratio meets a given target value.
-The nozzle velocity ratio is defined as,
-\begin{equation}
-    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
-    \label{eq:vratio}
-\end{equation}
-
-\noindent
-where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient which accounts for non-ideal effects.
-This adds a constraint to ensure that the core exit velocity is higher than the bypass exit velocity.
+The CRZ velocity ratio constraint ensures that the core exit velocity is higher than the bypass exit velocity.
 The TOC engine mass flow rate is set by the \emph{balance} component using the combustor temperature at RTO, $T_{4,\rm{RTO}}$.
-
 % [x] TODO: AL-PA, Combine these into a single sentence.
-The fuel properties used in the engine model are given in~\ref{fuel_props}.
-
-% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
-% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
-\begin{table}[hbt!]
-    \centering
-    \caption{
-        N+3 model fuel properties.
-        The lower heating values are given for each fuel used to compute TSEC.}
-    \begin{tabular}{r r r l}
-        \hline
-        Parameter              & Value   & Units        & Description                                                                                                            \\
-        \hline                                                                                                                                                                   \\
-        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
-        \hline
-    \end{tabular}
-    \label{fuel_props}
-\end{table}
 
@@
         \hline
-        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Thrust-specific energy consumption at CRZ (Equation~\eqref{eq:tsec})     & \si{lbm/hr/lbf} & 1        \\
+        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
                         &                                &                                                                          &                &          \\
-        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery fraction at CRZ                                           & -               & 1        \\
+        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery mass fraction at CRZ                                      & -              & 1        \\
                         & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                   & -              & 1        \\
@@
 
-During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time, they had opposite effects on the design.
+During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time they had opposite effects on the design.
 The optimizer increases $X_{\rm{H_2O,CRZ}}$ which allows for a lower optimal $T_{4,\rm{RTO}}$.
@@
 As the recovery water fraction increases less mass flow rate is required through the engine which lowers the required $T_{4,\rm{RTO}}$ for a required level of thrust.
-It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules.
+It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules that are injected.
 Since $T_{4,\rm{RTO}}$ would be pushed down to its lower limit, it was set as the optimal value from the optimizations with no water recovery.
 This allowed the optimizer to find the maximum $X_{\rm{H_2O,CRZ}}$ that would allow the most water to be recirculated.
-The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for H2.
+The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for \ce{H2}.
 
@@
 % [x] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
-The 4 optimizations mentioned in the section~\ref{sec:optprob} were run and solved.
-The optimality and feasibility targets for the optimizations was $1e-6$.
-These optimizations took between 20-30 major SNOPT iterations to reach optimality and run in approximately 36-48 minutes on a standard laptop.
+The 4 optimizations described in the section~\ref{sec:optprob} were run and solved.
+The optimality and feasibility targets for the optimizations was $10^{-6}$.
+These optimizations took between 20-30 major SNOPT iterations to reach optimality and were completed in approximately 36-48 minutes on a standard laptop.
 The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_summary}.
@@
     \centering
-    \caption{Optimization results of the N+3 engine for four optimizations using jet-A and hydrogen fuel with and without water recirculation.
+    \caption{Optimization results of the N+3 engine for four optimizations using Jet-A and hydrogen fuel with and without water recirculation.
     }
@@
 % [x] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
-$\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than the $\rm{OPR}_{\rm{TOC}}$.
-$V_{ratio,CRZ}$ goes toward its lower value since the engine is more efficient when the bypass stream is larger and has more mass flow through it.
+$\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than $\rm{OPR}_{\rm{TOC}}$.
+$V_{ratio,CRZ}$ tends toward its lower value since the engine is more efficient when the bypass stream is larger and has more mass flow through it.
 The main differences in the engine designs are the pressure ratios and temperatures.
@@
 It is noted that recovery fraction for \ce{H2} is smaller than the recovery fraction for Jet-A because there is more water produced in the combustion process.
-However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for jet-A.
+However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for Jet-A.
 The \ce{H2} fuel has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
@@
 The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of \ce{H2}.
-This is most likely due to the properties of \ce{H2} compared to Jet-A.
+This is most likely due to the combustion properties of \ce{H2} compared to Jet-A.
 \ce{H2} can has a wider combustion flammability limit and allows the engine to burn at a lower equivalence ratio to attain the same thrust requirements.
@@
 The breakdown of the gross thrust fractions from the core and bypass nozzles for each point is shown in Table~\ref{tab:thrust}.
-Table~\ref{tab:thrust} shows that the fraction of gross thrust generated by the core nozzle is decrease when we use \ce{H2} and add water recovery.
-Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel.
-The increase in $\rm{OPR}_{\rm{TOC}}$ reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
+Table~\ref{tab:thrust} shows that the fraction of gross thrust generated by the core nozzle decreases when we use \ce{H2} and decreases further when adding water recovery.
+Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel but is limited by the maximum size of the fan.
+The increase in $\rm{OPR}_{\rm{TOC}}$ mostly reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
 
@@
 
-We can see the $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels in Figure~\ref{fig:barchart}.
+The $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels is shown on a bar chart in Figure~\ref{fig:barchart}.
 
@@
 As~\citeauthor{Strom2002} points out, the water in the exhaust of a \ce{H2}-powered engine would have close to 3 times the amount of a similar Jet-A engine.
-Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser.
+Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser with more surface area.
 Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
@@
 The large efficiency improvement gained from water recirculation warrant a study of a condenser that could be developed to capture these gains.
-Companies that are developing engines with water recirculation suggest that hydrogen can be used to as a heat sink in a water condenser~\cite{arpa-e_2021}.
+Companies that are developing engines with water recirculation suggest that hydrogen can be used to as the heat sink for a water condenser~\cite{arpa-e_2021}.
 To motivate water recirculation technology it of interest to explore the design space for a condenser designed to fit inside the exhaust stream of a turbofan engine.
@@
 pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
-This coefficient is the pressure loss relative to the inlet pressure of the duct.
+This pressure loss coefficient represents is the total pressure loss relative to the inlet pressure of the duct.
 % [x] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
@@
 
-From this figure, we can see the design area in which the closed-loop water recovery model is beneficial.
-This model will offer efficiency benefits up until about $\rm{dPqP} = 0.16$ which means a 16\% loss of pressure from the condenser.
-This benefit area would be reduced if a smaller fraction of water recovered could be obtained.
-Figure~\ref{fig:dpqp_wdot} shows the total water available in the core stream as a function of the same pressure loss.
-
-This figure shows that the optimizer finds designs that increase the available water in the core stream.
-Since the water recovery fraction is always pushed to 17\%, the water recovered is increased to overcome the pressure loss.
-This effect helps the engine increase the benefit area in Figure~\ref{fig:dpqp_sweep}.
+From Figure~\ref{fig:dpqp_sweep}, we can see the design space in which the closed-loop water recovery model is feasible.
+The water recovery model will offer efficiency improvements up until about $\rm{dPqP} = 0.16$.
+A value of $\rm{dPqP} = 0.16$ means that a 16\% loss of pressure from the condenser is allowed assuming the maximum water recovery fraction of 17\% for \ce{H2}.
+This improvement design space would be reduced if only a smaller fraction of water recovered could be obtained.
+The total water available in the core stream as a function of the same pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
+Figure~\ref{fig:dpqp_wdot} shows that the optimizer finds designs that increase the available water in the core stream.
+Since the water recovery fraction is always pushed to 17\%, the water mass flow rate that is recovered increases to overcome the pressure loss.
+This effect helps the engine increase the feasible design space in Figure~\ref{fig:dpqp_sweep}.
 

### 2023-05-07 conference-paper/main.tex
Finished conclusion and updated figures

@@
 \label{sec:conc}
-In this paper, we describe a how a novel closed-loop water recirculation system would be integrated in a commercial aviation setting.
-The water recirculation system comprised was designed and implemented into the N+3 ultra-high bypass engine model.
+In this paper, we describe a novel closed-loop water recirculation system for commercial aviation engines.
+The water recirculation system was designed and implemented into the N+3 ultra-high bypass engine model.
 We have presented the results of four optimization problems demonstrating the use of this technology using the pyCycle cycle modeling tool for Jet-A and hydrogen fuel.
@@
 We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
-System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
-The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
-An additional design variable controlling how much water is recirculated is added at the CRZ point to improve the fuel burn.
-The optimization problem is then solved for four cases: with Jet-A or hydrogen fuel and with and without water recirculation.
+The optimization problem is then introduced with constraints on the thrust and overall engine size at the design point.
+The design variables used are thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
+An additional design variable controlling how much water is recirculated is added at the cruise point to improve the fuel burn.
+The optimization problem was solved for four cases: with Jet-A or hydrogen fuel, and with or without water recirculation.
 
-The results from the optimization problems show temperature, thrust, and efficiency improvements when using hydrogen as a fuel with water circulation.
-Thermal reductions will improve the lifetime of the engine which impact maintenance and overall costs.
-Between the two fuels, we see similar values of TSEC.
-Significant energy efficiency gains are seen with water recirculation and injection.
-This would lead to lower operating costs over the lifetime of the engine.
+The results from the optimization problems show temperature, thrust, and efficiency improvements when using hydrogen as a fuel and even further improvements with water circulation.
+Thermal reductions with hydrogen and water recirculation will improve the lifetime of the engine which would reduce maintenance and overall costs.
+Between the two fuels, we see similar values of the engine performance metric, TSEC.
+Significant energy efficiency gains are seen with water recirculation which would improve the overall costs of the engine during its operational lifecycle.
+At the same water recovery fraction, hydrogen with water recirculation could achieve a lower TSEC value.
 
-Technological problems do exist such as how to design a condenser that can recover a large portion of the exhaust water without large pressure losses.
-However, the thermal properties of hydrogen provide a heat sink and thus a readily available resource for condensation.
-Furthermore, using the exhaust stream to heat the hydrogen fuel has been proposed as an additional avenue to improve engine efficiency%~\cite{}.
-The results from this work outline the working space available for the design of such a condenser.
-% heavier engine due to condenser, but less fuel needed
+There are technological obstacles to overcome in order to implement this water recirculation system in a modern turbofan engine.
+The main obstacle would be how to design a condenser that can recover a portion of the exhaust water without a excessive drag pressure losses.
+Therefore, a condenser design space study was completed to show the feasible design space for such a condenser.
+The results showed that at the maximum possible water recovery fraction for hydrogen quite a large pressure loss can be imposed before the improvements are canceled out.
+Furthermore, using hydrogen as the fuel allows for designs that are not available for an engine using Jet-A.
+The thermal properties of hydrogen provide a heat sink and thus a readily available resource for water condensation within the condenser.
+The hydrogen fuel absorbs heat and is then used in the combustion process, further improving engine efficiency.
+The novel water recovery system with shows promising efficiency results when used with hydrogen fuel.
+This water recovery system provides a potential avenue for hydrogen engine design that could help overcome the technological issues associated with hydrogen as a fuel.
 
@@
 We would like to thank Justin Grey for his help with the pyCycle components of this work.
-Since there is very little pyCycle documentation, his expertise and knowledge of the tool helped make the development of the custom pyCycle components possible.
+Justin's expertise and knowledge of pyCycle tool helped make the development of the custom pyCycle components possible.
 

### 2023-05-09 conference-paper/main.tex
finished presentation and updated paper

@@
 % [x] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
+\noindent
 $\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than $\rm{OPR}_{\rm{TOC}}$.
@@
 The increase in $\rm{OPR}_{\rm{TOC}}$ mostly reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
+Additionally, the FAR of the engines with water recovery increases due to a decrease in overall and core mass flow.
+An increase in FAR likely requires a larger OPR to maintain the required thrust while minimizing fuel burn.
 
@@
 \section{Acknowledgements}
-We would like to thank Justin Grey for his help with the pyCycle components of this work.
+We would like to thank Justin Grey for his help with the pyCycle components in this work.
 Justin's expertise and knowledge of pyCycle tool helped make the development of the custom pyCycle components possible.

### 2023-05-10 conference-paper/main.tex
Adding more feedback

--- 2023-05-07 conference-paper/main.tex
@@
 \usepackage{latexsym}
+\usepackage{multicol}
 \usepackage{subcaption}
-\usepackage{latexsym}
 \usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
@@
 \usepackage{doi} % For getting hyperlinked DOI in the references
+
+%% Custom modifications of hyperlinks.
+% This is not from the AIAA template standard
+\usepackage{xcolor}
+\colorlet{mblue}{blue!40!black}
+\hypersetup{bookmarksnumbered=true,colorlinks=true,linkcolor=mblue,citecolor=mblue,urlcolor=mblue}
+
+\setlength\LTleft{0pt}
 
@@
 \begin{abstract}
-    Advances in commercial propulsion technology led to the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
+    % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
     Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
+    These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
     Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
@@
     We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
-    The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
+    The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
+    % The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
 \end{abstract}
@@
 The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
-N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiencies can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR).
+% [x] TODO: AL-AL, probably should cite the N+3 paper here
+N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiencies can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR)~\cite{Jones2017a}.
 Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
@@
 Traditional propulsion systems that burn hydrocarbon fuels would require external demineralized water storage on the aircraft for water injection~\cite{Mourouzidis2015}.
-The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft over the entire flight.
-The main product of hydrogen combustion is water vapor that we can recover from the exhaust stream~\cite{Strom2002}.
-Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
-This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
-Pratt and Whitney are actively researching this technology to improve the feasibility of hydrogen-powered propulsion~\cite{arpa-e_2021}.
-They suggest that water vapor can be recovered by utilizing the thermal properties of hydrogen to condense some of the water in the turbofan exhaust.
+The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
+The main product of hydrogen combustion is water vapor.
+We can recover the vapor from the exhaust stream~\cite{Strom2002} with condensers and recirculate it upstream to eliminate additional storage requirements.
+% Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
+This system represents a closed loop water feedback system inside the propulsion cycle.
+% This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
+Pratt and Whitney are actively researching this technology to increase the efficiency of hydrogen-powered propulsion~\cite{arpa-e_2021}.
+% They suggest that water vapor can be recovered by utilizing the thermal properties of hydrogen to condense some of the water in the turbofan exhaust.
 
@@
 The industry standard for thermodynamic cycle analysis is the Numerical Propulsion System Simulation (NPSS) framework~\cite{JonesNPSS}.
-NPSS is a modular object-oriented library that models engine components as individual blocks with several thermodynamic solvers.
-\citet{Hendricks2019} created a new tool called pyCycle with the same functionality as NPSS with analytical derivatives~\cite{Gray2017b}.
-pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to enable gradient-based optimization and leverage hierarchical nonlinear solver structures for robustness.
+NPSS is a modular object-oriented library that models engine components as individual blocks with specialized thermodynamic solvers.
+\citet{Hendricks2019} created a new tool called pyCycle with the same functionality as NPSS, with the addition of analytical derivatives~\cite{Gray2017b}.
+pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to facilitate gradient-based optimization and leverage hierarchical solver structures.
 % NOTE: AL-PA, I removed the MAUD sentence because it's a wormhole that you probably don't want to enter lol.
@@
 % Message 3: Introduce the extension of the HBTF and propose novel contributions
-In this work, we analyze the thermodynamic benefits of a closed-loop water vapor recovery and water injection system in a high-bypass turbofan engine.
+In this work, we analyze the thermodynamic benefits of a closed-loop water vapor recovery and injection system in a high-bypass turbofan engine.
 We develop pyCycle components for water injection and vapor recovery to quantify the benefit of a closed loop recirculation system.
@@
 The optimized results show the trade-off between complexity, performance, and efficiency for Jet-A and hydrogen fuels.
+Finally, we present a design space study that demonstrates the necessary condenser technology levels for efficient water recovery.
 
@@
 In section~\ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
-Finally, we present the optimized results and discuss the design space in section~\ref{sec:results}.
+Finally, we present the optimized results and discuss the condenser design space study in section~\ref{sec:results}.
 
@@
 \label{sec:method}
-
 % Engine Architecture: Describe the flow path of the engine and establish the mechanical coupling.
-The UHB turbofan model is the NASA advanced technology "N+3" engine~\cite{Jones2017a}.
+The UHB turbofan model is the NASA advanced technology N+3 engine~\cite{Jones2017a}.
 The N+3 reference cycle is a UHB ratio geared turbofan that could be available in the 2030 to 2040 time frame.
@@
 % [x] TODO: AL-PA, I think we need to reference the engine diagram figure here so the reader can visualize all this text.
-Figure~\ref{fig:n3_cycle} shows a standard high bypass turbofan engine flow connections.
+Figure~\ref{fig:n3_cycle} shows a simplified UHB turbofan engine flow path.
 % [x] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
-We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to a point upstream of the compressors.
+We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to upstream of the compressors.
 The recovery system injects vaporized water into the core stream that reduces the combustion temperature due to heat absorption.
-The vapor recovery component is placed directly before the core nozzle to extract water from the exhaust and recycles it back to the injector.
+The vapor recovery component is located just upstream of the core nozzle to extract water from the exhaust and recycle it back to the injector.
 Figure~\ref{fig:n3_clvr} shows the water vapor recovery loop implemented in a turbofan engine.
@@
 % [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
+% [ ] TODO: AL-PA, Missing station labels for the bypass duct, splitter, and inlet
 \begin{figure}[hbt!]
@@
 We implemented the closed-loop water recovery system as a feedback cycle that extracts water from the exhaust stream and injects it upstream of the HPC.
-We chose this injection location based on claims from a study by NASA, Boeing, and Rolls-Royce~\cite{Daggett2010} that water injection directly into the combustor is unnecessary.
+We chose this injection location following a study by NASA, Boeing, and Rolls-Royce~\cite{Daggett2010} that claims water injection directly into the combustor is unnecessary.
 The water vapor recovery component sits downstream of the LPT and extracts water from the flow before exiting the core nozzle.
@@
 % [x] TODO: AL-PA, Reference Table 1 with humidity values as well.
-\citet{Kalnay1996} give the humidity values for each flight condition and are shown in Table~\ref{tab:flight_conds}.
+\citet{Kalnay1996} give the humidity values for each flight condition, provided in Table~\ref{tab:flight_conds}.
 
-We introduce two new thermodynamic models for water recirculation in pyCycle.
+We introduce two thermodynamic models in pyCycle to capture the effects of water recirculation.
 A water injector adds water to the flow upstream of the HPC, while a water extractor diverts a portion of the water in the flow away from the exhaust stream.
@@
     % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
-    \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
+    \caption{Injector (left) and extractor (right) diagrams that show the inputs and output streams of each component.
         The inputs and outputs show which flow values are used to compute the amount of recirculated water.}
@@
 We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.
+
+% NOTE: AL-PA, I made this a new paragraph (no content change)
 The model results in a mismatch between the mass flow rate upstream of the HPC and the mass flow rate exiting the core nozzle.
@@
     \caption{
-        Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
+        Layout of the N+3 engine core with the closed-loop vapor recovery.
         Black arrows are flow connections, blue boxes are cycle elements.
@@
 
+% NOTE: AL-PA, this ended up a bit choppy, but I think it's better than before.  If you want to adjust things a bit go ahead.
+We impose \emph{balance} equations to satisfy the physical governing equations, conservation laws, and design rules.
+Balance relationships are formulated as equations in the form $r(u)=0$ where $r$ is a residual function and $u$ is an implicit state variable.
+We use Newton based solvers to find the value of the state variables that drive the set of balance residuals to zero.
+\citeauthor{Hendricks2019} provide the extensive set of balance equations with further details on the construction of the nonlinear system for the N+3 model.
+
 % NOTE: AL-PA, I added this blurb to introduce multipoint
@@
 The ``off-design'' mode inherits the flow path areas and turbo machinery map scalars from the ``on-design'' analysis.
-
-% NOTE: AL-PA, this ended up a bit choppy, but I think it's better than before.  If you want to adjust things a bit go ahead.
-We impose \emph{balance} equations to satisfy the physical governing equations, conservation laws, and design rules.
-\emph{Balance} relationships are formulated as equations in the form $r(u)=0$ where $r$ is a residual function and $u$ is an implicit state variable.
-We use Newton based solvers to find the value of the state variables that drive the set of balance residuals to zero.
-\citeauthor{Hendricks2019} provide the extensive set of balance equations with further details on the construction of the nonlinear system for the N+3 model.
+This approach is known as multi-design point (MDP)~\cite{Schutte2009} analysis.
+MDP analysis simultaneously considers the performance and design requirements at each operation to automatically calculate a feasible design.
 
 The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
+% To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
 Table~\ref{tab:flight_conds} shows the different altitudes and mach numbers for each flight condition.
-We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
+% We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
 % [x] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
@@
 Similarly to $\dot{m}_{\rm{cool},k}$, the water recovery mass flow rates ($\dot{m}_{\rm{water},k}$) are connected back to the other operating points.
-The interconnections between flight conditions create a complex nonlinear loop, shown in Figure~\ref{fig:N3_xdsm_full}.
+Figure~\ref{fig:N3_xdsm_full} is an extended design structure matrix (XDSM)~\cite{Lambe2012a} diagram depicting the coupled multipoint model.
+The interconnections between flight conditions create a nonlinear cyclic loop with feedback between flight conditions.
 The converged model represents a feasible multipoint engine that accounts for design considerations and conservation laws at all four operating conditions.
@@
 \label{sec:optprob}
-
 % NOTE: AL-PA, No reason to have an extra subsection here so I removed it
@@
 % NOTE: AL-PA, "We will perform" makes it seem like we haven't done the work yet.
-We performed multipoint gradient-based design optimization of the N+3 engine model considering the TOC, RTO, SLS, and CRZ flight conditions.
+We performed MDP gradient-based design optimization of the N+3 engine model considering the TOC, RTO, SLS, and CRZ flight conditions.
 % NOTE: AL-PA, I re-wrote this to be more direct
@@
 % [x] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
-
 Typical gas-turbine analysis measures the efficiency using the thrust-specific fuel consumption (TSFC).
@@
 \end{equation}
-
-For this work we are concerned with minimizing fuel burn of the engine subject to known thrust constraints.
+% In this work we are concerned with minimizing fuel burn of the engine subject to thrust constraints.
 % [x] TODO: AL-PA, TSEC is not the objective.  Fuel burn is the objective.  TSEC is the efficiency metric of interest.
@@
 
-Large multidisciplinary optimization problems are commonly represented with extended design structure matrix (XDSM) diagrams.
-XDSM diagrams are used to visualize the complex implicit and explicit relationships between functions, the solver, and optimizer.
-An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure~\ref{fig:N3_opt_xdsm}.
+We present a high-level summary of the optimization framework using an XDSM diagram in Figure~\ref{fig:N3_opt_xdsm}.
+The XDSM diagram shows the design variable, objective, and constraint connections between the optimization algorithm and the multipoint analysis model.
+The detailed optimization problem description is provided in Table~\ref{tab:opt_problem}.
+% Large multidisciplinary optimization problems are commonly represented with extended design structure matrix (XDSM) diagrams.
+% XDSM diagrams are used to visualize the complex implicit and explicit relationships between functions, the solver, and optimizer.
+% An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure~\ref{fig:N3_opt_xdsm}.
 
 % [x] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
+% [ ] TODO: AL-PA, Combine the TOC and Off design stack into a single block that just says (MDP Cycle Model)
+% [ ] TODO: AL-PA, Remove the map scalar, core area, and water recovery area connections
+% [ ] TODO: AL-PA, The symbol for thrust is "F" not "T"
+% [ ] TODO: AL-PA, Show the final outputs on the left side of the XDSM and include a superscript "*" to denote optimal values. i.e \dot{m}_\text{fuel}^*
 \begin{figure}[!hbt]
@@
 % [x] TODO: AL-PA, I would break this up into two or more sentences.
-The design variables for this problem are pressure controls such as fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$).
-Other design variables are temperature controls such as burner temperature at RTO ($T_{4,\rm{RTO}}$) and the TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$).
-TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
+The design variables are specified at different flight conditions.
+At the TOC point, we include the fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), LPC pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), and overall pressure ratio ($\rm{OPR}_{\rm{TOC}}$).
+We add a design variable for maximum turbine inlet temperature at RTO ($T_{4,\rm{RTO}}$).
+RTO is the limiting condition for the maximum allowable exit temperature of the burner.
+The turbine inlet temperature at TOC is specified by a temperature ratio design variable ($T_{4,\rm{ratio}}$) between the RTO and TOC points, calculated as
+% The design variables for this problem are pressure controls such as fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$).
+% Other design variables are temperature controls such as burner temperature at RTO ($T_{4,\rm{RTO}}$) and the TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$).
+% TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
 
 \begin{equation}
-    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
-    \label{t4ratio}
+    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}.
+    \label{eq:t4_ratio}
 \end{equation}
@@
 \noindent
-The nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$) is also added as a design variable to control the bypass ratio and mass flow rate through the engine.
-The nozzle velocity ratio is defined as,
+The nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$) is also added as a design variable to control the bypass ratio (BPR) at TOC.
+The nozzle velocity ratio is defined as
 
 \begin{equation}
-    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
+    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}},
     \label{eq:vratio}
 \end{equation}
-
-\noindent
-where $V_{ideal}$ is the exit velocity of a nozzle and $C_v$ is the velocity coefficient which accounts for non-ideal effects.
-Finally, the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$) is added as a design variable in order to take advantage of water recirculation.
+where $V_\text{ideal}$ is the ideal nozzle exit velocity and $C_v$ is the nozzle velocity coefficient that accounts for non-ideal effects.
+The final design variable is the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$).
 % [x] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
 % [x] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
-We only add the water recovery fraction at CRZ as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.
-The CRZ operating condition is also the longest flight segment and therefore contributes the most to long-term performance.
+We only include the water recovery fraction at cruise because it has the largest impact on the fuel mass flow rate objective function.
+Additionally, the CRZ operating condition is the longest flight segment and contributes the most to long-term engine performance.
+The range for each design variable and the associated units are shown in Table~\ref{tab:dv_table}.
+% We add the water recovery fraction only at the CRZ point as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.
 
@@
 %                  - i.e The interdependence of the TOC mass flow rate and the RTO temperature
+As aforementioned in Section~\ref{sec:method}, the N+3 model uses balance relationships to enforce design, conservation, and performance requirements.
+To create a reduced space optimization problem, the N+3 model imposes a set of constraints using additional balance relationships.
+These constraints are satisfied using a Newton solver at the analysis level instead of the optimization level.
+The advantage of the reduced space approach is that the design is feasible at the completion of each optimization iteration.
+\citet{Martins2013} classify this architecture as multidisciplinary design feasible (MDF).
+The balance relationships constrain the net thrust at the SLS and CRZ conditions, the BPR at TOC, and the turbine inlet temperature ($T_4$) at RTO.
+We summarize the constraints as residuals (r) and the associated implicit states ($\vec{u}$) in Equation~\eqref{eq:balance_cons}.
+\begin{equation}
+    \label{eq:balance_cons}
+    r(\vec{u}) \rightarrow
+    \begin{cases}
+        \setlength{\tabcolsep}{1pt}
+        \begin{tabular}{l l}
+            $r(\text{BPR}_\text{TOC})$    & $= (V_\text{ratio,TOC})_\text{des} - V_\text{ratio,TOC} = 0$, \\
+            $r(\dot{m}_\text{total,TOC})$ & $= (T_{4,\text{RTO}})_\text{des} - T_{4,\text{RTO}} = 0$,     \\
+            $r(\text{FAR}_\text{CRZ})$    & $= 0.9 F_\text{net, TOC} - F_\text{net, CRZ} = 0$,            \\
+            $r(\text{FAR}_\text{SLS})$    & $= 1.2553 F_\text{net,RTO} - F_\text{net, SLS} = 0$.          \\
+        \end{tabular}
+    \end{cases}
+\end{equation}
 
-The net thrust for the SLS and CRZ conditions are set using \emph{balance} components.
-Net thrust for SLS is constrained to be 1.2335 times the net thrust at RTO which itself is constrained to 22800 \si{lbf}.
-Similarly, the net thrust at CRZ is constrained to be 0.9 times the net thrust at TOC.
-The bypass ratio (BPR) at TOC is set by the \emph{balance} component such that the CRZ nozzle velocity ratio meets a given target value.
-The CRZ velocity ratio constraint ensures that the core exit velocity is higher than the bypass exit velocity.
-The TOC engine mass flow rate is set by the \emph{balance} component using the combustor temperature at RTO, $T_{4,\rm{RTO}}$.
+% The net thrust for the SLS and CRZ conditions are set using balance relationships between the RTO and TOC points respectively.
+% We prescribe an equality constraint using a balance residual to set the RTO net thrust to \SI{22800}{lbf}.
+% Another balance residual constrains the SLS net thrust to be 1.2335 the net thrust at RTO.
+% Similarly, the net thrust at CRZ is constrained to be 0.9 times the net thrust at TOC.
+% Net thrust for SLS is constrained to be 1.2335 times the net thrust at RTO.
+% The bypass ratio (BPR) at TOC is set by the \emph{balance} component such that the CRZ nozzle velocity ratio meets a given target value.
+% The CRZ velocity ratio constraint ensures that the core exit velocity is higher than the bypass exit velocity.
+% The TOC engine mass flow rate is set by the \emph{balance} component using the combustor temperature at RTO, $T_{4,\rm{RTO}}$.
 % [x] TODO: AL-PA, Combine these into a single sentence.
-
-The optimization problem objective function, design variables, and constraints are shown in Table~\ref{tab:opt_problem}.
-The thermodynamic cycle design variable ranges are determined from the expected N+3 technology limits~\cite{Hendricks2019}.
-Additionally, the design variable ranges are shown in Table~\ref{tab:dv_table}.
 
@@
         Multipoint optimization problem definition.
-        The objective function is the thrust specific energy consumption at the cruise condition.
-        The constraints are net thrust and engine diameter constraint at the design point, TOC.
+        The objective function is the fuel mass flow rate at the CRZ condition.
+        The constraints are the net thrust at TOC and an upper bound on engine diameter.
     }
@@
         \hline
-        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
+        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \unit{lbm/s}     & 1        \\
                         &                                &                                                                          &                  &          \\
@@
                         & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -                & 1        \\
-                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
-                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
+                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \unit{\degree R} & 1        \\
+                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{eq:t4_ratio})              & -                & 1        \\
                         & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -                & 1        \\
@@
                         &                                &                                                                          &                  &          \\
-        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
-                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{inch^2}    & 1        \\
+        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \unit{lbf}       & 1        \\
+                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \unit{inch^2}    & 1        \\
         \cline{3-5}
@@
 % NOTE: AL-PA, I re-wrote most of this to be more concise.
-The N+3 pyCycle model is implemented in OpenMDAO~\cite{Gray2019a} to enable multidisciplinary gradient-based optimization with analytic coupled derivatives.
+The N+3 pyCycle model is implemented in OpenMDAO~\cite{Gray2019a} to perform multidisciplinary gradient-based optimization with analytic coupled derivatives.
 We use pyOptSparse~\cite{Wu2020a} to facilitate the use of state-of-the-art optimization software through a unified python interface.
@@
 
-During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time they had opposite effects on the design.
-The optimizer increases $X_{\rm{H_2O,CRZ}}$ which allows for a lower optimal $T_{4,\rm{RTO}}$.
-This is likely due to the interdependency between engine mass flow rate and $T_{4,\rm{RTO}}$.
-As the recovery water fraction increases less mass flow rate is required through the engine which lowers the required $T_{4,\rm{RTO}}$ for a required level of thrust.
-It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules that are injected.
-Since $T_{4,\rm{RTO}}$ would be pushed down to its lower limit, it was set as the optimal value from the optimizations with no water recovery.
-This allowed the optimizer to find the maximum $X_{\rm{H_2O,CRZ}}$ that would allow the most water to be recirculated.
-The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for \ce{H2}.
+% NOTE: AL-PA, this was confusing and I don't think it add much useful information that the readers will actually understand.
+
+% During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time they had opposite effects on the design.
+% The optimizer increases $X_{\rm{H_2O,CRZ}}$ which allows for a lower optimal $T_{4,\rm{RTO}}$.
+% This is likely due to the interdependency between engine mass flow rate and $T_{4,\rm{RTO}}$.
+% As the recovery water fraction increases less mass flow rate is required through the engine which lowers the required $T_{4,\rm{RTO}}$ for a required level of thrust.
+% It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules that are injected.
+% Since $T_{4,\rm{RTO}}$ would be pushed down to its lower limit, it was set as the optimal value from the optimizations with no water recovery.
+% This allowed the optimizer to find the maximum $X_{\rm{H_2O,CRZ}}$ that would allow the most water to be recirculated.
+% The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for \ce{H2}.
 
@@
 % [x] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
-The 4 optimizations described in the section~\ref{sec:optprob} were run and solved.
-The optimality and feasibility targets for the optimizations was $10^{-6}$.
-These optimizations took between 20-30 major SNOPT iterations to reach optimality and were completed in approximately 36-48 minutes on a standard laptop.
-The optimality, feasibility, and merit function for each optimization is shown plotted in Figure \ref{fig:history_summary}.
+We performed four optimizations of the N+3 engine cycle.
+The optimizations considered Jet-A and hydrogen fuels with and without the water recovery loop.
+For the optimizations without water recovery, we removed the water mass fraction design variable in Table~\ref{tab:opt_problem}.
+In optimizations with water recovery, we use a constant $T_{4,\text{RTO}}$ from the optimizations without water recovery to aid comparisons between configurations.
+
+The optimality and feasibility targets for the optimizations are both $10^{-6}$.
+These optimizations took between 20-30 major SNOPT iterations to reach optimality and were completed in approximately 45 minutes on a standard laptop.
+The optimality, feasibility, and merit function for each optimization is shown in Figure \ref{fig:history_summary}.
+All four optimization problems converged to the requested feasibility and optimality tolerances.
+The optimal design variables for each of the four optimizations are presented in Table~\ref{tab:dv_opt}.
+% The merit function reached a final value in about 10 iterations for all cases.
 % [x] TODO: AL-PA, No need to explain this and then answer your own observation from the plot.  Just tell the reader what the plot shows.
@@
 % NOTE: AL-PA, The merit function is not a time-dependent quantity, so there's no "steady state".  Its enough to just say the merit function was reduced by X amount in X number of iterations...
-From Figure~\ref{fig:history_summary} we observe quadratic convergence in the optimality of the problem near the optimal solution as expected.
-A feasible design is reached and the merit function is reduced to its final value in about 10 iterations for all cases.
+% From Figure~\ref{fig:history_summary} we observe quadratic convergence in the optimality of the problem near the optimal solution.
 
@@
 
-The optimal design variables for each of the four optimizations is shown in Table~\ref{tab:dv_opt}.
 % [x] TODO: AL-PA, You should explain the plot before it's introduced to the reader.  Stating what's on the figure after it appears doesn't provide any insight.
 % [x] TODO: AL-PA, See my previous TODOs but this needs some more explanation in the optimization problem section.
-Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
+% Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
 
@@
         \hline
-        variables   & $x_{H2O,CRZ}$             & -         & 0.3       & -           & 0.17        & -               \\
+        variables   & $X_{\ce{H2O},\text{CRZ}}$ & -         & 0.3       & -           & 0.17        & -               \\
                     & $\rm{PR}_{fan,TOC}$       & 1.285     & 1.292     & 1.288       & 1.297       & -               \\
@@
                     & $\rm{OPR}_{\rm{TOC}}$     & 61.012    & 61.188    & 60.660      & 61.952      & -               \\
-                    & $T_{4,ratio}$             & 0.913     & 0.911     & 0.918       & 0.915       & -               \\
-                    & $T_{4,RTO}$               & 3220.574  & -         & 3204.071    & -           & $^\circ$R       \\
-                    & $V_{ratio,CRZ}$           & 1.35      & 1.35      & 1.35        & 1.35        & -               \\
+                    & $T_{4,\text{ratio}}$      & 0.913     & 0.911     & 0.918       & 0.915       & -               \\
+                    & $T_{4,\text{RTO}}$        & 3220.574  & -         & 3204.071    & -           & $^\circ$R       \\
+                    & $V_\text{ratio,CRZ}$      & 1.35      & 1.35      & 1.35        & 1.35        & -               \\
         \hline
-        constraints & $F_{net,TOC}$             & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf             \\
-                    & $D_{Fan}$                 & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$          \\
+        constraints & $F_\text{net,TOC}$        & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf             \\
+                    & $D_\text{fan}$            & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$          \\
         \bottomrule
@@
 % [x] TODO: AL-PA, Elaborate on why we include this parallel axis plot.  Why is it important?  What insight does it provide to the reader?  Compare and contrast the optimization results!
-The resulting optimal values from the optimization problems are shown in Figure~\ref{fig:parallel_coords} on a parallel coordinate plot.
-Figure~\ref{fig:parallel_coords} shows the how each of the optimal overall design of the engine compares across fuel type with and without water recovery.
+We summarize the optimal values of important thermodynamic variables on a parallel coordinate plot in Figure~\ref{fig:parallel_coords}.
+This figure compares the optimal overall design of the N+3 cycle across the four optimization problems.
+The TSEC of Jet-A is less than hydrogen with and without water recovery.
+However, the TSEC of the optimal cycle with hydrogen combustion and water recovery is less than Jet-A combustion without water recovery.
+This suggests that a hydrogen fueled N+3 UHB turbofan with water recovery can compete with the efficiency of a standard Jet-A fueled cycle.
+% Figure~\ref{fig:parallel_coords} shows the how each of the optimal overall design of the engine compares across fuel type with and without water recovery.
 % [x] TODO: AL-PA, How are they similar? Be specific.
 % [x] TODO: AL-PA, I would move a lot of this up to when you introduce the parallel axis plot.
-We see that across the range of values that each optimal value is very similar with the exception of water recovery fraction.
-As noted earlier, the water recovery fractions are different because the optimizer pushes $X_{\rm{{H_2O},CRZ}}$ to the highest value it can attain.
-The $\rm{PR}_{fan,TOC}$ and $V_{ratio,CRZ}$ design variables go to their upper and lower limits, respectively.
+% We see that across the range of values that each optimal value is very similar with the exception of water recovery fraction.
+
+With the addition of water recovery, the propulsive efficiency increases and leads to higher fan pressure ratios and lower TSEC for both fuels.
+Additionally, the $T_{4,\text{ratio}}$ is reduced with water recovery leading to cooler combustion temperatures at TOC and subsequently lower fuel burn at CRZ.
+We observe the optimal $T_{4,\text{RTO}}$ is larger for Jet-A than hydrogen because hydrogen has a larger combustion flammability limit and the engine can burn at a lower equivalence ratio to attain the same thrust requirements~\cite{Adler2023}.
+% [ ] TODO: AL-PA, why is this favorable for emissions reduction?  Need to cite or explain.
+Burning leaner reduces the fuel consumption and is favorable for emissions reduction.
+% The additional water in the combustion improves the propulsive efficiency and enables the increase in overall pressure ratio.
+% As noted earlier, the water recovery fractions are different because the optimizer pushes $X_{\rm{{H_2O},CRZ}}$ to the highest value it can attain.
+% The $\rm{PR}_{fan,TOC}$ and $V_{ratio,CRZ}$ design variables go to their upper and lower limits, respectively.
+$V_\text{ratio,CRZ}$ is at the lower bound for all four cases to maximize the amount of mass flow through the bypass stream.
 
@@
 % AL-PA, We can make another plot for the water fractions and the dpQp study.
+% [ ] TODO: AL-PA, Can you make the y-axis range for T4_ratio smaller so we can see the differences a bit better.  Maybe like 0.85 - 0.95
+% [ ] TODO: AL-PA, Same comment as above but for FPR, maybe 1.28-1.32
+% [ ] TODO: AL-PA, If a variable has bounds, can we make the y-axis limits match the bounds?
 \begin{figure}[hbt!]
@@
     \includegraphics[width=1.0\textwidth]{N3_parallel_coords.pdf}
-    \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
-        The red lines show Jet-A fuel and the blue lines show \ce{H2} fuel.
-        The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.}
+    \caption{
+        Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
+        The red lines show Jet-A fuel and the blue lines show hydrogen fuel.
+        The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.
+    }
     \label{fig:parallel_coords}
@@
 % [x] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
-$\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than $\rm{OPR}_{\rm{TOC}}$.
-$V_{ratio,CRZ}$ tends toward its lower value since the engine is more efficient when the bypass stream is larger and has more mass flow through it.
-The main differences in the engine designs are the pressure ratios and temperatures.
+% $\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than $\rm{OPR}_{\rm{TOC}}$.
+% The main differences in the engine designs are the pressure ratios and temperatures.
 % [x] TODO: AL-PA, Why is pushed to the upper limit?  Explain how it improves the combustion characteristics.
-Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
-One reason the water recovery fraction increases to its upper bound use to improve combustion characteristics of the core flow when fuel is injected.
-The same thrust output can be achieved with water recovery at a lower FAR, slightly lower temperature, and less total mass flow rate.
-The recovery fraction does not directly relate to the mass flow rate of recirculated water since more available water will increase the recirculation flow rate.
-It is noted that recovery fraction for \ce{H2} is smaller than the recovery fraction for Jet-A because there is more water produced in the combustion process.
-However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for Jet-A.
-The \ce{H2} fuel has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
-We see slightly higher pressure ratios across the fan with water recovery leading to a larger overall pressure ratio.
+% Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
+% One reason the water recovery fraction increases to its upper bound use to improve combustion characteristics of the core flow when fuel is injected.
+% The same thrust output can be achieved with water recovery at a lower FAR, slightly lower temperature, and less total mass flow rate.
+% The recovery fraction does not directly relate to the mass flow rate of recirculated water since more available water will increase the recirculation flow rate.
+% It is noted that recovery fraction for \ce{H2} is smaller than the recovery fraction for Jet-A because there is more water produced in the combustion process.
+% However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for Jet-A.
+% The \ce{H2} fuel has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
+% We see slightly higher pressure ratios across the fan with water recovery leading to a larger overall pressure ratio.
 % [x] TODO: AL-PA, I'm beating a dead horse here but you don't need to say this if you mention it earlier
 % [x] TODO: AL-PA, Why is the T4 ratio higher?  Explain it in terms of the fuel properties.  The reader can look at the plot themselves and see that it's higher.
-The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of \ce{H2}.
-This is most likely due to the combustion properties of \ce{H2} compared to Jet-A.
-\ce{H2} can has a wider combustion flammability limit and allows the engine to burn at a lower equivalence ratio to attain the same thrust requirements.
-Burning leaner not only cools the engine but also reduces fuel consumption.
+% The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of \ce{H2}.
+% This is most likely due to the combustion properties of \ce{H2} compared to Jet-A.
+% \ce{H2} can has a wider combustion flammability limit and allows the engine to burn at a lower equivalence ratio to attain the same thrust requirements.
+% Burning leaner not only cools the engine but also reduces fuel consumption.
 % [x] TODO: AL-PA, Why are the temperatures colder with the H2 fuel?  Why does water recovery make them even lower?
 % [x] TODO: AL-PA, I wouldn't say "cooler" I would say "less than" or "colder"
-Therefore, TOC temperatures are colder with the \ce{H2} fuel and even slightly colder when adding water recovery.
-The engine is likely able to size the components with water recovery so that the same thrust is generated at a lower fuel-to-air ratio.
-Furthermore, adding water recovery at CRZ slightly decreases the $T_{4,\rm{ratio}}$ value.
-As noted earlier, the water recovery and injection allows the engine achieve the same level of thrust at a lower temperature.
+% Therefore, TOC temperatures are colder with the \ce{H2} fuel and even slightly colder when adding water recovery.
+% The engine is likely able to size the components with water recovery so that the same thrust is generated at a lower fuel-to-air ratio.
+% Furthermore, adding water recovery at CRZ slightly decreases the $T_{4,\rm{ratio}}$ value.
+% As noted earlier, the water recovery and injection allows the engine achieve the same level of thrust at a lower temperature.
 % [x] TODO: AL-PA, Why did the optimizer push the value of T4 down with water recovery?  Dig into this more.
-In terms of pressure ratios we see that the fan pressure ratio increases with hydrogen fuel and even more with water recovery.
-This is again likely due to using \ce{H2} and water recovery each resizing the engine to increase the amount of thrust generated by the fan.
+% In terms of pressure ratios we see that the fan pressure ratio increases with hydrogen fuel and even more with water recovery.
+% This is again likely due to using \ce{H2} and water recovery each resizing the engine to increase the amount of thrust generated by the fan.
 % [x] TODO: AL-PA, We want to discuss how the thrust from the fan/core changes when we introduce water recovery.
 % NOTE: AL-PA, The idea here is to communicate the effect of water recovery on the core power vs. the fan power.
-The breakdown of the gross thrust fractions from the core and bypass nozzles for each point is shown in Table~\ref{tab:thrust}.
-Table~\ref{tab:thrust} shows that the fraction of gross thrust generated by the core nozzle decreases when we use \ce{H2} and decreases further when adding water recovery.
-Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel but is limited by the maximum size of the fan.
-The increase in $\rm{OPR}_{\rm{TOC}}$ mostly reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
+% We analyzed the gross thrust split between the core and bypass streams of the optimized engine cycles.
+% Table~\ref{tab:thrust} shows the breakdown between the two flow paths as percentages of the total gross thrust.
+% The breakdown of the gross thrust fractions from the core and bypass nozzles for each point is shown in Table~\ref{tab:thrust}.
+% The fraction of gross thrust generated by the core nozzle decreases when we use \ce{H2} and decreases further when adding water recovery.
+
+% Increasing the thrust produced in the bypass stream improves the propulsive efficiency.
+% Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel but is limited by the maximum size of the fan.
+% The increase in $\rm{OPR}_{\rm{TOC}}$ mostly reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
+% Additionally, the FAR of the engines with water recovery increases due to a decrease in overall and core mass flow.
+% An increase in FAR likely requires a larger OPR to maintain the required thrust while minimizing fuel burn.
 
@@
 %                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
-\begin{table}[hbt!]
-    \centering
-    \caption{Thrust breakdown for each flight operating condition.
-        The net thrust, gross thrust, and ram drag are shown for each optimization result.
-    }
-    \small
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{r l l l l l}
-        Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
-        \toprule
-        TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
-              & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
-        \hline
-        RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
-              & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
-        \hline
-        SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
-              & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
-        \hline
-        CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
-              & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
-        \bottomrule
-    \end{tabular}
-    \label{tab:thrust}
-\end{table}
+% \begin{table}[hbt!]
+%     \centering
+%     \caption{Thrust breakdown for each flight operating condition.
+%         The net thrust, gross thrust, and ram drag are shown for each optimization result.
+%     }
+%     \small
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{r l l l l l}
+%         Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
+%         \toprule
+%         TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
+%               & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
+%         \hline
+%         RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
+%               & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
+%         \hline
+%         SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
+%               & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
+%         \hline
+%         CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
+%               & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
+%         \bottomrule
+%     \end{tabular}
+%     \label{tab:thrust}
+% \end{table}
 
@@
 
-The $\rm{TSEC}_{\rm{CRZ}}$ improvement due to water recovery relative to no water recovery for both fuels is shown on a bar chart in Figure~\ref{fig:barchart}.
-
 % [x] TODO: I would change this to the horizontal bar chart and plot both H2 and Jet-A on the same axis
 % See this example in niceplots: https://github.com/mdolab/niceplots/blob/main/examples/plot_bar_chart.py and https://github.com/mdolab/niceplots/blob/main/examples/ref/bar_chart.png
+% [ ] TODO: Can you add a line to bar chart that shows the improvement between baseline Jet-A and hydrogen with water recovery?
 \begin{figure}[hbt!]
@@
 
-We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
+The TSEC improvement at CRZ due to water recovery for both fuels is shown on a bar chart in Figure~\ref{fig:barchart}.
+Water recovery improves the TSEC approximately 5\% for both Jet-A and hydrogen fueled cycles.
+% We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
 % [x] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
-Given that most of the design variables change only slightly between designs, most of the efficiency gains are driven by water recovery and injection.
-This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
+Most of the design variables for the optimal designs with and without water recovery vary only slightly for both fuels.
+This suggests that the water recovery system accounts for a majority of the efficiency improvements.
+Achieving a 5\% reduction in TSEC represents a large fuel savings over the lifecycle of an engine.
+% This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
 % [x] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
-As~\citeauthor{Strom2002} points out, the water in the exhaust of a \ce{H2}-powered engine would have close to 3 times the amount of a similar Jet-A engine.
-Due to the comparatively small amount of water in the exhaust stream for Jet-A, the Jet-A engine would require a larger condenser with more surface area.
-Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
+As~\citeauthor{Strom2002} point out, a hydrogen-fueled engine would have close to 3 times more water in the exhaust than a similar Jet-A fueled counterpart.
+% [ ] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
+% Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
+Hydrogen combustion offers an immediate reduction in emissions and produces more water in the exhaust stream.
+With an advanced water recovery system, we can achieve better TSEC with hydrogen fuel than Jet-A.
+To make hydrogen fueled engines a reality, we need to take advantage of the additional benefits of hydrogen combustion.
 \subsection{Condenser Design Space Study}
@@
 % [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
-The large efficiency improvement gained from water recirculation warrant a study of a condenser that could be developed to capture these gains.
+The efficiency improvement gained from water recirculation warrant a design space study for potential condenser technology.
 Companies that are developing engines with water recirculation suggest that hydrogen can be used to as the heat sink for a water condenser~\cite{arpa-e_2021}.
-To motivate water recirculation technology it of interest to explore the design space for a condenser designed to fit inside the exhaust stream of a turbofan engine.
-A relatively low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
+We consider a condenser designed to fit inside the exhaust stream of a hydrogen-fueled turbofan engine.
+The trade space for a condenser in the exhaust stream depends on the pressure loss and water recovery capability.
+% A low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
 % [x] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"
-pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
-This pressure loss coefficient represents is the total pressure loss relative to the inlet pressure of the duct.
+
+We model the pressure loss across the condenser by varying the relative total pressure loss across duct 5 just upstream of the core nozzle.
+% pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
+This pressure loss coefficient (dPqP) is the difference in total pressure across the duct divided by the total pressure at the duct inlet.
 % [x] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
 % [x] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
-We varied the total pressure loss across the extraction model to simulate drag from an increasingly large condenser.
-The rest of the engine design variables were optimized during this pressure loss sweep to determine the how the optimal amount of water recovery changed based on drag losses from the condenser.
-Figure~\ref{fig:dpqp_sweep} shows $\rm{TSEC}_{\rm{CRZ}}$ of this sweep relative to and engine with no water recovery.
-
+We varied the total pressure loss across the duct to simulate drag from an increasingly large condenser.
+We ran an optimization to minimize fuel mass flow rate of hydrogen at each pressure loss value using the formulation for water recovery in Table~\ref{tab:opt_problem}.
+% The rest of the engine design variables were optimized during this pressure loss sweep to determine the how the optimal amount of water recovery changed based on drag losses from the condenser.
+Figure~\ref{fig:dpqp_sweep} shows the $\rm{TSEC}_{\rm{CRZ}}$ of the optimal engine cycles plotted against dPqP.
+The red horizontal line is the $\text{TSEC}_\text{CRZ}$ value of the optimized engine with no water recovery.
+The blue region represents the feasible space for potential condenser technology.
 \begin{figure}[hbt!]
@@
         \includegraphics[width=\textwidth]{N3_dpqp.pdf}
-        \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-            The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery.
-            This shows the working space available for designing a water condenser while still gaining the benefits of water recovery.}
+        \caption{
+            Pressure loss sweep of duct 5 which is just upstream of the core nozzle.
+            The figure shows the optimized TSEC values (blue) for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery (red).
+            This shows the feasible space available for designing a water condenser while still benefiting from water recovery.
+        }
         \label{fig:dpqp_sweep}
@@
         % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
+        % [ ] TODO: AL-PA, The statement about the upper bound is weird.  If it hit the upper bound each time, either say it was constant or remove that part.
         \includegraphics[width=\textwidth]{N3_wdot.pdf}
-        \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+        \caption{
+            Pressure loss sweep of duct 5 which is just upstream of the core nozzle.
             The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
@@
 \end{figure}
-
-From Figure~\ref{fig:dpqp_sweep}, we can see the design space in which the closed-loop water recovery model is feasible.
-The water recovery model will offer efficiency improvements up until about $\rm{dPqP} = 0.16$.
-A value of $\rm{dPqP} = 0.16$ means that a 16\% loss of pressure from the condenser is allowed assuming the maximum water recovery fraction of 17\% for \ce{H2}.
-This improvement design space would be reduced if only a smaller fraction of water recovered could be obtained.
+% From Figure~\ref{fig:dpqp_sweep}, we can see the design space in which the closed-loop water recovery model is feasible.
+The breakeven point where water recovery is no longer beneficial occurs at a pressure loss of roughly 0.16, or 16\%.
+This estimate is based on an ideal condenser that can achieve the optimal water extraction for a given pressure loss.
+In reality, losses due to inefficiencies further reduce the size of the feasible space.
+% The water recovery model will offer efficiency improvements up until about $\rm{dPqP} = 0.16$.
+% A value of $\rm{dPqP} = 0.16$ means that a 16\% loss of pressure from the condenser is allowed assuming the maximum water recovery fraction of 17\% for \ce{H2}.
+% This improvement design space would be reduced if only a smaller fraction of water recovered could be obtained.
+% [ ] TODO: AL-PA, Re-write this part to match the new figure that shows the mass flow of water extracted (per our slack convo)
 The total water available in the core stream as a function of the same pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
@@
 % NOTE: PA-AL, any other plots to include?
+% AL, Nah we are good to go with plots
 
@@
 In this paper, we describe a novel closed-loop water recirculation system for commercial aviation engines.
-The water recirculation system was designed and implemented into the N+3 ultra-high bypass engine model.
-We have presented the results of four optimization problems demonstrating the use of this technology using the pyCycle cycle modeling tool for Jet-A and hydrogen fuel.
+The water recirculation system was designed and implemented within the N+3 ultra-high bypass engine model.
+We presented the results of four optimization problems demonstrating the use of this technology within pyCycle for Jet-A and hydrogen fuels.
 
-The recirculation system is implemented by introducing two new custom pyCycle components, the water extractor and injector, which form a continuous closed-loop feedback water flow in the engine.
-We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
-The optimization problem is then introduced with constraints on the thrust and overall engine size at the design point.
-The design variables used are thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
-An additional design variable controlling how much water is recirculated is added at the cruise point to improve the fuel burn.
-The optimization problem was solved for four cases: with Jet-A or hydrogen fuel, and with or without water recirculation.
+The water recirculation system introduces two pyCycle components, namely the water extractor and injector, that form a continuous closed-loop feedback cycle in the engine.
+% We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
+% The optimization problem is then introduced with constraints on the thrust and overall engine size at the design point.
+We optimize the engine cycle considering Jet-A and hydrogen fuels with and without water recovery.
+The objective is to minimize fuel mass flow rate subject to net thrust and fan diameter constraints.
+% The design variables used are thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
+% An additional design variable controlling how much water is recirculated is added at the cruise point to improve the fuel burn.
+% The optimization problem was solved for four cases: with Jet-A or hydrogen fuel, and with or without water recirculation.
+% The results from the optimization problems show temperature, thrust, and efficiency improvements for hydrogen as a fuel and even further improvements with water circulation.
+The results show that optimal hydrogen-fueled engines with water recirculation are more efficient than standard Jet-A with no water recovery.
+We demonstrate that the increased availability of water from hydrogen combustion proves the viability of this concept.
+Additionally, hydrogen combustion eliminates carbon emissions and the lean fuel-to-air ratios result in cooler turbine inlet temperatures compared to Jet-A.
+% Thermal reductions with hydrogen and water recirculation will improve the lifetime of the engine which would reduce maintenance and overall costs.
+% Between the two fuels, we see similar values of the engine performance metric, TSEC.
+% Significant energy efficiency gains are seen with water recirculation which would improve the overall costs of the engine during its operational lifecycle.
+% At the same water recovery fraction, hydrogen with water recirculation could achieve a lower TSEC value.
 
-The results from the optimization problems show temperature, thrust, and efficiency improvements when using hydrogen as a fuel and even further improvements with water circulation.
-Thermal reductions with hydrogen and water recirculation will improve the lifetime of the engine which would reduce maintenance and overall costs.
-Between the two fuels, we see similar values of the engine performance metric, TSEC.
-Significant energy efficiency gains are seen with water recirculation which would improve the overall costs of the engine during its operational lifecycle.
-At the same water recovery fraction, hydrogen with water recirculation could achieve a lower TSEC value.
-
-There are technological obstacles to overcome in order to implement this water recirculation system in a modern turbofan engine.
-The main obstacle would be how to design a condenser that can recover a portion of the exhaust water without a excessive drag pressure losses.
-Therefore, a condenser design space study was completed to show the feasible design space for such a condenser.
-The results showed that at the maximum possible water recovery fraction for hydrogen quite a large pressure loss can be imposed before the improvements are canceled out.
-Furthermore, using hydrogen as the fuel allows for designs that are not available for an engine using Jet-A.
+We performed a design space study to understand the technology requirements for a condenser that might operate in the proposed water recovery system.
+% There are technological obstacles to overcome in order to implement this water recirculation system in a modern turbofan engine.
+% The main obstacle would be how to design a condenser that can recover a portion of the exhaust water without a excessive drag pressure losses.
+% Therefore, a condenser design space study was completed to show the feasible design space for such a condenser.
+The results showed that a hydrogen-fueled cycle with water recovery can sustain a pressure loss of 16\% across a condenser before the efficiency benefits diminish.
+% The results of the study showed that at the maximum possible water recovery fraction for hydrogen quite a large pressure loss can be imposed before the improvements are canceled out.
+% Furthermore, using hydrogen as the fuel allows for designs that are not available for an engine using Jet-A.
+% [ ] TODO: AL-PA, I suggest you bolster the discussion of these two sentences in the results section and maybe add a citation?
 The thermal properties of hydrogen provide a heat sink and thus a readily available resource for water condensation within the condenser.
 The hydrogen fuel absorbs heat and is then used in the combustion process, further improving engine efficiency.
-The novel water recovery system with shows promising efficiency results when used with hydrogen fuel.
-This water recovery system provides a potential avenue for hydrogen engine design that could help overcome the technological issues associated with hydrogen as a fuel.
+% The novel water recovery system shows promising efficiency results when used with hydrogen fuel.
+Hydrogen-fueled UHBR turbofan engines can be more efficient than Jet-A counterparts when optimized considering water recovery.
+Taking advantage of the beneficial properties of hydrogen is paramount for new engine technologies that can reduce emissions while improving performance.
+% This water recovery system provides a potential avenue for hydrogen engine design that could help overcome the technological issues associated with hydrogen as a fuel.
 
 \section{Acknowledgements}
-We would like to thank Justin Grey for his help with the pyCycle components of this work.
-Justin's expertise and knowledge of pyCycle tool helped make the development of the custom pyCycle components possible.
+\noindent
+We would like to thank Justin Gray for his support in the development of the water recovery pyCycle models.
 

### 2023-05-10 conference-paper/main.tex
uploading some changes to merge

--- 2023-05-09 conference-paper/main.tex
@@
     \hline                                                                                                                                                                   \\
-        $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-        $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+    $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+    $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
     \hline

### 2023-05-10 conference-paper/main.tex

--- 2023-05-10 conference-paper/main.tex
@@
 \begin{abstract}
+  Advances in commercial propulsion technology led to the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
+  Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
+  Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
+  Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
+  In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
+  We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
+  The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
   % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
@@
   % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
-    \caption{Injector (left) and extractor (right) diagrams that show the inputs and output streams of each component.
+  \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
     The inputs and outputs show which flow values are used to compute the amount of recirculated water.}
@@
   \caption{
-        Layout of the N+3 engine core with the closed-loop vapor recovery.
+    Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
     Black arrows are flow connections, blue boxes are cycle elements.
@@
 \begin{equation}
-    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}.
-    \label{eq:t4_ratio}
+  T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
+  \label{t4ratio}
 \end{equation}
@@
 \begin{equation}
-    V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}},
+  V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
   \label{eq:vratio}
@@
     Multipoint optimization problem definition.
-        The objective function is the fuel mass flow rate at the CRZ condition.
-        The constraints are the net thrust at TOC and an upper bound on engine diameter.
+    The objective function is the thrust specific energy consumption at the cruise condition.
+    The constraints are net thrust and engine diameter constraint at the design point, TOC.
   }
@@
     \hline
-        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \unit{lbm/s}     & 1        \\
+    minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
                     &                                &                                                                          &                &          \\
@@
                     & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -              & 1        \\
-                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \unit{\degree R} & 1        \\
-                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{eq:t4_ratio})              & -                & 1        \\
+                    & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
+                    & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
                     & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -              & 1        \\
@@
                     &                                &                                                                          &                &          \\
-        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \unit{lbf}       & 1        \\
-                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \unit{inch^2}    & 1        \\
+    subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
+                    & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{inch^2}    & 1        \\
     \cline{3-5}
@@
     \hline
-        variables   & $X_{\ce{H2O},\text{CRZ}}$ & -         & 0.3       & -           & 0.17        & -               \\
+    variables   & $x_{H2O,CRZ}$             & -         & 0.3       & -           & 0.17        & -               \\
                 & $\rm{PR}_{fan,TOC}$       & 1.285     & 1.292     & 1.288       & 1.297       & -               \\
@@
                 & $\rm{OPR}_{\rm{TOC}}$     & 61.012    & 61.188    & 60.660      & 61.952      & -               \\
-                    & $T_{4,\text{ratio}}$      & 0.913     & 0.911     & 0.918       & 0.915       & -               \\
-                    & $T_{4,\text{RTO}}$        & 3220.574  & -         & 3204.071    & -           & $^\circ$R       \\
-                    & $V_\text{ratio,CRZ}$      & 1.35      & 1.35      & 1.35        & 1.35        & -               \\
+                & $T_{4,ratio}$             & 0.913     & 0.911     & 0.918       & 0.915       & -               \\
+                & $T_{4,RTO}$               & 3220.574  & -         & 3204.071    & -           & $^\circ$R       \\
+                & $V_{ratio,CRZ}$           & 1.35      & 1.35      & 1.35        & 1.35        & -               \\
     \hline
-        constraints & $F_\text{net,TOC}$        & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf             \\
-                    & $D_\text{fan}$            & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$          \\
+    constraints & $F_{net,TOC}$             & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf             \\
+                & $D_{Fan}$                 & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$          \\
     \bottomrule
@@
   \includegraphics[width=1.0\textwidth]{N3_parallel_coords.pdf}
-    \caption{
-        Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
-        The red lines show Jet-A fuel and the blue lines show hydrogen fuel.
-        The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.
-    }
+  \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
+    The red lines show Jet-A fuel and the blue lines show \ce{H2} fuel.
+    The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.}
   \label{fig:parallel_coords}
@@
 %                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
-% \begin{table}[hbt!]
-%     \centering
-%     \caption{Thrust breakdown for each flight operating condition.
-%         The net thrust, gross thrust, and ram drag are shown for each optimization result.
-%     }
-%     \small
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}{r l l l l l}
-%         Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
-%         \toprule
-%         TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
-%               & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
-%         \hline
-%         RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
-%               & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
-%         \hline
-%         SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
-%               & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
-%         \hline
-%         CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
-%               & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
-%         \bottomrule
-%     \end{tabular}
-%     \label{tab:thrust}
-% \end{table}
+\begin{table}[hbt!]
+  \centering
+  \caption{Thrust breakdown for each flight operating condition.
+    The net thrust, gross thrust, and ram drag are shown for each optimization result.
+  }
+  \small
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{r l l l l l}
+    Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
+    \toprule
+    TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
+          & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
+    \hline
+    RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
+          & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
+    \hline
+    SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
+          & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
+    \hline
+    CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
+          & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
+    \bottomrule
+  \end{tabular}
+  \label{tab:thrust}
+\end{table}
 
@@
     \includegraphics[width=\textwidth]{N3_dpqp.pdf}
-        \caption{
-            Pressure loss sweep of duct 5 which is just upstream of the core nozzle.
-            The figure shows the optimized TSEC values (blue) for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery (red).
-            This shows the feasible space available for designing a water condenser while still benefiting from water recovery.
-        }
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
+      The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery.
+      This shows the working space available for designing a water condenser while still gaining the benefits of water recovery.}
     \label{fig:dpqp_sweep}
@@
     % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
-        % [ ] TODO: AL-PA, The statement about the upper bound is weird.  If it hit the upper bound each time, either say it was constant or remove that part.
     \includegraphics[width=\textwidth]{N3_wdot.pdf}
-        \caption{
-            Pressure loss sweep of duct 5 which is just upstream of the core nozzle.
+    \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
       The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.

### 2023-05-10 conference-paper/main.tex
addressed changes and updated slides

@@
 The added weight of tanks, pumping, and ducting makes this concept infeasible for a conventional aircraft.
-The main product of hydrogen combustion is water vapor.
-We can recover the vapor from the exhaust stream~\cite{Strom2002} with condensers and recirculate it upstream to eliminate additional storage requirements.
+The main product of hydrogen combustion is water vapor~\cite{Strom2002}.
+We can recover the vapor from the exhaust stream with condensers and recirculate it upstream to eliminate additional storage requirements.
+If hydrogen is used as the fuel then it can be used as a heat sink for the condenser~\cite{Boggia2002}.
 % Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
@@
 % [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
-% [ ] TODO: AL-PA, Missing station labels for the bypass duct, splitter, and inlet
+% [x] TODO: AL-PA, Missing station labels for the bypass duct, splitter, and inlet
 \begin{figure}[hbt!]
@@
 % [x] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
-% [ ] TODO: AL-PA, Combine the TOC and Off design stack into a single block that just says (MDP Cycle Model)
-% [ ] TODO: AL-PA, Remove the map scalar, core area, and water recovery area connections
-% [ ] TODO: AL-PA, The symbol for thrust is "F" not "T"
-% [ ] TODO: AL-PA, Show the final outputs on the left side of the XDSM and include a superscript "*" to denote optimal values. i.e \dot{m}_\text{fuel}^*
+% [x] TODO: AL-PA, Combine the TOC and Off design stack into a single block that just says (MDP Cycle Model)
+% [x] TODO: AL-PA, Remove the map scalar, core area, and water recovery area connections
+% [x] TODO: AL-PA, The symbol for thrust is "F" not "T"
+% [x] TODO: AL-PA, Show the final outputs on the left side of the XDSM and include a superscript "*" to denote optimal values. i.e \dot{m}_\text{fuel}^*
 \begin{figure}[!hbt]
@@
     objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \si{lbm/s} \\
-                & $\rm{TSEC}_{\rm{CRZ}}$    & 8186.254  & 7766.338  & 8295.236    & 7859.635    & \si{lbm/hr/lbf} \\
+    % & $\rm{TSEC}_{\rm{CRZ}}$    & 8186.254  & 7766.338  & 8295.236    & 7859.635    & \si{lbm/hr/lbf} \\
     \hline
@@
 We observe the optimal $T_{4,\text{RTO}}$ is larger for Jet-A than hydrogen because hydrogen has a larger combustion flammability limit and the engine can burn at a lower equivalence ratio to attain the same thrust requirements~\cite{Adler2023}.
-% [ ] TODO: AL-PA, why is this favorable for emissions reduction?  Need to cite or explain.
-Burning leaner reduces the fuel consumption and is favorable for emissions reduction.
+% [x] TODO: AL-PA, why is this favorable for emissions reduction?  Need to cite or explain.
+Burning leaner lowers the FAR which reduces the fuel consumption for a given engine flow rate and is favorable for emissions reduction.
 % The additional water in the combustion improves the propulsive efficiency and enables the increase in overall pressure ratio.
@@
 % AL-PA, We can make another plot for the water fractions and the dpQp study.
-% [ ] TODO: AL-PA, Can you make the y-axis range for T4_ratio smaller so we can see the differences a bit better.  Maybe like 0.85 - 0.95
-% [ ] TODO: AL-PA, Same comment as above but for FPR, maybe 1.28-1.32
-% [ ] TODO: AL-PA, If a variable has bounds, can we make the y-axis limits match the bounds?
+% [x] TODO: AL-PA, Can you make the y-axis range for T4_ratio smaller so we can see the differences a bit better.  Maybe like 0.85 - 0.95
+% [x] TODO: AL-PA, Same comment as above but for FPR, maybe 1.28-1.32
+% [x] TODO: AL-PA, If a variable has bounds, can we make the y-axis limits match the bounds?
 \begin{figure}[hbt!]
@@
 % See this example in niceplots: https://github.com/mdolab/niceplots/blob/main/examples/plot_bar_chart.py and https://github.com/mdolab/niceplots/blob/main/examples/ref/bar_chart.png
-% [ ] TODO: Can you add a line to bar chart that shows the improvement between baseline Jet-A and hydrogen with water recovery?
+% [x] TODO: Can you add a line to bar chart that shows the improvement between baseline Jet-A and hydrogen with water recovery?
 \begin{figure}[hbt!]
@@
 As~\citeauthor{Strom2002} point out, a hydrogen-fueled engine would have close to 3 times more water in the exhaust than a similar Jet-A fueled counterpart.
-% [ ] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
+% [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
+The engine designs with water recovery showed that there was about 2.38\si{lbm/s} and 1.08\si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively
 % Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
@@
 % This improvement design space would be reduced if only a smaller fraction of water recovered could be obtained.
-% [ ] TODO: AL-PA, Re-write this part to match the new figure that shows the mass flow of water extracted (per our slack convo)
-The total water available in the core stream as a function of the same pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
-Figure~\ref{fig:dpqp_wdot} shows that the optimizer finds designs that increase the available water in the core stream.
-Since the water recovery fraction is always pushed to 17\%, the water mass flow rate that is recovered increases to overcome the pressure loss.
+% [x] TODO: AL-PA, Re-write this part to match the new figure that shows the mass flow of water extracted (per our slack convo)
+The water flow rate extracted from the core stream as a function of the same pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
+% Figure~\ref{fig:dpqp_wdot} shows that the optimizer finds designs that increase the available water in the core stream.
+Since the water recovery fraction is always pushed to 17\%, the optimizer increases the recovered water mass flow rate to overcome the pressure loss.
 This effect helps the engine increase the feasible design space in Figure~\ref{fig:dpqp_sweep}.
-
-% NOTE: PA-AL, any other plots to include?
-% AL, Nah we are good to go with plots
+The hydrogen fuel would serve a double purpose in this cycle.
+The cold hydrogen fuel can be used as a heat sink for the condenser and then injected into the combustor at a higher temperature, further improving efficiency~\cite{Boggia2002}.
 
@@
 % Furthermore, using hydrogen as the fuel allows for designs that are not available for an engine using Jet-A.
-% [ ] TODO: AL-PA, I suggest you bolster the discussion of these two sentences in the results section and maybe add a citation?
+% [x] TODO: AL-PA, I suggest you bolster the discussion of these two sentences in the results section and maybe add a citation?
 The thermal properties of hydrogen provide a heat sink and thus a readily available resource for water condensation within the condenser.

### 2023-05-10 conference-paper/main.tex
Intro and tables fixed

@@
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
 \usepackage{graphicx}
@@
 \usepackage{doi} % For getting hyperlinked DOI in the references
+\usepackage{hyperref}
 
@@
 \title{Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization} % change
-\author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
+\author{Peter N.~Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
 \author{Andrew H~.R.~Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
@@
   % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
-  Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
-  These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
-  Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
-  Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
-  In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
-  We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
-  The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
+  % Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
+  % These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
+  % Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
+  % Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
+  % In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
+  % We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
+  % The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
   % The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
@@
     \caption{
-      We extract a fraction of the moles of water from the out flow of duct 5.
-      The extracted water is routed back upstream to the injector and the rest is exhausted out the nozzle.
+      We extract a fraction of the mass flow of water determined by the molar composition.
+      The extracted water is routed from duct 5 back upstream to the injector and the rest is exhausted out the nozzle.
     }
@@
 We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
-A simple schematic of the extractor is shown in Figure~\ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the fraction of water that is recovered from the core stream.
+A simple schematic of the extractor is shown in Figure~\ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the mass fraction of water that is recovered from the core stream.
 We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.
@@
     Parameter              & Value & Units        & Description                                                                                                            \\
-    \hline                                                                                                                                                                   \\
-    $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-    $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+    \hline
+    $\rm{LHV}_{\rm{JetA}}$ & 18564 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
+    $\rm{LHV}_{\rm{H2}}$   & 51591 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
     \hline
@@
 \end{equation}
-where $V_\text{ideal}$ is the ideal nozzle exit velocity and $C_v$ is the nozzle velocity coefficient that accounts for non-ideal effects.
+where $V_\text{ideal}$ is the ideal nozzle exit velocity and $C_v$ is the nozzle velocity coefficient that accounts for non-ideal nozzle effects.
 The final design variable is the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$).
@@
     Multipoint optimization problem definition.
-    The objective function is the thrust specific energy consumption at the cruise condition.
+    The objective function is the fuel flow rate at the cruise condition.
     The constraints are net thrust and engine diameter constraint at the design point, TOC.
@@
 %                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
-\begin{table}[hbt!]
-  \centering
-  \caption{Thrust breakdown for each flight operating condition.
-    The net thrust, gross thrust, and ram drag are shown for each optimization result.
-  }
-  \small
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{r l l l l l}
-    Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
-    \toprule
-    TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
-          & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
-    \hline
-    RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
-          & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
-    \hline
-    SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
-          & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
-    \hline
-    CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
-          & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
-    \bottomrule
-  \end{tabular}
-  \label{tab:thrust}
-\end{table}
+% \begin{table}[hbt!]
+%   \centering
+%   \caption{Thrust breakdown for each flight operating condition.
+%     The net thrust, gross thrust, and ram drag are shown for each optimization result.
+%   }
+%   \small
+%   \renewcommand{\arraystretch}{1.2}
+%   \begin{tabular}{r l l l l l}
+%     Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
+%     \toprule
+%     TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
+%           & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
+%     \hline
+%     RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
+%           & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
+%     \hline
+%     SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
+%           & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
+%     \hline
+%     CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
+%           & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
+%     \bottomrule
+%   \end{tabular}
+%   \label{tab:thrust}
+% \end{table}
 
@@
 % [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
-The engine designs with water recovery showed that there was about 2.38\si{lbm/s} and 1.08\si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively
+The engine designs with water recovery showed that there was about 2.38 \si{lbm/s} and 1.08 \si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively.
 % Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
 Hydrogen combustion offers an immediate reduction in emissions and produces more water in the exhaust stream.
-With an advanced water recovery system, we can achieve better TSEC with hydrogen fuel than Jet-A.
+With an advanced water recovery system, we can achieve better TSEC with hydrogen fuel than a standard Jet-A engine without water recovery.
 To make hydrogen fueled engines a reality, we need to take advantage of the additional benefits of hydrogen combustion.

### 2023-05-10 figures/N3_cycle.tex
added presentation file
Intro and tables fixed

@@
     % Create station labels
-    % \node [station_label, below=8em of inlet.west] (1) {1};
-    \node [station_label, below=6em of fan.west] (1) {1};
-    % \node [station_label, below=8em of splitter.west] (13) {13};
+    \node [station_label, below=6em of inlet.west] (1) {1};
+    \node [station_label, below=6em of fan.west] (12) {12};
+    \node [station_label, below=6em of splitter.west] (13) {13};
     \node [station_label, below=6em of lpc.west] (2) {2};
@@
     \node [station_label, below=6em of corenozzle.west] (5) {5};
-    \node [station_label, below=6em of bypnozzle.west] (17) {17};
+    \node [station_label, below=6em of bypduct.west] (17) {17};
+    \node [station_label, below=6em of bypnozzle.west] (18) {18};
 
@@
     % Draw station label connections
-    % \path [line] (inlet.west) -- (1.north);
-    \path [line] (fan.west) -- (1.north);
-    % \path [line] (splitter.west) -- (13.north);
+    \path [line] (inlet.west) -- (1.north);
+    \path [line] (fan.west) -- (12.north);
+    \path [line] (splitter.west) -- (13.north);
     \path [line] (lpc.west) -- (2.north);
@@
     \path [line] (corenozzle.west) -- (5.north);
-    \path [line] (bypnozzle.west) -- (17.north);
+    \path [line] (bypduct.west) -- (17.north);
+    \path [line] (bypnozzle.west) -- (18.north);
 

### 2023-05-10 conference-paper/main.tex
More changes

@@
 \usepackage{subcaption}
+\usepackage{hyperref}
 \usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
@@
 \usepackage{doi} % For getting hyperlinked DOI in the references
-\usepackage{hyperref}
 
@@
 % Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
-This system represents a closed loop water feedback system inside the propulsion cycle.
+This system represents a closed water feedback loop inside the propulsion cycle.
 % This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
@@
             We extract a fraction of the mass flow of water determined by the molar composition.
-      The extracted water is routed from duct 5 back upstream to the injector and the rest is exhausted out the nozzle.
+            The extracted water is routed from Duct5 back upstream to the injector and the rest is exhausted out the nozzle.
         }
@@
 % [x] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
-The fuel properties used in the engine model are given in~\ref{fuel_props}.
+The fuel properties used in the engine model are given in~\ref{fuel_props}~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}}.
 
@@
         \hline
-    $\rm{LHV}_{\rm{JetA}}$ & 18564 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
-    $\rm{LHV}_{\rm{H2}}$   & 51591 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
+        $\rm{LHV}_{\rm{JetA}}$ & 18564 & \si{BTU/lbm} & Lower heating value of Jet-A \\
+        $\rm{LHV}_{\rm{H2}}$   & 51591 & \si{BTU/lbm} & Lower heating value of H2    \\
         \hline
@@
 \end{figure}
+
+\begin{table}[hbt!]
+    \centering
+    \caption{
+        Multipoint optimization problem definition.
+        The objective function is the fuel flow rate at the cruise condition.
+        The constraints are net thrust and engine diameter constraint at the design point, TOC.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{r l l r l}
+        \toprule
+                        & Variable/Function              & Description                                                              & Units            & Quantity \\
+        \hline
+        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \unit{lbm/s}     & 1        \\
+                        &                                &                                                                          &                  &          \\
+        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery mass fraction at CRZ                                      & -                & 1        \\
+                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                   & -                & 1        \\
+                        & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                               & -                & 1        \\
+                        & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -                & 1        \\
+                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \unit{\degree R} & 1        \\
+                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -                & 1        \\
+                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -                & 1        \\
+        \cline{3-5}
+                        &                                & Total                                                                    &                  & 7        \\
+                        &                                &                                                                          &                  &          \\
+        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \unit{lbf}       & 1        \\
+                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \unit{inch^2}    & 1        \\
+        \cline{3-5}
+                        &                                & Total                                                                    &                  & 2        \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:opt_problem}
+\end{table}
 
@@
 % We add the water recovery fraction only at the CRZ point as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.
-
+\begin{table}[hbt!]
+    \centering
+    \caption{Design variable ranges for the optimization problem.
+    }
+    \small
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{l l l l}
+        Design Variable          & Lower  & Upper  & Units            \\
+        \toprule
+        $X_{\rm{H_2O,CRZ}}$      & 0.0    & 1.0    & -                \\
+        $\rm{PR}_{\rm{fan,TOC}}$ & 1.2    & 1.4    & -                \\
+        $\rm{PR}_{\rm{LPC,TOC}}$ & 2.5    & 4.0    & -                \\
+        $\rm{OPR}_{\rm{TOC}}$    & 40.0   & 70.0   & -                \\
+        $T_{4,\rm{ratio}}$       & 0.5    & 0.95   & -                \\
+        $T_{4,RTO}$              & 3000.0 & 3600.0 & \unit{\degree R} \\
+        $V_{ratio,CRZ}$          & 1.35   & 1.45   & -                \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:dv_table}
+\end{table}
 % [x] TODO: AL-PA, You already explained the flight conditions in the multipoint section so not necessary here
@@
 % [x] TODO: PA-PA, explain variable ranges
-\begin{table}[hbt!]
-  \centering
-  \caption{
-    Multipoint optimization problem definition.
-    The objective function is the fuel flow rate at the cruise condition.
-    The constraints are net thrust and engine diameter constraint at the design point, TOC.
-  }
-  \small
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{r l l r l}
-    \toprule
-                    & Variable/Function              & Description                                                              & Units          & Quantity \\
-    \hline
-    minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
-                    &                                &                                                                          &                &          \\
-    with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery mass fraction at CRZ                                      & -              & 1        \\
-                    & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                   & -              & 1        \\
-                    & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                               & -              & 1        \\
-                    & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -              & 1        \\
-                    & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
-                    & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
-                    & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -              & 1        \\
-    \cline{3-5}
-                    &                                & Total                                                                    &                & 7        \\
-                    &                                &                                                                          &                &          \\
-    subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
-                    & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{inch^2}    & 1        \\
-    \cline{3-5}
-                    &                                & Total                                                                    &                & 2        \\
-    \bottomrule
-  \end{tabular}
-  \label{tab:opt_problem}
-\end{table}
-
-\begin{table}[hbt!]
-  \centering
-  \caption{Design variable ranges for the optimization problem.
-  }
-  \small
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{l l l l}
-    Design Variable          & Lower  & Upper  & Units     \\
-    \toprule
-    $X_{\rm{H_2O,CRZ}}$      & 0.0    & 1.0    & -         \\
-    $\rm{PR}_{\rm{fan,TOC}}$ & 1.2    & 1.4    & -         \\
-    $\rm{PR}_{\rm{LPC,TOC}}$ & 2.5    & 4.0    & -         \\
-    $\rm{OPR}_{\rm{TOC}}$    & 40.0   & 70.0   & -         \\
-    $T_{4,\rm{ratio}}$       & 0.5    & 0.95   & -         \\
-    $T_{4,RTO}$              & 3000.0 & 3600.0 & $^\circ$R \\
-    $V_{ratio,CRZ}$          & 1.35   & 1.45   & -         \\
-    \bottomrule
-  \end{tabular}
-  \label{tab:dv_table}
-\end{table}
 
@@
 We solve the optimization problem listed in Table~\ref{tab:opt_problem} with SNOPT~\cite{Gill2005a}, a gradient-based sequential quadratic programming (SQP) algorithm for large-scale constrained problems.
-
 % NOTE: AL-PA, this was confusing and I don't think it add much useful information that the readers will actually understand.
@@
 % The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for \ce{H2}.
-
 \section{Results}
@@
         \toprule
-    objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \si{lbm/s} \\
+        objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \unit{lbm/s} \\
         % & $\rm{TSEC}_{\rm{CRZ}}$    & 8186.254  & 7766.338  & 8295.236    & 7859.635    & \si{lbm/hr/lbf} \\
@@
 % [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
-The engine designs with water recovery showed that there was about 2.38 \si{lbm/s} and 1.08 \si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively.
+The optimal designs with water recovery have approximately \SI{2.38}{lbm/s} and \SI{1.08}{lbm/s} of water in the core stream for hydrogen and Jet-A, respectively.
 % Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
@@
 % [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
-The efficiency improvement gained from water recirculation warrant a design space study for potential condenser technology.
+The efficiency improvement due to water recirculation warrants a design space study for potential condenser technology.
 Companies that are developing engines with water recirculation suggest that hydrogen can be used to as the heat sink for a water condenser~\cite{arpa-e_2021}.
@@
 
-We model the pressure loss across the condenser by varying the relative total pressure loss across duct 5 just upstream of the core nozzle.
+We model the pressure loss across the condenser by varying the relative total pressure loss across Duct5 just upstream of the core nozzle.
 % pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
@@
 % [x] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
-We varied the total pressure loss across the duct to simulate drag from an increasingly large condenser.
+We varied the total pressure loss across the duct to simulate an increasingly larger condenser jutting out into the duct.
 We ran an optimization to minimize fuel mass flow rate of hydrogen at each pressure loss value using the formulation for water recovery in Table~\ref{tab:opt_problem}.

### 2023-05-10 conference-paper/main.tex
Final updates from me

@@
 We ran an optimization to minimize fuel mass flow rate of hydrogen at each pressure loss value using the formulation for water recovery in Table~\ref{tab:opt_problem}.
+The mass fraction of extracted water is held constant at 17\% to make a fair comparison at each pressure loss point.
+
+\begin{figure}[hbt!]
+    \centering
+    \begin{subfigure}[t]{0.48\textwidth}
+        % [x] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
+        \includegraphics[width=\textwidth]{N3_dpqp.pdf}
+        \caption{
+            The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery.
+            This shows the feasible space available for designing a water condenser while still benefiting from water recovery.}
+        \label{fig:dpqp_sweep}
+    \end{subfigure}
+    \hspace{2pt}
+    \begin{subfigure}[t]{0.48\textwidth}
+        % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
+        \includegraphics[width=\textwidth]{N3_wdot.pdf}
+        \caption{
+            The figure shows the optimal mass flow rate of water extracted at each pressure loss value.
+        }
+        \label{fig:dpqp_wdot}
+    \end{subfigure}
+    \caption{Pressure loss sweep of Duct5.
+        Duct5 is just upstream of the water vapor extractor component.}
+    \label{fig:dpqp_study}
+\end{figure}
+
 % The rest of the engine design variables were optimized during this pressure loss sweep to determine the how the optimal amount of water recovery changed based on drag losses from the condenser.
@@
 The blue region represents the feasible space for potential condenser technology.
-\begin{figure}[hbt!]
-    \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        % [x] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
-        \includegraphics[width=\textwidth]{N3_dpqp.pdf}
-        \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-            The figure shows the optimized TSEC values for varying levels of pressure loss due to the condensation of water compared to the optimization problem without water recovery.
-            This shows the working space available for designing a water condenser while still gaining the benefits of water recovery.}
-        \label{fig:dpqp_sweep}
-    \end{subfigure}
-    \hspace{2pt}
-    \begin{subfigure}[t]{0.49\textwidth}
-        % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
-        \includegraphics[width=\textwidth]{N3_wdot.pdf}
-        \caption{Pressure loss sweep of Duct5 which is just upstream of the water vapor extractor component.
-            The figure shows the resulting total available water in the exhaust stream for varying levels of pressure loss in the extractor flow path.
-            The engine was optimized with the water recovery upper bound of 17\%.
-        }
-        \label{fig:dpqp_wdot}
-    \end{subfigure}
-    \caption{}
-    \label{fig:dpqp_study}
-\end{figure}
 % From Figure~\ref{fig:dpqp_sweep}, we can see the design space in which the closed-loop water recovery model is feasible.
@@
 % [x] TODO: AL-PA, Re-write this part to match the new figure that shows the mass flow of water extracted (per our slack convo)
-The water flow rate extracted from the core stream as a function of the same pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
+The sensitivity of water extraction with respect to pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
 % Figure~\ref{fig:dpqp_wdot} shows that the optimizer finds designs that increase the available water in the core stream.
-Since the water recovery fraction is always pushed to 17\%, the optimizer increases the recovered water mass flow rate to overcome the pressure loss.
-This effect helps the engine increase the feasible design space in Figure~\ref{fig:dpqp_sweep}.
+The optimizer increases the amount of water extraction to compensate for the increasing pressure loss.
+% Since the water recovery fraction is always pushed to 17\%, the optimizer increases the recovered water mass flow rate to overcome the pressure loss.
+This represents a benchmark for designing condenser technology that can operate within the proposed water recirculation system.
 The hydrogen fuel would serve a double purpose in this cycle.

### 2023-05-11 conference-paper/main.tex
Fixes from Quims feedback

@@
 
-% [x] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
 \title{Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization} % change
@@
 \author{Andrew H~.R.~Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
-\author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
+\author{Joaquim R.~R.~A.~Martins\footnote{Pauline M. Sherman Collegiate Professor, Department of Aerospace Engineering, AIAA Fellow}}
 \affil{University of Michigan, Ann Arbor, MI, 48109}
-
-% ==================================================
-%	OVERALL TODOS
-% ==================================================
-% [x] TODO: AL-PA, Need to add equation labels
-% [x] TODO: AL-PA, When you are citing things you should include a "~" to link the citation to the text.  i.e, "OpenMDAO~\cite{Gray2019a}" (See my edits in the introduction)
-% [x] TODO: AL-PA, You should also use the "~" to link all equation, figure, and table references to the text.
-% [x] TODO: AL-PA, Make sure all acronyms and subscripts that are longer than a single letter or represent words are shown as text using \rm{} in math mode
 
@@
   Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
-    In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
+  In this study, we model a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
   We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
-    The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
-    % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
-    % Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
-    % These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
-    % Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
-    % Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
-    % In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
-    % We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
-    % The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
-    % The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
+  The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's thermodynamic properties to reduce emissions and improve performance.
 \end{abstract}
@@
 The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
-% [x] TODO: AL-AL, probably should cite the N+3 paper here
 N+3 technology estimates for engines that burn hydrocarbon fuels suggest that higher efficiencies can be achieved by designing ultra high bypass ratio (UHBR) turbofans with small cores and high overall pressure ratios (OPR)~\cite{Jones2017a}.
@@
 We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
-% [x] TODO: PA-PA, add section about MAUD and cite.
 
 % Message 2: Background and references to support using H2 and water injection in HBTF engines
-% [x] TODO: AL-PA, Need to find a journal/conference paper to cite for the following statement.  Maybe find one or more papers other than just the NASA report?
 Water injection is the process of introducing water upstream of the combustor as finely atomized droplets.
@@
 Additionally, water injection improves fuel efficiency and thrust output with lower combustion temperatures that can improve the lifetime of turbine blades and reduce noise~\cite{Daggett2010}.
-% [x] TODO: AL-PA, Should try to find a citation for this if one exists.
 Traditional propulsion systems that burn hydrocarbon fuels would require external demineralized water storage on the aircraft for water injection~\cite{Mourouzidis2015}.
@@
 We can recover the vapor from the exhaust stream with condensers and recirculate it upstream to eliminate additional storage requirements.
-If hydrogen is used as the fuel then it can be used as a heat sink for the condenser~\cite{Boggia2002}.
-% Condensing water vapor from the exhaust stream of hydrogen combustion and recirculating it eliminates any additional storage requirements.
+If hydrogen is used as the fuel it can then be used as a heat sink for the condenser~\cite{Boggia2002}.
 This system represents a closed water feedback loop inside the propulsion cycle.
-% This allows for the theoretical design of a closed loop water feedback system inside the propulsion cycle.
 Pratt and Whitney are actively researching this technology to increase the efficiency of hydrogen-powered propulsion~\cite{arpa-e_2021}.
-% They suggest that water vapor can be recovered by utilizing the thermal properties of hydrogen to condense some of the water in the turbofan exhaust.
 
 Zero-dimensional cycle modeling is an efficient tool for predicting the initial design, performance, and emissions of new propulsion concepts.
-% [x] TODO: AL-AL, Need to cite CEA paper.
 Zero-dimensional analysis uses a first-principles approach with a chemical equilibrium analysis (CEA) thermodynamics solver~\cite{Gordon1994} that considers the molecular species of different fuels.
@@
 pyCycle is built on top of the OpenMDAO framework~\cite{Gray2019a} to facilitate gradient-based optimization and leverage hierarchical solver structures.
-% NOTE: AL-PA, I removed the MAUD sentence because it's a wormhole that you probably don't want to enter lol.
 
@@
 This work is organized as follows. First, in Section~\ref{sec:method}, we introduce the turbofan model and explain the water injection and water recovery components.
-In section~\ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
-Finally, we present the optimized results and discuss the condenser design space study in section~\ref{sec:results}.
+In Section~\ref{sec:optprob} the implementation of the multipoint optimization problem is discussed.
+Finally, we present the optimized results and discuss the condenser design space study in Section~\ref{sec:results}.
 
@@
 The high pressure compressor (HPC) is connected to the high pressure turbine (HPT) by the high pressure shaft.
-% [x] TODO: AL-PA, I think we need to reference the engine diagram figure here so the reader can visualize all this text.
-Figure~\ref{fig:n3_cycle} shows a simplified UHB turbofan engine flow path.
-% [x] TODO: AL-PA, potentially move the commented line below about CEA into the subsection discussing the propulsion model.  I think it's too much detail for the setup of this section.
+Figure~\ref{fig:N3_original} shows a simplified UHB turbofan engine flow path.
 We introduce the closed-loop water recovery system as a feedback cycle that transports water from the exhaust to upstream of the compressors.
-The recovery system injects vaporized water into the core stream that reduces the combustion temperature due to heat absorption.
+The recovery system injects vaporized water into the core stream just upstream of the HPC.
 The vapor recovery component is located just upstream of the core nozzle to extract water from the exhaust and recycle it back to the injector.
 Figure~\ref{fig:n3_clvr} shows the water vapor recovery loop implemented in a turbofan engine.
-% [x] TODO: AL-PA, Again, probably should reference a figure to give context to the water recovery layout.
-% NOTE: AL-PA, don't discredit your work before you even explain the model and methods.  We can make this point in the results or conclusion.
 
@@
 
-% [x] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
-% [x] TODO: AL-PA, Add the description of the figure elements to the caption.
-% [x] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
-% [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
-% [x] TODO: AL-PA, Missing station labels for the bypass duct, splitter, and inlet
 \begin{figure}[hbt!]
@@
 The water vapor recovery component sits downstream of the LPT and extracts water from the flow before exiting the core nozzle.
-% [x] TODO: AL-PA, add a sentence about the assumptions for the vapor recovery instead of the mentioning the condenser
 We assume that a fraction of the total water available in the exhaust stream is recovered and that there are no pressure or temperature losses associated with this process.
-% NOTE: AL-PA, we will talk about the condenser when we discuss the results of the pressure recovery parameter sweep.
 The component flow interface and mechanical connections, including the water injector and water extractor, are depicted in Figure~\ref{fig:n3_cycle}.
@@
   \caption{
-        The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
+    Configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
     The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and re-injects it upstream of the high-pressure compressor.
@@
 We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of \ce{H2O} to air in the reactants of the inflow mixture.
-% [x] TODO: AL-PA, Reference Table 1 with humidity values as well.
 \citet{Kalnay1996} give the humidity values for each flight condition, provided in Table~\ref{tab:flight_conds}.
@@
 
-% NOTE: AL-PA, I turned this into a subfigure to save some space
 \begin{figure}[hbt!]
@@
   \end{subfigure}
-    % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
   \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
@@
 
-% NOTE: AL-PA, I made this a new paragraph (no content change)
 The model results in a mismatch between the mass flow rate upstream of the HPC and the mass flow rate exiting the core nozzle.
@@
 We also assume the injected water molecules are at the same pressure and temperature as the air flow just before the HPC.
-% NOTE: AL-PA, I removed this because I don't think the reader will understand the phase-change nuances with 0D cycle and CEA
 We illustrate the water recirculation loop and the nonlinear solver connections in Figure~\ref{fig:N3_xdsm_full}.
@@
 
-% NOTE: AL-PA, this ended up a bit choppy, but I think it's better than before.  If you want to adjust things a bit go ahead.
 We impose \emph{balance} equations to satisfy the physical governing equations, conservation laws, and design rules.
@@
 
-% NOTE: AL-PA, I added this blurb to introduce multipoint
 We operate the engine cycle in different modes depending on the desired conservation relationships, design rules, and flight conditions.
@@
 The ``on-design'' point is top-of-climb (TOC) with ``off-design'' conditions at rolling takeoff (RTO), sea-level static (SLS), and cruise (CRZ).
-% To account for each of these operating conditions, the N+3 model uses a technique called Multipoint Design Point (MDP) modeling to converge the model to an engine design.
 Table~\ref{tab:flight_conds} shows the different altitudes and mach numbers for each flight condition.
-% We consider these points because they either limit the performance at cruise or present critical design considerations for the propulsion system.
-% [x] TODO: AL-PA, Add a small table to show the mach and altitude of each flight condition
+
 \begin{table}[hbt!]
@@
 \end{table}
-% [x] TODO: AL-PA, You should explain why each design point is important in a separate sentence for each.
-%   - For example, the SLS point is important for making sure the turbo machinery and flow paths are designed to meet a static thrust target
-%   - The RTO point is limiting for temperature, etc...
-% [x] TODO: AL-PA, Consider re-writing this section using the comments from the previous TODO.  Be more concise and direct with the language here.
-% [x] TODO: AL-PA, This is a big run-on sentence.  Consider breaking it up and being more specific about the requirements at each design point.  See previous comments.
+
 The design rules at SLS ensure that the turbo machinery and flow paths meet the static thrust target.
@@
 The converged model represents a feasible multipoint engine that accounts for design considerations and conservation laws at all four operating conditions.
-% [x] TODO: AL-PA, I removed a lot of stuff here to simplify this section.
-%                  - Ultimately I think we need to reference the pyCycle paper to prevent duplicating a bunch of math/text
-%                  - If you are okay with this check off this TODO.  If not feel free to add a bit more and then check it off.
 We direct the reader to the N+3 multipoint model definition in the paper by \citet{Hendricks2019} for the detailed description of the balance relationships.
 
-% [x] TODO: AL-PA, Already discussed, but this should be the only "fine-detail" XDSM in the paper.
-% [x] TODO: AL-PA, Make the figure use the entire text width so that it's easier to read.  Might have to reposition a bit.
-% [x] TODO: AL-PA, Remove the mdot_inject and mdot_extract stuff, just call it mdot_water
-% [x] TODO: AL-PA, copy the format of the cooling flow connections for the water mass flow rates
-% [x] TODO: AL-PA, "Area" should be abbreviated to just the letter "A"
-% [x] TODO: AL-PA, Change the component types for TOC, RTO, SLS, CRZ, and BALANCE to be implicit groups. They should show up as red polygons.
 \begin{figure}[hbt!]
@@
 \label{sec:optprob}
-% NOTE: AL-PA, No reason to have an extra subsection here so I removed it
-% \subsection{Problem Statement}
-% Briefly discuss the optimization problem
-% NOTE: AL-PA, "We will perform" makes it seem like we haven't done the work yet.
+
 We performed MDP gradient-based design optimization of the N+3 engine model considering the TOC, RTO, SLS, and CRZ flight conditions.
-% NOTE: AL-PA, I re-wrote this to be more direct
 The objective is to minimize fuel burn subject to design and performance constraints.
-% [x] TODO: AL-PA, This is a good place to discuss the performance metrics and add the equations for TSEC and explain why it's better for this study than TSFC.
 Typical gas-turbine analysis measures the efficiency using the thrust-specific fuel consumption (TSFC).
-% For measuring the efficiency of Jet engines, thrust-specific fuel consumption (TSFC) is used in cycle analysis since it represents how much fuel is burned at a given thrust level.
 However, this metric is not useful in the comparison of efficiency between Jet-A and hydrogen fueled cycle models because of the differences in fuel density and energy capacity.
-% However, when comparing Jet-A and hydrogen fuels this is not such a good metric since a given mass flow rate of hydrogen has an energy content almost 3 times that of Jet-A.
 A better metric for comparing Jet-A versus hydrogen is thrust-specific energy consumption (TSEC)~\cite{Adler2023}.
@@
 \end{equation}
-% In this work we are concerned with minimizing fuel burn of the engine subject to thrust constraints.
-% [x] TODO: AL-PA, TSEC is not the objective.  Fuel burn is the objective.  TSEC is the efficiency metric of interest.
+
 TSEC will be used as a efficiency metric at the cruise condition to compare the two fuels in the results.
-% [x] TODO: AL-PA, explain the important aspects of the XDSM in writing before referencing the figure.
-The fuel properties used in the engine model are given in~\ref{fuel_props}~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}}.
+The fuel properties used in the engine model are given in Table~\ref{fuel_props}~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}}.
 
-% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
-% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
 \begin{table}[hbt!]
@@
 The detailed optimization problem description is provided in Table~\ref{tab:opt_problem}.
-% Large multidisciplinary optimization problems are commonly represented with extended design structure matrix (XDSM) diagrams.
-% XDSM diagrams are used to visualize the complex implicit and explicit relationships between functions, the solver, and optimizer.
-% An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure~\ref{fig:N3_opt_xdsm}.
 
-% [x] TODO: AL-PA, simplify this XDSM to show just the optimization setup. Condense the MDA into a single block and remove all the multipoint acronyms.
-% [x] TODO: AL-PA, Combine the TOC and Off design stack into a single block that just says (MDP Cycle Model)
-% [x] TODO: AL-PA, Remove the map scalar, core area, and water recovery area connections
-% [x] TODO: AL-PA, The symbol for thrust is "F" not "T"
-% [x] TODO: AL-PA, Show the final outputs on the left side of the XDSM and include a superscript "*" to denote optimal values. i.e \dot{m}_\text{fuel}^*
 \begin{figure}[!hbt]
@@
                     & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -              & 1        \\
-                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \unit{\degree R} & 1        \\
+                    & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
                     & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
@@
                     &                                &                                                                          &                &          \\
-        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \unit{lbf}       & 1        \\
-                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \unit{inch^2}    & 1        \\
+    subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
+                    & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{in^2}      & 1        \\
     \cline{3-5}
@@
 
-% [x] TODO: AL-PA, I would elaborate on this a bit more.  Are these the on-design parameters?  Are they constraints?
-% [x] TODO: AL-PA, The N+3 model has a bunch of constraints imposed on the multipoint problem via balance comps.  This is a good place to talk about those.
-% [x] TODO: AL-PA, Discuss how using balance comps instead of constraints represents a reduced space problem for the optimizer. (See pycycle paper for more information).
-% [x] TODO: AL-AL, I decided this is no longer necessary
-
-% [x] TODO: AL-PA, I would break this up into two or more sentences.
 The design variables are specified at different flight conditions.
@@
 The turbine inlet temperature at TOC is specified by a temperature ratio design variable ($T_{4,\rm{ratio}}$) between the RTO and TOC points, calculated as
-% The design variables for this problem are pressure controls such as fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$).
-% Other design variables are temperature controls such as burner temperature at RTO ($T_{4,\rm{RTO}}$) and the TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$).
-% TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation~\eqref{t4ratio}.
 
@@
 The final design variable is the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$).
-% [x] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
-% [x] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
 We only include the water recovery fraction at cruise because it has the largest impact on the fuel mass flow rate objective function.
@@
 The range for each design variable and the associated units are shown in Table~\ref{tab:dv_table}.
-% We add the water recovery fraction only at the CRZ point as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.
+
 \begin{table}[hbt!]
@@
     $T_{4,\rm{ratio}}$       & 0.5    & 0.95   & -              \\
-        $T_{4,RTO}$              & 3000.0 & 3600.0 & \unit{\degree R} \\
-        $V_{ratio,CRZ}$          & 1.35   & 1.45   & -                \\
+    $T_{4,\rm{RTO}}$         & 3000.0 & 3600.0 & \si{\degree R} \\
+    $V_{\rm{ratio,CRZ}}$     & 1.35   & 1.45   & -              \\
     \bottomrule
@@
 \end{table}
-% [x] TODO: AL-PA, You already explained the flight conditions in the multipoint section so not necessary here
-% [x] TODO: AL-PA, I would describe the constraints in more detail here.  This might be a good spot to talk about the constraints imposed by the balance comps at the top level.
-%                  - i.e the SLS and CRZ net thrust constraints
-%                  - i.e how the BPR is set by the nozzle velocity ratio
-%                  - i.e The interdependence of the TOC mass flow rate and the RTO temperature
+
 As aforementioned in Section~\ref{sec:method}, the N+3 model uses balance relationships to enforce design, conservation, and performance requirements.
@@
 
-% The net thrust for the SLS and CRZ conditions are set using balance relationships between the RTO and TOC points respectively.
-% We prescribe an equality constraint using a balance residual to set the RTO net thrust to \SI{22800}{lbf}.
-% Another balance residual constrains the SLS net thrust to be 1.2335 the net thrust at RTO.
-% Similarly, the net thrust at CRZ is constrained to be 0.9 times the net thrust at TOC.
-% Net thrust for SLS is constrained to be 1.2335 times the net thrust at RTO.
-% The bypass ratio (BPR) at TOC is set by the \emph{balance} component such that the CRZ nozzle velocity ratio meets a given target value.
-% The CRZ velocity ratio constraint ensures that the core exit velocity is higher than the bypass exit velocity.
-% The TOC engine mass flow rate is set by the \emph{balance} component using the combustor temperature at RTO, $T_{4,\rm{RTO}}$.
-% [x] TODO: AL-PA, Combine these into a single sentence.
-
-% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
-% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
-% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
-% [x] TODO: PA-PA, explain variable ranges
-
-% Blurb about PyOptSparse and SNOPT
-% NOTE: AL-PA, This can all be part of the optimization problem section you don't need a new subsection
-% \subsection{Optimization Software}
-% NOTE: AL-PA, "pyOptSparse" not "PyOptSparse", i.e the first "p" is not capitalized.
-% [x] TODO: AL-AL, need to cite pyOptSparse, SNOPT, and OpenMDAO
-% NOTE: AL-PA, I re-wrote most of this to be more concise.
 The N+3 pyCycle model is implemented in OpenMDAO~\cite{Gray2019a} to perform multidisciplinary gradient-based optimization with analytic coupled derivatives.
@@
 We solve the optimization problem listed in Table~\ref{tab:opt_problem} with SNOPT~\cite{Gill2005a}, a gradient-based sequential quadratic programming (SQP) algorithm for large-scale constrained problems.
-% NOTE: AL-PA, this was confusing and I don't think it add much useful information that the readers will actually understand.
-
-% During initial optimization studies of this model, it was found that when $T_{4,\rm{RTO}}$ and $X_{\rm{H_2O,CRZ}}$ are design variables at the same time they had opposite effects on the design.
-% The optimizer increases $X_{\rm{H_2O,CRZ}}$ which allows for a lower optimal $T_{4,\rm{RTO}}$.
-% This is likely due to the interdependency between engine mass flow rate and $T_{4,\rm{RTO}}$.
-% As the recovery water fraction increases less mass flow rate is required through the engine which lowers the required $T_{4,\rm{RTO}}$ for a required level of thrust.
-% It was also observed that $X_{\rm{H_2O,CRZ}}$ is increased until the model breaks due to the CEA solver not being able resolve the increased \ce{H2O} molecules that are injected.
-% Since $T_{4,\rm{RTO}}$ would be pushed down to its lower limit, it was set as the optimal value from the optimizations with no water recovery.
-% This allowed the optimizer to find the maximum $X_{\rm{H_2O,CRZ}}$ that would allow the most water to be recirculated.
-% The upper bound on $X_{\rm{H_2O,CRZ}}$ was found to be around 30\% for Jet-A and 17\% for \ce{H2}.
 \section{Results}
@@
 \label{sub:opt_res}
-% [x] TODO: AL-PA, I would move the following two lines into the optimization problem section and re-write them to be a single concise sentence.
 
-% [x] TODO: AL-PA, This is confusing.  You have two different optimization problem formulations and that is not clear here.
-%                  - I think you need to add information to the previous section about the optimization problem that explains all of this information.
-%                    Introducing this at the beginning of the results does not make sense.
-
-% Results of optimization problems
-% [x] TODO: AL-PA, Include the optimization and feasibility targets and talk about the number of iterations for each optimization.
-% [x] TODO: AL-PA, Add that you are running these optimizations on a laptop and provide a rough estimate for the wall time. i.e "These optimizations run in approximately X number of hours on a laptop"
 We performed four optimizations of the N+3 engine cycle.
@@
 The optimality and feasibility targets for the optimizations are both $10^{-6}$.
-These optimizations took between 20-30 major SNOPT iterations to reach optimality and were completed in approximately 45 minutes on a standard laptop.
+These optimizations took between 10--17 major SNOPT iterations to reach optimality and were completed in approximately 45 minutes on a standard laptop.
 The optimality, feasibility, and merit function for each optimization is shown in Figure \ref{fig:history_summary}.
@@
 The optimal design variables for each of the four optimizations are presented in Table~\ref{tab:dv_opt}.
-% The merit function reached a final value in about 10 iterations for all cases.
-% [x] TODO: AL-PA, No need to explain this and then answer your own observation from the plot.  Just tell the reader what the plot shows.
-% [x] TODO: AL-PA, Be cognizant that latex will not always put the figure right above a paragraph.  So saying "From this plot" might not make sense.  Need to directly reference the figure.
-% NOTE: AL-PA, The merit function is not a time-dependent quantity, so there's no "steady state".  Its enough to just say the merit function was reduced by X amount in X number of iterations...
-% From Figure~\ref{fig:history_summary} we observe quadratic convergence in the optimality of the problem near the optimal solution.
 
-% [x] TODO: AL-PA, Stretch the aspect ratio of this figure and squeeze the height in matplotlib.  You don't need this many values on the y-axis for the summary plots.
 % Feasibility, Optimality, Merit history
@@
   \caption{The optimality, feasibility, and merit function history for each optimization problem.
-        Jet-A without water recovery is shown with the solid lines, the Jet-A with water recovery is shown with dashed lines, hydrogen without water recovery is shown with dash-dot lines, and hydrogen with water recovery is shown with dotted lines.}
+    The red lines show Jet-A fuel and the blue lines show \ce{H2} fuel.
+    The solid lines show the engine without water recovery and the dashed lines show the engine with water recovery.}
   \label{fig:history_summary}
 \end{figure}
-
-% [x] TODO: AL-PA, You should explain the plot before it's introduced to the reader.  Stating what's on the figure after it appears doesn't provide any insight.
-% [x] TODO: AL-PA, See my previous TODOs but this needs some more explanation in the optimization problem section.
-% Note that the $T_{4,\rm{RTO}}$ variables are only present for the optimizations without water recovery and the $X_{\rm{{H_2O},CRZ}}$ variables are present only for the optimizations with water recovery.
 
@@
     \toprule
-        objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \unit{lbm/s} \\
+    objective   & $\dot{m}_{\rm{fuel,CRZ}}$ & 0.639     & 0.606     & 0.233       & 0.221       & \si{lbm/s}     \\
     % & $\rm{TSEC}_{\rm{CRZ}}$    & 8186.254  & 7766.338  & 8295.236    & 7859.635    & \si{lbm/hr/lbf} \\
     \hline
-        variables   & $x_{H2O,CRZ}$             & -         & 0.3       & -           & 0.17        & -            \\
+    variables   & $X_{\rm{H_2O,CRZ}}$       & -         & 0.3       & -           & 0.17        & -              \\
                 & $\rm{PR}_{fan,TOC}$       & 1.285     & 1.292     & 1.288       & 1.297       & -              \\
@@
                 & $\rm{OPR}_{\rm{TOC}}$     & 61.012    & 61.188    & 60.660      & 61.952      & -              \\
-                    & $T_{4,ratio}$             & 0.913     & 0.911     & 0.918       & 0.915       & -            \\
-                    & $T_{4,RTO}$               & 3220.574  & -         & 3204.071    & -           & $^\circ$R    \\
-                    & $V_{ratio,CRZ}$           & 1.35      & 1.35      & 1.35        & 1.35        & -            \\
+                & $T_{4,\rm{ratio}}$        & 0.913     & 0.911     & 0.918       & 0.915       & -              \\
+                & $T_{4,\rm{RTO}}$          & 3220.574  & -         & 3204.071    & -           & \si{\degree R} \\
+                & $V_{\rm{ratio,CRZ}}$      & 1.35      & 1.35      & 1.35        & 1.35        & -              \\
     \hline
-        constraints & $F_{net,TOC}$             & 5800.0    & 5800.0    & 5800.0      & 5800.0      & lbf          \\
-                    & $D_{Fan}$                 & 100.0     & 100.0     & 100.0       & 100.0       & $in^2$       \\
+    constraints & $F_{\rm{net,TOC}}$        & 5800.0    & 5800.0    & 5800.0      & 5800.0      & \si{lbf}       \\
+                & $D_{\rm{Fan}}$            & 100.0     & 100.0     & 100.0       & 100.0       & \si{in^2}      \\
     \bottomrule
@@
 
-% [x] TODO: AL-PA, Constraints are either feasible or they aren't, can't be "for the most part"
-% [x] TODO: AL-PA, Elaborate on why we include this parallel axis plot.  Why is it important?  What insight does it provide to the reader?  Compare and contrast the optimization results!
 We summarize the optimal values of important thermodynamic variables on a parallel coordinate plot in Figure~\ref{fig:parallel_coords}.
@@
 This suggests that a hydrogen fueled N+3 UHB turbofan with water recovery can compete with the efficiency of a standard Jet-A fueled cycle.
-% Figure~\ref{fig:parallel_coords} shows the how each of the optimal overall design of the engine compares across fuel type with and without water recovery.
-% [x] TODO: AL-PA, How are they similar? Be specific.
-% [x] TODO: AL-PA, I would move a lot of this up to when you introduce the parallel axis plot.
-% We see that across the range of values that each optimal value is very similar with the exception of water recovery fraction.
 
@@
 We observe the optimal $T_{4,\text{RTO}}$ is larger for Jet-A than hydrogen because hydrogen has a larger combustion flammability limit and the engine can burn at a lower equivalence ratio to attain the same thrust requirements~\cite{Adler2023}.
-% [x] TODO: AL-PA, why is this favorable for emissions reduction?  Need to cite or explain.
 Burning leaner lowers the FAR which reduces the fuel consumption for a given engine flow rate and is favorable for emissions reduction.
-% The additional water in the combustion improves the propulsive efficiency and enables the increase in overall pressure ratio.
-% As noted earlier, the water recovery fractions are different because the optimizer pushes $X_{\rm{{H_2O},CRZ}}$ to the highest value it can attain.
-% The $\rm{PR}_{fan,TOC}$ and $V_{ratio,CRZ}$ design variables go to their upper and lower limits, respectively.
 $V_\text{ratio,CRZ}$ is at the lower bound for all four cases to maximize the amount of mass flow through the bypass stream.
 
-% NOTE: PA-PA/AL replace this with a parallel axis plot?
-% [x] TODO: AL-PA, Yeah let's do the parallel axis plot for the basic thermodynamic parameters
-% AL-PA, We can make another plot for the water fractions and the dpQp study.
-% [x] TODO: AL-PA, Can you make the y-axis range for T4_ratio smaller so we can see the differences a bit better.  Maybe like 0.85 - 0.95
-% [x] TODO: AL-PA, Same comment as above but for FPR, maybe 1.28-1.32
-% [x] TODO: AL-PA, If a variable has bounds, can we make the y-axis limits match the bounds?
 \begin{figure}[hbt!]
@@
   \includegraphics[width=1.0\textwidth]{N3_parallel_coords.pdf}
-    \caption{Optimization results of the N+3 engine with and without no water recovery using Jet-A and H2 as the fuel.
+  \caption{Optimization results of the N+3 engine with and without water recovery using Jet-A and \ce{H2} as the fuel.
     The red lines show Jet-A fuel and the blue lines show \ce{H2} fuel.
@@
 
-% [x] TODO: AL-PA, How are the pressure ratios and temperatures different?  Which optimizations resulted in different values?
-% $\rm{PR}_{fan,TOC}$ likely goes to its upper value since its more efficient to increase $\rm{PR}_{fan,TOC}$ than $\rm{OPR}_{\rm{TOC}}$.
-% The main differences in the engine designs are the pressure ratios and temperatures.
-% [x] TODO: AL-PA, Why is pushed to the upper limit?  Explain how it improves the combustion characteristics.
-% Between the two fuel types, the water recovery fraction for both is pushed up to the upper limit of the design space.
-% One reason the water recovery fraction increases to its upper bound use to improve combustion characteristics of the core flow when fuel is injected.
-% The same thrust output can be achieved with water recovery at a lower FAR, slightly lower temperature, and less total mass flow rate.
-% The recovery fraction does not directly relate to the mass flow rate of recirculated water since more available water will increase the recirculation flow rate.
-% It is noted that recovery fraction for \ce{H2} is smaller than the recovery fraction for Jet-A because there is more water produced in the combustion process.
-% However, the mass flow rate of water is larger for \ce{H2} at \SI{0.405}{lbm/s} as opposed to \SI{0.324}{lbm/s} for Jet-A.
-% The \ce{H2} fuel has the benefit of recovering more water at a lower fraction of the overall water in the core exhaust.
-% We see slightly higher pressure ratios across the fan with water recovery leading to a larger overall pressure ratio.
-% [x] TODO: AL-PA, I'm beating a dead horse here but you don't need to say this if you mention it earlier
-% [x] TODO: AL-PA, Why is the T4 ratio higher?  Explain it in terms of the fuel properties.  The reader can look at the plot themselves and see that it's higher.
-% The $T_{4,\rm{RTO}}$ value for Jet-A is slightly higher than that of \ce{H2}.
-% This is most likely due to the combustion properties of \ce{H2} compared to Jet-A.
-% \ce{H2} can has a wider combustion flammability limit and allows the engine to burn at a lower equivalence ratio to attain the same thrust requirements.
-% Burning leaner not only cools the engine but also reduces fuel consumption.
-% [x] TODO: AL-PA, Why are the temperatures colder with the H2 fuel?  Why does water recovery make them even lower?
-% [x] TODO: AL-PA, I wouldn't say "cooler" I would say "less than" or "colder"
-% Therefore, TOC temperatures are colder with the \ce{H2} fuel and even slightly colder when adding water recovery.
-% The engine is likely able to size the components with water recovery so that the same thrust is generated at a lower fuel-to-air ratio.
-% Furthermore, adding water recovery at CRZ slightly decreases the $T_{4,\rm{ratio}}$ value.
-% As noted earlier, the water recovery and injection allows the engine achieve the same level of thrust at a lower temperature.
-% [x] TODO: AL-PA, Why did the optimizer push the value of T4 down with water recovery?  Dig into this more.
-% In terms of pressure ratios we see that the fan pressure ratio increases with hydrogen fuel and even more with water recovery.
-% This is again likely due to using \ce{H2} and water recovery each resizing the engine to increase the amount of thrust generated by the fan.
-% [x] TODO: AL-PA, We want to discuss how the thrust from the fan/core changes when we introduce water recovery.
-% NOTE: AL-PA, The idea here is to communicate the effect of water recovery on the core power vs. the fan power.
-% We analyzed the gross thrust split between the core and bypass streams of the optimized engine cycles.
-% Table~\ref{tab:thrust} shows the breakdown between the two flow paths as percentages of the total gross thrust.
-% The breakdown of the gross thrust fractions from the core and bypass nozzles for each point is shown in Table~\ref{tab:thrust}.
-% The fraction of gross thrust generated by the core nozzle decreases when we use \ce{H2} and decreases further when adding water recovery.
-
-% Increasing the thrust produced in the bypass stream improves the propulsive efficiency.
-% Utilizing the fan more than the core nozzle increases the efficiency of the engine since we are not burning as much fuel but is limited by the maximum size of the fan.
-% The increase in $\rm{OPR}_{\rm{TOC}}$ mostly reflects the increase in $\rm{PR}_{fan,TOC}$ and resizes of the turbojet section of the engine with water recovery.
-% Additionally, the FAR of the engines with water recovery increases due to a decrease in overall and core mass flow.
-% An increase in FAR likely requires a larger OPR to maintain the required thrust while minimizing fuel burn.
-
-% Thrust splits
-% [x] TODO: PA-PA: Add thrust splits for each opt
-% [x] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
-%                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
-% \begin{table}[hbt!]
-%   \centering
-%   \caption{Thrust breakdown for each flight operating condition.
-%     The net thrust, gross thrust, and ram drag are shown for each optimization result.
-%   }
-%   \small
-%   \renewcommand{\arraystretch}{1.2}
-%   \begin{tabular}{r l l l l l}
-%     Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
-%     \toprule
-%     TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
-%           & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
-%     \hline
-%     RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
-%           & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
-%     \hline
-%     SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
-%           & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
-%     \hline
-%     CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
-%           & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
-%     \bottomrule
-%   \end{tabular}
-%   \label{tab:thrust}
-% \end{table}
-
-% [x] TODO: AL-PA, Again, this table might not be directly above this text in the PDF so you need to use \ref{tab:thrust}.
-% [x] TODO: AL-PA, You already showed the constraint values and that the design is feasible, the reader knows what the net thrust should be from that information.
-% [x] TODO: AL-PA, Thrust differences?  These values change with mass flow rate which we know is affected by water recovery.  Probably need to remove the following stuff discussing this.
-% NOTE: AL-PA, I think you misunderstood what happens in the ram drag/gross thrust calculations.  They are just simple control volume thrust equations.
-%              If your mass flow rate changes with water recirculation these will change, but that is expected and not super informative in terms of a comparison.
-
-% [x] TODO: I would change this to the horizontal bar chart and plot both H2 and Jet-A on the same axis
-% See this example in niceplots: https://github.com/mdolab/niceplots/blob/main/examples/plot_bar_chart.py and https://github.com/mdolab/niceplots/blob/main/examples/ref/bar_chart.png
-% [x] TODO: Can you add a line to bar chart that shows the improvement between baseline Jet-A and hydrogen with water recovery?
 \begin{figure}[hbt!]
@@
   \caption{Percent relative improvement in thrust specific energy consumption (TSEC) of the N+3 engine with water recovery.
-        This plot compares the relative improvement of the two optimization problems with water recovery compared to the optimization problems without water recovery.}
+    This plot compares the relative improvement of the two optimization problems with water recovery compared to the optimization problems without water recovery.
+    The relative performance of hydrogen with water recovery compared to Jet-A without water recovery is also shown.}
   \label{fig:barchart}
@@
 Water recovery improves the TSEC approximately 5\% for both Jet-A and hydrogen fueled cycles.
-% We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
-% [x] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
 Most of the design variables for the optimal designs with and without water recovery vary only slightly for both fuels.
@@
 Achieving a 5\% reduction in TSEC represents a large fuel savings over the lifecycle of an engine.
-% This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
-% [x] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
 As~\citeauthor{Strom2002} point out, a hydrogen-fueled engine would have close to 3 times more water in the exhaust than a similar Jet-A fueled counterpart.
-% [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
 The optimal designs with water recovery have approximately \SI{2.38}{lbm/s} and \SI{1.08}{lbm/s} of water in the core stream for hydrogen and Jet-A, respectively.
-% Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
 Hydrogen combustion offers an immediate reduction in emissions and produces more water in the exhaust stream.
@@
 \label{sub:dpqp_sweep}
-% [x] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
-%                  Might be worth moving this into a new subsection.
-% [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
+
 The efficiency improvement due to water recirculation warrants a design space study for potential condenser technology.
@@
 The trade space for a condenser in the exhaust stream depends on the pressure loss and water recovery capability.
-% A low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
-% [x] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"
 
 We model the pressure loss across the condenser by varying the relative total pressure loss across Duct5 just upstream of the core nozzle.
-% pyCycle handles pressure losses in ducts by specifying a pressure loss coefficient, dPqP.
 This pressure loss coefficient (dPqP) is the difference in total pressure across the duct divided by the total pressure at the duct inlet.
-% [x] TODO: AL-PA, Try rewording to: "We varied the total pressure loss across the extraction model to simulate drag from an increasingly larger condenser"
-% [x] TODO: AL-PA, Elaborate on why we re-optimized the design.  It is because we want to see how the optimal amount of water recovery changes based on the drag incurred by the condenser.
 We varied the total pressure loss across the duct to simulate an increasingly larger condenser jutting out into the duct.
@@
   \begin{subfigure}[t]{0.48\textwidth}
-        % [x] TODO: AL-PA, I don't think its benefit vs no-benefit.  The message here is that the blue region is the design space where we can potentially design condenser.
     \includegraphics[width=\textwidth]{N3_dpqp.pdf}
@@
   \begin{subfigure}[t]{0.48\textwidth}
-        % [x] TODO: AL-PA, Rotate the y-axis label to go vertically to save space
     \includegraphics[width=\textwidth]{N3_wdot.pdf}
@@
 
-% The rest of the engine design variables were optimized during this pressure loss sweep to determine the how the optimal amount of water recovery changed based on drag losses from the condenser.
 Figure~\ref{fig:dpqp_sweep} shows the $\rm{TSEC}_{\rm{CRZ}}$ of the optimal engine cycles plotted against dPqP.
@@
 The blue region represents the feasible space for potential condenser technology.
-% From Figure~\ref{fig:dpqp_sweep}, we can see the design space in which the closed-loop water recovery model is feasible.
 The breakeven point where water recovery is no longer beneficial occurs at a pressure loss of roughly 0.16, or 16\%.
@@
 In reality, losses due to inefficiencies further reduce the size of the feasible space.
-% The water recovery model will offer efficiency improvements up until about $\rm{dPqP} = 0.16$.
-% A value of $\rm{dPqP} = 0.16$ means that a 16\% loss of pressure from the condenser is allowed assuming the maximum water recovery fraction of 17\% for \ce{H2}.
-% This improvement design space would be reduced if only a smaller fraction of water recovered could be obtained.
-% [x] TODO: AL-PA, Re-write this part to match the new figure that shows the mass flow of water extracted (per our slack convo)
 The sensitivity of water extraction with respect to pressure loss is shown in Figure~\ref{fig:dpqp_wdot}.
-% Figure~\ref{fig:dpqp_wdot} shows that the optimizer finds designs that increase the available water in the core stream.
 The optimizer increases the amount of water extraction to compensate for the increasing pressure loss.
-% Since the water recovery fraction is always pushed to 17\%, the optimizer increases the recovered water mass flow rate to overcome the pressure loss.
 This represents a benchmark for designing condenser technology that can operate within the proposed water recirculation system.
@@
 \label{sec:conc}
-In this paper, we describe a novel closed-loop water recirculation system for commercial aviation engines.
+In this paper, we described a novel closed-loop water recirculation system for commercial aviation engines.
 The water recirculation system was designed and implemented within the N+3 ultra-high bypass engine model.
-We presented the results of four optimization problems demonstrating the use of this technology within pyCycle for Jet-A and hydrogen fuels.
+We presented the results of four optimization problems demonstrating the use of this technology within a pyCycle model for Jet-A and hydrogen fuels.
 
-The water recirculation system introduces two pyCycle components, namely the water extractor and injector, that form a continuous closed-loop feedback cycle in the engine.
-% We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
-% The optimization problem is then introduced with constraints on the thrust and overall engine size at the design point.
-We optimize the engine cycle considering Jet-A and hydrogen fuels with and without water recovery.
-The objective is to minimize fuel mass flow rate subject to net thrust and fan diameter constraints.
-% The design variables used are thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
-% An additional design variable controlling how much water is recirculated is added at the cruise point to improve the fuel burn.
-% The optimization problem was solved for four cases: with Jet-A or hydrogen fuel, and with or without water recirculation.
-% The results from the optimization problems show temperature, thrust, and efficiency improvements for hydrogen as a fuel and even further improvements with water circulation.
+The water recirculation system introduced two pyCycle components, namely the water extractor and injector, that form a continuous closed-loop feedback cycle in the engine.
+We optimized the engine cycle considering Jet-A and hydrogen fuels with and without water recovery.
+The objective was to minimize fuel mass flow rate subject to net thrust and fan diameter constraints.
 The results show that optimal hydrogen-fueled engines with water recirculation are more efficient than standard Jet-A with no water recovery.
-We demonstrate that the increased availability of water from hydrogen combustion proves the viability of this concept.
+We demonstrated that the increased availability of water from hydrogen combustion proves the viability of this concept.
 Additionally, hydrogen combustion eliminates carbon emissions and the lean fuel-to-air ratios result in cooler turbine inlet temperatures compared to Jet-A.
-% Thermal reductions with hydrogen and water recirculation will improve the lifetime of the engine which would reduce maintenance and overall costs.
-% Between the two fuels, we see similar values of the engine performance metric, TSEC.
-% Significant energy efficiency gains are seen with water recirculation which would improve the overall costs of the engine during its operational lifecycle.
-% At the same water recovery fraction, hydrogen with water recirculation could achieve a lower TSEC value.
 
 We performed a design space study to understand the technology requirements for a condenser that might operate in the proposed water recovery system.
-% There are technological obstacles to overcome in order to implement this water recirculation system in a modern turbofan engine.
-% The main obstacle would be how to design a condenser that can recover a portion of the exhaust water without a excessive drag pressure losses.
-% Therefore, a condenser design space study was completed to show the feasible design space for such a condenser.
 The results showed that a hydrogen-fueled cycle with water recovery can sustain a pressure loss of 16\% across a condenser before the efficiency benefits diminish.
-% The results of the study showed that at the maximum possible water recovery fraction for hydrogen quite a large pressure loss can be imposed before the improvements are canceled out.
-% Furthermore, using hydrogen as the fuel allows for designs that are not available for an engine using Jet-A.
-% [x] TODO: AL-PA, I suggest you bolster the discussion of these two sentences in the results section and maybe add a citation?
 The thermal properties of hydrogen provide a heat sink and thus a readily available resource for water condensation within the condenser.
 The hydrogen fuel absorbs heat and is then used in the combustion process, further improving engine efficiency.
-% The novel water recovery system shows promising efficiency results when used with hydrogen fuel.
 Hydrogen-fueled UHBR turbofan engines can be more efficient than Jet-A counterparts when optimized considering water recovery.
 Taking advantage of the beneficial properties of hydrogen is paramount for new engine technologies that can reduce emissions while improving performance.
-% This water recovery system provides a potential avenue for hydrogen engine design that could help overcome the technological issues associated with hydrogen as a fuel.
 
